### 2024-02-29 docs/paper.qmd
first commit

---
title: |
  | Accountants' Attitudes Towards Open Science^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank the audience of a workshop at Humboldt University for providing helpful feedback. Excellent research assistance by Benedikt Hahn is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

editor: visual

bibliography: references.bib
biblio-style: apsr

always_allow_html: yes

header-includes:
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \setlength{\skip\footins}{2em}
  - \usepackage[hang]{footmisc}
  - \setlength{\footnotemargin}{1em}
  - \usepackage{pdfpages}
  - \usepackage{pdflscape}
  - \usepackage{csquotes}
  - \renewcommand{\mkbegdispquote}[2]{\itshape}
---

```{r setup, include=FALSE}
library(knitr)
library(rmarkdown)
library(gt)
library(modelsummary)
# opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
opts_chunk$set(out.width = '80%', dpi=600)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache = FALSE)

source("../code/table_functions.R")
source("../code/figure_functions.R")

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors.csv", show_col_types = FALSE)
```

```{=tex}
\thispagestyle{empty}
\begin{abstract}
\singlespace
Surveying a sample of scholars that have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs. Also, we are less familiar with public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research. Our respondents state that they are open to sharing and would be likely to share research materials under a hypothetical scenario, regardless of the experimental framing. They also believe that other accounting researchers, as well as editors, are in favor of research material sharing. However, they are skeptical about the actual prevalence of research material sharing in the accounting research community. In addition, they are more reluctant than researchers from neighboring fields to pre-register their study plans. We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
\end{abstract}
```
\vspace{2cm}

```{=tex}
\begin{flushleft}
\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Pre-Registration, Survey \newline
\textbf{Data Availability}: Data available in code repository \newline
\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{github.com/joachim-gassen/osacc}  \newline
\textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
\end{flushleft}
```
\pagebreak

\setcounter{page}{1}

## Introduction

Cumulative science builds on reproducible research.[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated open science methods like public sharing of research materials and the pre-registration of study plans as potential strategies to improve the reproducibility of our work. Prior work across the social sciences [@FLCPSWMBP_2023] has documented an overall uptake of open sciences approaches across several disciplines. We contrast these findings with a survey that we conducted among accounting researchers to explore the perceptions and attitudes toward open science in our field.

[^1]: While in the survey itself, we use the term reproducibility without an exact definition, throughout this article, we follow the notion of @NSF_2015 to define reproducibility as the "ability of a researcher to duplicate the results of a prior study using the same materials and procedures as were used by the original investigator" while replicability "refers to the ability of a researcher to duplicate the results of a prior study if the same procedures are followed but new data are collected". For a more in-depth discussion of the related terminological debate, see @GFI_2016. The key reason why we do not provide an exact definition in the survey is that the differences between reproducibility and replicability are subtle and vary across accounting subfields: For archival studies, reproducibility and replicability should be essentially the same, while for experimental studies they clearly differ.

Based on the responses of `r nrow(sd)` published accounting researchers, we find that our attitudes towards open science clearly differ from those of other researchers in the social sciences. Most prominently, we tend to hold a generally more critical view of the reproducibility of our influential work. Compared to the fields of economics and sociology, for example, we are about half a point more skeptical about the reproducibility of the influential work in our field on a 5-point Likert scale. This is a sizable difference.

Exploring this assessment across our respondents' demographics, we find it to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic than the other methodologies. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a proactive stand and embrace two prominent open science approaches that methodological work has identified to increase the reproducibility of research: the public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.

Turning first to the public sharing of research materials, we document that, again compared with researchers from other social science areas, we accounting researchers are somewhat less familiar with this activity. Also, we find it somewhat less important. Familiarity is generally largest for respondents using archival, field, and experimental methods and smallest for respondents using qualitative methods, which also perceive sharing to be less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in our perceived (prescriptive) importance of research material sharing, our stated willingness to share research materials, and our (descriptive) perception about actual sharing behavior. In a hypothetical scenario, the average stated likelihood for sharing research materials by our respondents is relatively high (i.e., 72%), and this likelihood is more or less unaffected by the randomized nature of the rationale (i.e., collaboration or control) and the sharing scope (public or private).[^2] Also, 50% of our respondents state that they at least sometimes publicly share their research materials. In addition, we think that about 44% of us favor publicly sharing research materials, and we assess 61% of the top-six accounting editors to be in favor of publicly sharing research materials.

[^2]: We pre-registered this experimental part of our study. The pre-registration materials can be accessed [here](https://osf.io/frmzt/).

All this sounds comforting and consistent with a general supportive stand of the accounting community towards public research material sharing. However, when questioned about the actual percentage of us sharing research materials publicly, the number comes down to a much more sobering 28%. This number and the prescriptive/descriptive gap that it reveals differ significantly across methods: Analytical researchers have the narrowest gap (43% of researchers expected to be in favor and 38% expected to actually share) and archival researchers the widest (45% versus 24%). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

In light of these numbers, it is a logical next step to explore the main reasons against sharing research materials. Overall, the most commonly stated reasons are the proprietary nature of used data (56% of respondents give this reason), the time that it takes to make materials available (30%) and the fear of being scooped when materials become publicly available (23%). Also, 34% of respondents state there is no need for sharing as their data are already publicly available. Unsurprisingly, the reasons clearly differ across methods. For qualitative researchers, deidentification problems are very prominent (46%) and analytical researchers consider the time that it takes to make materials available far less of a reason than researchers using the other methods (i.e., 9.5% versus 30% overall).

Turning to pre-registration, it seems that we accounting researchers are at least as familiar with the concept as other social science researchers. However, we started using it later (roughly 2 years) and use it less frequently (17% versus 27%). Our trust in pre-registered work is generally comparable with other social scientists but significantly lower than trust levels of researchers in Psychology (the field that reports the highest usage rates of pre-registration). A detailed look into differences among the different methodological fields within accounting also reflects this as we find that experimental researchers use pre-registration most (28%) and express the strongest belief that the practice increases the trustworthiness of research.

Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both, the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it. This results in these tools currently being less established in the accounting domain than in other fields. In addition, the challenges that hinder reproducibility and the potential effectiveness of open science tools vary across methodological paradigms. Qualitative research faces different challenges than archival quantitative work, and its differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

## Survey Methodology and Variable Measurement

### Survey Design and Administration

To collect the attitudes of accounting researchers towards open science, we conducted a survey among members of the academic accounting community. The survey has been designed using oTree [@CSW_2016]. To recruit respondents for our survey, we identified authors who published in the "Top 6" accounting journals, i.e., Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review, over the period 2016 to 2021. We chose these six accounting journals because they are commonly known to be top accounting journals within the academic accounting community. We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community. Yet, we believe that, taken together, these journals provide us with a somewhat representative list of publishing accounting academics. We started compiling the list of authors from 2016 onward because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017]. After receiving approval from an ethical review board, also guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total three reminders. We allowed potential respondents to opt out of future emails every time we reached out to them. Please see Appendix A for the invitation emails.

\centerline{--- Insert Table 1 about here ---}

Table 1 displays our sample selection procedures. Of the 2,660 potential respondents we approached, we excluded 118 for various reasons.[^3] Furthermore, for 206 emails bounced, we received a notification that the email address was unreachable. Of the remaining 2,336 successfully reached accounting researchers, 391 started the study (15,4% of the total emails sent), 254 partially completed the study (10,9% of the total emails sent), and 222 fully completed the study (8,7% of the total emails sent).[^4] Table 2 displays our final sample's demographics and characteristics. Panel A reveals that the majority of the respondents is male, 35 years or older (87.8%), specializes in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).

[^3]: 41 authors were removed because we found no email address, 41 authors were removed because they appeared in the data twice with two author IDs but were the same person, 28 authors were removed because they were a current member of one of our affiliated universities or academic research centers, 5 authors were removed because they gave us advice for this study, 2 authors were removed because they had passed away, and 1 author was removed due to an incorrect email address.

[^4]: As the dependent variable of our hypothetical scenario analysis outlined below is the first data that we collect, 254 is the sample size for this analysis. For the descriptive analyses, we settle for the number of participants that answered the respective question and, if applicable, also provided the necessary demographics for cross-sectional splits. Depending on this, the sample sizes vary from 222 to 229 responses. 
\centerline{--- Insert Table 2 about here ---}

Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we are able to collect about our population we are only able to compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from Europe are over-represented and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently hard, we generally abstain from speculating about potential reasons for this sampling imbalance. However, it seems likely that the all-European author team of the study might have had an influence. While we control for geographical effects in our response (not-tabulated) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia that happen to have a very low response rate.

### Variable Measurement

To ensure that our findings are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], which has been recently published in Nature Communications. Very similar to our survey, this study solicits the view by published researchers and PhD students on reproducibilty, research material sharing, and pre-registration. Given that it differs in survey detail (app. 45 minutes while our survey was designed to be completed in less than 10 minutes), and data collection procedure (confidential with compensation element while we use an anonymous survey with very mild incentivization), we had to make some adjustments. However, the ordering and phrasing of questions in our survey are similar and their content and answer scales are identical or differ in a negligible way. Specifically, we decided to alter the framing and expand some of the questions to make it easier for accounting researchers to understand the questions and connect them to their common research practices. We also pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions.

The first stage of the survey included questions about respondents' views on publicly sharing research materials, which we described as comprising of data, code, and research procedures. Specifically, we asked respondents about their familiarity with public sharing of research materials and their views of its importance. We also asked them about their perceptions of the prevalence of sharing in the accounting research community, how often they tended to share, and whether they planned to share in the future. Conditional on whether respondents indicated that they do not always share, we also asked them for the reasons behind not sharing. Lastly, we asked respondents to estimate what percentage of accounting researchers favor sharing and their approximation of the percentage of editors of the top six accounting journals that believe sharing increases the value of a manuscript.

The second stage of the survey featured a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023 . First, we asked respondents about their confidence in the reproducibility of accounting research. We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible. Next, we asked the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other). Subsequently, we asked respondents about their familiarity and experience with the practice of pre-registration. Lastly, we asked them about their perceptions of trustworthiness of pre-registered research compared to non-pre-registered research. We completed the survey with asking a few demographic questions that are mostly presented in Table 2. For a complete overview of the survey questions included in our study, please see Appendix A.

## Findings

### Reproducibility

The first goal of the survey was to gauge the perceptions of accounting researchers regarding the reproducibility of influential findings in the accounting literature. Table 3 displays a detailed overview of our respondents' answers to the question "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicating" to "reproducing" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community. Namely, the term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000]. In contrast, the term"replication" may or may not have different interpretations for different researchers. For instance, experimental researchers it refers to distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).

\centerline{--- Insert Table 3 about here ---}

The results in Table 3 suggest that we accounting researchers hold a generally more critical view of the reproducibility of our influential findings. Compared to researchers in the fields of economics and sociology, accounting researchers who took part in our survey are about a half a point more skeptical about the reproducibility of their influential work (on a 5-point Likert scale). This difference is less stark when we compare accounting researchers to researchers in the fields of Political Science and Psychology. In a field fixed effect regression, in which we use Accounting as the baseline, we find that all four fixed field effects are statistically different from zero (two-tailed p-value \< 0.01). Hence, the field of Accounting is generally more skeptical about the reproducibility of its research than other social science fields.

\centerline{--- Insert Figure 1 about here ---}

Figure 1 visually represents the data from Table 3 by plotting them on a horizontal axis and aligning them around a neutral midpoint. The figure shows that accounting researchers are the most skeptical (i.e., "Not at all confident") about the reproducibility of influential findings in their field (10.5%). This difference is much higher than the percentage of skeptics reported by @FLCPSWMBP_2023: 0.7% for Economics, 2.1% for Political Science, and 1.1% for Psychology, and 1.3% for Sociology. The field of Accounting, therefore, also has the lowest percentage of non-skeptics (i.e., researchers who are either moderately or extremely confident in the reproducibility of influential findings). That is, Accounting has about 39.3% non-skeptics, while Economics has 61.1%, Political Science has 45.8%, Psychology has 41.3%, and Sociology has 61.7%. The differences with Economics and Sociology again are the largest, while the differences with Political Science and Psychology are smaller.

Next, we compare assessments of accounting researchers regarding reproducibility across different methodologies. Accounting is not only a diverse discipline in terms of orientation and topic, but also in terms of the methodologies its researchers employ. We distinguish among five categories: Analytical, Archival/Field, Experimental, Qualitative, and Survey. We asked respondents which of those categories best described their main methodological area, enabling us to categorize them in the data. Table 4 displays their assessments regarding the reproducibility of influential findings across three panels. Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.

\centerline{--- Insert Table 4 about here ---}

The findings in Table 4 Panel A suggest that analytical and qualitative researchers are more pessimistic and skeptical about the reproducibility of influential findings in accounting as whole than accounting researchers using other methodologies. In particular, analytical researchers are significantly less confident about the reproducibility of influential findings in accounting in general than researchers in the Archival/Field and Experimental categories (two-tailed p-value \< 0.100). When turning to respondents' assessments of the reproducibility of influential findings in their own methodological area, we find that analytical researchers have the most confidence in the influential findings within their methodological area as their average confidence is statistically higher from those reported by the average reported for the other four methodologies (two-tailed p-value \< 0.100). Qualitative research reports a significantly lower average confidence than Analytical, Archival/Field, and Experimental research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).

Panel C reports the "assessment gap," which captures the difference in assessments of the reproducibility of influential findings in respondents' own methodological area versus accounting in general. A higher (lower) assessment gap indicates that respondents are more (less) confident in the reproducibility of influential findings in their methodological area compared to accounting in general. The findings of Panel C report that analytical researchers report the largest assessment gap, implying they are relatively skeptical about reproducibility of influential findings in accounting as a whole compared to their own methodology. The average assessment gap reported for the Analytical category is also statistically different from the averages reported in the other four categories (two-tailed p-value \< 0.100). The other four categories exhibit no clear assessment gap (with averages hovering around zero) and are statistically indistinguishable form each other.

### Sharing Research Materials - Familiarity and Importance

Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field and with some variation across methodologies. Given the skepticism,we have observed so far, one would expect accounting researchers to take a more proactive stance on open science approaches, like the practice of research materials sharing. The survey assessed respondents' evaluations of the practice of research materials sharing next. Specifically, we asked respondents two questions about the practice of sharing research materials, which we defined as the practice of sharing data, code, and research procedures. These two questions were also close adaptions of the survey done by @FLCPSWMBP_2023.

\centerline{--- Insert Table 5 about here ---}

The first question assesses respondents' familiarity with the practice of research materials sharing: "How familiar are you with the practice of publicly sharing research materials (i.e., data, code, and research procedures) for a completed study?"[^5] Table 5 Panel A shows respondents' answers to the question about familiarity, including benchmark answers of respondents in different fields originating from the survey by @FLCPSWMBP_2023 . Generally speaking, academics in the social sciences report being relatively aware of and familiar with the practice of research material sharing. However, the results do suggest that, compared to each of the other four fields in the social sciences, accounting researchers are significantly less familiar with the practice (two-tailed p-value \< 0.010). The second question captures respondents' assessed importance of research material sharing: "To what extent do you believe that publicly sharing research materials (i.e., data, code, and research procedures) is important for the advancement of accounting research?"[^6] Table 5 Panel B suggests that accounting researchers also find the practice of research material sharing less important than academics in each of the other four fields (two-tailed p-value \< 0.010).

[^5]: The corresponding question in @FLCPSWMBP_2023 is "Have you ever heard of the practice of publicly posting data or code online for a completed study?" We deviated from this original question by using the term "research materials" and defining it as "sharing data, code, and research procedures" in our version of the question because we wanted to cover all aspects of this Open Science practice in one question.

[^6]: The corresponding question in @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting data or code online is important for progress in \[Discipline\]?" We adapted this question for terminological consistency across our survey.

\centerline{--- Insert Figure 2 about here ---}

Figure 2 reproduces the data reported in Table 5 Panel B by presenting the frequencies along horizontal axes and centering them to a neutral midpoint. It reveals that, compared to the social science disciplines, relatively less respondents in our sample are strong supporters of the practice of research material sharing. That is, our of the total sample, 39.6% of the respondents consider it "very important" (Accounting) versus 51.7% in Economics, 48.1% in Political Science, and 43.8% in Psychology. Only Sociologists report a lower percentage of strong supporters (i.e., 29.4%) than the accounting researchers in our sample.

\centerline{--- Insert Table 6 about here ---}

Next, we examine familiarity with and perceived importance of research materials sharing across methodologies within accounting. We again distinguish among five methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey). Table 6 displays assessments of the practice of research material sharing using two panels. Similar to Table 5, Table 6 Panel A reports about the familiarity with the practice (i.e., "How familiar are you with the practice of publicly sharing research materials (i.e., data, code, and research procedures) for a completed study?") and Panel B reports about assessed importance ("To what extent do you believe that publicly sharing research materials (i.e., data, code, and research procedures) is important for the advancement of accounting research?").

Panel A shows that familiarity is larger for respondents using Archival and Field methods compared to respondents using Qualitative, Analytical, and Survey methods (two-tailed p-value \< 0.100). Moreover, we also find that respondents using Qualitative methods are less familiar with research material sharing compared to all four other categories (two-tailed p-value \< 0.100). Panel B shows that there are few significant differences in terms of assessed importance of research material sharing across the methodologies. Only respondents in the Archival/Field category assess research material sharing as significantly more important than respondents using the Qualitative and Survey category.

### Sharing Research Materials - Rationale and Scope

So far, we document that, compared with researchers from other social sciences, we accounting researchers are less familiar with research sharing and find it less important. Since we also wanted to understand what drives accounting researchers' willingness to share research materials, our survey contained a hypothetical scenario in which another (hypothetical) fellow researcher asked respondents whether they would like to share the research materials (i.e., data, code, and research procedures) of a paper they published in an academic journal.

#### Hypothetical Scenario - Design

We manipulated two between-subjects factors in the hypothetical scenario. First, we manipulated the rationale used by the fellow researcher requesting access to the researcher materials. In the *collaboration rationale* treatment, the fellow researcher requested access to researcher materials to understand the work better and build on it. In the *control rationale* treatment, the fellow researcher requested access to verify and potentially correct the research. Second, we manipulated whether the fellow researcher requested the research materials to be shared publicly (i.e., *public scope*) or privately (i.e., *private scope*). Respondents were randomly assigned to receive only one stated rationale (*control* *rationale* versus *collaboration rationale*) and one sharing scope (*public* versus *private scope*). We measured respondents' willingness to comply with the fellow researcher's request on a scale, ranging from 0% (definitely not) to 100% (definitely). The hypothetical scenario was, like the survey, designed using oTree [@CSW_2016].

We predicted that the effect of using a collaborative versus controlling rationale increases accounting researchers' willingness to share their research materials because it communicates a potential benefit rather than cost in terms of reputation (our first hypothesis). We also predicted that a private sharing request leads to a higher willingness to share than a public sharing requests because the former involves a lower potential downside risk in terms of reputation than the latter (our second hypothesis). Finally, we predicted that the effect of stating a collaborative versus controlling rationale is larger in the case of a private sharing request as opposed to a public sharing request (our third hypothesis). The conceptual reasoning behind this interaction effect is that, besides the additive effects of private sharing and a collaboration rationale, the perceived benefit of sharing under the collaboration rationale should be amplified when the scope of sharing is private rather than public. Namely, for a private scope, a collaboration rationale implies more direct benefits of sharing than for a public scope. We pre-registered our predictions and design at the \href{https://osf.io/4akyd}{Open Science Foundation}.

#### Hypothetical Scenario - Procedures

After accepting the terms and conditions, respondents were told that they would read a short scenario and that they would answer questions about it. The scenario included a description that they just conducted a study and published it in an academic journal. Respondents were also told that a fellow researcher contacted them for access of their research materials, which we specified as 'data, code, and research procedures'. Next, we provided four pieces of information about the request made by the fellow researcher. In this part of the scenario, we manipulated whether the request was to make the research materials publicly accessible (*public scope*) or share them only with the requesting fellow researcher (*private scope*). We also featured our second manipulation, specifically, whether the provided rationale was to collaborate with or control the research of the respondent (*collaboration rationale* versus *control rationale*). Appendix B contains an overview of the manipulations and the materials.

\centerline{--- Insert Table 7 about here ---}

#### Hypothetical Scenario - Findings

Table 7 shows the findings of the hypothetical scenario. On average, we find a relatively high willingness to share research materials in the hypothetical scenario and across different variations of rationale and scope (mean = 72%, s.d. = 28%). However, we do not find statistical support for our three predictions. First, Table 7 Column 1 reports no significant effect of using a *collaboration rationale* over a *control rationale* (two-tailed p-value \> 0.100). Moreover, Column 2 shows no support for a main effect of *private scope* on respondents' willingness to share research materials (two-tailed p-value \> 0.100). Lastly, column 3 shows no support for an interaction effect between *collaboration rationale* and *private scope* (two-tailed p-value \> 0.100). In sum, although we find that respondents express a high willingness to share research materials in our hypothetical scenario, we don't find any evidence it is affected by the way the request for sharing is made. At least in our hypothetical scenario, it does not matter whether the request is made to make the materials private (rather than public) and whether the request is made to promote collaboration as a research community or to verify whether the research has been conducted appropriately.

### Sharing Research Materials - Prescriptive versus Descriptive Views and Rationales

Our respondents report a high willingness to share research materials in a hypothetical scenario and do not seem moved by the circumstances under which requests for research materials are made. Next, our survey focuses on the perceived prescriptive and descriptive importance of research material sharing. Table 8 Panel A reports data on respondents' answers to the question "How often do you publicly share research materials (i.e., data, code, and research procedures)?" It also splits the data into main methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey). The results in Panel A reveal that 50% of the respondents state that they at least sometimes publicly share their research materials. We also find that stated sharing tendencies are significantly lower for respondents in the Qualitative and Survey categories compared to each of the three other methodological areas, i.e., the respondents in the Analytical, Archival, and Experimental categories (two-tailed p-value \< 0.100).

\centerline{--- Insert Table 8 about here ---}

Table 8 Panel B reports answers to three questions measuring respondents' perceptions of how important others consider research material sharing to be (i.e., prescriptive and descriptive importance). Namely, these three questions ask (1) what percentage of accounting researchers in general favor research material sharing, (2) what percentage of editors of the top six accounting journals believe it increases the value of a manuscript, and (3) what percentage of accounting researchers publicly share research materials. The data in Panel B reveal that respondents believe about 44% of accounting researchers favor publicly sharing research materials, they believe 60.8% of the top-six accounting editors to be in favor of publicly sharing research materials, and they believe 27.6% of accounting researchers actually share research materials.

\centerline{--- Insert Figure 3 about here ---}

To understand the differences between these three questions, Figure 3 displays box plots, one for each question and separately for each methodology. First, examining the three box plots for the sample as a whole, the visual pattern emerges that the perceptions of actual sharing behavior among accounting researchers lags behind perceptions of whether accounting researchers favor sharing, which, in turn, lags behind perceptions of whether editors value sharing. This pattern seems starker for respondents in the Archival/Field category. In this category, the box plot for the perceptions of actual sharing does not to overlap with the other two, i.e., the box plots for the perceptions of accounting researchers favoring sharing and the perceptions of whether editors value sharing. These findings suggest a contrast in the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior.

### Sharing Research Materials - Rationales

So, what prevents accounting researchers from sharing? Our survey also included questions about the rationales against sharing. When respondents reported that they did not always publicly share research materials, we asked them which reasons would make them withhold their research materials. Respondents were able to provide more than one reason.

\centerline{--- Insert Table 9 about here ---}

Table 9 Panel A displays the frequencies and percentages for each reason featured and provided in our survey. Aside from reporting the total frequencies for the entire sample, it also (again) splits them up into the five methodological fields (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey). The most commonly stated reason that respondents gave for not sharing research materials is that the data are proprietary. 56.3% of all respondents give this reason and it also ranks first for all methodological areas. This is somewhat surprising because not all methodological areas regularly deal with proprietary data. In a shared second place, are three more prominent reasons respondents provided, namely, (1) the time that it takes to make materials available (29.9% of all respondents), (2) the fear of being scooped when materials become publicly available (23.2% of all respondents), and (3) no need for sharing as their data are already publicly available (33.9% of all respondents). There are some other notable differences across the methods. For qualitative researchers, deidentification problems are a relatively important reason (45.8%) compared to the others. Also, analytical researchers consider the time that it takes to make materials available far less of a reason than researchers using the other methods (i.e., 9.5%).

Besides this multiple choice questions soliciting the reasons for not sharing research materials, we also ask our participants to reflect on their answer in our hypothetical sharing scenario. The answers that they provided in this free form field have been coded by a research assistant that was not informed about the experimental design of the study. The resulting categories characterizing the coded answers and their respective frequencies are presented in Panel B, for the total sample as well as for the different treatment cells.

Different from the findings in Panel A, we are now also able to identify reasons for and not just against sharing. First and foremost our participants share because they believe that this enhances the quality of research. Another strong argument is that it helps other researchers. This argument is significantly more likely to be provided by participants that faced the collaboration treatment, in line with our theoretical predictions and providing evidence that the framing of the sharing situation has an effect on the decision-making of our participants.

The main rationales against sharing are related to the materials being considered valuable intellectual property that can potentially be reused for other research projects. A typical example for such a statement is:

\begin{displayquote}
"There might have been substantial workload flown into collecting data that also will benefit follow-up projects. Giving away the data might harm future projects without remuneration for the collection effort."
\end{displayquote}

Another interesting aspect, that does not become apparent from the pre-conditioned analysis in Panel A, is that a sizable amount of participants indicate that they are concerned about unethical use of their research materials. These concerns are related to other researchers using their work for "reverse p-hacking", trying to discredit prior findings to establish a contribution. Again, an example for such a statement:

\begin{displayquote}
"It sounds like they are trying to disprove me. They're on a witch hunt. There's a good chance they are doing this to a lot of people and are, themselves, going to suffer from a file drawer problem. If they re-run 100 people's studies and find that 1 doesn't replicate, that's the one they will publish and discredit and shame the researcher, ignoring the fact that it was likely due to chance, and not noting the 99 who got it right."
\end{displayquote}

But even without reverse p-hacking, research material sharing requests can create career concerns. An example:

\begin{displayquote}
"I would want to share my materials but I would be nervous that I did something 'wrong'  and it would make me look bad if my study didn't replicate. I'm a junior faculty and wouldn't want to do anything to jeopardize my reputation or likelihood of getting tenure."
\end{displayquote}

Another aspect, which also featured prominently in Panel A, is the time that it takes to entertain research material sharing and potential followup requests. For example:

\begin{displayquote}
"Many academics, including me, are constantly working under high pressure to deliver performance and short of time to fulfill a large range of commitments. It is simply impossible to entertain each and every such request, especially when replying to the first might lead to feeling the obligation to answer more questions from the requester in the future. A requester can be a relatively inexperienced graduate student exploring a doctoral topic, which has implications to how many questions s/he might have in the future. Thus, the propensity to reply to a request often depends on the status of the requester in the field and the anticipated consequences (or the lack of) of entertaining the request (or not)."
\end{displayquote}

The last aspect of the this quote also hints at a rationale that was commonly featured in the "it depends" category: the personality of the requesting person and their reputation. A final example:

\begin{displayquote}
"It depends on whether I know the person and their reputation in the research community. I think my reputation would be tarnished if I didn't provide but I would also be skeptical of providing someone I didn't know my hand-collected data and code that took years of work to produce."
\end{displayquote}

These statements indicate the potential for selective sharing among well-connected researchers, which would benefit an "in-crowd" of academics while at the same time unleveling the academic playing field and increasing  inequality. Taken together, we conclude from the rationale analysis that our participants give more consideration to potential sharing costs then they give to potential sharing benefits. While the sharing benefits become more prevalent with a collaboration framing, the sharing costs are prominent regardless of the hypothetical scenario.

### Pre-registration

Our survey has so far revealed that accounting researchers who participated in our survey are more skeptical about reproducibility than other social science areas. We also find that they are less familiar with research materials sharing as an open science practice that helps address reproducibility and that they find that practice less important. There seem to be various reasons why accounting researchers share and even more why they do not share their research materials. Besides research material sharing, our survey also covered a second Open Science practice: Pre-registration.

\centerline{--- Insert Table 10 about here ---}

Table 10 lists the frequencies and percentages for three questions about pre-registration. Panel A considers respondents' familiarity with the practice itself. Namely, we asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^7] The results in Panel A suggest accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology. They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010). While this finding might appear surprising at first glance one has to factor in that the practice of pre-registration is gaining traction over time and our survey was fielded two years later than the second wave of our benchmark survey.

\centerline{--- Insert Figure 4 about here ---}

Panel B reports data on the first year respondents pre-registered. Namely, we asked them: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^8] The findings exhibit a clear pattern: Accounting researchers started considering pre-registration for the first time significantly later than researchers in other social science fields (two-tailed p-value \< 0.010). The take-up started around 2018 compared to 2015-2016 for the other fields. This finding is also supported by Figure 4 showing that the take-up of pre-registration in accounting over time lags behind the other social science areas.

Panel C shows data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^9] Results indicate no clear differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100). However, the perceived increase in trustworthiness when pre-registering is less in accounting compared to psychology and sociology (two-tailed p-value \< 0.010).

[^7]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".

[^8]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"

[^9]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?". We found this question to be quite broad yet it used a trustworthiness scale. So, we chose more specific framing for our question.

\centerline{--- Insert Table 11 about here ---}

In this final part of our analysis, we examine differences in familiarity, usage, and trustworthiness of pre-registration across the different methodological areas within accounting. Table 11 displays respondents' frequencies using three panels. Similar to Table 10 Panel A, Panel A of Table 11 reports on familiarity, i.e., the question: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?" Somewhat unsurprisingly, Panel A shows that qualitative accounting researchers are less familiar with the practice than accounting researchers belonging to the Archival, Experimental, and Survey categories (two-tailed p-value \< 0.100). Yet, there is no statistical difference between qualitative and analytical accounting researchers. Panel B reports on differences in usage, specifically, the question "`r vars$text[100]`", similar to the question featured in Table 10 Panel B. We find that accounting researchers in the experimental field report the highers usage of pre-registration, while none of the qualitative accounting researchers report using it. Lastly, Panel C reports differences in perceived trustworthiness. Specifically, it features answers to the question "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?" which is identical to the question featured in Table 10 Panel C. We find no clear evidence of differences among the different methodologies in whether they trust pre-registered work more than work that has not been pre-registered.

## Discussion and Conclusion

Our results support the conclusion that us accountants face an "open science dilemma". On the one hand, we are more skeptical about the reproducibility of our influential findings than other social science researchers are about their respective findings. On the other hand, we seem to be a little bit behind the curve in terms of research material sharing and research design pre-registration.

If these conclusions are descriptive: What should be our reaction? While we are not in the position to advise our profession on how to proceed, we feel that a two-pronged approach might be in order. First: Why are we so skeptical about our own work? Is this an example of the anecdotal "professional skepticism" that leads us accountants to over-weight bad signals in general? Or do we indeed have good reasons to be concerned? The only way to find out is to take stock.

As @LSA_2024 indicate, reproduction studies in accounting are not rare, and a majority of those confirms prior results. However, we need more systematic evidence on whether our findings reproduce and also hold in new settings and/or with new data. A very impressive exercise in that regard is the recent large-scale reproduction attempt of studies published in Management Science [@FGHKO_2023] that systematically reproduced almost 500 articles that were published in Management Science before and after their establishment of a Data and Code Policy in 2019. One interesting finding from that study is that accounting studies in Management Science are -if anything- more reproducible than studies in neighboring fields like finance. Based on this it seems as if professional skepticism might indeed be partly responsible for our open science dilemma.

It would be insightful to compare the findings for Management Science, which also document an impressive effect of their data and code policy, with data on studies published in the Journal of Accounting Research, again pre and post their data policy. These findings could in turn then be compared with those for studies published in other leading journals that do not have a dedicated data and code policy (yet). But not only systematic large-scale reproduction studies can update our priors about the reproducibility of our work. Replication games, potentially embodied in doctoral education, are an alternative means to assess the reproducibility of our work while at same time helping researchers to grow their network and empirical skill-sets alike. Taken together, we believe that the academic accounting profession should be well positioned to take a leading role in verifying its own output. In the end, assessing the reproducibility of scientific work is an assurance and auditing process, an area we know quite a bit about!

The second element of our two-pronged approach would be to promote research material sharing and pre-registration, potentially in combination with other open science measures that are aiming to increase the accessibility and re-usability of scientific work. As economists, we are quick to jump on the incentive problems in this regard. Why should we do it? Does sharing code and data help to build academic careers? While some associative evidence from other fields indicates that papers that share their data are cited more often [@PDF_2007], currently, as hard as it seems, the answer to this is not clearly affirmative. Research material sharing requires skills and time, and, to the extreme, devoting this time might even be regarded as a negative signal by tenure and promotion committees, assuming that it crowds out time spent on producing "more tenurable output".

To us, this mindset seems to be the core of the the problem. We believe that it is misguided as research material sharing constitutes a public good that is crucial for scientific progress. Think about a scientific computing world without open source contributions. Without the BSD/Linux operating system and its tools, without Python, R, git, Latex, and the accompanying library ecosystem. The scientific advancements in areas like Econometrics, Machine Learning, and Natural Language Processing would be -if at all feasible- severely delayed. As our field builds on the insights of these areas, we benefit from the open science paradigm in our every day work.

Given that, one might wonder whether data and code sharing by accounting researchers can create similar positive externalities. As our comparative competitive advantage lies less in methodological aspects but more in institutional expertise, we sense potential candidates in the area of carefully curated and pre-processed data building on the universe of firm disclosures. Prominent examples include curated word lists for sentiment analyses in financial settings [e.g., @LM_2011], topic model-based measures of specific firm risks [e.g., @H_2019], and industry classifications based on financial disclosures [e.g., @HP_2016].

A closely related area where we see the potential of accounting data to develop an impact is the collection and pre-processing of web and electronic filing data. For the former, web scraping of corporate webpages can provide informative data [e.g., @BBB_2021] and for the latter, in particular the upcoming electronic filing requirements for sustainability reports hold promise. While in this area, researchers are competing with established commercial data providers, the need of research to study also unstructured textual data makes it necessary and useful to build research-focused data pipelines and products instead of simply trusting (and paying) commercial data vendors. An additional aspect of this is that freely licensable research data can remove one of the largest entry hurdles for empirical archival accounting researchers.

While these flagship projects are useful showcases that data and code sharing in the accounting domain can be very impactful also for other domains, in order to promote reproducible workflows overall we need to make the case that adopting such a workflow not only contributes to the public good by making research materials accessible but also enhances research efficiency at the individual level. In order to be able to share code and data, one has to adopt a workflow that integrates reusability aspects into project development. The data and code requirements of leading journals in economics, finance, and accounting are not only pushing the availability of research materials but also impose substantial costs on researchers that have to provide more or less complete replication package upon acceptance. As many affected by these regulations will be open to admit, transforming an empirical project from an internal "well it works" scripting exercise to a well documented replication package that ideally works across multiple platforms is far from trivial. This process becomes significantly easier and also more enjoyable if an open science oriented workflow is adopted throughout all stages of project development. Besides this, it also makes it easier for co-author teams to cooperate.

As lack of time has been identified as one of the biggest roadblocks against research material sharing in our survey, educational activities targeted at the PhD-level in scientific computing and project management in general seem important. While well-funded research institutions might have the opportunity to outsource these skills to research professionals, the vast majority of researchers world-wide need to acquire them themselves. This is not necessarily a bad thing, as we believe that having these skills as a researcher enables one to develop more creative research projects compared to researchers that are unaware of what is feasible with state-of-the-art scientific computing. In the old days, many accounting PhD programs were implicit- or explicitly relying on scientific computing skills to be handed down from one PhD generation to another as tacit knowledge. It seem that these days are over and that dedicated scientific computing courses should become as a central component of the scientific education in the quantitative social sciences as lab training is in the natural sciences.

A lot of the above applies mostly to the empirical and quantitative areas of our discipline. What about analytical and qualitative researchers and their studies? As becomes apparent from our findings, their views on open science differ quite prominently from the "accounting mainstream". Analytical researchers seem to be much more confident in their own work, potentially in line with theoretical work being easier to verify during the review process. Then again, in order to develop the impact that it deserves, analytical work not only needs to be reproducible but also accessible and reusable, ideally also by non-expert researchers from neighboring methods. Qualitative work, on the other hand, faces challenges that sets it apart from typical quantitative work. First, its data is often collected under confidentiality, legally restricting future sharing. Second, its unique richness makes it inherently hard to share across subjects, especially if re-identification issues are present. Third, related and maybe more epistemological in nature, the assumption of objectivity, which allows research materials to be detached from the individual researcher and to be re-used by others, is questioned within the qualitative realm. This implies that qualitative scholars have to develop -and are developing [e.g., @M_2014; @FRV_2022]- their own understanding what reproducibility means within their methodological paradigm.

Finally, fears and a general lack of trust in fellow researchers also seem to be important deterrents to the adoption of open science methods. This is human but unfortunate, also because it leads to subtle "home biases" when it comes to sharing, potentially increasing academic inequality and hindering scientific progress. While the fear of being "scooped" can be addressed by publishing materials later in the publication progress or publicly claiming intellectual ownership to ideas via registration and use of well-established repositories, fears with regards to future researchers pointing to deficiencies in ones work and/or a general lack of trust are harder to overcome. For both aspects, we need to work towards changing the error climate in the academic discipline. Also, we believe that it might be helpful to move away from the "policing" aspect of reproducibility and instead stress the collaborative public good character of open science activities. With them, we can help each other, promote our field and, yes, make the research process even more fun!

\newpage

## References {.unnumbered}

\singlespacing

\small

::: {#refs}
:::

\doublespacing

\newpage

## Figures {.unnumbered}

### Figure 1: Reproducibility of Influential Findings Across the Social Sciences {.unnumbered}

```{r Figure1, fig.width=8, fig.height=5}
likert_plot(mr, "reprod", "demog_discipline", title_str = "How confident are you that the influential reserach findings in your area will replicate/reproduce?", llevels = vars$resp_label[80:84])
```

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023. The question asked in our survey is "`r vars$text[80]`" while the original question used in the survey of @FLCPSWMBP_2023 is "How confident are you that the influential research findings in \[Discipline\] would replicate?". The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S. Our survey was conducted in 2022 among accounting researchers world-wide. Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
```
\newpage

### Figure 2: Importance of Research Material Sharing Across the Social Sciences {.unnumbered}

```{r Figure2, fig.width=9, fig.height=5}
mr$sharing_important_rescaled = floor(mr$sharing_important)
likert_plot(mr, "sharing_important_rescaled", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53])
```

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023. The question asked in our survey is "`r vars$text[49]`" while the original question used in the survey of @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting data or code online is important for progress in \[Discipline\]?". The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S. Our survey was conducted in 2022 among accounting researchers world-wide. Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.

```{=tex}
\end{singlespace}
\setlength{\parindent}{4em}
```
\newpage

### Figure 3: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}

```{r Figure3, fig.width=8, fig.height=6}
pres_desc_plot(sd)
```

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
This figure is based on our survey data and summarizes the findings from three separate questions. The first question, related to the preferences of editors is "`r vars$text[79]`". The second question, related to the preferences of other researchers, is "`r vars$text[78]`". The third question, related to the the actual behavior of other researchers, is "`r vars$text[54]`". Our survey is discussed in more detail in section 2 of the paper.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
```
\newpage

### Figure 4: Pre-Registration: Take-up over Time Across the Social Sciences {.unnumbered}

```{r Figure4, fig.width=8, fig.height=6}
pre_reg_over_time_plot(mr)
```

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023. The question of our survey is "`r vars$text[102]`". The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?". The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S. Our survey was conducted in 2022 among accounting researchers world-wide. Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
```{=tex}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}
```
## Tables {.unnumbered}

### Table 1: Sample Composition {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
|                                 |                    N (%) |
|:--------------------------------|-------------------------:|
| Authors identified (Raw Sample) |                    2,660 |
| \- Excluded or missing          | 118 (4.4% of identified) |
| = Emails sent                   |                    2,542 |
| \- Emails bounced               |       206 (8.1% of sent) |
| = Emails received               |                    2,336 |
| Surveys Started                 |      391 (15.4% of sent) |
| Surveys Partially Completed     |      254 (10.9% of sent) |
| Surveys Fully Completed         |       222 (8.7% of sent) |

This table reports on our sample composition. Starting with a list of authors that we identified by Scopus to have published in the "Top 6" accounting journals (Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review) over the period 2016 to 2021, we excluded all authors with missing email information. We recorded any email bounce messages that we received but report the response rate based on the emails that we sent out. Our survey is discussed in more detail in section 2 of the paper.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
```
\newpage

### Table 2: Sample Demographics {.unnumbered}

#### Panel A: Sample Descriptives {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
```{r Tab2aDemographics, asis = TRUE}
extract_df <- function(dvar, title) {
	df <- create_demog_table(sd, dvar, df_only = TRUE)
	names(df) <- c("Characteristic", "n", "%")
	bind_rows(
		tibble(
			Characteristic = title,
			n = "",
			`%` = ""
		),
		df %>% mutate(Characteristic = paste0("- ", Characteristic))
	)
}

tab <- bind_rows(
	extract_df("demog_field", "Subfield"),
	extract_df("demog_method", "Method"),
	extract_df("demog_age", "Age Group"),
	extract_df("demog_gender", "Gender"),
	extract_df("demog_region", "Geographic Region")
)
gt(tab) %>% as_latex()

```

\newpage

#### Panel B Regional Representativeness {.unnumbered}

```{r Tab2bGeoRep, asis = TRUE}
tab <- create_regions_rep_table(pop, sd)
tab_latex <- gt(tab) %>% 
	cols_align("right", -1) %>% 
	tab_spanner(label = "Population", columns = starts_with("Population")) %>%
	tab_spanner(label = "Sample", columns = starts_with("Sample")) %>%
	cols_label(
    ends_with(" n") ~ "n",
    ends_with(" %") ~ "%",
    ends_with("Rate") ~ "Regional RR"
	) %>%
		as_latex() 
# tab_latex[1] <- sub("\\\\toprule\\n", "", tab_latex)
tab_latex[1] <- sub("\\{Sample\\} &  ", "{Sample} &  \\\\multirowcell{2}{Regional \\\\\\\\ Response Rate}", tab_latex)
sub("& Regional RR", "& ", tab_latex)
```

This table details the demographics of our sample. As respondents were free not to answer any given question, the total number of answers vary by demographic. In Panel B, we contrast the geographical distribution of our sample with the geographical distribution of the survey population. For this, we use the affiliation of our authors as indicated by Scopus. For `r sum(is.na(pop$affil_country))` cases, the affiliation's country is unavailable on Scopus. Our survey is discussed in more detail in section 2 of the paper.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
### Table 3: Reproducibility of Influential Findings Across the Social Sciences {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
How confident are you that the influential research findings in your field would reproduce/replicate?

```{r Tab3ReprodSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(mr, "reprod", "demog_discipline", get_resp_label("reprod_acc"), df_only = TRUE)
gt(tab) %>% as_latex()
```

This table is based on our survey data merged with the data collected by @FLCPSWMBP_2023. The question asked in our survey is "`r vars$text[80]`" while the original question used in the survey of @FLCPSWMBP_2023 is "How confident are you that the influential research findings in \[Discipline\] would replicate?". The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S. Our survey was conducted in 2022 among accounting researchers world-wide. Our survey and the merging process of the data are discussed in more detail in section 2 of the paper. The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field. (\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respectively.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
### Table 4: Reproducibility of Influential Findings: Assessment Across Methods {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
#### Panel A: General Assessment by Method {.unnumbered}

```{r Tab4aReprMethod, asis = TRUE}
tab <- create_pct_cross_tab_table(
	sd, "reprod_acc", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab %>% select(-Other)) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel B: Method-Specific Assessment {.unnumbered}

```{r Tab4bReprMethod, asis = TRUE}
tab <- create_pct_cross_tab_table(
	sd, "reprod_method", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab %>% select(-Other)) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel C: Assessment Gap (Method - General) {.unnumbered}

```{r Tab4cReprMethod, asis = TRUE}
sd$reprod_method_delta <- as.numeric(sd$reprod_method) - as.numeric(sd$reprod_acc)
tab <- create_pct_cross_tab_table(
	sd, "reprod_method_delta", "demog_method", 
	resp_label = sort(na.omit((unique(sd$reprod_method_delta)))),
	ctests = TRUE, add_num_labels = FALSE, df_only = TRUE 
) 
gt(tab %>% select(-Other)) %>%
	cols_align("right", -1) %>% 
	as_latex()
```

This table is based on our survey data and two separate questions. The response presented in Panel A is based on the question "`r vars$text[80]`" while the response presented in Panel B is based on the question "`r vars$text[90]`". Panel C reports the individual level differences, measured in likert steps, between the answers given for Panel B and Panel A. In all Panels, answers from two respondents who classified their method as "Other" are excluded. Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
```{=tex}
\begin{landscape}
\begin{singlespace}
\setlength{\parindent}{0em}
```
### Table 5: Sharing of Research Materials Across the Social Sciences {.unnumbered}

#### Panel A: Familiarity {.unnumbered}

```{r Tab5aSharingHeardSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "sharing_heard", "demog_discipline", 
	resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel B: Assessed Importance {.unnumbered}

```{r Tab5bSharingImportanceSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "sharing_important_rescaled", "demog_discipline", 
	resp_label = get_resp_label("sharing_important"), df_only = TRUE
) 
gt(tab ) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

This table is based on our survey data merged with the data collected by @FLCPSWMBP_2023. For Panel A, the question of our survey is "`r vars$text[44]`" where we code the response "Not at all familiar" as "No". The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of publicly posting data or code online for a completed study?". For Panel B, the question of our survey is "`r vars$text[49]`". The question used in the survey of @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting data or code online is important for progress in \[Discipline\]?" The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S. Our survey was conducted in 2022 among accounting researchers world-wide. Our survey and the merging process of the data are discussed in more detail in section 2 of the paper. The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field. (\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respectively.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
### Table 6: Sharing of Research Materials Across Methods {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
#### Panel A: Familiarity {.unnumbered}

```{r Tab6aSharingFamiliarity, asis = TRUE}
df <- sd %>% filter(demog_method != "Other")
tab <- create_pct_cross_tab_table(
	df, "sharing_familiar", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel B: Assessed Importance {.unnumbered}

```{r Tab6bSharingImportance, asis = TRUE}

tab <- create_pct_cross_tab_table(
	df, "sharing_important", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

This table is based on our survey data and two separate questions. The response presented in Panel A is based on the question "`r vars$text[44]`" while the response presented in Panel B is based on the question "`r vars$text[49]`". In all Panels, answers from two respondents who classified their method as "Other" are excluded. Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\end{landscape}
\newpage
```
### Table 7: Scenario Analysis: Hypothetical Sharing Likelihood {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
#### Panel A: Descriptive Statistics {.unnumbered}

```{r Tab7aExpDescriptives, asis = TRUE}
stats <- sd %>%
	group_by(exp_tment_control, exp_tment_private) %>%
	select(exp_tment_control, exp_tment_private,exp_pct_share) %>%
	summarise(
		N = sprintf("%d", n()),
		Mean = sprintf("%.1f%%", mean(exp_pct_share)),
		`Std. Dev.` = sprintf("%.1f%%", sd(exp_pct_share)),
		Minimum = sprintf("%.1f%%", min(exp_pct_share)),
		`25%` = sprintf("%.1f%%", quantile(exp_pct_share, 0.25)),
		Median = sprintf("%.1f%%", median(exp_pct_share)),
		`75%` = sprintf("%.1f%%", quantile(exp_pct_share, 0.75)),
		Maximum = sprintf("%.1f%%", max(exp_pct_share))
	) %>%
	ungroup() %>%
	mutate(
		Rationale = c(rep("Collaboration", 2), rep("Control", 2)),
		Scope = c(rep(c("Public", "Private"), 2))
	) %>%
	select(-exp_tment_control, -exp_tment_private) %>%
	select(Rationale, Scope, everything())
tab <- create_pct_cross_tab_table(
	sd, "reprod_acc", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(stats) %>% 
	cols_align("right", -1:-2) %>% 
	as_latex()
```

#### Panel B: Regression Results {.unnumbered}

```{r Tab7bExpRegResults, asis = TRUE}
sd$exp_tment_collab <- 1 - sd$exp_tment_control
modh1 <- lm(exp_pct_share ~ exp_tment_collab, data = sd)
modh2 <- lm(exp_pct_share ~ exp_tment_private, data = sd)
modh3 <- lm(exp_pct_share ~ exp_tment_collab*exp_tment_private, data = sd)
tab_latex  <- modelsummary(
	list(H1 = modh1, H2 = modh2, H3 = modh3), output = "gt",
	coef_rename = function(x) {
		x <- str_replace(x, fixed("exp_tment_collab"), "Collaboration rationale")
		x <- str_replace(x, fixed("exp_tment_private"), "Private scope")
		str_replace(x, fixed(":"), "×")
	},
	gof_map = list(
		list(raw = "adj.r.squared", clean = "Adjusted R2", fmt = 3),
		list(
			raw = "nobs", clean = "Number of observations", 
			fmt = function(x) format(x, big.mark=",")
		)
	),
	stars = c('*' = .1, '**' = 0.05, '***' = .01),
	estimate  = "{estimate}{stars}",
) %>% as_latex()

# The below is needed since some tex environment chock on the longtable environment
# See https://github.com/vincentarelbundock/modelsummary/issues/50
tab_latex[1] <- sub("\\(Intercept\\)", "Intercept", tab_latex)

sub("Adjusted R2", "\\\\midrule\\\\addlinespace[2.5pt]\nAdjusted R²", tab_latex)
```

This table reports the results from the pre-registered experimental design contained in our survey. Is is based on a hypothetical code and data sharing scenario were we manipulated the sharing rationale (collaboration versus control) and the sharing scope (private versus public). All experimental materials are detailed in the Online Appendix of this study. The outcome variable is the stated likelihood that the respondent would share their code and data under the hypothetical scenario. Panel A reports the descriptive statistics for this outcome, conditional for the different treatment cells. Panel B reports the results from OLS regressions of the outcome on the binary treatments (H1 and H2) and their interaction (H3).

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
### Table 8: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
#### Panel A: Stated sharing frequency across fields {.unnumbered}

```{r Tab8aSharingUse, asis = TRUE}

tab <- create_pct_cross_tab_table(
	df, "sharing_use", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel B: Sharing preference and sharing behavior believes across fields {.unnumbered}

```{r Tab8bSharingPreDes, asis = TRUE}
stats <- df %>%
	select(
		demog_method, sharing_perc_other_prefer, 
		sharing_perc_editor_prefer, sharing_perc_other_share
	) %>%
	na.omit() %>%
	group_by(demog_method) %>%
	pivot_longer(-1, names_to = "var", values_to = "values") %>%
	group_by(var, demog_method) %>%
	summarise(
		Mean = sprintf("%.1f%%", mean(values)),
		`Std. Dev.` = sprintf("%.1f%%", sd(values)),
		`25%` = sprintf("%.1f%%", quantile(values, 0.25)),
		Median = sprintf("%.1f%%", median(values)),
		`75%` = sprintf("%.1f%%", quantile(values, 0.75)),
	) %>% 
	pivot_longer(-1:-2, names_to = "stat", values_to = "values") %>%
	pivot_wider(
		id_cols = c(var, stat), 
		names_from = demog_method, values_from = "values"
	) %>% 
	ungroup() %>%
	select(-var) %>%
	rename(" " = stat)

tab <- rbind(
	c("General Preference for Sharing", rep("", 5)),
	stats[6:10,],
	c("Editor Preference for Sharing", rep("", 5)),
	stats[1:5,],
	c("Believes About Actual Sharing Behavior", rep("", 5)),
	stats[11:15,]
)

tab_latex <- gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()

tab_latex <- sub("General Preference for Sharing &  &  &  &  &", "\\\\multicolumn{6}{l}{General Preference for Sharing}", tab_latex)
tab_latex <- sub("Editor Preference for Sharing &  &  &  &  &", "\\\\multicolumn{6}{l}{Editor Preference for Sharing}", tab_latex)
sub("Believes About Actual Sharing Behavior &  &  &  &  & ", "\\\\multicolumn{6}{l}{Believes About Actual Sharing Behavior}", tab_latex)

```

This table is based on our survey data and several separate questions. The response presented in Panel A is based on the question "`r vars$text[55]`" while the response presented in Panel B is based on the questions "`r vars$text[78]`" (general preference for sharing), "`r vars$text[79]`" (editor preference for sharing) and "`r vars$text[54]`" (actual sharing behavior). In all Panels, answers from two respondents who classified their method as "Other" are excluded. Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
### Table 9: Sharing of Research Materials: Rationales {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
#### Panel A: Reasons against Sharing (Close-Ended Question) {.unnumbered}

```{r Tab9aSharingReasons, asis = TRUE}
tab <- sd %>%
	select(starts_with("sharing_reason"), -starts_with("sharing_reason_other")) %>% 
	na.omit() %>%
	pivot_longer(everything(), names_to = "reason", values_to = "val") %>%
	group_by(reason) %>%
	summarise(
		sum = sum(val),
		Total = sprintf("%d (%.1f %%)", sum(val), 100*sum(val)/n())
	) %>%
	arrange(-sum) %>% 
	select(-sum) %>%
	left_join(
		sd %>%
			select(demog_method, starts_with("sharing_reason"), -starts_with("sharing_reason_other")) %>% 
			filter(demog_method != "Other") %>%
			na.omit() %>%
			pivot_longer(-1, names_to = "reason", values_to = "val") %>%
			group_by(demog_method, reason) %>%
			filter(sum(val) != 0) %>%
			summarise(
				stat = sprintf("%d (%.1f %%)", sum(val), 100*sum(val)/n())
			) %>%
			pivot_wider(id_cols = reason, names_from = demog_method, values_from = stat), 
		by="reason"
	) %>%
	mutate(
		reason =str_remove(reason, fixed("sharing_reason_")) %>% 
				str_replace_all(fixed("_"), " ") %>% str_to_sentence()
		) %>%
	rename(Reason = reason)

gt(tab) %>% 
	cols_align("right", -1) %>% 
	sub_missing(missing_text = "") %>%
	as_latex()
```

```{=tex}
\newpage
\begin{landscape}
```
#### Panel B: Rationales about Sharing (Open-Ended based on Hypothetical Scenario) {.unnumbered}

```{r Tab9bSharingRationales, asis = TRUE}
df <- sd %>% left_join(
	readRDS("../data/generated/verbal_response_coded.rds") %>% 
		select(-exp_reflect),
	by = "id"
) %>% mutate(
	verbal_gave_reasons = !is.na(verbal_n_reasons),
	verbal_mostly_positive = 1*(verbal_positive_reasons > verbal_negative_reasons),
	exp_tment_colab = 1 - exp_tment_control,
	exp_tment_group = 2*exp_tment_colab + exp_tment_private,
	demog_active_res = as.numeric(demog_active_res) - 1,
	demog_trust = (demog_trusting + demog_trustworthy)/2
)

reasons_overall <- df %>%
	filter(verbal_gave_reasons) %>%
	summarise(across(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), sum
	)) %>%
	pivot_longer(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), values_to = "n", names_to = "reason"
	) %>% mutate(
		reason = str_remove(reason, fixed("verbal_")),
		pct_all = n/sum(df$verbal_gave_reasons) 		
	)

reasons_by_tgroup <- df %>%
	filter(verbal_gave_reasons) %>%
	group_by(exp_tment_group) %>%
	summarise(across(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), 
		~ {sum(.x)/n()} 
	)) %>%
	pivot_longer(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), values_to = "pct", names_to = "reason"
	) %>% pivot_wider(
		names_from = "exp_tment_group", names_prefix = "pct_tg", values_from = "pct"
	) %>%
	mutate(
		reason = str_remove(reason, fixed("verbal_"))
	)

reasons <- reasons_overall %>% left_join(reasons_by_tgroup, by = "reason")

tab <- reasons %>%
	mutate(
		type = str_extract(reason, "pos|neg|dep"),
		reason = paste(
			"...",
			str_remove(reason, "pos_|neg_|dep_") %>% 
				str_replace_all(fixed("_"), " ") %>%
				tolower()
		),
		across(starts_with("pct"), ~ sprintf("%.1f %%", 100 * .x))
	) %>%
	mutate(other = (reason == "... other reasons")) %>%
	arrange(type, other, -n) %>%
	select(type, everything()) %>%
	select(-other)

names(tab) <- c(
	"Rationale", "Reason", "N", 
	"% Total", "% Control/Public", "% Control/Private", 
	"% Collab/Public", "% Collab/Private"
)

tab <- rbind(
	c("I share because it ... ", rep("", 6)),
	tab %>% filter(Rationale == "pos") %>% select(-Rationale),
	c("I do not share because ... ", rep("", 6)),
	tab %>% filter(Rationale == "neg") %>% select(-Rationale),
	c("It depends ... ", rep("", 6)),
	tab %>% filter(Rationale == "dep") %>% select(-Rationale)
)

tab_latex <- gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()

sub(
	"career concerns related to failed replications or corrections",
	"career concerns related to failed replications", tab_latex
)
```

This table is based on our survey data and two separate questions. The response presented in Panel A is based on the multiple choice answer to the close-ended question "`r vars$text[60]`". Panel B is based on the answer to the open-ended question that we pose as a follow-up in our experimental scenario: "`r vars$text[7]`". The free form answers to this question have been coded by an research assistant that had no information about the experimental design or the respective treatments. In Panel A, answers from two respondents who classified their method as "Other" are included in the Total column, but excluded from the methods break-up.

```{=tex}
\setlength{\parindent}{4em}
\end{landscape}
\end{singlespace}
\newpage
```
```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
### Table 10: Pre-Registration Across the Social Sciences {.unnumbered}

#### Panel A: Awareness {.unnumbered}

```{r Tab10aPreRegAwareSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "prereg_heard", "demog_discipline", 
	resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel B: Take-up over Time {.unnumbered}

```{r Tab10bPreRegTimeSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "prereg_use_first_time", "demog_discipline", 
	resp_label = na.omit(sort(unique(mr$prereg_use_first_time))), 
	add_num_labels = FALSE, df_only = TRUE
)

# NOTE: This hack Needs to be checked manually whenever something 
# the underlying data changes - which it should not

up_to_2010 <- c(
	"<= 2010", 
	sum(as.numeric(substr(tab$Accounting[1:13], 1, 1))),
	sum(as.numeric(substr(tab$Economics[1:13], 1, 1))),
	sum(as.numeric(substr(tab$`Political Science`[1:13], 1, 1))),
	sum(as.numeric(substr(tab$Psychology[1:13], 1, 1))),
	sum(as.numeric(substr(tab$Sociology[1:13], 1, 1)))
)
up_to_2010[2:6] <- sprintf(
	"%s (%.1f %%)", 
	up_to_2010[2:6],
	100*as.numeric(up_to_2010[2:6])/as.numeric(tab[26,2:6])
)
tab <- rbind(up_to_2010, tab[14:28,])

gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

```{=tex}
\newpage
\begin{landscape}
```
#### Panel C: Trustworthiness {.unnumbered}

```{r Tab10cPreRegTimeSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "prereg_opinion", "demog_discipline", 
	resp_label = get_resp_label("prereg_trust"), df_only = TRUE
) 
gt(tab ) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

This table is based on our survey data merged with the data collected by @FLCPSWMBP_2023. For Panel A, the question of our survey is "`r vars$text[95]`" where we code the response "Not at all familiar" as "No". The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?". For Panel B, the question of our survey is "`r vars$text[102]`". The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?". For Panel C, the question of our survey is "`r vars$text[103]`". The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?". The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S. Our survey was conducted in 2022 among accounting researchers world-wide. Our survey and the merging process of the data are discussed in more detail in section 2 of the paper. The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field. (\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respecively.

```{=tex}
\setlength{\parindent}{4em}
\end{landscape}
\end{singlespace}
\newpage
```
### Table 11: Pre-Registration Across Methods {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
```
#### Panel A: Familiarity {.unnumbered}

```{r Tab11aPreRegFamiliarity, asis = TRUE}
df <- sd %>% filter(demog_method != "Other")
tab <- create_pct_cross_tab_table(
	df, "prereg_familiar", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel B: Usage {.unnumbered}

```{r Tab11bPreRegUse, asis = TRUE}

tab <- create_pct_cross_tab_table(
	df, "prereg_use", "demog_method", 
	resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
) 
# Adjust levels to be zero based.
tab[4,2:6] <- t(sprintf("%.2f", as.numeric(tab[4,2:6]) - 1))
tab[5,2:6] <- t(sprintf("%.2f", as.numeric(tab[5,2:6]) - 1))
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

#### Panel C: Trustworthiness {.unnumbered}

```{r Tab11cPreRegTrust, asis = TRUE}

tab <- create_pct_cross_tab_table(
	df, "prereg_trust", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()
```

This table is based on our survey data and three separate questions. The response presented in Panel A is based on the question "`r vars$text[95]`", the response presented in Panel B is based on the question "`r vars$text[100]`", and the response presented in Panel C is based on the question "`r vars$text[103]`". In all Panels, answers from two respondents who classified their method as "Other" are excluded. Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.

```{=tex}
\setlength{\parindent}{4em}
\end{singlespace}
\newpage
```
## Online Supplement {.unnumbered}

The public GitHub repository at \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc} contains the data and the code of this project.

## Appendix A: Survey Administration and Instrument {.unnumbered}

```{=tex}
\begin{singlespace}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
```
### Initial Invitation - November 21, 2022 {.unnumbered}

\[Title: Share your views on Accounting Research\]

Dear colleague,

We are conducting a study about sharing research materials, reproducibility, and pre-registration in accounting research. You have been chosen to provide your opinion on this subject because you are a published author in one of the leading accounting journals. We obtained your email address from publicly available sources.

Participating in our study takes around 7 minutes of your time. We will publicly share the anonymized data and results with the academic community in due course.

As a token of gratitude for your time, we will donate 1,000 € multiplied by the response rate to the United Nations International Children's Emergency Fund (UNICEF).

Click or copy and paste the URL below in your internet browser to participate in our study:\
\[URL\]

Should you have any other comments or questions, please feel free to contact us via \[EMAIL\].

We thank you for your consideration and participation.

Sincerely,

Joachim Gassen\
Humboldt-Universität zu Berlin\
TRR 266 Accounting for Transparency

Jacqueline Klug, Victor van Pelt\
WHU -- Otto Beisheim School of Management

Click here to unsubscribe from future e-mails. Click here to view our data protection guidelines.

Further information:

This study has been approved by the ethical review board of the WHU -- Otto Beisheim School of Management.

Participation in our study is entirely voluntary, and there are no consequences for you if you choose not to take part in it. We will ask for your consent to participate at the beginning of the study.

The data will only be analyzed and stored in anonymous form. This anonymous data will only be used for academic purposes and will be shared with other academics for research purposes.

\newpage

### Reminder 1 - November 28, 2022 {.unnumbered}

\[Title: Reminder: Share your views on Accounting Research\]

Dear colleague,

If you have not completed our **study** about **sharing research materials, reproducibility, and pre-registration in accounting research** yet, you still have time!

Participate in our **7-minute** study by following the URL below:

\[URL\]

As a token of gratitude for your time, we will **donate 1,000 € multiplied by the response rate** to the United Nations International Children's Emergency Fund (**UNICEF**).

Should you have any other comments or questions, please feel free to contact us via \[EMAIL\].

We thank you for your consideration and participation.

Sincerely,

Joachim Gassen\
Humboldt-Universität zu Berlin\
TRR 266 Accounting for Transparency

Jacqueline Klug, Victor van Pelt\
WHU -- Otto Beisheim School of Management

Click here to unsubscribe from future e-mails.

Click here to view our data protection guidelines.

Further information:

This study has been approved by the ethical review board of the WHU -- Otto Beisheim School of Management.

Participation in our study is entirely voluntary, and there are no consequences for you if you choose not to take part in it. We will ask for your consent to participate at the beginning of the study.

The data will only be analyzed and stored in anonymous form. This anonymous data will only be used for academic purposes and will be shared with other academics for research purposes.

\newpage

### Reminder 2 - December 5, 2022 {.unnumbered}

\[Title: Reminder: Share your views on Accounting Research\]

Dear colleague,

If you have not completed our **study** about **sharing research materials, reproducibility, and pre-registration in accounting research** yet, you still have time **until next Monday**. We will close the study after that date.

Participate in our **7-minute** study by following the URL below:

\[URL\]

As a token of gratitude for your time, we will **donate 1,000 € multiplied by the response rate** to the United Nations International Children's Emergency Fund (**UNICEF**).

Should you have any other comments or questions, please feel free to contact us via \[EMAIL\]

We thank you for your consideration and participation.

Sincerely,

Joachim Gassen\
Humboldt-Universität zu Berlin\
TRR 266 Accounting for Transparency

Jacqueline Klug, Victor van Pelt\
WHU -- Otto Beisheim School of Management

Click here to unsubscribe from future e-mails.

Click here to view our data protection guidelines.

Further information:

This study has been approved by the ethical review board of the WHU -- Otto Beisheim School of Management.

Participation in our study is entirely voluntary, and there are no consequences for you if you choose not to take part in it. We will ask for your consent to participate at the beginning of the study.

The data will only be analyzed and stored in anonymous form. This anonymous data will only be used for academic purposes and will be shared with other academics for research purposes.

\newpage

### Reminder 3 - December 12, 2022 {.unnumbered}

\[Title: Last Chance to Participate: Share your views on Accounting Research\]

Dear colleague,

If you have not completed our **study** about **sharing research materials, reproducibility, and pre-registration in accounting research** yet, this **Monday** is your **last chance to participate!** We will close the study by the end of today.

Participate in our **7-minute** study by following the URL below:

\[URL\]

As a token of gratitude for your time, we will **donate 1,000 € multiplied by the response rate** to the United Nations International Children's Emergency Fund (**UNICEF**).

Should you have any other comments or questions, please feel free to contact us via \[EMAIL\].

We thank you for your consideration and participation.

Sincerely,

Joachim Gassen\
Humboldt-Universität zu Berlin\
TRR 266 Accounting for Transparency

Jacqueline Klug, Victor van Pelt\
WHU -- Otto Beisheim School of Management

Click here to view our data protection guidelines.

Further information:

This study has been approved by the ethical review board of the WHU -- Otto Beisheim School of Management.

Participation in our study is entirely voluntary, and there are no consequences for you if you choose not to take part in it. We will ask for your consent to participate at the beginning of the study.

The data will only be analyzed and stored in anonymous form. This anonymous data will only be used for academic purposes and will be shared with other academics for research purposes.

\newpage

```{=tex}
\includepdf[scale=0.7, pages=1,pagecommand={\hypertarget{survey-instrument}{\subsection*{Survey Instrument}\label{survey-instrument}}\addcontentsline{toc}{subsubsection}{Survey Instrument}}]{materials/survey.pdf}
\includepdf[scale=0.7, pages=2-, pagecommand={}]{materials/survey.pdf}
```
## Appendix B: Scenario Manipulations and Instrument {.unnumbered}

### Manipulations {.unnumbered}

+---------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Rationale     | Private Request                                                                                                                                                                                                         | Public Request                                                                                                                                                                                                                                   |
+---------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Control       | You conducted a study and published it in an academic journal. Another researcher contacts you and asks for access to your research materials (i.e., the data, code, and research procedures). The researcher wants to: | You conducted a study and published it in an academic journal. Another researcher contacts you and asks you to publicly share your research materials (i.e., the data, code, and research procedures). The researcher wants to enable others to: |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   verify how your study was conducted,                                                                                                                                                                                | -   verify how your study was conducted,                                                                                                                                                                                                         |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   investigate whether your data and methodology are sound,                                                                                                                                                            | -   investigate whether your data and methodology are sound,                                                                                                                                                                                     |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   control whether your findings can be reproduced, and                                                                                                                                                                | -   control whether your findings can be reproduced, and                                                                                                                                                                                         |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   potentially conduct a new study that corrects your study.                                                                                                                                                           | -   potentially conduct a new study that corrects your study.                                                                                                                                                                                    |
+---------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Collaboration | You conducted a study and published it in an academic journal. Another researcher contacts you and asks for access to your research materials (i.e., the data, code, and research procedures). The researcher wants to: | You conducted a study and published it in an academic journal. Another researcher contacts you and asks you to publicly share your research materials (i.e., the data, code, and research procedures). The researcher wants to enable others to: |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   understand how your study was conducted,                                                                                                                                                                            | -   understand how your study was conducted,                                                                                                                                                                                                     |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   learn from your data and methodology,                                                                                                                                                                               | -   learn from your data and methodology,                                                                                                                                                                                                        |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   contribute by generating new insights, and                                                                                                                                                                          | -   contribute by generating new insights, and                                                                                                                                                                                                   |
|               |                                                                                                                                                                                                                         |                                                                                                                                                                                                                                                  |
|               | -   potentially conduct a new study that builds on your study.                                                                                                                                                          | -   potentially conduct a new study that builds on your study.                                                                                                                                                                                   |
+---------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

: {tbl-colwidths="\[20,40,40\]"}

```{=tex}
\end{singlespace}
```
```{=tex}
\includepdf[scale=0.7, pages=1,pagecommand={\hypertarget{scenario-instrument}{\subsection*{Instrument}\label{scenario-instrument}}\addcontentsline{toc}{subsubsection}{Scenario Instrument}}]{materials/scenario.pdf}
\includepdf[scale=0.7, pages=2-, pagecommand={}]{materials/scenario.pdf}
```

### 2024-02-29 docs/presentation.qmd
first commit

---
title: "Accountants' Attitudes Towards Open Science"
author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
institute: "HU Berlin and WHU – Otto Beisheim School of Management"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format: 
  beamer: 
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3
classoption: "aspectratio=169"
bibliography: references.bib

header-includes:
- \usepackage{booktabs} 
- \usepackage{tabularx}
- \usepackage{multirow,makecell}
- \usepackage{array}
- \renewcommand\tabularxcolumn[1]{m{#1}}
- \usepackage{makecell}
- \usepackage{colortbl}
- \usepackage{adjustbox}
- \usepackage{tikz}
- \usepackage{siunitx}
- \usepackage{tabu}
- \usetikzlibrary{arrows,arrows.meta,calc,positioning,matrix}
- \input{materials/beamer_theme_trr266_16x9.sty}
---

```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)

suppressMessages({
  library(tidyverse)
  library(gt)
  library(kableExtra)
  library(modelsummary)
  library(showtext)

  devtools::source_url(
    "https://raw.githubusercontent.com/trr266/treat/main/code/R/theme_trr.R"
  )
})

set.seed(42)

source("../code/table_functions.R")
source("../code/figure_functions.R")

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv(
	"../data/external/invited_authors_retracted.csv", show_col_types = FALSE
)

# Needs \usepackage{adjustbox} in preamble
fit_gt_table_to_slide <- function(x, scale = 1) {
	if (scale == 1) repstr <- "\\\\resizebox{\\\\columnwidth}{!}{\\\\begin{tabular}"
	else repstr <- paste0("\\\\resizebox{", scale, "\\\\columnwidth}{!}{\\\\begin{tabular}")
  x <- sub("\\\\begin\\{longtable\\}", repstr, x)
  x <- sub("\\\\end\\{longtable\\}", "\\\\end{tabular}}", x)
  x
}

fit_gt_table_to_slide_long <- function(x, scale = 1) {
	if (scale == 1) repstr <- "\\\\resizebox*{!}{\\\\textheight}{\\\\begin{tabular}"
	else repstr <- paste0("\\\\resizebox*{!}{", scale, "\\\\textheight}{\\\\begin{tabular}")
  x <- sub("\\\\begin\\{longtable\\}", repstr, x)
  x <- sub("\\\\end\\{longtable\\}", "\\\\end{tabular}}", x)
  x
}

center_table <- function(x) {
	x[1] <- paste0("\\begin{center}", x[1], "\\end{center}")
	x
}
```

```{r InstallTRRFonts}
trr266_fonts_available <- all(c("Cambria", "Calibri Light") %in% font_families())

if (!trr266_fonts_available) {
  # On Mac with MS Office installation you need to add the Office
  # Fonts to the font path. The following depends on your 
  # installation but _should_ work in most cases

  office_font_path <- "/Applications/Microsoft Word.app/Contents/Resources/DFonts"
  if (Sys.info()["sysname"] == "Darwin") {
    if (dir.exists(office_font_path)) font_paths(office_font_path)
    else stop("MS Office font path not found")
  }

  rv <- tryCatch({
    font_add(family = "Cambria", regular = "Cambria.ttc")
    font_add(family = "Calibri Light", regular = "calibril.ttf")
  }, error = function(e) {
    message(sprintf("Failed to install TRR 266 fonts: %s", e))
    invisible(font_families())        
  })

  trr266_fonts_available <- all(c("Cambria", "Calibri Light") %in% rv)
  if (trr266_fonts_available) message("Successfully installed TRR 266 fonts") 
}
```

## Motivation

\begin{center}
\includegraphics[height =0.7\textheight]{"materials/ferguson_et_al_2023_uptake_over_time.png"} \\
Ferguson et al. (2023, Nature Communications)
\end{center}

## Our Study

Survey of authors that published in top six accounting journals over the period 2016-2021

Descriptive Research Questions (relative to general social science results)

- How do accountants assess the reproducibility of influential accounting work?
- How do they perceive and use two prominent open science approaches to promote reproducibility:
	- Public sharing of research materials (i.e., data, code, and procedures)
	- Pre-registration of study designs

Experimental Question: Is the stated willingness to share research materials ...

- ... affected by the rationale (collaboration versus control) and/or
- ... affected by the scope (public or private sharing) of the sharing request?

## Sample Composition

|                                 |                    N (%) |
|:--------------------------------|-------------------------:|
| Authors identified (Raw Sample) |                    2,660 |
| \- Excluded or missing          | 118 (4.4% of identified) |
| = Emails sent                   |                    2,542 |
| \- Emails bounced               |       206 (8.1% of sent) |
| = Emails received               |                    2,336 |
| Surveys Started                 |      391 (15.4% of sent) |
| Surveys Partially Completed     |      254 (10.9% of sent) |
| Surveys Fully Completed         |       222 (8.7% of sent) |

## Invitation Email

\begin{small}

Subject: Share your views on Accounting Research

Dear colleague,

We are conducting a study about sharing research materials, reproducibility, and pre-registration in accounting research. You have been chosen to provide your opinion on this subject because you are a published author in one of the leading accounting journals. We obtained your email address from publicly available sources.

Participating in our study takes around 7 minutes of your time. We will publicly share the anonymized data and results with the academic community in due course.

As a token of gratitude for your time, we will donate 1,000 € multiplied by the response rate to the United Nations International Children's Emergency Fund (UNICEF).

[...]

\end{small}

## Geographical Response Representation

```{r Tab4GeoRep, asis = TRUE}
tab <- create_regions_rep_table(pop, sd)
tab_latex <- gt(tab) %>% 
	cols_align("right", -1) %>% 
	tab_spanner(label = "Population", columns = starts_with("Population")) %>%
	tab_spanner(label = "Sample", columns = starts_with("Sample")) %>%
	cols_label(
    ends_with(" n") ~ "n",
    ends_with(" %") ~ "%",
    ends_with("Rate") ~ "Regional RR"
	) %>%
	tab_options(column_labels.vlines.style = "hidden") %>%
	as_latex() %>%
	fit_gt_table_to_slide()
# tab_latex[1] <- sub("\\\\toprule\\n", "", tab_latex)
tab_latex[1] <- sub("\\{Sample\\} &  ", "{Sample} &  \\\\multirowcell{2}{Regional \\\\\\\\ Response Rate}", tab_latex)
sub("& Regional RR", "& ", tab_latex)
```

## Reproducibility Assessed Across the Social Sciences

```{r Figure1, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
p <- likert_plot(mr, "reprod", "demog_discipline", title_str = "How confident are you that the influential reserach findings in your area will replicate/reproduce?", llevels = vars$resp_label[80:84])
if (trr266_fonts_available) {
	p + theme(text = element_text(family = "Calibri Light", size = 7))
} else p + theme(
	title = element_text(size = 10),
	legend.text = element_text(size = 6)
)
```

## Accounting Assessment by Method

```{r Tab4aReprMethod, asis = TRUE}
tab <- create_pct_cross_tab_table(
	sd, "reprod_acc", "demog_method", 
	ctests = TRUE, df_only = TRUE
)

gt(tab %>% select(-Other)) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()

```

## Assessment Gap (Method - General)

```{r Tab4cReprMethod, asis = TRUE}
sd$reprod_method_delta <- as.numeric(sd$reprod_method) - as.numeric(sd$reprod_acc)
tab <- create_pct_cross_tab_table(
	sd, "reprod_method_delta", "demog_method", 
	resp_label = sort(na.omit((unique(sd$reprod_method_delta)))),
	ctests = TRUE, add_num_labels = FALSE, df_only = TRUE 
) 
gt(tab %>% select(-Other)) %>%
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Importance of Research Material Sharing Across the Social Sciences

```{r Figure2, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
mr$sharing_important_rescaled = floor(mr$sharing_important)
p <- likert_plot(mr, "sharing_important_rescaled", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53]) +
	theme(legend.text = element_text(size = 6))
if (trr266_fonts_available) {
	p + theme(
		text = element_text(family = "Calibri Light", size = 7),
		legend.text = element_text(size = 6)
	)
} else p + theme(legend.text = element_text(size = 6))

```

## Accounting Assessment of Sharing Importance by Method

```{r Tab6bSharingImportance, asis = TRUE}
df <- sd %>% filter(demog_method != "Other")
tab <- create_pct_cross_tab_table(
	df, "sharing_important", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Research Material Sharing: Prescriptive versus Descriptive Views

```{r Figure3, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
p <- pres_desc_plot(sd) + theme(legend.position = "right")
if (trr266_fonts_available) {
	p + theme(text = element_text(family = "Calibri Light", size = 7))
} else p
```

## Sharing Determinants: Experimental Manipulation

You conducted a study and published it in an academic journal. Another researcher contacts you and asks you *(to publicly share | for access to)* your research materials (i.e., the data, code, and research procedures). The researcher wants *(others)* to:

\begin{columns}
\begin{column}{0.5\textwidth}
\begin{itemize}
\item verify how your study was conducted,
\item investigate whether your data and methodology are sound,
\item control whether your findings can be reproduced, and
\item potentially conduct a new study that corrects your study.                                \end{itemize}

\end{column}
\begin{column}{0.5\textwidth}
\begin{itemize}
\item understand how your study was conducted,
\item learn from your data and methodology,
\item contribute by generating new insights, and
\item potentially conduct a new study that builds on your study.                               
\end{itemize}
\end{column}
\end{columns}

## Experimental Findings on Sharing Determinants

```{r, asis = TRUE}
sd$exp_tment_collab <- 1 - sd$exp_tment_control
modh1 <- lm(exp_pct_share ~ exp_tment_collab, data = sd)
modh2 <- lm(exp_pct_share ~ exp_tment_private, data = sd)
modh3 <- lm(exp_pct_share ~ exp_tment_collab*exp_tment_private, data = sd)
tab_latex  <- modelsummary(
	list(H1 = modh1, H2 = modh2, H3 = modh3), output = "gt",
	coef_rename = function(x) {
		x <- str_replace(x, fixed("exp_tment_collab"), "Collaboration rationale")
		x <- str_replace(x, fixed("exp_tment_private"), "Private scope")
		str_replace(x, fixed(":"), "×")
	},
	gof_map = list(
		list(raw = "adj.r.squared", clean = "Adjusted R2", fmt = 3),
		list(
			raw = "nobs", clean = "Number of observations", 
			fmt = function(x) format(x, big.mark=",")
		)
	),
	stars = c('*' = .1, '**' = 0.05, '***' = .01),
	estimate  = "{estimate}{stars}",
) %>% as_latex()

# The below is needed since some tex environment chock on the longtable environment
# See https://github.com/vincentarelbundock/modelsummary/issues/50
tab_latex[1] <- sub("\\(Intercept\\)", "Intercept", tab_latex)

sub("Adjusted R2", "\\\\midrule\\\\addlinespace[2.5pt]\nAdjusted R²", tab_latex)
```

## Reasons against Sharing (Close-Ended Question)

```{r Tab9aSharingReasons, asis = TRUE}
tab <- sd %>%
	select(starts_with("sharing_reason"), -starts_with("sharing_reason_other")) %>% 
	na.omit() %>%
	pivot_longer(everything(), names_to = "reason", values_to = "val") %>%
	group_by(reason) %>%
	summarise(
		sum = sum(val),
		Total = sprintf("%d (%.1f %%)", sum(val), 100*sum(val)/n())
	) %>%
	arrange(-sum) %>% 
	select(-sum) %>%
	left_join(
		sd %>%
			select(demog_method, starts_with("sharing_reason"), -starts_with("sharing_reason_other")) %>% 
			filter(demog_method != "Other") %>%
			na.omit() %>%
			pivot_longer(-1, names_to = "reason", values_to = "val") %>%
			group_by(demog_method, reason) %>%
			filter(sum(val) != 0) %>%
			summarise(
				stat = sprintf("%d (%.1f %%)", sum(val), 100*sum(val)/n())
			) %>%
			pivot_wider(id_cols = reason, names_from = demog_method, values_from = stat), 
		by="reason"
	) %>%
	mutate(
		reason =str_remove(reason, fixed("sharing_reason_")) %>% 
				str_replace_all(fixed("_"), " ") %>% str_to_sentence()
		) %>%
	rename(Reason = reason)

gt(tab) %>% 
	cols_align("right", -1) %>% 
	sub_missing(missing_text = "") %>%
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Rationales about Sharing (Experimental Evidence)

```{r Tab9bSharingRationales, asis = TRUE}
df <- sd %>% left_join(
	readRDS("../data/generated/verbal_response_coded.rds") %>% 
		select(-exp_reflect),
	by = "id"
) %>% mutate(
	verbal_gave_reasons = !is.na(verbal_n_reasons),
	verbal_mostly_positive = 1*(verbal_positive_reasons > verbal_negative_reasons),
	exp_tment_colab = 1 - exp_tment_control,
	exp_tment_group = 2*exp_tment_colab + exp_tment_private,
	demog_active_res = as.numeric(demog_active_res) - 1,
	demog_trust = (demog_trusting + demog_trustworthy)/2
)

reasons_overall <- df %>%
	filter(verbal_gave_reasons) %>%
	summarise(across(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), sum
	)) %>%
	pivot_longer(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), values_to = "n", names_to = "reason"
	) %>% mutate(
		reason = str_remove(reason, fixed("verbal_")),
		pct_all = n/sum(df$verbal_gave_reasons) 		
	)

reasons_by_tgroup <- df %>%
	filter(verbal_gave_reasons) %>%
	group_by(exp_tment_group) %>%
	summarise(across(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), 
		~ {sum(.x)/n()} 
	)) %>%
	pivot_longer(
		starts_with(c("verbal_pos_", "verbal_neg_", "verbal_dep_")), values_to = "pct", names_to = "reason"
	) %>% pivot_wider(
		names_from = "exp_tment_group", names_prefix = "pct_tg", values_from = "pct"
	) %>%
	mutate(
		reason = str_remove(reason, fixed("verbal_"))
	)

reasons <- reasons_overall %>% left_join(reasons_by_tgroup, by = "reason")

tab <- reasons %>%
	mutate(
		type = str_extract(reason, "pos|neg|dep"),
		reason = paste(
			"...",
			str_remove(reason, "pos_|neg_|dep_") %>% 
				str_replace_all(fixed("_"), " ") %>%
				tolower()
		),
		across(starts_with("pct"), ~ sprintf("%.1f %%", 100 * .x))
	) %>%
	mutate(other = (reason == "... other reasons")) %>%
	arrange(type, other, -n) %>%
	select(type, everything()) %>%
	select(-other)

names(tab) <- c(
	"Rationale", "Reason", "N", 
	"% Total", "% Control/Public", "% Control/Private", 
	"% Collab/Public", "% Collab/Private"
)

tab <- rbind(
	c("I share because it ... ", rep("", 6)),
	tab %>% filter(Rationale == "pos") %>% select(-Rationale),
	c("I do not share because ... ", rep("", 6)),
	tab %>% filter(Rationale == "neg") %>% select(-Rationale),
	c("It depends ... ", rep("", 6)),
	tab %>% filter(Rationale == "dep") %>% select(-Rationale)
)

tab_latex <- gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex()

sub(
	"career concerns related to failed replications or corrections",
	"career concerns related to failed replications", tab_latex
) %>%
	fit_gt_table_to_slide(0.9) %>% center_table()
```

## Rationales for/against Sharing: Some Quotes

```{r}

# Later quotes need checking still - lots of potentially interesting stuff
quotes <-c(11, 16, 18, 66, 67, 72, 80, 82, 84)
# 83, 87, 88, 91, 105, 110
 sd %>%
 	filter(row_number() %in% quotes) %>%
 	transmute(
 		Condition = sprintf(
 			"%s/%s", ifelse(exp_tment_collab, "Collab", "Control"),
 			ifelse(exp_tment_private, "Private", "Public")
 		),
 		Quote = exp_reflect
 	) %>% kable(booktabs = TRUE, linesep = "") %>% 
 	kable_styling(full_width = TRUE, font_size = 7)  %>% 
 	column_spec(1, width = "1.5cm")

```

## Pre-Registration: Awareness Across the Social Sciences

```{r Tab10aPreRegAwareSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "prereg_heard", "demog_discipline", 
	resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Pre-Registration: Take-up over Time Across the Social Sciences

```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
p <- pre_reg_over_time_plot(mr) + theme(legend.position = "right") 
if (trr266_fonts_available) {
	p + theme(text = element_text(family = "Calibri Light", size = 7))
} else p

```

## Pre-Registration: Opinion Across the Social Sciences

```{r Tab10cPreRegTimeSocSciResp, asis = TRUE}
tab <- create_pct_cross_tab_table(
	mr, "prereg_opinion", "demog_discipline", 
	resp_label = get_resp_label("prereg_trust"), df_only = TRUE
) 
gt(tab ) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Pre-Registration: Familiarity by Method

```{r Tab11aPreRegFamiliarity, asis = TRUE}
df <- sd %>% filter(demog_method != "Other")
tab <- create_pct_cross_tab_table(
	df, "prereg_familiar", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Pre-Registration: Usage by Method

```{r Tab11bPreRegUse, asis = TRUE}

tab <- create_pct_cross_tab_table(
	df, "prereg_use", "demog_method", 
	resp_label = c("No (0)", "Yes (1)"), 
	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
) 
# Adjust levels to be zero based.
tab[4,2:6] <- t(sprintf("%.2f", as.numeric(tab[4,2:6]) - 1))
tab[5,2:6] <- t(sprintf("%.2f", as.numeric(tab[5,2:6]) - 1))
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Pre-Registration: Trust Effect by Method

```{r Tab11cPreRegTrust, asis = TRUE}

tab <- create_pct_cross_tab_table(
	df, "prereg_trust", "demog_method", 
	ctests = TRUE, df_only = TRUE
) 
gt(tab) %>% 
	cols_align("right", -1) %>% 
	as_latex() %>%
	fit_gt_table_to_slide()
```

## Summary

We seem to face an **"accounting open science dilemma"**

- We are skeptical about the reproducibility of our work and at the same time
- somewhat behind the curve with regards to research material sharing and pre-registration

## Discussion

What now? We suggest a two-pronged approach

- Take stock of the reproducibility of our work
- Promote incentive-compatible open science approaches

## Taking stock... It might not be as bad as we think!

\begin{center}
\includegraphics[width =0.7\textwidth]{"materials/fisar_et_al_2023_fields.jpeg"} \\
Fišar et al. (2023, Management Science)
\end{center}

## Reproducibility Across Methods

\begin{center}
\includegraphics[width =0.8\textwidth]{"materials/fisar_et_al_2023_methods.jpeg"} \\
Fišar et al. (2023, Management Science)
\end{center}

## Promote Incentive-Compatible Open Science Approaches

- Use flagship projects to show that sharing can boost academic careers
- Demonstrate that scientific programming skills (i) enhance efficiency, (ii) open up avenues for creative research ideas, and (iii) make it easier to share.
- Change the error climate and move from the "policing" to a "collaboration" narrative for open science!

Interesting aspect for further study: Role of open science in theoretical/analytical and qualitative work (e.g., Moravcsik PolSci 2014; Freese et al. SocSciRes 2022)

## Reasons Against Sharing

\begin{center}
\includegraphics[height =0.7\textheight]{"materials/gomes_et_al_2022_sharing_concerns.jpeg"}\\
Gomes et al. (2022, Proceedings of the Royal Society Series B)
\end{center}

### 2024-02-29 code/clean_3s_data.R

@@ -1,0 +1,68 @@
+# ------------------------------------------------------------------------------
+# Reads Social Science Survey data (https://doi.org/10.1038/s41467-023-41111-1)
+#
+# See LICENSE file for license
+# ------------------------------------------------------------------------------
+
+
+suppressMessages(library(tidyverse))
+
+response_overall <- read_csv(
+	"data/external/sss_response_overall.csv", 
+	guess_max = Inf, show_col_types = FALSE
+)
+
+sss_resp <- response_overall %>%
+	select(
+		pid, resp_type = Respondent_type, 
+		discipline = Discipline, field = subfield,
+		year_complete_phd, 
+		career_stage = `Career stage`,
+		method = `Research type`, 
+		sharing_dc_ever = publicly_posting_have_you_ever,
+		sharing_dc_how_many = publicly_posting_approximately_how_many,
+		sharing_dc_first_year = publicly_posting_approximately_when_was,
+		sharing_dc_opinion = publicly_posting_what_is_your_opinion,
+		sharing_dc_share = publicly_posting_what_percentage_discipline,
+		sharing_dc_share_subfield = publicly_posting_what_percentage_subfield,
+		sharing_dc_pref_other_4 = publicly_posting_distribution_of_opinion_discipline_4,
+		sharing_dc_pref_other_5 = publicly_posting_distribution_of_opinion_discipline_5,
+		sharing_dc_pref_other_subfield_4 = publicly_posting_distribution_of_opinion_subfield_4,
+		sharing_dc_pref_other_subfield_5 = publicly_posting_distribution_of_opinion_subfield_5,
+		sharing_dc_attitude = publicly_posting_attitude,
+		sharing_dc_behavior = publicly_posting_behavior,
+		sharing_dc_desc_norm = publicly_posting_descriptive_norm,
+		sharing_dc_presc_norm = publicly_posting_prescriptive_norm,
+		sharing_inst_ever = posting_study_instruments_have_you_ever,
+		sharing_inst_how_many = posting_study_instruments_approximately_how_many,
+		sharing_inst_first_year = posting_study_instruments_approximately_when_was,
+		sharing_inst_opinion = posting_study_instruments_what_is_your_opinion,
+		sharing_inst_attitude = posting_study_instruments_attitude,
+		sharing_inst_behavior = posting_study_instruments_behavior,
[…]

### 2024-02-29 code/create_audit_sample.R

@@ -1,0 +1,22 @@
+suppressMessages(library(tidyverse))
+
+set.seed(42)
+
+N_TO_SAMPLE <- 100
+
+# To create the actual audit sample, you would need to have the 
+# unrestricted authors file, containing their access information.
+# If you feel that you need this file, please contact the 
+# authors.
+
+pop <- read_csv("data/external/invited_authors.csv")
+table(pop$affil_country)
+
+smp <- pop %>%
+	group_by(affil_country) %>%
+	sample_frac(N_TO_SAMPLE/nrow(pop))
+
+smp <- smp[sample(nrow(smp)),]
+table(smp$affil_country)
+
+write_csv(smp, "data/generated/audit_sample.csv")

### 2024-02-29 code/figure_functions.R

@@ -1,0 +1,170 @@
+library(tidyverse)
+library(ggbeeswarm)
+
+# Inspiration for plot below is from 
+# http://rnotr.com/likert/ggplot/barometer/likert-plots/
+
+likert_plot <- function(
+		data, lvar, gvar, title_str = "", 
+		llevels = NULL, glevels = NULL, include_n = TRUE
+	) {
+	df <- data %>%
+		transmute(gvar = .data[[gvar]], lvar = .data[[lvar]]) %>%
+		filter(!is.na(lvar), !is.na(gvar))
+	if (!is.factor(df$lvar)) df$lvar <- factor(df$lvar)
+	if (!is.factor(df$gvar)) df$gvar <- factor(df$gvar)
+	if (!is.null(llevels)) levels(df$lvar) <- llevels
+	if (!is.null(glevels)) levels(df$gvar) <- glevels
+	if (include_n) {
+		ngrp <- as.vector(table(df$gvar))
+		levels(df$gvar) <- sprintf("%s\n(n=%d)", levels(df$gvar), ngrp)
+	}
+	
+	df <- df %>%
+		group_by(gvar) %>%
+		mutate(n = n()) %>%
+		group_by(gvar, lvar) %>%
+		arrange(gvar, lvar) 
+	
+	nl <- length(levels(df$lvar))
+	sl <- ceiling(nl/2)
+	
+	pal <- RColorBrewer::brewer.pal(nl ,"RdBu")
+	pal[sl] <- "#DFDFDF"
+	likert_pal <- pal
+	
+	df_pct <- df %>%
+		summarise(value = unique(n()/n), .groups = "drop") 
+	
+	df_low <- df_pct %>% 
+		filter(lvar %in% levels(lvar)[1:sl]) %>%
+		mutate(value = ifelse(lvar == levels(lvar)[sl], value/2, value))
+	
+	df_high <- df_pct %>% 
+		filter(lvar %in% levels(lvar)[sl:nl]) %>%
+		mutate(value = ifelse(lvar == levels(lvar)[sl], value/2, value))
+	
+	fill_scale <- likert_pal
+	names(fill_scale) <- levels(df$lvar)
+	
+	ggplot() + 
+		geom_bar(
+			data=df_low, aes(x = gvar, y = -value, fill = lvar), 
+			position = "stack", stat = "identity"
+		) +
+		geom_bar(
+			data=df_high, aes(x = gvar, y = value, fill = lvar),  
[…]

### 2024-02-29 code/get_papers_scopus.py

@@ -1,0 +1,23 @@
+# This code is not needed to reproduce the paper but together with
+# the file get_top6_acc_authors.R it shows how we constructed the 
+# population for the Survey from Scopus. In any case,
+# you will need a Scopus license and a Scopus API key to run the code.
+
+from pybliometrics.scopus import ScopusSearch
+import pandas as pd
+
+START_YEAR=2016
+END_YEAR=2021
+journals = pd.read_csv('data/external/top6_acc_journals.csv', dtype=str)
+
+for index, row in journals.iterrows():
+    print(f"Reading {row['journal']} (ISSN {row['issn']})")
+    q = f"ISSN({row['issn']}) AND PUBYEAR > {START_YEAR - 1} AND PUBYEAR < {END_YEAR + 1}"  
+    s = ScopusSearch(q)  
+    pubs = s.results  
+    new_pubs = pd.DataFrame.from_dict(pubs)
+    if index > 0:
+        df_pubs = pd.concat([df_pubs, new_pubs], ignore_index = True, sort = False)
+    else: df_pubs = new_pubs 
+
+df_pubs.to_csv('data/generated/top6_acc_papers.csv', index=False)

### 2024-02-29 code/get_top6_acc_authors.R

@@ -1,0 +1,110 @@
+# This code is not needed to reproduce the paper but together with
+# the file get_papers_scopus.py it shows how we constructed the 
+# population for the Survey from Scopus. The code below that
+# we used to obtain the emails of authors is somewhat undocumented
+# by Scopus so use at your own risk. It currently errors out in 
+# our environment due to a Scopus security check. In any case,
+# you will need a Scopus license and a Scopus API key to run the code.
+
+library(tidyverse)
+library(lubridate)
+library(httr)
+library(jsonlite)
+
+scopus_key = MYKEYHERE
+
+raw_papers <- read_csv(
+	"data/generated/top6_acc_papers.csv", guess_max = Inf,
+	show_col_types = FALSE
+)
+
+issn <- raw_papers %>%
+  group_by(issn, publicationName) %>%
+  mutate(npn = n()) %>%
+  group_by(issn) %>%
+  arrange(-npn) %>%
+  summarise(
+    journal = publicationName[1],
+    npapers = n()
+  )
+
+
+acc_papers <- raw_papers %>%
+  filter(!is.na(author_count)) %>%
+  select(
+    eid, issn, publicationName, coverDate, coverDisplayDate, volume, issueIdentifier, 
+    subtypeDescription, pageRange, openaccess, freetoreadLabel,
+    doi, title, description, authkeywords, citedby_count, fund_no,
+    fund_sponsor, author_count
+  ) %>%
+  arrange(publicationName, volume, issueIdentifier, pageRange)
+
+acc_authors <- raw_papers %>%
+  filter(!is.na(author_count)) %>%
+  # the below fixes data errors in paper 2-s2.0-84866769562 and
+  # paper 2-s2.0-85106699685
+  mutate(
+    author_names = str_remove(author_names, fixed(";rregaard")),
+    author_names = str_replace(
+      author_names,
+      fixed("C&cedil;o&die;teliog&caron;lu, Efe"),
+      "Çötelioğlu, Efe"
+    )
+  ) %>%
+  select(eid, author_ids, author_names, author_afids) %>%
+  separate_rows(author_ids, author_names, author_afids, sep = ";") %>%
+  rename(
+    author_id = author_ids, author_name = author_names, affil_id = author_afids
+  )
+    
+acc_affiliations <- raw_papers %>%
+  filter(!is.na(author_count)) %>%
+  mutate(
[…]

### 2024-02-29 code/merge_3s_data.R

@@ -1,0 +1,79 @@
+# ------------------------------------------------------------------------------
+# Reads Social Science Survey data (https://doi.org/10.1038/s41467-023-41111-1)
+# and creates a merged sample for the overlapping questions
+#
+# See LICENSE file for license
+# ------------------------------------------------------------------------------
+
+
+suppressMessages(library(tidyverse))
+
+sss_resp <- readRDS("data/generated/sss_response.rds")
+resp <- readRDS("data/generated/survey_response.rds")
+
+comp <- resp %>%
+	mutate(
+		survey = "acc",
+		id = id,
+		demog_published = TRUE,
+		demog_discipline = "Accounting",
+		demog_field = as.character(demog_field),
+		demog_method = factor(case_when(
+			demog_method == "Experimental" ~ "Experimental",
+			demog_method == "Archival/Field" |
+				demog_method == "Survey" ~ "Quantitative non-experimental",
+			demog_method == "Theory" |
+				demog_method == "Qualitative" ~ "Qualitative or Theoretical",
+			!is.na(demog_method) ~ "Other"
+		), level = c(
+			"Experimental", "Quantitative non-experimental", 
+			"Qualitative or Theoretical", "Other"
+		)),
+		sharing_heard = sharing_familiar != "Not at all familiar",
+		sharing_important = as.numeric(sharing_important),
+		sharing_use = !sharing_use == "Never",
+		sharing_perc_other_share = sharing_perc_other_share,
+		sharing_perc_other_prefer = sharing_perc_other_prefer,
+		sharing_perc_subfield_prefer = sharing_perc_other_prefer,
+		reprod = as.integer(reprod_acc),
+		prereg_heard = prereg_familiar != "Not at all familiar",
+		prereg_use_first_time = prereg_use_first_time,
+		prereg_opinion = as.numeric(prereg_trust),
+		.keep = "none"
+	)
+		
+comp_sss <- sss_resp %>%
+	mutate(
+		survey = "sss",
+		id = pid,
+		demog_published = career_stage == "Published Author",
+		demog_discipline = as.character(discipline),
+		demog_field = field,
+		demog_method = factor(case_when(
+			method == "Experimental" ~ "Experimental",
+			method == "Quantitative non-experimental" ~ "Quantitative non-experimental",
[…]

### 2024-02-29 code/otree/end/__init__.py

@@ -1,0 +1,31 @@
+from otree.api import *
+
+
+doc = """
+Your app description
+"""
+
+
+class C(BaseConstants):
+    NAME_IN_URL = 'End'
+    PLAYERS_PER_GROUP = None
+    NUM_ROUNDS = 1
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    pass
+
+
+# PAGES
+class Thank(Page):
+    pass
+
+page_sequence = [Thank]

### 2024-02-29 code/otree/epq/__init__.py

@@ -1,0 +1,450 @@
+import itertools
+import json
+import random
+
+from otree.api import *
+
+
+author = 'Victor van Pelt'
+doc = """
+Ex-post Questionnaire
+"""
+
+
+class C(BaseConstants):
+    NAME_IN_URL = 'epq'
+    PLAYERS_PER_GROUP = None
+    NUM_ROUNDS = 1
+    STANDARDCHOICESFIVE = [
+        [1, 'Disagree strongly'],
+        [2, 'Disagree'],
+        [3, 'Neither agree nor disagree'],
+        [4, 'Agree'],
+        [5, 'Agree strongly'],
+    ]
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    # EPQ 1 - Randomization and reflection
+    reflect = models.TextField(
+        label="", blank=False
+    )
+    researcher_feedback = models.TextField(
+        label="TESTING ONLY: Do you have any feedback for us about the study?", blank=True
+    )
+
+    # EPQ 2 - Demographics
+    continent = models.IntegerField(
+        label="On which continent do you live?",
+        blank=False,
+        choices=[
+            [0, 'Asia (including the Middle East)'],
+            [1, 'Australia and Oceania'],
+            [2, 'Africa'],
+            [3, 'Central and South America (including the Caribbean)'],
+            [4, 'Europe'],
+            [5, 'North America'],
+        ],
+    )
+    gender = models.IntegerField(
+        label="Please select your gender.",
+        blank=False,
+        choices=[
+            [1, 'Male'],
+            [2, 'Female'],
+            [3, 'Other'],
+        ],
+    )
+    age = models.IntegerField(
+        label="What is your age?",
+        choices=[
+            [1, 'Under 25 years'],
+            [2, '25 to 35 years'],
+            [3, '35 to 45 years'],
+            [4, '45 to 55 years'],
+            [5, '55 to 65 years'],
+            [6, '65 years or over'],
+        ],
+        blank=False)
+    risk = models.IntegerField(
+        label="Please rate your willingness to take risks in general on a scale from 1 (not at all willing) to 10 (very willing).",
+        choices=[
+            [1, '1 (not at all willing)'],
+            [2, '2'],
+            [3, '3'],
+            [4, '4'],
+            [5, '5'],
+            [6, '6'],
+            [7, '7'],
+            [8, '8'],
[…]

### 2024-02-29 code/otree/epq/tests.py

@@ -1,0 +1,21 @@
+from otree.api import Currency as c, currency_range
+from . import *
+from otree.api import Bot
+
+
+
+class PlayerBot(Bot):
+
+    def play_round(self):
+        yield Introduction
+
+        yield Introduction, dict(accept_info = True)
+        yield Checks, dict(
+            serious=1,
+            lose_interest=1,
+            cared=1,
+            randomization=1,
+            self_select_manager=1,
+            concerned_about_honest=1,
+            attractive_dishonesty=1
+        )

### 2024-02-29 code/otree/instructions/__init__.py

@@ -1,0 +1,88 @@
+import time
+
+from otree.api import *
+
+
+doc = """
+Instructions
+"""
+
+
+class C(BaseConstants):
+    NAME_IN_URL = 'instructions'
+    PLAYERS_PER_GROUP = None
+    NUM_ROUNDS = 1
+
+
+class Subsession(BaseSubsession):
+    pass
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    # drop_out = models.BooleanField(initial=False)
+
+    # Control questions for instructions (removed blank=False)
+    confirm_one = models.IntegerField(initial=0, min=0, max=1, blank=True)
+
+# FUNCTIONS
+# def creating_session(subsession: Subsession):
+#     for p in subsession.get_players():
+#         p.participant.dofus = False
+
+# PAGES
+# class Anonymous(Page):
+#     @staticmethod
+#     def is_displayed(player: Player):
+#         import random
+#
+#         global TAKEN_LABELS  # stored in RAM outside of oTree
+#
+#         try:
+#             if player.participant.label is None:
+#                 # runs if one is not using a room
+#                 return False
+#             if player.participant.label in TAKEN_LABELS:
+#                 # this indicates that player is a duplicate
+#                 player.participant.label = None  # optional: gives even duplicates some privacy
+#                 player.participant.dofus = True
+#                 return False
+#         except NameError:
+#             # runs if this is the first subject
+#             TAKEN_LABELS = list()
+#
+#         TAKEN_LABELS.append(player.participant.label)  # mark subject as having participated
+#         random.shuffle(TAKEN_LABELS)  # improves anonymity even if this variable were read
+#
+#         player.participant.label = None  # overwrite label
+#
+#         return False
+#
+# class Cleaning(Page):
+#     @staticmethod
+#     def is_displayed(player: Player):
+#         return (
+#                 player.participant.dofus == True
+#         )
+#
+#     @staticmethod
+#     def app_after_this_page(player: Player, upcoming_apps):
+#             return upcoming_apps[-1]
+
+class Welcome(Page):
+    form_model = 'player'
+    form_fields = ['confirm_one']
+
+class Instruct_one(Page):
+    # form_model = 'player'
+    # form_fields = ['confirm_one']
+    pass
+
+page_sequence = [
+    # Anonymous,
+    # Cleaning,
+    Welcome,
+    Instruct_one,
+]

### 2024-02-29 code/otree/science_study/__init__.py

@@ -1,0 +1,130 @@
+from otree.api import *
+import itertools
+
+doc = """
+Your app description
+"""
+
+
+class C(BaseConstants):
+    NAME_IN_URL = 'science_study'
+    PLAYERS_PER_GROUP = None
+    NUM_ROUNDS = 1
+
+
+class Subsession(BaseSubsession):
+    pass
+
+
+class Group(BaseGroup):
+    pass
+
+
+class Player(BasePlayer):
+    # control_treatment = models.IntegerField(initial=None, min=0, max=1)
+    # private_treatment = models.IntegerField(initial=None, min=0, max=1)
+    # journal_treatment = models.IntegerField(initial=None, min=0, max=1)
+    share = models.IntegerField(initial=None, blank=False, max=100, min=0)
+    check_share = models.IntegerField(initial=None, blank=True)
+
+# FUNCTIONS
+def creating_session(subsession: Subsession):
+    randomdraw = itertools.cycle([1, 2, 3, 4, 5, 6])
+    randomdrawp = itertools.cycle([1, 2, 3, 4])
+    c_random = itertools.cycle([0, 1])
+    p_random = itertools.cycle([0, 1])
+    j_random = itertools.cycle([0, 1])
+
+    #assign treatment based on config OR balanced randomization
+    for p in subsession.get_players():
+        if subsession.session.config['full_random'] == 0:
+            # Assign control
+            if subsession.session.config['control'] == 1:
+                p.participant.control_treatment = 1
+            elif subsession.session.config['control'] == 0:
+                p.participant.control_treatment = 0
+            elif subsession.session.config['control'] is None:
+                p.participant.control_treatment = next(c_random)
+
+            # Assign private
+            if subsession.session.config['private'] == 1:
+                p.participant.private_treatment = 1
+            elif subsession.session.config['private'] == 0:
+                p.participant.private_treatment = 0
+            elif subsession.session.config['private'] is None:
+                p.participant.private_treatment = next(p_random)
+
+            # Assign journal
+            if subsession.session.config['journal'] == 1:
+                p.participant.journal_treatment = 1
+            elif subsession.session.config['journal'] == 0:
+                p.participant.journal_treatment = 0
+            elif subsession.session.config['journal'] is None:
+                p.participant.journal_treatment = next(j_random)
+        elif subsession.session.config['full_random'] == 1:
+            treat = next(randomdraw)
+            if treat == 1:
+                p.participant.control_treatment = 1
[…]

### 2024-02-29 code/otree/settings.py

@@ -1,0 +1,133 @@
+from os import environ
+
+ROOMS = [
+    dict(
+        name='pre_test',
+        display_name='Pre-test',
+        participant_label_file='_rooms/pre_test.txt',
+        use_secure_urls=False
+    ),
+    dict(
+        name='science_study',
+        display_name='Science Study',
+        participant_label_file='_rooms/science_study.txt',
+        use_secure_urls=False
+    ),
+]
+
+SESSION_CONFIGS = [
+    {
+        'name': 'science_study_main_test',
+        'app_sequence': ['instructions', 'science_study', 'epq', 'end'],
+        'num_demo_participants': 20,
+        'display_name': "Science Study - Main test",
+        'control': None,
+        'private': None,
+        'journal': 0,
+        'full_random': 0.5
+    },
+    {
+        'name': 'science_study_random',
+        'app_sequence': ['instructions', 'science_study', 'epq'],
+        'num_demo_participants': 6,
+        'display_name': "Science Study - Random Treatment",
+        'control': None,
+        'private': None,
+        'journal': None,
+        'full_random': 1
+    },
+    {
+        'name': 'science_study_ctrl_private',
+        'app_sequence': ['instructions', 'science_study', 'epq'],
+        'num_demo_participants': 4,
+        'display_name': "Science Study - Control and Private",
+        'control': 1,
+        'private': 1,
+        'journal': 0,
+        'full_random': 0
+    },
+    {
+        'name': 'science_study_ctrl_public',
+        'app_sequence': ['instructions', 'science_study', 'epq'],
+        'num_demo_participants': 4,
+        'display_name': "Science Study - Control and Public",
+        'control': 1,
+        'private': 0,
+        'journal': 0,
+        'full_random': 0
+    },
+    {
+        'name': 'science_study_collab_private',
+        'app_sequence': ['instructions', 'science_study', 'epq'],
+        'num_demo_participants': 4,
+        'display_name': "Science Study - Collab and Private",
+        'control': 0,
+        'private': 1,
+        'journal': 0,
+        'full_random': 0
+    },
+    {
+        'name': 'science_study_collab_public',
+        'app_sequence': ['instructions', 'science_study', 'epq'],
+        'num_demo_participants': 4,
[…]

### 2024-02-29 code/recode_survey_response.R

@@ -1,0 +1,33 @@
+# ------------------------------------------------------------------------------
+# Reads oTree data and codes variable based on data contained in
+# data/external/variables.csv
+#
+# See LICENSE file for license
+# ------------------------------------------------------------------------------
+
+suppressMessages(library(tidyverse))
+
+raw_df <- read_csv(
+	"data/external/otree_output_wide_2022-12-14.csv", show_col_types = FALSE
+)
+vars <- read_csv("data/external/variables.csv", show_col_types = FALSE)
+
+df <- raw_df %>% select(any_of(vars$otree_var)) %>% 
+	filter(!is.na(participant.share)) 
+
+names(df) <- vars$var[match(names(df), vars$otree_var)]
+
+recode_var <- function(x) {
+	if (!any(is.na(vars$resp_no[vars$var == names(df[x])]))) {
+		ret_val <- factor(
+			pull(df[x]), 
+			labels = vars$resp_label[vars$var == names(df[x])]
+		)
+	} else ret_val <- pull(df[x])
+	ret_val
+}
+
+recoded_df <- as.data.frame(lapply(seq_along(df), recode_var))
+names(recoded_df) <- names(df)
+
+saveRDS(recoded_df, "data/generated/survey_response.rds")

### 2024-02-29 code/recode_verbal_response.R

@@ -1,0 +1,29 @@
+# ------------------------------------------------------------------------------
+# Reads coded verbal response data and calculates some simple summary measures.
+# Stores resulting data frame in `data/generated`. 
+#
+# See LICENSE file for license
+# ------------------------------------------------------------------------------
+
+suppressMessages(library(tidyverse))
+
+vc <- read_csv(
+	"data/external/verbal_responses_coded.csv", show_col_types = FALSE
+) %>%
+	select(-exp_pct_share)
+
+df_vc <- vc %>%
+  mutate(
+    positive_reasons = rowSums(across(starts_with("pos_"))),
+    negative_reasons = rowSums(across(starts_with("neg_"))),
+    neutral_reasons = rowSums(across(starts_with("dep_"))),
+    n_reasons = positive_reasons + negative_reasons + 
+    	neutral_reasons,
+    share_positive = positive_reasons/n_reasons,
+    share_negative = negative_reasons/n_reasons,
+    share_neutral = neutral_reasons/n_reasons
+  ) %>%
+  filter(n_reasons > 0)
+
+names(df_vc)[3:ncol(df_vc)] <- paste0("verbal_", names(df_vc)[3:ncol(df_vc)])
+saveRDS(df_vc, "data/generated/verbal_response_coded.rds")

### 2024-02-29 code/table_functions.R

@@ -1,0 +1,557 @@
+# ------------------------------------------------------------------------------
+# Functions to create tables on the survey data.
+# Example use cases are at the end of file.
+#
+# See LICENSE file for license
+# ------------------------------------------------------------------------------
+
+library(tidyverse)
+library(kableExtra)
+library(xml2)
+library(countrycode)
+
+GROUPS <- c(
+	"region", "age", "gender", "active_res", "tenured", "fars", "archival", 
+	"qualitative", "risk", "trust", "tment_ctrl", "tment_prvt"
+)
+
+myfmt <- function(x, ndigits = 3) format(round(x, ndigits), nsmall = ndigits)
+
+get_resp_label <- function(v) {
+	# relies on vars being present in environment
+	vars %>% filter(var == v) %>% pull(resp_label)
+}
+
+remove_quarto_formatting <- function(k) {
+	k_xml <- kable_as_xml(k)
+	xml_set_attr(k_xml, "data-quarto-disable-processing", "true")
+	xml_as_kable(k_xml) 
+}
+
+starme <- function(v) {
+	ifelse(v < 0.01, '***', ifelse(v < 0.05, '**', ifelse(v < 0.1, '*', '')))
+}
+
+create_split <- function(df, group) {
+	if (!group %in% GROUPS) stop(
+		sprintf(
+			"Invalid group string. Valid strings are %s",
+			paste0("'", paste0(GROUPS, collapse = "', '"), "'")
+		)
+	)
+	case_when(
+		group == "region" ~ 
+			df %>% mutate(split_var = demog_region == "North America"),
+		group == "age" ~
+			df %>% mutate(split_var = as.numeric(demog_age) > 3),
+		group == "gender" ~
+			df %>% mutate(split_var = demog_gender == "Male"),
+		group == "active_res" ~
+			df %>% mutate(split_var = demog_active_res == "Yes"),
+		group == "tenured" ~
+			df %>% mutate(split_var = demog_job_cat == "Tenured faculty"),
+		group == "fars" ~
[…]

### 2024-02-29 docs/paper.qmd
Switched to retracted data version

@@
 vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
-pop <- read_csv("../data/external/invited_authors.csv", show_col_types = FALSE)
+pop <- read_csv("../data/external/invited_authors_retracted.csv", show_col_types = FALSE)
 ```

### 2024-04-17 docs/paper.qmd
Added observational data analyses

--- 2024-02-29 docs/paper.qmd
@@
   | Accountants' Attitudes Towards Open Science^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management.
-We thank the audience of a workshop at Humboldt University for providing helpful feedback.
-Excellent research assistance by Benedikt Hahn is gratefully acknowledged.
+We thank Kris Hardies and  audiences of workshops at University of Antwerp and Humboldt University Berlin for providing helpful feedback.
+Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged.
 This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
@@
 vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
-pop <- read_csv("../data/external/invited_authors.csv", show_col_types = FALSE)
+pop <- read_csv("../data/external/invited_authors_anon.csv", show_col_types = FALSE)
+
+authors <- read_csv("../data/external/obs_data_authors_anon.csv", show_col_types = FALSE)
+papers <- read_csv("../data/external/obs_data_papers_anon.csv", show_col_types = FALSE)
+
+source("../code/obs_data_analyses.R")
 ```
@@
 Surveying a sample of scholars that have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs.
-Also, we are less familiar with public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research.
-Our respondents state that they are open to sharing and would be likely to share research materials under a hypothetical scenario, regardless of the experimental framing.
+Also, we are less familiar with the public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research.
+Our respondents state that they are open to sharing and would likely share research materials under a hypothetical scenario, regardless of provided rationale and scope.
 They also believe that other accounting researchers, as well as editors, are in favor of research material sharing.
@@
 Cumulative science builds on reproducible research.[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated open science methods like public sharing of research materials and the pre-registration of study plans as potential strategies to improve the reproducibility of our work.
-Prior work across the social sciences [@FLCPSWMBP_2023] has documented an overall uptake of open sciences approaches across several disciplines.
+Prior work across the social sciences has documented an overall uptake of open sciences approaches across several disciplines [@FLCPSWMBP_2023].
 We contrast these findings with a survey that we conducted among accounting researchers to explore the perceptions and attitudes toward open science in our field.
@@
 For a more in-depth discussion of the related terminological debate, see @GFI_2016.
-The key reason why we do not provide an exact definition in the survey is that the differences between reproducibility and replicability are subtle and vary across accounting subfields: For archival studies, reproducibility and replicability should be essentially the same, while for experimental studies they clearly differ.
+The key reason why we do not provide an exact definition in the survey is that the differences between reproducibility and replicability are subtle and vary across accounting subfields.
+For archival studies, reproducibility and replicability should be essentially the same, while for experimental studies they clearly differ.
 
@@
 Compared to the fields of economics and sociology, for example, we are about half a point more skeptical about the reproducibility of the influential work in our field on a 5-point Likert scale.
-This is a sizable difference.
-
-Exploring this assessment across our respondents' demographics, we find it to be relatively stable.
+Exploring this assessment across our respondents' demographics, we find this skepticism to be relatively stable.
 Analytical and qualitative researchers are somewhat more pessimistic than the other methodologies.
@@
 
-Given this finding, one would expect accounting researchers to take a proactive stand and embrace two prominent open science approaches that methodological work has identified to increase the reproducibility of research: the public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.
-
-Turning first to the public sharing of research materials, we document that, again compared with researchers from other social science areas, we accounting researchers are somewhat less familiar with this activity.
+Given this finding, one would expect accounting researchers to take a more proactive stance and embrace two prominent open science approaches that methodological work has identified to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.
+Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, we accounting researchers are somewhat less familiar with this activity.
 Also, we find it somewhat less important.
-Familiarity is generally largest for respondents using archival, field, and experimental methods and smallest for respondents using qualitative methods, which also perceive sharing to be less important.
+Familiarity is generally largest for respondents using archival, field, and experimental methods and smallest for respondents using qualitative methods, which also perceive sharing as less important.
 
 Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in our perceived (prescriptive) importance of research material sharing, our stated willingness to share research materials, and our (descriptive) perception about actual sharing behavior.
-In a hypothetical scenario, the average stated likelihood for sharing research materials by our respondents is relatively high (i.e., 72%), and this likelihood is more or less unaffected by the randomized nature of the rationale (i.e., collaboration or control) and the sharing scope (public or private).[^2] Also, 50% of our respondents state that they at least sometimes publicly share their research materials.
-In addition, we think that about 44% of us favor publicly sharing research materials, and we assess 61% of the top-six accounting editors to be in favor of publicly sharing research materials.
+In a hypothetical scenario, the average stated likelihood for sharing research materials by our respondents is relatively high (i.e., 72%), and this likelihood is more or less unaffected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope (public versus private sharing).[^2] Also, 50% of our respondents state that they, at least sometimes, publicly share their research materials.
+In addition, our respondents believe that about 44% of us favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials.
 
@@
 All this sounds comforting and consistent with a general supportive stand of the accounting community towards public research material sharing.
-However, when questioned about the actual percentage of us sharing research materials publicly, the number comes down to a much more sobering 28%.
-This number and the prescriptive/descriptive gap that it reveals differ significantly across methods: Analytical researchers have the narrowest gap (43% of researchers expected to be in favor and 38% expected to actually share) and archival researchers the widest (45% versus 24%).
+However, when asked about respondents' perceptions about actual sharing behavior, the percentage comes down to a much more sobering 28%.
+This sober number and the gap it reveals differ significantly across the different accounting methodological areas.
+Analytical researchers have the narrowest gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials).
+Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share).
 The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).
 
+Using observational data from a country-stratified random sample of `r nrow(authors)` authors from our target population to contrast these perceptions with actual behavior, we find at least some evidence for research material sharing for 39 % of this random sample.
+This number is largely in line with the self-reported figures but masks that research material sharing in accounting seems to be largely an occasional compliance activity: Only for 7.5 % of the papers that we analyze we find evidence for research material sharing and when we exclude Journal of Accounting Research and Management Science, two journals with data and code policies in place, the share of authors for which we document research material sharing evidence drops from 39 to 23 %.
+
 In light of these numbers, it is a logical next step to explore the main reasons against sharing research materials.
-Overall, the most commonly stated reasons are the proprietary nature of used data (56% of respondents give this reason), the time that it takes to make materials available (30%) and the fear of being scooped when materials become publicly available (23%).
-Also, 34% of respondents state there is no need for sharing as their data are already publicly available.
+Overall, the most commonly stated reasons for not sharing research materials are the proprietary nature of the used data (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%).
+Additionally, 34% of respondents state that there is no need for sharing as their data is already publicly available.
 Unsurprisingly, the reasons clearly differ across methods.
-For qualitative researchers, deidentification problems are very prominent (46%) and analytical researchers consider the time that it takes to make materials available far less of a reason than researchers using the other methods (i.e., 9.5% versus 30% overall).
-
-Turning to pre-registration, it seems that we accounting researchers are at least as familiar with the concept as other social science researchers.
-However, we started using it later (roughly 2 years) and use it less frequently (17% versus 27%).
-Our trust in pre-registered work is generally comparable with other social scientists but significantly lower than trust levels of researchers in Psychology (the field that reports the highest usage rates of pre-registration).
-A detailed look into differences among the different methodological fields within accounting also reflects this as we find that experimental researchers use pre-registration most (28%) and express the strongest belief that the practice increases the trustworthiness of research.
-
-Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both, the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it.
+For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).
+
+Regarding pre-registration, it seems that we accounting researchers are at least as familiar with the concept as other social science researchers.
+However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%).
+Our trust in pre-registered work is generally comparable with other social scientists but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rates of pre-registration).
+A detailed look into differences among the different methodological fields within accounting also reflects this, as we find that experimental researchers use pre-registration the most (28%) and express the strongest belief that the practice increases the trustworthiness of research.
+
+Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it.
 This results in these tools currently being less established in the accounting domain than in other fields.
 In addition, the challenges that hinder reproducibility and the potential effectiveness of open science tools vary across methodological paradigms.
-Qualitative research faces different challenges than archival quantitative work, and its differ again from experimental studies.
+Qualitative research faces different challenges than archival quantitative work, and they both differ again from experimental studies.
 We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.
@@
 We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community.
-Yet, we believe that, taken together, these journals provide us with a somewhat representative list of publishing accounting academics.
-We started compiling the list of authors from 2016 onward because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017].
-After receiving approval from an ethical review board, also guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total three reminders.
+Yet, we believe that, taken together, these journals provide us with a representative list of publishing accounting academics.
+We started compiling the list of authors from 2016 because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017].
+After receiving approval from an ethical review board, also guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total of three reminders.
 We allowed potential respondents to opt out of future emails every time we reached out to them.
@@
 Table 1 displays our sample selection procedures.
-Of the 2,660 potential respondents we approached, we excluded 118 for various reasons.[^3] Furthermore, for 206 emails bounced, we received a notification that the email address was unreachable.
+Of the 2,660 potential respondents we identified, we excluded 118 for various reasons.[^3] Furthermore, for 206 emails bounced, we received a notification that the email address was unreachable.
 Of the remaining 2,336 successfully reached accounting researchers, 391 started the study (15,4% of the total emails sent), 254 partially completed the study (10,9% of the total emails sent), and 222 fully completed the study (8,7% of the total emails sent).[^4] Table 2 displays our final sample's demographics and characteristics.
-Panel A reveals that the majority of the respondents is male, 35 years or older (87.8%), specializes in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).
-
-[^3]: 41 authors were removed because we found no email address, 41 authors were removed because they appeared in the data twice with two author IDs but were the same person, 28 authors were removed because they were a current member of one of our affiliated universities or academic research centers, 5 authors were removed because they gave us advice for this study, 2 authors were removed because they had passed away, and 1 author was removed due to an incorrect email address.
-
-[^4]: As the dependent variable of our hypothetical scenario analysis outlined below is the first data that we collect, 254 is the sample size for this analysis.
+Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specialize in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).
+
+\centerline{--- Insert Table 2 about here ---}
+
+[^3]: We removed 41 authors because we found no email address, 41 authors because they appeared in the data twice with two author IDs but were the same person, 28 authors because they were a current member of one of our affiliated universities or academic research centers, 5 authors because they gave us advice for this study, 2 authors because they had passed away, and 1 author due to an incorrect email address.
+
+[^4]: As the dependent variable of our hypothetical scenario analysis outlined below is the first data we collect, 254 is the sample size for this analysis.
 For the descriptive analyses, we settle for the number of participants that answered the respective question and, if applicable, also provided the necessary demographics for cross-sectional splits.
-Depending on this, the sample sizes vary from 222 to 229 responses.
-\centerline{--- Insert Table 2 about here ---}
+Depending on this, the sample sizes for the descriptive analyses vary from 222 to 229 responses.
 
 Panel B of Table 2 contrasts our respondent sample with our sampling population.
-Given the anonymity of our response and the data that we are able to collect about our population we are only able to compare the geographic dispersion of our sample.
-Panel B reveals that, in particular, researchers from Europe are over-represented and researchers from Asia are under-represented in the sample.
-Given that response rate assessment is inherently hard, we generally abstain from speculating about potential reasons for this sampling imbalance.
-However, it seems likely that the all-European author team of the study might have had an influence.
-While we control for geographical effects in our response (not-tabulated) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia that happen to have a very low response rate.
+Given the anonymity of our response and the data that we can collect about our population, we can only compare the geographic dispersion of our sample.
+Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample.
+Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance.
+However, it seems likely that the study's all-European author team might have positively influenced the European response.
+While we control for geographical effects in our response (not-tabulated) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.
 
@@
 To ensure that our findings are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], which has been recently published in Nature Communications.
-Very similar to our survey, this study solicits the view by published researchers and PhD students on reproducibilty, research material sharing, and pre-registration.
-Given that it differs in survey detail (app.
-45 minutes while our survey was designed to be completed in less than 10 minutes), and data collection procedure (confidential with compensation element while we use an anonymous survey with very mild incentivization), we had to make some adjustments.
-However, the ordering and phrasing of questions in our survey are similar and their content and answer scales are identical or differ in a negligible way.
-Specifically, we decided to alter the framing and expand some of the questions to make it easier for accounting researchers to understand the questions and connect them to their common research practices.
+Similar to our survey, this study solicits the views of published researchers and PhD students on reproducibility, research material sharing, and pre-registration.
+Given that it differs in depth (approximately 45 minutes while our survey was designed to be completed in less than 10 minutes) and data collection procedure (confidential with compensation element while we use an anonymous survey with mild incentivization), we had to make some adjustments.
+However, the ordering and phrasing of questions in our survey are similar, and their content and answer scales are identical or differ in a negligible way.
+Specifically, we decided to alter the framing and expand some of the questions to make it easier for accounting researchers to understand the questions and connect them to their commonly accepted research practices.
 We also pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions.
 
-The first stage of the survey included questions about respondents' views on publicly sharing research materials, which we described as comprising of data, code, and research procedures.
-Specifically, we asked respondents about their familiarity with public sharing of research materials and their views of its importance.
+The first stage of the survey included questions about respondents' views on publicly sharing research materials, which we described as comprising data, code, and research procedures.
+Specifically, we asked respondents about their familiarity with the public sharing of research materials and their views of their importance.
 We also asked them about their perceptions of the prevalence of sharing in the accounting research community, how often they tended to share, and whether they planned to share in the future.
@@
 Subsequently, we asked respondents about their familiarity and experience with the practice of pre-registration.
-Lastly, we asked them about their perceptions of trustworthiness of pre-registered research compared to non-pre-registered research.
-We completed the survey with asking a few demographic questions that are mostly presented in Table 2.
+Lastly, we asked them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research.
+We completed the survey by asking a few demographic questions that are primarily presented in Table 2.
 For a complete overview of the survey questions included in our study, please see Appendix A.
@@
 The first goal of the survey was to gauge the perceptions of accounting researchers regarding the reproducibility of influential findings in the accounting literature.
-Table 3 displays a detailed overview of our respondents' answers to the question "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicating" to "reproducing" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community.
+Table 3 displays a detailed overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicating" to "reproducing" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community.
 Namely, the term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000].
 In contrast, the term"replication" may or may not have different interpretations for different researchers.
-For instance, experimental researchers it refers to distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).
+For instance, experimental researchers it refers to a distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).
 
@@
 That is, Accounting has about 39.3% non-skeptics, while Economics has 61.1%, Political Science has 45.8%, Psychology has 41.3%, and Sociology has 61.7%.
-The differences with Economics and Sociology again are the largest, while the differences with Political Science and Psychology are smaller.
+The differences with Economics and Sociology again are the largest, while the differences between Political Science and Psychology are smaller.
 
 Next, we compare assessments of accounting researchers regarding reproducibility across different methodologies.
-Accounting is not only a diverse discipline in terms of orientation and topic, but also in terms of the methodologies its researchers employ.
+Accounting is not only a diverse discipline in terms of orientation and topic but also in terms of the methodologies its researchers employ.
 We distinguish among five categories: Analytical, Archival/Field, Experimental, Qualitative, and Survey.
@@
 
-The findings in Table 4 Panel A suggest that analytical and qualitative researchers are more pessimistic and skeptical about the reproducibility of influential findings in accounting as whole than accounting researchers using other methodologies.
+The findings in Table 4 Panel A suggest that analytical and qualitative researchers are more pessimistic and skeptical about the reproducibility of influential findings in accounting as a whole than accounting researchers using other methodologies.
 In particular, analytical researchers are significantly less confident about the reproducibility of influential findings in accounting in general than researchers in the Archival/Field and Experimental categories (two-tailed p-value \< 0.100).
 When turning to respondents' assessments of the reproducibility of influential findings in their own methodological area, we find that analytical researchers have the most confidence in the influential findings within their methodological area as their average confidence is statistically higher from those reported by the average reported for the other four methodologies (two-tailed p-value \< 0.100).
-Qualitative research reports a significantly lower average confidence than Analytical, Archival/Field, and Experimental research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).
+Qualitative research reports a significantly lower average confidence than Analytical, Archival/Field, and Experimental Research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).
 
@@
 A higher (lower) assessment gap indicates that respondents are more (less) confident in the reproducibility of influential findings in their methodological area compared to accounting in general.
-The findings of Panel C report that analytical researchers report the largest assessment gap, implying they are relatively skeptical about reproducibility of influential findings in accounting as a whole compared to their own methodology.
+The findings of Panel C report that analytical researchers report the largest assessment gap, implying they are relatively skeptical about the reproducibility of influential findings in accounting as a whole compared to their own methodology.
 The average assessment gap reported for the Analytical category is also statistically different from the averages reported in the other four categories (two-tailed p-value \< 0.100).
-The other four categories exhibit no clear assessment gap (with averages hovering around zero) and are statistically indistinguishable form each other.
+The other four categories exhibit no clear assessment gap (with averages hovering around zero) and are statistically indistinguishable from each other.
 
@@
 Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field and with some variation across methodologies.
-Given the skepticism,we have observed so far, one would expect accounting researchers to take a more proactive stance on open science approaches, like the practice of research materials sharing.
+Given the skepticism, we have observed so far, one would expect accounting researchers to take a more proactive stance on open science approaches, like the practice of research materials sharing.
 The survey assessed respondents' evaluations of the practice of research materials sharing next.
@@
 Figure 2 reproduces the data reported in Table 5 Panel B by presenting the frequencies along horizontal axes and centering them to a neutral midpoint.
-It reveals that, compared to the social science disciplines, relatively less respondents in our sample are strong supporters of the practice of research material sharing.
-That is, our of the total sample, 39.6% of the respondents consider it "very important" (Accounting) versus 51.7% in Economics, 48.1% in Political Science, and 43.8% in Psychology.
+It reveals that, compared to the social science disciplines, relatively fewer respondents in our sample are strong supporters of the practice of research material sharing.
+That is, of the total sample, 39.6% of the respondents consider it "very important" (Accounting) versus 51.7% in Economics, 48.1% in Political Science, and 43.8% in Psychology.
 Only Sociologists report a lower percentage of strong supporters (i.e., 29.4%) than the accounting researchers in our sample.
@@
 Next, we examine familiarity with and perceived importance of research materials sharing across methodologies within accounting.
-We again distinguish among five methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
+We again distinguish between five methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
 Table 6 displays assessments of the practice of research material sharing using two panels.
@@
 Moreover, we also find that respondents using Qualitative methods are less familiar with research material sharing compared to all four other categories (two-tailed p-value \< 0.100).
-Panel B shows that there are few significant differences in terms of assessed importance of research material sharing across the methodologies.
-Only respondents in the Archival/Field category assess research material sharing as significantly more important than respondents using the Qualitative and Survey category.
+Panel B shows that there are few significant differences in terms of the assessed importance of research material sharing across the methodologies.
+Only respondents in the Archival/Field category assess research material sharing as significantly more important than respondents using the Qualitative and Survey categories.
 
@@
 We manipulated two between-subjects factors in the hypothetical scenario.
-First, we manipulated the rationale used by the fellow researcher requesting access to the researcher materials.
+First, we manipulated the rationale used by the fellow researcher requesting access to the researcher's materials.
 In the *collaboration rationale* treatment, the fellow researcher requested access to researcher materials to understand the work better and build on it.
@@
 Respondents were randomly assigned to receive only one stated rationale (*control* *rationale* versus *collaboration rationale*) and one sharing scope (*public* versus *private scope*).
-We measured respondents' willingness to comply with the fellow researcher's request on a scale, ranging from 0% (definitely not) to 100% (definitely).
+We measured respondents' willingness to comply with the fellow researcher's request on a scale ranging from 0% (definitely not) to 100% (definitely).
 The hypothetical scenario was, like the survey, designed using oTree [@CSW_2016].
@@
 The scenario included a description that they just conducted a study and published it in an academic journal.
-Respondents were also told that a fellow researcher contacted them for access of their research materials, which we specified as 'data, code, and research procedures'.
+Respondents were also told that a fellow researcher contacted them for access to their research materials, which we specified as 'data, code, and research procedures'.
 Next, we provided four pieces of information about the request made by the fellow researcher.
@@
 
-### Sharing Research Materials - Prescriptive versus Descriptive Views and Rationales
+### Sharing Research Materials - Prescriptive versus Descriptive Views
 
@@
 Next, our survey focuses on the perceived prescriptive and descriptive importance of research material sharing.
-Table 8 Panel A reports data on respondents' answers to the question "How often do you publicly share research materials (i.e., data, code, and research procedures)?" It also splits the data into main methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
+Table 8 Panel A reports data on respondents' answers to the question, "How often do you publicly share research materials (i.e., data, code, and research procedures)?" It also splits the data into main methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
 The results in Panel A reveal that 50% of the respondents state that they at least sometimes publicly share their research materials.
@@
 Namely, these three questions ask (1) what percentage of accounting researchers in general favor research material sharing, (2) what percentage of editors of the top six accounting journals believe it increases the value of a manuscript, and (3) what percentage of accounting researchers publicly share research materials.
-The data in Panel B reveal that respondents believe about 44% of accounting researchers favor publicly sharing research materials, they believe 60.8% of the top-six accounting editors to be in favor of publicly sharing research materials, and they believe 27.6% of accounting researchers actually share research materials.
+The data in Panel B reveal that respondents believe about 44% of accounting researchers favor publicly sharing research materials, they believe 60.8% of the top-six accounting editors are in favor of publicly sharing research materials, and they believe 27.6% of accounting researchers actually share research materials.
 
@@
 To understand the differences between these three questions, Figure 3 displays box plots, one for each question and separately for each methodology.
-First, examining the three box plots for the sample as a whole, the visual pattern emerges that the perceptions of actual sharing behavior among accounting researchers lags behind perceptions of whether accounting researchers favor sharing, which, in turn, lags behind perceptions of whether editors value sharing.
+First, examining the three box plots for the sample as a whole, the visual pattern emerges that the perceptions of actual sharing behavior among accounting researchers lag behind perceptions of whether accounting researchers favor sharing, which, in turn, lags behind perceptions of whether editors value sharing.
 This pattern seems starker for respondents in the Archival/Field category.
-In this category, the box plot for the perceptions of actual sharing does not to overlap with the other two, i.e., the box plots for the perceptions of accounting researchers favoring sharing and the perceptions of whether editors value sharing.
-These findings suggest a contrast in the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior.
+In this category, the box plot for the perceptions of actual sharing does not overlap with the other two, i.e., the box plots for the perceptions of accounting researchers favoring sharing and the perceptions of whether editors value sharing.
+These findings suggest a contrast between the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior.
+
+### Sharing Research Materials - Observational Data
+
+To contrast the perception of our our survey participants with actual research material sharing behavior, we collect observational data on research material sharing for a random country-stratified sample of `r nrow(authors)` authors from our target population.
+To assess whether these authors share research materials, we systematically search their homepages for evidence and also assess whether they have GitHub, Open Science Foundation, Dataverse, or Zenodo accounts linked to their name.
+If they do, we verify whether they share research materials over these channels.
+In addition, we use Scopus to identify all studies that these authors published since 2016 and verify whether these publications' DOI URLs reference research material sharing.[^7]
+
+[^7]: The data collection manual for this process is available in this project's GitHub repository.
+
+\centerline{--- Insert Table 9 about here ---}
+
+Table 9 reports our findings based on this sample of `r nrow(authors)` authors and their `r nrow(papers)` papers.
+Panel A summarizes the data by author.
+We find that `r sum(by_author$has_made_resmat_available)` % of our authors share research materials.
+This number and its according binomial confidence interval is overall consistent with the perceptions voiced in the survey.
+
+\centerline{--- Insert Figure 4 about here ---}
+
+However, as becomes also apparent from Panel B, our authors only share research materials occasionally.
+Only 7.5 % of the paper DOI URLs reference research material sharing.
+As Figure 4 indicates, this share is mildly increasing over time but even in recent years, the sharing percentage seems relatively modest.
+
+The journal breakdown in Panel B provides clear evidence that the data and code policies established by the Journal of Accounting Research and Management Science affect the tendency of research material sharing.
+This also becomes apparent from Panel A.
+If one omits research material sharing via these journals, the share of sharing accounting researchers drops from 39 % to 23 %.[^8]
+
+[^8]: Untabulated analyses based on small frequencies provide suggestive evidence that, overall, the sharing frequencies are higher for general economics journals than for journals in the areas of accounting and finance.
+
+Overall, our observational data supports the survey findings.
+It seems that research material sharing takes place only occasionally in accounting and in many instances only if required by the publishing journal.
+In the next section, we will return to our survey data to explore stated rationales for or against research material sharing.
 
@@
 
-\centerline{--- Insert Table 9 about here ---}
-
-Table 9 Panel A displays the frequencies and percentages for each reason featured and provided in our survey.
+\centerline{--- Insert Table 10 about here ---}
+
+Table 10 Panel A displays the frequencies and percentages for each reason featured and provided in our survey.
 Aside from reporting the total frequencies for the entire sample, it also (again) splits them up into the five methodological fields (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
 The most commonly stated reason that respondents gave for not sharing research materials is that the data are proprietary.
-56.3% of all respondents give this reason and it also ranks first for all methodological areas.
+56.3% of all respondents give this reason, ranking first for all methodological areas.
 This is somewhat surprising because not all methodological areas regularly deal with proprietary data.
-In a shared second place, are three more prominent reasons respondents provided, namely, (1) the time that it takes to make materials available (29.9% of all respondents), (2) the fear of being scooped when materials become publicly available (23.2% of all respondents), and (3) no need for sharing as their data are already publicly available (33.9% of all respondents).
+In a shared second place are three more prominent reasons respondents provided, namely, (1) the time that it takes to make materials available (29.9% of all respondents), (2) the fear of being scooped when materials become publicly available (23.2% of all respondents), and (3) no need for sharing as their data are already publicly available (33.9% of all respondents).
 There are some other notable differences across the methods.
@@
 
-Besides this multiple choice questions soliciting the reasons for not sharing research materials, we also ask our participants to reflect on their answer in our hypothetical sharing scenario.
-The answers that they provided in this free form field have been coded by a research assistant that was not informed about the experimental design of the study.
+Besides these multiple-choice questions soliciting the reasons for not sharing research materials, we also ask our participants to reflect on their answers in our hypothetical sharing scenario.
+The answers they provided in this free-form field have been coded by a research assistant who was not informed about the study's experimental design.
 The resulting categories characterizing the coded answers and their respective frequencies are presented in Panel B, for the total sample as well as for the different treatment cells.
@@
 Different from the findings in Panel A, we are now also able to identify reasons for and not just against sharing.
-First and foremost our participants share because they believe that this enhances the quality of research.
+First and foremost, our participants share this because they believe it enhances the research's quality.
 Another strong argument is that it helps other researchers.
-This argument is significantly more likely to be provided by participants that faced the collaboration treatment, in line with our theoretical predictions and providing evidence that the framing of the sharing situation has an effect on the decision-making of our participants.
+This argument is significantly more likely to be provided by participants that faced the collaboration treatment, in line with our theoretical predictions and providing evidence that the framing of the sharing situation affects the decision-making of our participants.
 
 The main rationales against sharing are related to the materials being considered valuable intellectual property that can potentially be reused for other research projects.
-A typical example for such a statement is:
-
+A typical example of such a statement is:
+
+```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-
-Another interesting aspect, that does not become apparent from the pre-conditioned analysis in Panel A, is that a sizable amount of participants indicate that they are concerned about unethical use of their research materials.
-These concerns are related to other researchers using their work for "reverse p-hacking", trying to discredit prior findings to establish a contribution.
-Again, an example for such a statement:
-
+```
+Another interesting aspect that does not become apparent from the pre-conditioned analysis in Panel A is that a sizable amount of participants indicate that they are concerned about unethical use of their research materials.
+These concerns are related to other researchers using their work for "reverse p-hacking," trying to discredit prior findings to establish a contribution.
+Again, an example of such a statement:
+
+```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-
+```
 But even without reverse p-hacking, research material sharing requests can create career concerns. An example:
 
+```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-
-Another aspect, which also featured prominently in Panel A, is the time that it takes to entertain research material sharing and potential followup requests. For example:
-
+```
+Another aspect, which also featured prominently in Panel A, is the time that it takes to entertain research material sharing and potential follow-up requests. For example:
+
+```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-
-The last aspect of the this quote also hints at a rationale that was commonly featured in the "it depends" category: the personality of the requesting person and their reputation. A final example:
-
+```
+The last aspect of this quote also hints at a rationale commonly featured in the "it depends" category: the requesting person's personality and reputation. A final example:
+
+```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-
-These statements indicate the potential for selective sharing among well-connected researchers, which would benefit an "in-crowd" of academics while at the same time unleveling the academic playing field and increasing  inequality.
-Taken together, we conclude from the rationale analysis that our participants give more consideration to potential sharing costs then they give to potential sharing benefits.
+```
+These statements indicate the potential for selective sharing among well-connected researchers, which would benefit an "in-crowd" of academics while at the same time unraveling the academic playing field and increasing inequality.
+Taken together, we conclude from the rationale analysis that our participants give more consideration to potential sharing costs than to potential sharing benefits.
 While the sharing benefits become more prevalent with a collaboration framing, the sharing costs are prominent regardless of the hypothetical scenario.
@@
 
-\centerline{--- Insert Table 10 about here ---}
-
-Table 10 lists the frequencies and percentages for three questions about pre-registration.
+\centerline{--- Insert Table 11 about here ---}
+
+Table 11 lists the frequencies and percentages for three questions about pre-registration.
 Panel A considers respondents' familiarity with the practice itself.
-Namely, we asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^7] The results in Panel A suggest accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
+Namely, we asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^9] The results in Panel A suggest accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
 They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010).
-While this finding might appear surprising at first glance one has to factor in that the practice of pre-registration is gaining traction over time and our survey was fielded two years later than the second wave of our benchmark survey.
-
-\centerline{--- Insert Figure 4 about here ---}
-
-Panel B reports data on the first year respondents pre-registered.
-Namely, we asked them: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^8] The findings exhibit a clear pattern: Accounting researchers started considering pre-registration for the first time significantly later than researchers in other social science fields (two-tailed p-value \< 0.010).
+While this finding might appear surprising at first glance, one has to factor in that the practice of pre-registration is gaining traction over time, and our survey was fielded two years later than the second wave of our benchmark survey.
+
+[^9]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
+
+\centerline{--- Insert Figure 5 about here ---}
+
+Panel B reports data on the first-year respondents pre-registered.
+Namely, we asked them: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^10] The findings exhibit a clear pattern: Accounting researchers started considering pre-registration for the first time significantly later than researchers in other social science fields (two-tailed p-value \< 0.010).
 The take-up started around 2018 compared to 2015-2016 for the other fields.
@@
 
-Panel C shows data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^9] Results indicate no clear differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100).
+[^10]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"
+
+Panel C shows data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^11] Results indicate no apparent differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100).
 However, the perceived increase in trustworthiness when pre-registering is less in accounting compared to psychology and sociology (two-tailed p-value \< 0.010).
 
-[^7]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
-
-[^8]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"
-
-[^9]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
+[^11]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
 We found this question to be quite broad yet it used a trustworthiness scale.
-So, we chose more specific framing for our question.
-
-\centerline{--- Insert Table 11 about here ---}
+So, we chose a more specific framing for our question.
+
+\centerline{--- Insert Table 12 about here ---}
 
 In this final part of our analysis, we examine differences in familiarity, usage, and trustworthiness of pre-registration across the different methodological areas within accounting.
-Table 11 displays respondents' frequencies using three panels.
-Similar to Table 10 Panel A, Panel A of Table 11 reports on familiarity, i.e., the question: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?" Somewhat unsurprisingly, Panel A shows that qualitative accounting researchers are less familiar with the practice than accounting researchers belonging to the Archival, Experimental, and Survey categories (two-tailed p-value \< 0.100).
+Table 12 displays respondents' frequencies using three panels.
+Similar to Table 11 Panel A, Panel A of Table 12 reports on familiarity, i.e., the question: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?" Somewhat unsurprisingly, Panel A shows that qualitative accounting researchers are less familiar with the practice than accounting researchers belonging to the Archival, Experimental, and Survey categories (two-tailed p-value \< 0.100).
 Yet, there is no statistical difference between qualitative and analytical accounting researchers.
-Panel B reports on differences in usage, specifically, the question "`r vars$text[100]`", similar to the question featured in Table 10 Panel B.
-We find that accounting researchers in the experimental field report the highers usage of pre-registration, while none of the qualitative accounting researchers report using it.
+Panel B reports on differences in usage, specifically, the question "`r vars$text[100]`", similar to the question featured in Table 11 Panel B.
+We find that accounting researchers in the experimental field report the highest usage of pre-registration, while none of the qualitative accounting researchers report using it.
 Lastly, Panel C reports differences in perceived trustworthiness.
-Specifically, it features answers to the question "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?" which is identical to the question featured in Table 10 Panel C.
-We find no clear evidence of differences among the different methodologies in whether they trust pre-registered work more than work that has not been pre-registered.
+Specifically, it features answers to the question, "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?" which is identical to the question featured in Table 11 Panel C.
+We find no clear evidence of differences among the different methodologies in whether they trust pre-registered work more than work that has not been pre-registered.[^12]
+
+[^12]: Similar to the observational data on research material sharing, we also collected observational data on pre-registration.
+However, for our random sample of `r nrow(authors)` authors, we find only for `r sum(by_author$has_prereged)` authors clear evidence that they have pre-registered a study.
+These cases are linked to the registered report initiative of JAR.
 
@@
 
-Our results support the conclusion that us accountants face an "open science dilemma".
-On the one hand, we are more skeptical about the reproducibility of our influential findings than other social science researchers are about their respective findings.
+Our results support the conclusion that we accountants face an "open science dilemma." On the one hand, we are more skeptical about the reproducibility of our influential findings than other social science researchers are about their respective findings.
 On the other hand, we seem to be a little bit behind the curve in terms of research material sharing and research design pre-registration.
-
-If these conclusions are descriptive: What should be our reaction?
-While we are not in the position to advise our profession on how to proceed, we feel that a two-pronged approach might be in order.
-First: Why are we so skeptical about our own work?
-Is this an example of the anecdotal "professional skepticism" that leads us accountants to over-weight bad signals in general?
+If these conclusions are descriptive, what should be our reaction?
+
+While we are not in a position to advise our profession on how to proceed, we feel that a two-pronged approach might be desirable.
+First, why are we so skeptical about our work?
+Is this an example of the anecdotal "professional skepticism" that leads us accountants to over-weight wrong signals in general?
 Or do we indeed have good reasons to be concerned?
 The only way to find out is to take stock.
-
-As @LSA_2024 indicate, reproduction studies in accounting are not rare, and a majority of those confirms prior results.
-However, we need more systematic evidence on whether our findings reproduce and also hold in new settings and/or with new data.
-A very impressive exercise in that regard is the recent large-scale reproduction attempt of studies published in Management Science [@FGHKO_2023] that systematically reproduced almost 500 articles that were published in Management Science before and after their establishment of a Data and Code Policy in 2019.
+@LSA_2024 suggest reproduction studies in accounting might not be rare, and a majority of those confirm prior results.
+However, we need more systematic evidence on whether our findings reproduce, with or without new data, and hold in new settings.
+An impressive exercise in that regard is the recent large-scale reproduction attempt of studies published in Management Science [@FGHKO_2023].
+This endeavor systematically reproduced almost 500 articles published in Management Science before and after the establishment of a Data and Code Policy in 2019.
 One interesting finding from that study is that accounting studies in Management Science are -if anything- more reproducible than studies in neighboring fields like finance.
-Based on this it seems as if professional skepticism might indeed be partly responsible for our open science dilemma.
-
-It would be insightful to compare the findings for Management Science, which also document an impressive effect of their data and code policy, with data on studies published in the Journal of Accounting Research, again pre and post their data policy.
-These findings could in turn then be compared with those for studies published in other leading journals that do not have a dedicated data and code policy (yet).
+Based on this, it seems that professional skepticism might indeed be partly responsible for our open science dilemma.
+
+It would be insightful to compare the findings for Management Science, which also documents an impressive effect of their data and code policy, with data on studies published in the Journal of Accounting Research, again pre and post their data policy.
+These findings could, in turn, be compared with those for studies published in other leading journals that do not have a dedicated data and code policy (yet).
 But not only systematic large-scale reproduction studies can update our priors about the reproducibility of our work.
-Replication games, potentially embodied in doctoral education, are an alternative means to assess the reproducibility of our work while at same time helping researchers to grow their network and empirical skill-sets alike.
-Taken together, we believe that the academic accounting profession should be well positioned to take a leading role in verifying its own output.
+Replication games, potentially embodied in doctoral education, are an alternative means to assess the reproducibility of our work while at the same time helping researchers to grow their network and empirical skill sets alike.
+Taken together, we believe that the academic accounting profession should be well-positioned to take a leading role in verifying its output.
 In the end, assessing the reproducibility of scientific work is an assurance and auditing process, an area we know quite a bit about!
 
-The second element of our two-pronged approach would be to promote research material sharing and pre-registration, potentially in combination with other open science measures that are aiming to increase the accessibility and re-usability of scientific work.
-As economists, we are quick to jump on the incentive problems in this regard.
+The second element of the two-pronged approach would be to promote research material sharing and pre-registration, potentially in combination with other open science measures that aim to increase the accessibility and re-usability of scientific work.
+The economists among us might be quick to point out the incentive problems in this regard.
 Why should we do it?
@@
 While some associative evidence from other fields indicates that papers that share their data are cited more often [@PDF_2007], currently, as hard as it seems, the answer to this is not clearly affirmative.
-Research material sharing requires skills and time, and, to the extreme, devoting this time might even be regarded as a negative signal by tenure and promotion committees, assuming that it crowds out time spent on producing "more tenurable output".
-
-To us, this mindset seems to be the core of the the problem.
+Research material sharing requires skills and time, and, to the extreme, devoting this time might even be regarded as a negative signal by tenure and promotion committees, assuming that it crowds out time spent on producing "more tenurable output."
+
+To us, this mindset seems to be the core of the problem.
 We believe that it is misguided as research material sharing constitutes a public good that is crucial for scientific progress.
-Think about a scientific computing world without open source contributions.
+Think about a scientific computing world without open-source contributions.
 Without the BSD/Linux operating system and its tools, without Python, R, git, Latex, and the accompanying library ecosystem.
 The scientific advancements in areas like Econometrics, Machine Learning, and Natural Language Processing would be -if at all feasible- severely delayed.
-As our field builds on the insights of these areas, we benefit from the open science paradigm in our every day work.
-
-Given that, one might wonder whether data and code sharing by accounting researchers can create similar positive externalities.
-As our comparative competitive advantage lies less in methodological aspects but more in institutional expertise, we sense potential candidates in the area of carefully curated and pre-processed data building on the universe of firm disclosures.
+As our field builds on the insights of these areas, we benefit from the open science paradigm in our everyday work.
+
+Given that, one might ask whether data and code sharing by accounting researchers can create similar positive externalities.
+As our competitive advantage stems more from institutional expertise than methodological aspects, we are well-suited to become vital for carefully curating and pre-processing data based on extensive firm disclosures.
 Prominent examples include curated word lists for sentiment analyses in financial settings [e.g., @LM_2011], topic model-based measures of specific firm risks [e.g., @H_2019], and industry classifications based on financial disclosures [e.g., @HP_2016].
@@
 A closely related area where we see the potential of accounting data to develop an impact is the collection and pre-processing of web and electronic filing data.
-For the former, web scraping of corporate webpages can provide informative data [e.g., @BBB_2021] and for the latter, in particular the upcoming electronic filing requirements for sustainability reports hold promise.
-While in this area, researchers are competing with established commercial data providers, the need of research to study also unstructured textual data makes it necessary and useful to build research-focused data pipelines and products instead of simply trusting (and paying) commercial data vendors.
-An additional aspect of this is that freely licensable research data can remove one of the largest entry hurdles for empirical archival accounting researchers.
-
-While these flagship projects are useful showcases that data and code sharing in the accounting domain can be very impactful also for other domains, in order to promote reproducible workflows overall we need to make the case that adopting such a workflow not only contributes to the public good by making research materials accessible but also enhances research efficiency at the individual level.
-In order to be able to share code and data, one has to adopt a workflow that integrates reusability aspects into project development.
-The data and code requirements of leading journals in economics, finance, and accounting are not only pushing the availability of research materials but also impose substantial costs on researchers that have to provide more or less complete replication package upon acceptance.
-As many affected by these regulations will be open to admit, transforming an empirical project from an internal "well it works" scripting exercise to a well documented replication package that ideally works across multiple platforms is far from trivial.
-This process becomes significantly easier and also more enjoyable if an open science oriented workflow is adopted throughout all stages of project development.
+For the former, web scraping of corporate webpages can provide informative data [e.g., @BBB_2021], and for the latter, in particular, the upcoming electronic filing requirements for sustainability reports hold promise.
+While researchers compete with established commercial data providers in this area, the need for research to study unstructured textual data makes it necessary and valuable to build research-focused data pipelines and products instead of simply trusting (and paying) commercial data vendors.
+Another aspect is that freely licensable research data can remove one of the most significant entry hurdles for empirical archival accounting researchers.
+
+While these flagship projects are useful showcases that data and code sharing in the accounting domain can also be impactful for other domains, to promote reproducible workflows overall, we need to make the case that adopting such a workflow not only contributes to the public good by making research materials accessible but also enhances research efficiency at an individual level.
+To be able to share research materials, such as code and data, researchers must adopt a workflow that integrates reusability aspects into project development.
+The data and code requirements of leading journals in economics, finance, and accounting are not only pushing the availability of research materials but also imposing substantial costs on researchers who have to provide more or less complete replication packages upon acceptance.
+As many researchers affected by these regulations will admit, transforming an empirical project from an internal "well it works" scripting exercise to a well-documented replication package that ideally works across multiple platforms is far from trivial.
+This process becomes significantly more manageable and enjoyable if an open science-oriented workflow is adopted throughout all stages of project development.
 Besides this, it also makes it easier for co-author teams to cooperate.
 
-As lack of time has been identified as one of the biggest roadblocks against research material sharing in our survey, educational activities targeted at the PhD-level in scientific computing and project management in general seem important.
-While well-funded research institutions might have the opportunity to outsource these skills to research professionals, the vast majority of researchers world-wide need to acquire them themselves.
-This is not necessarily a bad thing, as we believe that having these skills as a researcher enables one to develop more creative research projects compared to researchers that are unaware of what is feasible with state-of-the-art scientific computing.
-In the old days, many accounting PhD programs were implicit- or explicitly relying on scientific computing skills to be handed down from one PhD generation to another as tacit knowledge.
-It seem that these days are over and that dedicated scientific computing courses should become as a central component of the scientific education in the quantitative social sciences as lab training is in the natural sciences.
-
-A lot of the above applies mostly to the empirical and quantitative areas of our discipline.
+As the lack of time is one of the biggest roadblocks to research material sharing in our survey, educational activities targeted at the PhD level in scientific computing and project management, in general, seem important.
+While well-funded research institutions might have the opportunity to outsource these skills to research professionals, the vast majority of researchers worldwide need to acquire them themselves.
+This is not necessarily undesirable, as having these skills enables one to develop more creative research projects than researchers unaware of what is feasible with state-of-the-art scientific computing.
+In the early days, many accounting PhD programs were implicit- or explicitly relying on scientific computing skills to be handed down from one PhD generation to another.
+It seems that these days are over and that dedicated scientific computing courses should become a central component of scientific education in the quantitative social sciences as lab training is in the natural sciences.
+
+Much of the above applies primarily to our discipline's empirical and quantitative areas.
 What about analytical and qualitative researchers and their studies?
-As becomes apparent from our findings, their views on open science differ quite prominently from the "accounting mainstream".
-Analytical researchers seem to be much more confident in their own work, potentially in line with theoretical work being easier to verify during the review process.
-Then again, in order to develop the impact that it deserves, analytical work not only needs to be reproducible but also accessible and reusable, ideally also by non-expert researchers from neighboring methods.
-Qualitative work, on the other hand, faces challenges that sets it apart from typical quantitative work.
+As it becomes apparent from our findings, their views on open science differ pretty prominently from those of the "accounting mainstream." Analytical researchers seem to be much more confident in their work than others, potentially in line with theoretical work being more accessible to verify during the review process.
+Then again, to develop the impact that it deserves, analytical work not only needs to be reproducible but also accessible and reusable, ideally also by non-expert researchers from neighboring methods.
+Qualitative work, on the other hand, faces challenges that set it apart from typical quantitative work.
 First, its data is often collected under confidentiality, legally restricting future sharing.
-Second, its unique richness makes it inherently hard to share across subjects, especially if re-identification issues are present.
-Third, related and maybe more epistemological in nature, the assumption of objectivity, which allows research materials to be detached from the individual researcher and to be re-used by others, is questioned within the qualitative realm.
-This implies that qualitative scholars have to develop -and are developing [e.g., @M_2014; @FRV_2022]- their own understanding what reproducibility means within their methodological paradigm.
-
-Finally, fears and a general lack of trust in fellow researchers also seem to be important deterrents to the adoption of open science methods.
+Second, its unique richness makes it inherently challenging to share across subjects, especially if re-identification issues are present.
+Third, related and maybe more epistemological in nature, the assumption of objectivity, which allows research materials to be detached from the individual researcher and re-used by others, is questioned within the qualitative realm.
+This implies that qualitative scholars have to develop -and are developing [e.g., @M_2014; @FRV_2022]- their own understanding of what reproducibility means within their methodological paradigm.
+
+Finally, fears and a general lack of trust in fellow researchers are also essential deterrents to adopting open science methods.
 This is human but unfortunate, also because it leads to subtle "home biases" when it comes to sharing, potentially increasing academic inequality and hindering scientific progress.
-While the fear of being "scooped" can be addressed by publishing materials later in the publication progress or publicly claiming intellectual ownership to ideas via registration and use of well-established repositories, fears with regards to future researchers pointing to deficiencies in ones work and/or a general lack of trust are harder to overcome.
+While the fear of being "scooped" can be addressed by publishing materials later in the publication process or publicly claiming intellectual ownership of ideas via registration and use of well-established repositories, fears with regards to future researchers pointing to deficiencies in one's work and/or a general lack of trust are more challenging to overcome.
 For both aspects, we need to work towards changing the error climate in the academic discipline.
-Also, we believe that it might be helpful to move away from the "policing" aspect of reproducibility and instead stress the collaborative public good character of open science activities.
-With them, we can help each other, promote our field and, yes, make the research process even more fun!
+Additionally, it might be helpful to move away from the "policing" aspect of reproducibility and instead stress the collaborative public good character of open science activities.
+With them, we can help each other, promote our field, and make the research process even more fun!
 
@@
 
-### Figure 4: Pre-Registration: Take-up over Time Across the Social Sciences {.unnumbered}
+### Figure 4: Share of Papers with Shared Research Materials over Time {.unnumbered}
 
 ```{r Figure4, fig.width=8, fig.height=6}
+plot_resmat_sharing_over_cyear
+```
+
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
+This figure is based on `r nrow(papers)` papers, published since 2016 by a country-stratified random sample of `r nrow(authors)` authors from our target participant population.
+We collect the papers' DOIs from Scopus.
+For each paper, we observe whether research material availability is mentioned on the paper's DOI URL.
+The respective shares of papers are plotted by DOI creation year, along with their binomial confidence intervals.
+DOI creation years with less than 50 papers are excluded.
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
+```
+### Figure 5: Pre-Registration: Take-up over Time Across the Social Sciences {.unnumbered}
+
+```{r Figure5, fig.width=8, fig.height=6}
 pre_reg_over_time_plot(mr)
@@
 ```{r Tab3ReprodSocSciResp, asis = TRUE}
-tab <- create_pct_cross_tab_table(mr, "reprod", "demog_discipline", get_resp_label("reprod_acc"), df_only = TRUE)
+tab <- create_pct_cross_tab_table(
+	mr, "reprod", "demog_discipline",
+	resp_label =  get_resp_label("reprod_acc"), df_only = TRUE
+)
 gt(tab) %>% as_latex()
@@
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_acc", "demog_method", 
-	ctests = TRUE, df_only = TRUE
-) 
-gt(tab %>% select(-Other)) %>% 
+	sd, "reprod_acc", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
+) 
+gt(tab) %>% 
 	cols_align("right", -1) %>% 
@@
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_method", "demog_method", 
-	ctests = TRUE, df_only = TRUE
-) 
-gt(tab %>% select(-Other)) %>% 
+	sd, "reprod_method", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
+) 
+gt(tab) %>% 
 	cols_align("right", -1) %>% 
@@
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_method_delta", "demog_method", 
+	sd, "reprod_method_delta", "demog_method", include_total = TRUE,
+	drop_levels = "Other", 
 	resp_label = sort(na.omit((unique(sd$reprod_method_delta)))),
@@
 ) 
-gt(tab %>% select(-Other)) %>%
+gt(tab) %>%
 	cols_align("right", -1) %>% 
@@
 Panel C reports the individual level differences, measured in likert steps, between the answers given for Panel B and Panel A.
-In all Panels, answers from two respondents who classified their method as "Other" are excluded.
+In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other" are excluded.
 Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
@@
 ```{r Tab6aSharingFamiliarity, asis = TRUE}
-df <- sd %>% filter(demog_method != "Other")
 tab <- create_pct_cross_tab_table(
-	df, "sharing_familiar", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "sharing_familiar", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 ) 
@@
 tab <- create_pct_cross_tab_table(
-	df, "sharing_important", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "sharing_important", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 ) 
@@
 The response presented in Panel A is based on the question "`r vars$text[44]`" while the response presented in Panel B is based on the question "`r vars$text[49]`".
-In all Panels, answers from two respondents who classified their method as "Other" are excluded.
+In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other", and one observation from a person who chose not self-classify into a main method are excluded.
 Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
@@
 ```
-#### Panel A: Stated sharing frequency across fields {.unnumbered}
+#### Panel A: Stated sharing frequency across methods {.unnumbered}
 
@@
 tab <- create_pct_cross_tab_table(
-	df, "sharing_use", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "sharing_use", "demog_method", include_total = TRUE, 
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 ) 
@@
 ```{r Tab8bSharingPreDes, asis = TRUE}
-stats <- df %>%
+base_df <- sd %>%
 	select(
@@
 	) %>%
-	na.omit() %>%
+	na.omit()
+
+stats_total <- base_df %>%
+	pivot_longer(-1, names_to = "var", values_to = "values") %>%
+	group_by(var) %>%
+	summarise(
+		Mean = sprintf("%.1f%%", mean(values)),
+		`Std. Dev.` = sprintf("%.1f%%", sd(values)),
+		`25%` = sprintf("%.1f%%", quantile(values, 0.25)),
+		Median = sprintf("%.1f%%", median(values)),
+		`75%` = sprintf("%.1f%%", quantile(values, 0.75)),
+	) %>% 
+	pivot_longer(-1, names_to = "stat", values_to = "Total") %>% 
+	select(Total)
+
+stats_fields <- base_df %>%
+	filter(as.character(demog_method) != "Other") %>%
 	group_by(demog_method) %>%
@@
 
+stats <- bind_cols(stats_total, stats_fields) %>%
+	select(" ", Total, everything())
+
 tab <- rbind(
-	c("General Preference for Sharing", rep("", 5)),
+	c("General Preference for Sharing", rep("", 6)),
 	stats[6:10,],
-	c("Editor Preference for Sharing", rep("", 5)),
+	c("Editor Preference for Sharing", rep("", 6)),
 	stats[1:5,],
-	c("Believes About Actual Sharing Behavior", rep("", 5)),
+	c("Believes About Actual Sharing Behavior", rep("", 6)),
 	stats[11:15,]
@@
 
-tab_latex <- sub("General Preference for Sharing &  &  &  &  &", "\\\\multicolumn{6}{l}{General Preference for Sharing}", tab_latex)
-tab_latex <- sub("Editor Preference for Sharing &  &  &  &  &", "\\\\multicolumn{6}{l}{Editor Preference for Sharing}", tab_latex)
-sub("Believes About Actual Sharing Behavior &  &  &  &  & ", "\\\\multicolumn{6}{l}{Believes About Actual Sharing Behavior}", tab_latex)
+tab_latex <- sub("General Preference for Sharing &  &  &  &  &  &", "\\\\multicolumn{7}{l}{General Preference for Sharing}", tab_latex)
+tab_latex <- sub("Editor Preference for Sharing &  &  &  &  &  &", "\\\\multicolumn{7}{l}{Editor Preference for Sharing}", tab_latex)
+sub("Believes About Actual Sharing Behavior &  &  &  &  &  &", "\\\\multicolumn{7}{l}{Believes About Actual Sharing Behavior}", tab_latex)
 
@@
 The response presented in Panel A is based on the question "`r vars$text[55]`" while the response presented in Panel B is based on the questions "`r vars$text[78]`" (general preference for sharing), "`r vars$text[79]`" (editor preference for sharing) and "`r vars$text[54]`" (actual sharing behavior).
-In all Panels, answers from two respondents who classified their method as "Other" are excluded.
+In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other", and one observation from a person who chose not self-classify into a main method are excluded.
 Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
@@
 ```
-### Table 9: Sharing of Research Materials: Rationales {.unnumbered}
-
 ```{=tex}
@@
 ```
+### Table 9: Observational Data on Research Material Sharing {.unnumbered}
+
+#### Panel A: By Author {.unnumbered}
+
+```{r Tab9aObservationalDataByAuthor, asis = TRUE}
+gt(tab_by_author) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+```
+
+#### Panel B: By Journal {.unnumbered}
+
+```{r Tab9bObservationalDataByJournal, asis = TRUE}
+gt(tab_by_journal) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+
+```
+
+This table is based on on a country-stratified random sample of `r nrow(authors)` authors from our target participant population and `r nrow(papers)` papers that they published since 2016.
+We collect these publications' DOIs using Scopus.
+To identify research material sharing, we search homepages and the established open science platforms GitHub, Open Science Foundation (OSF), Dataverse, and Zenodo.
+For each paper, we observe whether research material availability is mentioned on the paper's DOI URL.
+The data collection manual for this process is available in this project's GitHub repository.
+In Panel A, the overall share of authors that we identify to share research materials is reported, along with its binomial confidence interval in brackets.
+We also report the share of authors that we document to provide research materials when we ignore the Journal of Accounting Research and Management Science, as both journals have mandatory data and code sharing policies in place.
+In addition, we report the share of authors that have accounts linked to their names on the open science platforms mentioned above.
+Panel B reports the paper-level data in total and separately for all journals for which we evaluated at least 20 papers.
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
+```
+### Table 10: Sharing of Research Materials: Rationales {.unnumbered}
+
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
 #### Panel A: Reasons against Sharing (Close-Ended Question) {.unnumbered}
 
-```{r Tab9aSharingReasons, asis = TRUE}
+```{r Tab10aSharingReasons, asis = TRUE}
 tab <- sd %>%
@@
 
-```{r Tab9bSharingRationales, asis = TRUE}
+```{r Tab10bSharingRationales, asis = TRUE}
 df <- sd %>% left_join(
@@
 ```
-### Table 10: Pre-Registration Across the Social Sciences {.unnumbered}
+### Table 11: Pre-Registration Across the Social Sciences {.unnumbered}
 
@@
 
-```{r Tab10aPreRegAwareSocSciResp, asis = TRUE}
+```{r Tab11aPreRegAwareSocSciResp, asis = TRUE}
 tab <- create_pct_cross_tab_table(
@@
 
-```{r Tab10bPreRegTimeSocSciResp, asis = TRUE}
+```{r Tab11bPreRegTimeSocSciResp, asis = TRUE}
 tab <- create_pct_cross_tab_table(
@@
 
-```{r Tab10cPreRegTimeSocSciResp, asis = TRUE}
+```{r Tab11cPreRegTimeSocSciResp, asis = TRUE}
 tab <- create_pct_cross_tab_table(
@@
 \setlength{\parindent}{4em}
-\end{landscape}
-\end{singlespace}
-\newpage
-```
-### Table 11: Pre-Registration Across Methods {.unnumbered}
-
-```{=tex}
-\begin{singlespace}
+\newpage
+```
+### Table 12: Pre-Registration Across Methods {.unnumbered}
+
 \setlength{\parindent}{0em}
-```
+
 #### Panel A: Familiarity {.unnumbered}
 
-```{r Tab11aPreRegFamiliarity, asis = TRUE}
-df <- sd %>% filter(demog_method != "Other")
+```{r Tab12aPreRegFamiliarity, asis = TRUE}
 tab <- create_pct_cross_tab_table(
-	df, "prereg_familiar", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "prereg_familiar", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 ) 
@@
 
-```{r Tab11bPreRegUse, asis = TRUE}
+```{r Tab12bPreRegUse, asis = TRUE}
 
 tab <- create_pct_cross_tab_table(
-	df, "prereg_use", "demog_method", 
+	sd, "prereg_use", "demog_method", include_total = TRUE,
+	drop_levels = "Other", 
 	resp_label = c("No (0)", "Yes (1)"), 
@@
 # Adjust levels to be zero based.
-tab[4,2:6] <- t(sprintf("%.2f", as.numeric(tab[4,2:6]) - 1))
-tab[5,2:6] <- t(sprintf("%.2f", as.numeric(tab[5,2:6]) - 1))
+tab[4,2:7] <- t(sprintf("%.2f", as.numeric(tab[4,2:7]) - 1))
+tab[5,2:7] <- t(sprintf("%.2f", as.numeric(tab[5,2:7]) - 1))
 gt(tab) %>% 
@@
 
+\newpage
+
 #### Panel C: Trustworthiness {.unnumbered}
 
-```{r Tab11cPreRegTrust, asis = TRUE}
+```{r Tab12cPreRegTrust, asis = TRUE}
 
 tab <- create_pct_cross_tab_table(
-	df, "prereg_trust", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "prereg_trust", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 ) 
@@
 The response presented in Panel A is based on the question "`r vars$text[95]`", the response presented in Panel B is based on the question "`r vars$text[100]`", and the response presented in Panel C is based on the question "`r vars$text[103]`".
-In all Panels, answers from two respondents who classified their method as "Other" are excluded.
+In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other" are excluded.
 Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
@@
 \setlength{\parindent}{4em}
+\end{landscape}
 \end{singlespace}

### 2024-04-17 docs/presentation.qmd
Added observational data analyses

@@
 title: "Accountants' Attitudes Towards Open Science"
+subtitle: "" # we use this for the venue
 author: Joachim Gassen, Jacqueline Klug, and Victor van Pelt
 institute: "HU Berlin and WHU – Otto Beisheim School of Management"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
+date: today
+date-format: "MMMM D, YYYY"
 format: 
@@
     slide_level: 3
+
 classoption: "aspectratio=169"
@@
 pop <- read_csv(
-	"../data/external/invited_authors_retracted.csv", show_col_types = FALSE
+	"../data/external/invited_authors_anon.csv", show_col_types = FALSE
 )
+
+authors <- read_csv("../data/external/obs_data_authors_anon.csv", show_col_types = FALSE)
+papers <- read_csv("../data/external/obs_data_papers_anon.csv", show_col_types = FALSE)
+
+source("../code/obs_data_analyses.R")
 
@@
 
-## Sample Composition
-
-|                                 |                    N (%) |
-|:--------------------------------|-------------------------:|
-| Authors identified (Raw Sample) |                    2,660 |
-| \- Excluded or missing          | 118 (4.4% of identified) |
-| = Emails sent                   |                    2,542 |
-| \- Emails bounced               |       206 (8.1% of sent) |
-| = Emails received               |                    2,336 |
-| Surveys Started                 |      391 (15.4% of sent) |
-| Surveys Partially Completed     |      254 (10.9% of sent) |
-| Surveys Fully Completed         |       222 (8.7% of sent) |
-
 ## Invitation Email
@@
 \end{small}
+
+## Sample Composition
+
+|                                 |                    N (%) |
+|:--------------------------------|-------------------------:|
+| Authors identified (Raw Sample) |                    2,660 |
+| \- Excluded or missing          | 118 (4.4% of identified) |
+| = Emails sent                   |                    2,542 |
+| \- Emails bounced               |       206 (8.1% of sent) |
+| = Emails received               |                    2,336 |
+| Surveys Started                 |      391 (15.4% of sent) |
+| Surveys Partially Completed     |      254 (10.9% of sent) |
+| Surveys Fully Completed         |       222 (8.7% of sent) |
 
@@
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_acc", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "reprod_acc", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 )
 
-gt(tab %>% select(-Other)) %>% 
+gt(tab) %>% 
 	cols_align("right", -1) %>% 
@@
 ```{r Tab6bSharingImportance, asis = TRUE}
-df <- sd %>% filter(demog_method != "Other")
 tab <- create_pct_cross_tab_table(
-	df, "sharing_important", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "sharing_important", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 ) 
@@
 sub("Adjusted R2", "\\\\midrule\\\\addlinespace[2.5pt]\nAdjusted R²", tab_latex)
+```
+
+## Observational Data on Sharing Behavior: Author Level
+
+```{r, asis = TRUE}
+gt(tab_by_author) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+## Observational Data on Sharing Behavior: Journal Level
+
+```{r, asis = TRUE}
+gt(tab_by_journal) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+## Observational Data: Paper-level Sharing over Time
+
+```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
+p <- plot_resmat_sharing_over_cyear
+if (trr266_fonts_available) {
+	p + theme(text = element_text(family = "Calibri Light", size = 12))
+} else p
 ```
@@
 
-```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
+```{r Figure5, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
 p <- pre_reg_over_time_plot(mr) + theme(legend.position = "right") 
 if (trr266_fonts_available) {
-	p + theme(text = element_text(family = "Calibri Light", size = 7))
+	p + theme(text = element_text(family = "Calibri Light", size = 12))
 } else p
@@
 ```{r Tab11aPreRegFamiliarity, asis = TRUE}
-df <- sd %>% filter(demog_method != "Other")
 tab <- create_pct_cross_tab_table(
-	df, "prereg_familiar", "demog_method", 
+	sd, "prereg_familiar", "demog_method", include_total = TRUE,
+	drop_levels = "Other", 
 	ctests = TRUE, df_only = TRUE
@@
 tab <- create_pct_cross_tab_table(
-	df, "prereg_use", "demog_method", 
-	resp_label = c("No (0)", "Yes (1)"), 
+	sd, "prereg_use", "demog_method", include_total = TRUE,
+	drop_levels = "Other", resp_label = c("No (0)", "Yes (1)"), 
 	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
@@
 tab <- create_pct_cross_tab_table(
-	df, "prereg_trust", "demog_method", 
-	ctests = TRUE, df_only = TRUE
+	sd, "prereg_trust", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
 ) 

### 2024-04-17 code/create_obs_sample.R

@@ -4,9 +4,9 @@ set.seed(42)
 
 N_TO_SAMPLE <- 100
 
-# To create the actual audit sample, you would need to have the 
-# unrestricted authors file, containing their access information.
-# If you feel that you need this file, please contact the 
+# To create the actual observational data sample, you would need to 
+# have the unrestricted authors file, containing their access 
+# information. If you feel that you need this file, please contact the 
 # authors.
 
 pop <- read_csv("data/external/invited_authors.csv")
@@ -19,4 +19,4 @@ smp <- pop %>%
 smp <- smp[sample(nrow(smp)),]
 table(smp$affil_country)
 
-write_csv(smp, "data/generated/audit_sample.csv")
+write_csv(smp, "data/generated/obs_sample.csv")

### 2024-04-17 code/obs_data_analyses.R

@@ -1,0 +1,153 @@
+suppressMessages({
+	library(tidyverse)
+	library(kableExtra)
+})	
+
+# The code below relies on the dataframes papers and authors being
+# available 
+
+papers_by_author <- papers %>%
+	mutate(
+		mand_resmat = journal %in% 
+			c("Journal of Accounting Research", "Management Science")
+	) %>%	
+	group_by(scopus_id) %>%
+	summarise(
+		papers_n = n(),
+		papers_mn_resmat = mean(resmat),
+		papers_mn_resmat_wo_mand = mean(resmat * (! mand_resmat)),
+		papers_mn_prereg = mean(prereg)
+	)
+
+by_author <- authors %>%
+	left_join(papers_by_author, by = "scopus_id") %>%
+	transmute(
+		papers_n = papers_n,
+		papers_mn_resmat = papers_mn_resmat,
+		papers_mn_resmat_wo_mand = papers_mn_resmat_wo_mand,
+		has_made_resmat_available = hpage_resmat | github_resmat |
+			osf_resmat | dverse_resmat | zenodo_resmat | aearep_resmat |
+			papers_mn_resmat > 0,
+		has_made_resmat_available_vol = hpage_resmat | github_resmat |
+			osf_resmat | dverse_resmat | zenodo_resmat | aearep_resmat |
+			papers_mn_resmat_wo_mand > 0,
+		has_prereged = hpage_prereg | github_prereg |
+			osf_prereg | dverse_prereg | zenodo_prereg | aearct_prereg |
+			papers_mn_prereg > 0,
+		uses_os_repos = github_author + osf_author + dverse_author + 
+			zenodo_author + aearct_prereg + aearep_resmat > 0
+	)
+
+ci_has_made_resmat_available <- prop.test(
+	sum(by_author$has_made_resmat_available),
+	nrow(by_author)
+)$conf.int
+ci_has_made_resmat_available_vol <- prop.test(
+	sum(by_author$has_made_resmat_available_vol),
+	nrow(by_author)
+)$conf.int
+ci_uses_os_repos <- prop.test(
+	sum(by_author$uses_os_repos),
+	nrow(by_author)
+)$conf.int
+
+tab_by_author <- by_author %>%
+	summarise(
+		`... has made research material available` = 
+			sprintf(
[…]

### 2024-04-17 code/table_functions.R

@@ -236,10 +236,11 @@ create_continuous_table <- function(df, var, groups = GROUPS) {
 }
 
 ttest_group_by_group <- function(df, var, groupvar, xg, yg) {
-	rv <- t.test(
-		as.numeric(df[df[, groupvar] == xg, var]), 
-		as.numeric(df[df[, groupvar] == yg, var])
-	)
+	x <- as.numeric(df[df[, groupvar] == xg, var]) %>% na.omit()
+	y <- as.numeric(df[df[, groupvar] == yg, var]) %>% na.omit()
+	if (length(x) <= 1) return(1)
+	if (length(y) <= 1) return(1)
+	rv <- t.test(x, y)
 	rv$p.value
 }
 
@@ -299,17 +300,28 @@ create_cross_tab_table <- function(df, var, cross_var, df_only = FALSE) {
 }
 
 create_pct_cross_tab_table <- function(
-		df, var, cross_var, resp_label = NULL, 
-		ctests = FALSE, ctests_level = 0.1, 
+		df, var, cross_var, include_total = FALSE, resp_label = NULL, 
+		ctests = FALSE, ctests_level = 0.1, drop_levels = "",
 		add_num_labels = TRUE, df_only = FALSE
 ) {
 	df$var <- as.numeric(df[[var]])
-	if (is.factor(df[[cross_var]])) {
-		df$cross_var <- droplevels(df[[cross_var]])
-	} else df$cross_var <- df[[cross_var]]
+	df$cross_var <- df[[cross_var]]
+	if (include_total) full_df <- df
+	if (drop_levels != "") {
+		df <- df %>% filter(! as.character(cross_var) %in% drop_levels) 
+	}
+	if (is.factor(df$cross_var)) df$cross_var <- droplevels(df$cross_var)
 	if (is.null(resp_label)) resp_label <- get_resp_label(var)
-	tab <- table(df$var, df$cross_var)
-	freqs <- data.frame(tab) %>%
+	if (is.numeric(df$cross_var)) df$cross_var <- as.factor(df$cross_var)
+	
+	tab_df <- data.frame(table(df$var, df$cross_var))
+	if (include_total) {
+		full_df$total <- "Total"
+		total_df <- data.frame(table(full_df$var, full_df$total))
+		tab_df <- bind_rows(total_df, tab_df)
+	}
+	
+	freqs <- tab_df %>%
[…]

### 2024-04-17 docs/paper.qmd
Added refs to survey dashboard

@@
 \textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{github.com/joachim-gassen/osacc}  \newline
+\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc/} \newline
 \textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
@@
 
-\centerline{--- Insert Table 2 about here ---}
-
 [^3]: We removed 41 authors because we found no email address, 41 authors because they appeared in the data twice with two author IDs but were the same person, 28 authors because they were a current member of one of our affiliated universities or academic research centers, 5 authors because they gave us advice for this study, 2 authors because they had passed away, and 1 author due to an incorrect email address.
@@
 Depending on this, the sample sizes for the descriptive analyses vary from 222 to 229 responses.
+
+\centerline{--- Insert Table 2 about here ---}
 
@@
 However, it seems likely that the study's all-European author team might have positively influenced the European response.
-While we control for geographical effects in our response (not-tabulated) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.
+While we control for geographical effects in our response (not-tabulated but available using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.
 
@@
 For a complete overview of the survey questions included in our study, please see Appendix A.
+Besides the findings that follow, all answers to these questions can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}.
 
@@
 The public GitHub repository at \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc} contains the data and the code of this project.
+
+To explore our survey data in more depth, we encourage the use of our [online survey dashboard](https://jgassen.shinyapps.io/osacc/).
+Using this dashboard, you can explore the response to all survey questions, partitioning it by respondents' demographics.
+
+\newpage
 

### 2024-04-26 docs/paper.qmd
Edits prior to next brown bag

@@
   | Accountants' Attitudes Towards Open Science^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management.
-We thank Kris Hardies and  audiences of workshops at University of Antwerp and Humboldt University Berlin for providing helpful feedback.
+We thank Kris Hardies as well as audiences at University of Antwerp, Humboldt University Berlin, and WHU for providing helpful feedback.
 Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged.
@@
 \singlespace
-Surveying a sample of scholars that have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs.
+Surveying a sample of scholars who have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs.
 Also, we are less familiar with the public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research.
@@
 ```
-\vspace{2cm}
-
-```{=tex}
+
+```{=tex}
+\vspace{0.5cm}
+\begin{center}
+\textbf{Preliminary and Incomplete}
+\end{center}
+\vspace{0.75cm}
 \begin{flushleft}
@@
 \textbf{Data Availability}: Data available in code repository \newline
-\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{github.com/joachim-gassen/osacc}  \newline
-\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc/} \newline
+\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc}  \newline
+\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc} \newline
 \textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
@@
 The first goal of the survey was to gauge the perceptions of accounting researchers regarding the reproducibility of influential findings in the accounting literature.
-Table 3 displays a detailed overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicating" to "reproducing" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community.
+Table 3 displays a detailed overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicate" to "reproduce" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community.
 Namely, the term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000].
-In contrast, the term"replication" may or may not have different interpretations for different researchers.
-For instance, experimental researchers it refers to a distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).
+In contrast, the term "replication" may or may not have different interpretations for different researchers.
+For instance, for experimental researchers it refers to a distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).
+
+<!-- Definition of replicability in the Fergusson et al study (from the survey materials on OSF): "For these questions, please define replication as a test of whether (a) new studies (b) on the same topic (c) in a broadly similar sample support the same results." --!>
 
@@
 The take-up started around 2018 compared to 2015-2016 for the other fields.
-This finding is also supported by Figure 4 showing that the take-up of pre-registration in accounting over time lags behind the other social science areas.
+This finding is also supported by Figure 5 showing that the take-up of pre-registration in accounting over time lags behind the other social science areas.
 

### 2024-04-26 docs/presentation.qmd
Added refs to survey dashboard
Edits prior to next brown bag

@@
 
-## Observational Data on Sharing Behavior: Author Level
-
-```{r, asis = TRUE}
-gt(tab_by_author) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
-
-## Observational Data on Sharing Behavior: Journal Level
-
-```{r, asis = TRUE}
-gt(tab_by_journal) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
-
-## Observational Data: Paper-level Sharing over Time
-
-```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
-p <- plot_resmat_sharing_over_cyear
-if (trr266_fonts_available) {
-	p + theme(text = element_text(family = "Calibri Light", size = 12))
-} else p
-```
-
 ## Reasons against Sharing (Close-Ended Question)
@@
 
+## Observational Data on Sharing Behavior: Author Level
+
+```{r, asis = TRUE}
+gt(tab_by_author) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+## Observational Data on Sharing Behavior: Journal Level
+
+```{r, asis = TRUE}
+gt(tab_by_journal) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+## Observational Data: Paper-level Sharing over Time
+
+```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
+p <- plot_resmat_sharing_over_cyear
+if (trr266_fonts_available) {
+	p + theme(text = element_text(family = "Calibri Light", size = 12))
+} else p
+```
+
+<!---
 ## Pre-Registration: Awareness Across the Social Sciences
@@
 ```
+--->
 
@@
 
-## Reasons Against Sharing
+## Reasons Against Sharing and Their Counter Arguments
 
@@
 \end{center}
+
+## Thank You!
+
+\begin{center}
+For additional descriptive analyses of our survey data, check out our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}.
+
+All code and data of this project are available on \href{https://github.com/joachim-gassen/osacc}{GitHub}.
+\end{center}

### 2024-10-26 docs/paper.qmd
presentation changes for brown bag
Pre SSRN

@@
 title: |
-  | Accountants' Attitudes Towards Open Science^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management.
-We thank Kris Hardies as well as audiences at University of Antwerp, Humboldt University Berlin, and WHU for providing helpful feedback.
+  | How does the Accounting Research Community
+  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management.
+We thank Kris Hardies as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback.
+Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings.
 Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged.
@@
   - \usepackage{csquotes}
+  - \usepackage{lscape}
+  - \usepackage{graphicx}
+  - \usepackage{pdflscape}
   - \renewcommand{\mkbegdispquote}[2]{\itshape}
+  - \usepackage{longtable}
+  - \usepackage{geometry}
+  - \geometry{a4paper, margin=1in}
+  - \usepackage{setspace}
 ---
@@
 pop <- read_csv("../data/external/invited_authors_anon.csv", show_col_types = FALSE)
+byu <- read_csv("../data/external/byu_author_data_anon.csv", show_col_types = FALSE)
 
@@
 source("../code/obs_data_analyses.R")
+
+gt_add_header_mpage_table <- function(x) {
+  x <- sub("\\\\midrule", "\\\\midrule \\\\endhead", x)
+  x
+}
+
 ```
@@
 \singlespace
-Surveying a sample of scholars who have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs.
-Also, we are less familiar with the public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research.
-Our respondents state that they are open to sharing and would likely share research materials under a hypothetical scenario, regardless of provided rationale and scope.
-They also believe that other accounting researchers, as well as editors, are in favor of research material sharing.
-However, they are skeptical about the actual prevalence of research material sharing in the accounting research community.
-In addition, they are more reluctant than researchers from neighboring fields to pre-register their study plans.
+To understand how the accounting research community thinks about open science, we survey a sample of scholars who have published in leading accounting journals.
+Building on a voluntary disclosure-themed discussion of the costs and benefits of open accounting research, we document that accounting researchers tend to be more skeptical about the reproducibility of their influential findings than researchers from other social science areas are about theirs.
+Also, they are less familiar with the public sharing of research materials and pre-register their study designs less often.
+While they believe that accounting researchers in general and editors in particular favor research material sharing, they are skeptical about its actual prevalence in the accounting research community.
+We contrast these survey results with observational data, documenting that research material sharing is indeed relatively rare and often linked to journals with data and code sharing policies.
 We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
@@
 ```
-
 ```{=tex}
 \vspace{0.5cm}
-\begin{center}
-\textbf{Preliminary and Incomplete}
-\end{center}
-\vspace{0.75cm}
 \begin{flushleft}
-\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Pre-Registration, Survey \newline
+\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Research Material Sharing, Pre-Registration, Survey \newline
 \textbf{Data Availability}: Data available in code repository \newline
@@
 
-Cumulative science builds on reproducible research.[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated open science methods like public sharing of research materials and the pre-registration of study plans as potential strategies to improve the reproducibility of our work.
-Prior work across the social sciences has documented an overall uptake of open sciences approaches across several disciplines [@FLCPSWMBP_2023].
-We contrast these findings with a survey that we conducted among accounting researchers to explore the perceptions and attitudes toward open science in our field.
-
-[^1]: While in the survey itself, we use the term reproducibility without an exact definition, throughout this article, we follow the notion of @NSF_2015 to define reproducibility as the "ability of a researcher to duplicate the results of a prior study using the same materials and procedures as were used by the original investigator" while replicability "refers to the ability of a researcher to duplicate the results of a prior study if the same procedures are followed but new data are collected".
-For a more in-depth discussion of the related terminological debate, see @GFI_2016.
-The key reason why we do not provide an exact definition in the survey is that the differences between reproducibility and replicability are subtle and vary across accounting subfields.
-For archival studies, reproducibility and replicability should be essentially the same, while for experimental studies they clearly differ.
-
-Based on the responses of `r nrow(sd)` published accounting researchers, we find that our attitudes towards open science clearly differ from those of other researchers in the social sciences.
-Most prominently, we tend to hold a generally more critical view of the reproducibility of our influential work.
-Compared to the fields of economics and sociology, for example, we are about half a point more skeptical about the reproducibility of the influential work in our field on a 5-point Likert scale.
-Exploring this assessment across our respondents' demographics, we find this skepticism to be relatively stable.
-Analytical and qualitative researchers are somewhat more pessimistic than the other methodologies.
+Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as were used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods.
+Open science implies conducting research in ways that allow others to collaborate and contribute.
+Two central open science methods that have been put forward as strategies to improve the reproducibility of our work are the public sharing of research materials and the pre-registration of study plans.
+Over the last years, there has been a significant uptake of these open sciences methods in social science areas outside of accounting [@FLCPSWMBP_2023].
+
+Research material sharing and pre-registrations can be understood as disclosure mechanisms that allow researchers to contribute public goods to the research community while also signaling the quality of their work.
+However, limited individual benefits and significant direct as well as indirect costs make it likely that researchers, on average, will rationally under-engage in these activities, potentially resulting in a socially sub-optimal under-provision of public research materials and on overall lacking research transparency.
+Following these thoughts and building on prior literature in neighboring fields, we conduct a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.
+
+Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes towards open science clearly differ from those of other social science researchers.
+Most prominently, accounting researchers tend to hold a generally more pessimistic view of the reproducibility of influential work within their field.
+Compared to economists and sociologists, for example, accounting researchers are about half a point more skeptical on a 5-point Likert scale.
+Exploring this assessment across the respondents' demographics, we find this skepticism to be relatively stable.
+Analytical and qualitative researchers are somewhat more pessimistic.
 Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.
 
-Given this finding, one would expect accounting researchers to take a more proactive stance and embrace two prominent open science approaches that methodological work has identified to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.
-Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, we accounting researchers are somewhat less familiar with this activity.
-Also, we find it somewhat less important.
-Familiarity is generally largest for respondents using archival, field, and experimental methods and smallest for respondents using qualitative methods, which also perceive sharing as less important.
-
-Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in our perceived (prescriptive) importance of research material sharing, our stated willingness to share research materials, and our (descriptive) perception about actual sharing behavior.
-In a hypothetical scenario, the average stated likelihood for sharing research materials by our respondents is relatively high (i.e., 72%), and this likelihood is more or less unaffected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope (public versus private sharing).[^2] Also, 50% of our respondents state that they, at least sometimes, publicly share their research materials.
-In addition, our respondents believe that about 44% of us favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials.
-
-[^2]: We pre-registered this experimental part of our study. The pre-registration materials can be accessed [here](https://osf.io/frmzt/).
-
-All this sounds comforting and consistent with a general supportive stand of the accounting community towards public research material sharing.
-However, when asked about respondents' perceptions about actual sharing behavior, the percentage comes down to a much more sobering 28%.
-This sober number and the gap it reveals differ significantly across the different accounting methodological areas.
-Analytical researchers have the narrowest gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials).
+Given this finding, one would expect accounting researchers to take a proactive stance and embrace two prominent open science methods that are expected to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.
+Turning first to the public sharing of research materials, we document that, again compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important.
+Familiarity is largest for respondents using archival, field, and experimental methods and lowest for respondents using qualitative methods, who also perceive the sharing of research materials as less important.
+
+Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in accounting researchers' perceived (prescriptive) importance of research material sharing, their stated willingness to share research materials, and their (descriptive) perception about actual sharing behavior in the accounting research community.
+57% of our respondents state that they, at least sometimes, publicly share their research materials.
+In addition, our respondents believe that about 44% of them favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials.
+Although this sounds comforting and consistent with a general supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community.
+This assessment and the gap it reveals differ significantly across methodological areas.
+Analytical researchers have the most narrow gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials).
 Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share).
@@
 
-Using observational data from a country-stratified random sample of `r nrow(authors)` authors from our target population to contrast these perceptions with actual behavior, we find at least some evidence for research material sharing for 39 % of this random sample.
-This number is largely in line with the self-reported figures but masks that research material sharing in accounting seems to be largely an occasional compliance activity: Only for 7.5 % of the papers that we analyze we find evidence for research material sharing and when we exclude Journal of Accounting Research and Management Science, two journals with data and code policies in place, the share of authors for which we document research material sharing evidence drops from 39 to 23 %.
-
-In light of these numbers, it is a logical next step to explore the main reasons against sharing research materials.
-Overall, the most commonly stated reasons for not sharing research materials are the proprietary nature of the used data (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%).
-Additionally, 34% of respondents state that there is no need for sharing as their data is already publicly available.
-Unsurprisingly, the reasons clearly differ across methods.
+Regarding pre-registration, accounting researchers seem as familiar with the concept as other social science researchers.
+However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%).
+Their trust in pre-registered work is generally comparable with other social science researchers but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rate of pre-registration).
+A detailed look into differences across methodological fields also reflects this, as we find that experimental researchers use pre-registration most (28%) and express the strongest belief that it increases the trustworthiness of research.
+
+To contrast these perceptions from our survey with actual behavior, we gather additional observational data from a country-stratified random sample of `r nrow(authors)` authors of our target population.
+We find evidence for at least some form of research material sharing for 39% of the authors in this sample.
+This number is similar to the self-reported perception of actual research material sharing in our survey (i.e., 38%).
+However, when we inspect the observational data further, we find that research material sharing in accounting is largely an occasional compliance activity.
+For instance for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing.
+Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%.
+Furthermore, we document very few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.
+
+In light of these numbers, a logical next step is to explore the main rationales for and against sharing research materials.
+We do so based on a short experimental design using a hypothetical scenario and by using our survey data.[^2] In our hypothetical scenario involving a fellow researcher requesting access to participants' research materials, our participants state that they would be very likely to share on average (mean probability is 72%).
+We find no evidence that this probability is affected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope of the sharing decision (public versus private sharing).
+Based on the verbal response of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general.
+Also, they share because they want to support their fellow researchers.
+The most commonly stated reasons for not sharing research materials are the proprietary nature of the data used (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%).
+The reasons differ across methods.
 For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).
 
-Regarding pre-registration, it seems that we accounting researchers are at least as familiar with the concept as other social science researchers.
-However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%).
-Our trust in pre-registered work is generally comparable with other social scientists but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rates of pre-registration).
-A detailed look into differences among the different methodological fields within accounting also reflects this, as we find that experimental researchers use pre-registration the most (28%) and express the strongest belief that the practice increases the trustworthiness of research.
-
 Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it.
-This results in these tools currently being less established in the accounting domain than in other fields.
-In addition, the challenges that hinder reproducibility and the potential effectiveness of open science tools vary across methodological paradigms.
+This is consistent with these tools currently being less established in the accounting domain than in other fields.
+The challenges that hinder reproducibility and the potential effectiveness of open science methods vary across methodological paradigms.
 Qualitative research faces different challenges than archival quantitative work, and they both differ again from experimental studies.
@@
 
-## Survey Methodology and Variable Measurement
-
-### Survey Design and Administration
-
-To collect the attitudes of accounting researchers towards open science, we conducted a survey among members of the academic accounting community.
-The survey has been designed using oTree [@CSW_2016].
+## Expectations and Study Design
+
+### Costs and Benefits of Open Accounting Research
+
+Accounting is a field within the social sciences.
+As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting.
+In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@BCLW_2010].
+For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration.
+Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good.
+To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and very likely also the quality of research.
+Even if they are not really reusable or reusing them would be prohibitively costly, they still reduce the costs of reproducing the original work, thereby reducing assurance costs.
+As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions) resulting in better financial reporting quality (better research).
+
+This means that similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large.
+While intrinsic motivation for good research can be expected to be a strong determinant for individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public.
+So, are there any private benefits of research material sharing?
+Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output.
+First, it increases the likelihood that mistakes, conditionally on being present, are being detected.
+As it seems safe to assume that such incidents impose a cost on sharing researchers, this should increase their incentives to increase research quality prior to sharing.
+Second, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study.
+Finally, uncovered mistakes are an important learning opportunity, likely improving research quality in the long run.
+
+Based on these arguments, there are reasons to believe that voluntary research material sharing can act as a signal for research quality, creating an incentive for researchers to use it to signal the quality of their work in the publishing and career process.
+In ideal circumstances, we should obtain the well-known unraveling result where researchers even share and improve low-quality research because the research community would otherwise assume the worst [@M_1981].
+One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the contemporary disclosure literature.
+Thus, for research materials sharing to be viable it is important that the costs of sharing are sufficiently low, especially for researchers that produce high quality work.
+Thus, it critically hinges on the above quality assurance process.
+Also, it depends on the direct and indirect costs of research material sharing to be bearable and to be at least comparable for high and low quality researchers.
+
+The direct costs of research material sharing can be sizable.
+Preparing data, code and research procedures for dissemination requires time.
+While this time can be expected to also have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work.
+Another important factor to consider is the cost of maintaining publicly available materials.
+While some replication packages or similar materials are static in nature and require only limited maintenance, data and code packages can require ongoing updating and support activities.
+One important aspect of maintenance costs is that they increase significantly with public demand.
+As demand is directly linked to the scientific impact of the underlying work it can be argued that high maintenance cost sharing activities are likely to also be high benefit activities.
+
+The indirect costs of research material sharing are first and foremost linked to the quality assurance process outlined above.
+Flaws in publicly shared research materials can trigger more behavioral effects (shame, regret) but also reputation costs.
+Another important aspect are proprietary costs from scientific competition.
+While likely to be positive from the societal perspective, the indirect individual costs of being "scooped" for an interesting follow-up project can be sizable.
+Finally, there is also the possibility of unethical misuse of shared research materials.
+Malevolent researchers might use shared materials without proper attribution or use it with a strategy of "reverse p-hacking", meaning creating reproductions or replications that communicate a biased picture of the overall evidence to increase their chances for publication.
+
+Rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs.
+Whether this happens will critically depend on whether the signaling mechanism outlined above unfolds.
+In a credence good market like research, signaling is a key mechanism to avoid market failure.
+Based on the discussion above, a critical aspect could be the proprietary cost of competition as one could argue that this cost is higher for high quality researchers with innovative ideas than for low quality researchers that will likely face limited demand for their materials.
+Also the risks of reputation costs or misuse of materials could be higher for high quality researchers.
+On the other hand, it can be argued that direct costs should be lower for high quality researchers because of superior skills.
+Finally, outside options should be generally higher for high quality researchers meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.
+
+The discussion should sound somewhat familiar to those that study voluntary disclosures by firms.
+What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs.
+Instead, they are employed by academic institutions or act as civil servants.
+This can to some extend mute the relevance of the benefits and the costs outlined above, at least for those researchers that hold tenured positions.
+In addition, the employing institutions might also interact with the decision whether or not to make research materials available.
+They are designing performance and tenure evaluation criteria that incentivize researchers.
+Also, they compensate researchers for their time and they provide them with infrastructure that influences and at times drastically reduces the direct costs of research material sharing.
+They might even hold property rights on the intellectual capital that their employees generate.
+Based on the public announcements of many leading academic institutions, it seems as if these are generally advocating the positive externalities of research material sharing.
+However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they are valuing individual research achievements in form of publications and only rarely publicly available research materials.
+
+Finally, publishers and journals are influential for research material sharing decisions as well.
+Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision to a mandatory disclosure requirement.
+While journals also compete for the best papers and it is an interesting question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.
+
+### Research Questions and Survey Design
+
+Following the discussion above, we designed our survey to address three overlapping research questions.
+
+1.  How does the accounting research community assess the reproducibility of their influential work?
+
+2.  What are the views of the accounting research community about research material sharing and pre-registration, two prominent open science methods to increase the reproducibility of research?
+
+3.  What are the (perceived) costs and benefits of research material sharing?
+
+The first two questions are descriptive in nature.
+Assuming that the signaling mechanism above or other incentives have not succeeded in removing all insecurity about the reproducibility of influential accounting work, we expect to find some variation in our response with regard to research question one.
+More importantly, we want to compare the response of our sample with responses by researchers from other social science fields.
+The second question explores whether accounting researchers believe that research material sharing and pre-registration are viable strategies to increase the reproducibility of research.
+Again, comparing the views of accounting academics with the views of neighboring fields will be instrumental here.
+
+The third question strives to understand the potential causes behind these assessments.
+Using a small experimental component, our survey tests whether two aspects of a hypothetical sharing request, its rationale (collaboration or control) and its scope (public versus private), affect the stated hypothetical likelihood of sharing.
+Our motivation for the treatments is that the rationale should shift the focus from benefits (collaboration) to costs (control) while the scope treatment should manipulate the salience of indirect costs.
+Besides studying the effect of these two experimental treatments, we also use verbal and structured survey response data to uncover perceived benefits and costs from research material sharing.
+
+To verify whether the assessments provided by our survey participants are consistent with their behavior in the field, we also conduct an observational study that uses data from 100 authors of our target population to contrast the survey response with the actual research material sharing and pre-registration behavior in the field.
+
+To ensure that our findings with respect to research questions one and two are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], published in Nature Communications.
+Similar to our survey, this study solicits the views of published researchers and PhD students on reproducibility, research material sharing, and pre-registration.
+However, there are key differences between the depth and target audience of our study and the study of @FLCPSWMBP_2023, warranting some adjustments.
+The latter lasted approximately 45 minutes and had a compensation element rewarding respondents for their participation.
+Our study, in contrast, is anonymous and has been designed to be completed in less than 10 minutes.
+It includes only mild incentivization in the form of a donation to UNICEF.
+Regardless of our adaptions, the ordering, phrasing, and answering scales of questions in our survey are similar.
+The adaptions enable us to considerably shorten the survey and to ensure that accounting researchers can relate the questions to their commonly accepted research practices.
+We pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions.
+Appendix C includes a matching table providing an overview of every question and answer scale that we adapted from @FLCPSWMBP_2023.
+
+Our survey has been designed using oTree [@CSW_2016].
+The first stage of the survey includes questions about respondents' views on publicly sharing research materials, which we describe as comprising data, code, and research procedures.
+Specifically, we ask respondents about their familiarity with the public sharing of research materials and their views of its importance.
+We also ask them about their perceptions of the prevalence of sharing in the accounting research community, how often they tend to share, and whether they plan to share in the future.
+Conditional on whether respondents indicate that they do not always share, we also ask them for the reasons behind not sharing.
+Lastly, we ask respondents to estimate what percentage of accounting researchers favor sharing and their approximation of the percentage of editors of the top six accounting journals that believe sharing increases the value of a manuscript.
+
+The second stage of the survey features a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023.
+First, we ask respondents about their confidence in the reproducibility of accounting research.
+We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible.
+Next, we ask the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other).
+
+After eliciting respondents' perceptions on reproducibility, a set of questions explores their familiarity and experience with the practice of pre-registration.
+Lastly, we ask them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research.
+The survey ends with a few demographic questions.
+For a complete overview of the survey questions included in our study, please see Appendix A.
+All answers can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard} and the data itself are available in our public \href{https://github.com/joachim-gassen/osacc/}{GitHub repository} .
+
+### Survey Administration and Response Sample
+
 To recruit respondents for our survey, we identified authors who published in the "Top 6" accounting journals, i.e., Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review, over the period 2016 to 2021.
-We chose these six accounting journals because they are commonly known to be top accounting journals within the academic accounting community.
+We chose these six accounting journals because they are commonly characterized as the leading accounting journals within the academic accounting community.
 We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community.
-Yet, we believe that, taken together, these journals provide us with a representative list of publishing accounting academics.
-We started compiling the list of authors from 2016 because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017].
-After receiving approval from an ethical review board, also guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total of three reminders.
+Yet, we believe that, taken together, these journals provide a sufficiently broad target population of accounting academics.
+
+We start compiling the list of authors from 2016 because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017].
+After receiving approval from an ethical review board and guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total of three reminders.
 We allowed potential respondents to opt out of future emails every time we reached out to them.
-Please see Appendix A for the invitation emails.
+Please see Appendix A for the invitation emails and all reminders.
 
@@
 
-Table 1 displays our sample selection procedures.
-Of the 2,660 potential respondents we identified, we excluded 118 for various reasons.[^3] Furthermore, for 206 emails bounced, we received a notification that the email address was unreachable.
-Of the remaining 2,336 successfully reached accounting researchers, 391 started the study (15,4% of the total emails sent), 254 partially completed the study (10,9% of the total emails sent), and 222 fully completed the study (8,7% of the total emails sent).[^4] Table 2 displays our final sample's demographics and characteristics.
-Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specialize in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).
-
-[^3]: We removed 41 authors because we found no email address, 41 authors because they appeared in the data twice with two author IDs but were the same person, 28 authors because they were a current member of one of our affiliated universities or academic research centers, 5 authors because they gave us advice for this study, 2 authors because they had passed away, and 1 author due to an incorrect email address.
-
-[^4]: As the dependent variable of our hypothetical scenario analysis outlined below is the first data we collect, 254 is the sample size for this analysis.
-For the descriptive analyses, we settle for the number of participants that answered the respective question and, if applicable, also provided the necessary demographics for cross-sectional splits.
-Depending on this, the sample sizes for the descriptive analyses vary from 222 to 229 responses.
+Table 1 presents our sample selection procedures.
+Out of 2,660 potential respondents identified, 118 were excluded due to operational reasons.[^3] Additionally, 206 respondents' initial emails bounced, indicating unreachable email addresses.
+Among the remaining 2,336 successfully contacted accounting researchers, 391 initiated the study (15.4% of the total emails sent), 254 partially completed it (10.9% of the total emails sent), and 222 fully completed it (8.7% of the total emails sent).
+For our analyses, we employed a floating sample, which dynamically changes based on specific criteria, to maximize the use of the available data.
+For most descriptive analyses, we relied on the number of respondents who completed the entire study (n = 222).
+However, for certain descriptive analyses, depending on the specific question, we utilized a broader sample (n = 229) as seven respondents decided to leave out some of the demographic questions.
+Since our survey experiment component forms the first part of the study, we use the sample of respondents who completed the study up to that point (n = 254) for analysis.
 
@@
 
+Table 2 displays response demographics and characteristics based on a sample of up to 229 observations.
+Panel A reveals that the majority of the respondents is male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).
 Panel B of Table 2 contrasts our respondent sample with our sampling population.
-Given the anonymity of our response and the data that we can collect about our population, we can only compare the geographic dispersion of our sample.
+Given the anonymity of our response and the data that we can collect about our population, we can only directly compare the geographic dispersion of our sample.
 Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample.
@@
 
-### Variable Measurement
-
-To ensure that our findings are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], which has been recently published in Nature Communications.
-Similar to our survey, this study solicits the views of published researchers and PhD students on reproducibility, research material sharing, and pre-registration.
-Given that it differs in depth (approximately 45 minutes while our survey was designed to be completed in less than 10 minutes) and data collection procedure (confidential with compensation element while we use an anonymous survey with mild incentivization), we had to make some adjustments.
-However, the ordering and phrasing of questions in our survey are similar, and their content and answer scales are identical or differ in a negligible way.
-Specifically, we decided to alter the framing and expand some of the questions to make it easier for accounting researchers to understand the questions and connect them to their commonly accepted research practices.
-We also pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions.
-
-The first stage of the survey included questions about respondents' views on publicly sharing research materials, which we described as comprising data, code, and research procedures.
-Specifically, we asked respondents about their familiarity with the public sharing of research materials and their views of their importance.
-We also asked them about their perceptions of the prevalence of sharing in the accounting research community, how often they tended to share, and whether they planned to share in the future.
-Conditional on whether respondents indicated that they do not always share, we also asked them for the reasons behind not sharing.
-Lastly, we asked respondents to estimate what percentage of accounting researchers favor sharing and their approximation of the percentage of editors of the top six accounting journals that believe sharing increases the value of a manuscript.
-
-The second stage of the survey featured a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023 .
-First, we asked respondents about their confidence in the reproducibility of accounting research.
-We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible.
-Next, we asked the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other).
-Subsequently, we asked respondents about their familiarity and experience with the practice of pre-registration.
-Lastly, we asked them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research.
-We completed the survey by asking a few demographic questions that are primarily presented in Table 2.
-For a complete overview of the survey questions included in our study, please see Appendix A.
-Besides the findings that follow, all answers to these questions can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}.
+We further evaluate the representativeness of our sample by comparing it to a sample of published authors on the BYU accounting rankings platform [@SW_2023].
+Specifically, the BYU accounting rankings rank individual authors based on classifications of peer-reviewed articles in 12 accounting journals since 1990.
+We contacted the team behind the BYU rankings, and they generously provided their data to us.
+The data includes `r format(nrow(byu), big.mark = ",")` authors and information on their methodologies as well as subfields.
+As these data are based on the papers contained in the BYU database as well as by self-classification by authors, one author can be associated with several subfields and methodologies in the BYU data.
+Therefore, we compare 2,114 classified methodologies in the BYU sample to 229 primary methodologies in our sample.
+Also, we compare 2,877 classified subfields in the BYU sample to 229 primary subfields in our sample.
+
+\centerline{--- Insert Figures 1 and 2 about here ---}
+
+Figure 1 reveals the frequency distributions of subfields in the BYU and our sample.
+We can observe some differences between these two distributions.
+First, our sample has disproportionately more mentions of authors publishing in financial accounting and reporting and managerial accounting than the BYU sample (49% versus 36%).
+As a result, we see disproportionately fewer authors working in the other subfields in our sample.
+A chi-square test confirms the frequencies of the two distributions significantly vary (chi-square = 36.415, two-tailed p-value \< 0.001).
+Figure 2 reveals the frequency distributions of the methodologies in the BYU and our sample.
+These two frequency distributions are very similar; a little over half of the observations fall into the Archival/Field category for both samples.
+About one-fifth of the sample falls into the experimental category, and the rest is comprised of analytical and other methodologies.
+A chi-square test does not reject the null that the two frequency distributions are the same (chi-square = 2.270, two-tailed p-value = 0.518).
 
@@
 
-The first goal of the survey was to gauge the perceptions of accounting researchers regarding the reproducibility of influential findings in the accounting literature.
-Table 3 displays a detailed overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicate" to "reproduce" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community.
-Namely, the term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000].
-In contrast, the term "replication" may or may not have different interpretations for different researchers.
-For instance, for experimental researchers it refers to a distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).
-
-<!-- Definition of replicability in the Fergusson et al study (from the survey materials on OSF): "For these questions, please define replication as a test of whether (a) new studies (b) on the same topic (c) in a broadly similar sample support the same results." --!>
+The first research question of our study is to explore how accounting researchers perceive the reproducibility of influential findings in their field.
+Table 3 provides a comprehensive overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers with those of researchers in other disciplines as recorded by @FLCPSWMBP_2023, based on their question, "How confident are you that the influential research findings in \[discipline\] would replicate?" Notably, we adapted the wording in this question from "replicate" to "reproduce" to ensure clarity for our audience, recognizing the nuanced distinctions between these terms across various research methodologies.
+The term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000].
+It implies the ability to recreate the results of prior studies using the same materials, procedures, and data as were used by the original researchers [@NSF_2015].
+In contrast, the term "replication" has different interpretations for different fields.
+For instance, for experimental researchers, it refers to a distinct activity than reproduction (i.e., repeating an experimental study with new participants), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same or similar data using the same procedures).
+In turn, the definition that @FLCPSWMBP_2023 use for replication ("test of whether new studies on the same topic in a broadly similar sample support the same results.") seems relatively close to what we believe the common understanding of reproduction is in the area of accounting is.
+If anything, our notion of reproduction seems less demanding than the replication definition by @FLCPSWMBP_2023.
 
@@
 
-The results in Table 3 suggest that we accounting researchers hold a generally more critical view of the reproducibility of our influential findings.
-Compared to researchers in the fields of economics and sociology, accounting researchers who took part in our survey are about a half a point more skeptical about the reproducibility of their influential work (on a 5-point Likert scale).
+The results in Table 3 reveal that accounting researchers generally hold a more critical view of the reproducibility of our influential findings.
+Compared to their peers in economics and sociology, accounting researchers exhibit a greater degree of doubt about the reproducibility of their influential work, with a difference of about half a point on a 5-point Likert scale.
 This difference is less stark when we compare accounting researchers to researchers in the fields of Political Science and Psychology.
 In a field fixed effect regression, in which we use Accounting as the baseline, we find that all four fixed field effects are statistically different from zero (two-tailed p-value \< 0.01).
-Hence, the field of Accounting is generally more skeptical about the reproducibility of its research than other social science fields.
-
-\centerline{--- Insert Figure 1 about here ---}
-
-Figure 1 visually represents the data from Table 3 by plotting them on a horizontal axis and aligning them around a neutral midpoint.
-The figure shows that accounting researchers are the most skeptical (i.e., "Not at all confident") about the reproducibility of influential findings in their field (10.5%).
-This difference is much higher than the percentage of skeptics reported by @FLCPSWMBP_2023: 0.7% for Economics, 2.1% for Political Science, and 1.1% for Psychology, and 1.3% for Sociology.
-The field of Accounting, therefore, also has the lowest percentage of non-skeptics (i.e., researchers who are either moderately or extremely confident in the reproducibility of influential findings).
+This skepticism is consistent with us accountants being more concerned about research quality hinting at the existence of a credence-good problem that open science methods are designed to address.
+
+\centerline{--- Insert Figure 3 about here ---}
+
+Figure 3 visually represents this skepticism, showing that 10.5% of accounting researchers are "Not at all confident" about the reproducibility of influential findings in their field.
+This percentage starkly contrasts the skepticism reported by economists (0.7%), political scientists (2.1%), psychologists (1.1%), and sociologists (1.3%), as found by @FLCPSWMBP_2023.
+In addition, this figure reveals that Accounting also has the lowest percentage of non-skeptics (i.e., researchers who are either moderately or extremely confident in the reproducibility of influential findings).
 That is, Accounting has about 39.3% non-skeptics, while Economics has 61.1%, Political Science has 45.8%, Psychology has 41.3%, and Sociology has 61.7%.
-The differences with Economics and Sociology again are the largest, while the differences between Political Science and Psychology are smaller.
-
-Next, we compare assessments of accounting researchers regarding reproducibility across different methodologies.
+The differences to Economics and Sociology, again, are the largest, while the differences to Political Science and Psychology are smaller.
+
+To delve deeper, we examine the assessments of reproducibility across different methodologies within Accounting.
 Accounting is not only a diverse discipline in terms of orientation and topic but also in terms of the methodologies its researchers employ.
@@
 We asked respondents which of those categories best described their main methodological area, enabling us to categorize them in the data.
-Table 4 displays their assessments regarding the reproducibility of influential findings across three panels.
+Table 4 presents their assessments regarding the reproducibility of influential findings across three panels.
 Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.
@@
 The findings in Table 4 Panel A suggest that analytical and qualitative researchers are more pessimistic and skeptical about the reproducibility of influential findings in accounting as a whole than accounting researchers using other methodologies.
-In particular, analytical researchers are significantly less confident about the reproducibility of influential findings in accounting in general than researchers in the Archival/Field and Experimental categories (two-tailed p-value \< 0.100).
-When turning to respondents' assessments of the reproducibility of influential findings in their own methodological area, we find that analytical researchers have the most confidence in the influential findings within their methodological area as their average confidence is statistically higher from those reported by the average reported for the other four methodologies (two-tailed p-value \< 0.100).
-Qualitative research reports a significantly lower average confidence than Analytical, Archival/Field, and Experimental Research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).
-
-Panel C reports the "assessment gap," which captures the difference in assessments of the reproducibility of influential findings in respondents' own methodological area versus accounting in general.
+In particular, analytical researchers are significantly less confident about the reproducibility of influential findings in accounting in general compared to those using Archival/Field and Experimental categories (two-tailed p-value \< 0.100).
+Interestingly, when evaluating their own methodological areas, analytical researchers display the highest confidence levels, as their average confidence is statistically higher than those reported by the other four methodologies (two-tailed p-value \< 0.100), suggesting a discrepancy between their views on the field as a whole and their specific research approaches.
+Qualitative research reports significantly lower average confidence than Analytical, Archival/Field, and Experimental Research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).
+
+Panel C presents the "assessment gap," which captures the difference in assessments of the reproducibility of influential findings in respondents' own methodological area versus accounting in general.
 A higher (lower) assessment gap indicates that respondents are more (less) confident in the reproducibility of influential findings in their methodological area compared to accounting in general.
-The findings of Panel C report that analytical researchers report the largest assessment gap, implying they are relatively skeptical about the reproducibility of influential findings in accounting as a whole compared to their own methodology.
+The findings of Panel C report that analytical researchers report the largest assessment gap, implying greater skepticism about the field's reproducibility as a whole compared to their own methodology.
 The average assessment gap reported for the Analytical category is also statistically different from the averages reported in the other four categories (two-tailed p-value \< 0.100).
-The other four categories exhibit no clear assessment gap (with averages hovering around zero) and are statistically indistinguishable from each other.
+In contrast, the other methodological categories show no significant differences, suggesting a more uniform view across different research approaches within accounting.
 
@@
 
-Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field and with some variation across methodologies.
-Given the skepticism, we have observed so far, one would expect accounting researchers to take a more proactive stance on open science approaches, like the practice of research materials sharing.
-The survey assessed respondents' evaluations of the practice of research materials sharing next.
-Specifically, we asked respondents two questions about the practice of sharing research materials, which we defined as the practice of sharing data, code, and research procedures.
-These two questions were also close adaptions of the survey done by @FLCPSWMBP_2023.
+Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field relative to neighboring fields.
+Given this skepticism and following our discussion in section 2, one might expect accounting researchers to take a proactive stance on open science approaches, particularly regarding the sharing of research materials.
+Following the old proverb by Supreme Court Justice Luis Brandeis "sunlight is the best disinfectant" one would expect accountants to support increased transparency in research.
+The survey assesses this argument by asking respondents two questions about the practice of sharing research materials, which we define as the practice of sharing data, code, and research procedures.
+These two questions are also close adaptions of the survey done by @FLCPSWMBP_2023.
 
@@
 
-The first question assesses respondents' familiarity with the practice of research materials sharing: "How familiar are you with the practice of publicly sharing research materials (i.e., data, code, and research procedures) for a completed study?"[^5] Table 5 Panel A shows respondents' answers to the question about familiarity, including benchmark answers of respondents in different fields originating from the survey by @FLCPSWMBP_2023 .
+The first question assesses respondents' familiarity with the practice of research materials sharing: "How familiar are you with the practice of publicly sharing research materials (i.e., data, code, and research procedures) for a completed study?"[^4] Table 5 Panel A shows that accounting researchers are generally less familiar with research materials sharing than their counterparts in other social sciences from the survey by @FLCPSWMBP_2023.
 Generally speaking, academics in the social sciences report being relatively aware of and familiar with the practice of research material sharing.
 However, the results do suggest that, compared to each of the other four fields in the social sciences, accounting researchers are significantly less familiar with the practice (two-tailed p-value \< 0.010).
-The second question captures respondents' assessed importance of research material sharing: "To what extent do you believe that publicly sharing research materials (i.e., data, code, and research procedures) is important for the advancement of accounting research?"[^6] Table 5 Panel B suggests that accounting researchers also find the practice of research material sharing less important than academics in each of the other four fields (two-tailed p-value \< 0.010).
-
-[^5]: The corresponding question in @FLCPSWMBP_2023 is "Have you ever heard of the practice of publicly posting data or code online for a completed study?" We deviated from this original question by using the term "research materials" and defining it as "sharing data, code, and research procedures" in our version of the question because we wanted to cover all aspects of this Open Science practice in one question.
-
-[^6]: The corresponding question in @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting data or code online is important for progress in \[Discipline\]?" We adapted this question for terminological consistency across our survey.
-
-\centerline{--- Insert Figure 2 about here ---}
-
-Figure 2 reproduces the data reported in Table 5 Panel B by presenting the frequencies along horizontal axes and centering them to a neutral midpoint.
-It reveals that, compared to the social science disciplines, relatively fewer respondents in our sample are strong supporters of the practice of research material sharing.
-That is, of the total sample, 39.6% of the respondents consider it "very important" (Accounting) versus 51.7% in Economics, 48.1% in Political Science, and 43.8% in Psychology.
-Only Sociologists report a lower percentage of strong supporters (i.e., 29.4%) than the accounting researchers in our sample.
+The second question captures respondents' perceived importance of research material sharing.
+[^5] Table 5 Panel B suggests a similar trend, whereby accounting researchers consider this practice less important than researchers in other social sciences (two-tailed p-value \< 0.010), a finding that underscores potential barriers to the adoption of open science principles.
+
+\centerline{--- Insert Figure 4 about here ---}
+
+Figure 4 graphically presents these findings, showing the frequencies along horizontal axes and centering them to a neutral midpoint.
+Only 39.6% of the accounting researchers deem research material sharing "very important" compared to higher percentages in other fields like Economics (51.7%), Political Science (48.1%), and Psychology (43.8%).
+Sociologists report a lower percentage of strong supporters (29.4%) than the accounting researchers in our sample, suggesting varied attitudes towards open science across the disciplines.
 
@@
 
-Next, we examine familiarity with and perceived importance of research materials sharing across methodologies within accounting.
-We again distinguish between five methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
+We further examine attitudes, namely familiarity with and the perceived importance of research materials sharing across methodologies within accounting.
+Again, we distinguish between five methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
 Table 6 displays assessments of the practice of research material sharing using two panels.
@@
 Moreover, we also find that respondents using Qualitative methods are less familiar with research material sharing compared to all four other categories (two-tailed p-value \< 0.100).
-Panel B shows that there are few significant differences in terms of the assessed importance of research material sharing across the methodologies.
+Panel B shows that there are few significant differences in terms of the perceived importance of research material sharing across the methodologies.
 Only respondents in the Archival/Field category assess research material sharing as significantly more important than respondents using the Qualitative and Survey categories.
-
-### Sharing Research Materials - Rationale and Scope
-
-So far, we document that, compared with researchers from other social sciences, we accounting researchers are less familiar with research sharing and find it less important.
-Since we also wanted to understand what drives accounting researchers' willingness to share research materials, our survey contained a hypothetical scenario in which another (hypothetical) fellow researcher asked respondents whether they would like to share the research materials (i.e., data, code, and research procedures) of a paper they published in an academic journal.
-
-#### Hypothetical Scenario - Design
-
-We manipulated two between-subjects factors in the hypothetical scenario.
-First, we manipulated the rationale used by the fellow researcher requesting access to the researcher's materials.
-In the *collaboration rationale* treatment, the fellow researcher requested access to researcher materials to understand the work better and build on it.
-In the *control rationale* treatment, the fellow researcher requested access to verify and potentially correct the research.
-Second, we manipulated whether the fellow researcher requested the research materials to be shared publicly (i.e., *public scope*) or privately (i.e., *private scope*).
-Respondents were randomly assigned to receive only one stated rationale (*control* *rationale* versus *collaboration rationale*) and one sharing scope (*public* versus *private scope*).
-We measured respondents' willingness to comply with the fellow researcher's request on a scale ranging from 0% (definitely not) to 100% (definitely).
+Overall, these findings indicate that accounting researchers are, at the very least, not strong believers in the signaling value of research material sharing.
+This might be because they are simply relatively more unaware of the activity and/or they are assessing the benefits to be relatively lower or the costs to be relatively higher.
+
+### Sharing Research Materials - Prescriptive versus Descriptive Views
+
+Next, our survey focuses on the perceived prescriptive and descriptive importance of research material sharing.
+Table 7 Panel A reports data on the frequency of sharing, revealing that an impressive 57% of the respondents state that they at least sometimes publicly share their research materials.
+We also find that stated sharing tendencies are significantly lower for respondents in the Qualitative and Survey categories compared to each of the three other methodological areas, i.e., the respondents in the Analytical, Archival, and Experimental categories (two-tailed p-value \< 0.100).
+
+\centerline{--- Insert Table 7 about here ---}
+
+Table 7 Panel B reports answers to three questions measuring respondents' perceptions of how important others consider research material sharing to be (i.e., prescriptive and descriptive importance).
+Namely, these three questions ask (1) what percentage of accounting researchers in general favor research material sharing, (2) what percentage of editors of the top six accounting journals believe it increases the value of a manuscript, and (3) what percentage of accounting researchers publicly share research materials.
+The data in Panel B reveal that respondents believe about 44% of accounting researchers favor publicly sharing research materials, they believe 61% of the top-six accounting editors are in favor of publicly sharing research materials, and they believe 27% of accounting researchers actually share research materials.
+
+\centerline{--- Insert Figure 5 about here ---}
+
+To visualize the differences between these three questions, Figure 5 displays scatter box plots, one for each question and separately for each methodology.
+First, examining the three plots for the sample as a whole, the clear visual pattern emerges that the assessments of actual sharing behavior among accounting researchers lag behind assessments of whether accounting researchers favor sharing, which, in turn, lags behind assessment of whether editors value sharing.
+This pattern seems starker for respondents in the Archival/Field category.
+These findings suggest a contrast between the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior.
+In other words: We believe that we should share and we also state that we do but we do not believe that others do.
+
+### Pre-registration
+
+Our survey has so far revealed that accounting researchers who participated in our survey are more skeptical about reproducibility than other social science areas.
+We also find that they are less familiar with research materials sharing as an open science practice that helps address reproducibility and that they find that practice less important.
+Besides research material sharing, our survey also covers a second Open Science practice: Pre-registration.
+
+\centerline{--- Insert Table 8 about here ---}
+
+Table 8 summarizes three questions about pre-registration.
+Panel A considers respondents' familiarity with the practice itself.
+We asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^6] The results in Panel A suggest accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
+They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010).
+While this finding might appear surprising at first glance, one has to factor in that the practice of pre-registration is gaining traction over time, and our survey was fielded two years later than the second wave of our benchmark survey.
+
+\centerline{--- Insert Figure 6 about here ---}
+
+Panel B reports data on the first-time respondents pre-registered.
+It is based on the question: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^7] The findings show a clear pattern: Accounting researchers started pre-registering their studies significantly later than researchers in other social science fields (two-tailed p-value \< 0.010).
+They started around 2018, compared to 2015-2016 for the other fields.
+This finding is also supported by Figure 6, which shows that the take-up of pre-registration in accounting over time lags behind the other social science areas.
+
+Panel C examines trustworthiness, showing data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^8] Results indicate no apparent differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100).
+However, the perceived increase in trustworthiness when pre-registering is less in accounting compared to psychology and sociology (two-tailed p-value \< 0.010).
+However, it should be noted that for this question, the comparability across fields is limited as we asked explicitly about trustworthiness, whereas @FLCPSWMBP_2023 referred more generally on a general opinion.
+
+\centerline{--- Insert Table 9 about here ---}
+
+To conclude our descriptive evidence on pre-registration, we examine differences in familiarity, usage, and trustworthiness of pre-registration across the different methodological areas within accounting.
+Table 9 displays respondents' frequencies using three panels.
+Similar to Table 8 Panel A, Panel A of Table 9 reports on familiarity, i.e., the question: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?" Somewhat unsurprisingly, Panel A shows that qualitative accounting researchers are less familiar with the practice than accounting researchers belonging to the Archival, Experimental, and Survey categories (two-tailed p-value \< 0.100).
+Yet, there is no statistical difference between qualitative and analytical accounting researchers.
+Panel B reports on differences in usage, specifically, the question "`r vars$text[100]`", similar to the question featured in Table 8 Panel B.
+We find that accounting researchers in the experimental field report the highest usage of pre-registration, while none of the qualitative accounting researchers report using it.
+Lastly, Panel C reports differences in perceived trustworthiness.
+Specifically, it features answers to the question, "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?" which is identical to the question featured in Table 8 Panel C.
+We find no clear evidence of differences among the different methodologies in whether they trust pre-registered work more than work that has not been pre-registered.
+
+### Usage of Open Science Methods - Observational Data
+
+To contrast these perceptions with reality, we collect observational data on actual research material sharing behavior and the use of pre-registration behavior for a random country-stratified sample of `r nrow(authors)` authors from our target population.
+To assess whether these authors share research materials, we systematically search their homepages for evidence and also verify whether they have relevant online accounts linked to their names on platforms such as GitHub, Open Science Foundation, Dataverse, or Zenodo.
+If they do, we collect whether they share research materials over these channels.
+In addition, we use Scopus to identify all studies that these authors published since 2016 and verify whether these publications' DOI URLs reference research material sharing.[^9] We also assess various pre-registration platforms to assess whether our authors have used pre-registration.
+We only were able to identify for `r sum(by_author$has_prereged)` authors clear evidence that they have pre-registered a study.
+These cases are linked to the registered report initiative of JAR.
+Therefore, this reminder of this section solely focuses on research material sharing.
+
+\centerline{--- Insert Table 10 about here ---}
+
+Table 10 reports our findings based on this sample of `r nrow(authors)` authors and their `r nrow(papers)` papers.
+Panel A summarizes the data by author.
+We find that `r sum(by_author$has_made_resmat_available)` % of our authors share research materials.
+This number and its corresponding binomial confidence interval (30 to 49 %) are lower that the percentage of respondents that stated in the survey that they at least sometimes share (57 %) but a little bit higher than the prescriptive sharing frequency that our respondents attributed to other researchers (27 %).
+
+\centerline{--- Insert Figure 7 about here ---}
+
+As becomes apparent from Panel B, our authors only share research materials occasionally.
+Only 7.5 % of the paper DOI URLs reference research material sharing.
+As Figure 7 indicates, this share has mildly increased over time but even in recent years, the paper-level sharing percentage seems relatively modest.
+
+The journal breakdown in Panel B provides clear evidence that the data and code sharing policies established by the Journal of Accounting Research and Management Science drastically influence research material sharing behavior.
+This also becomes apparent from Panel A.
+If one omits research material sharing via these journals, the percentage of sharing accounting researchers drops from 39 % to 23 %.[^10]
+
+Overall, our observational data supports the survey findings. It seems that research material sharing only takes place sporadically in accounting and is often driven by journal requirements.
+
+### Rationales Related to Research Material Sharing - Experimental Findings
+
+We now turn to our third and final research question: An attempt to understand how our participants decide on whether to share research materials.
+As a first step, we use a small experimental design.
+For this, we create a hypothetical scenario.
+The scenario outlines that the participating researcher has just conducted a study and published it in an academic journal.
+Next, participants are informed that a fellow researcher has contacted them for access to their research materials.
+Next, we provide four pieces of information about the request made by a fellow researcher.
+In these statements, we manipulate two between-subjects factors: the rationale behind the request for research materials and the scope of sharing.
+First, we manipulate the rationale used by the fellow researcher requesting access to the researcher's materials.
+In the *collaboration rationale* treatment, the fellow researcher requests access to researcher materials to understand the work better and build on it.
+In the *control rationale* treatment, the request aims to verify and potentially correct the research.
+Second, we vary whether the fellow researcher requests the research materials to be shared publicly (i.e., *public scope*) or privately (i.e., *private scope*).
+Respondents were randomly assigned one stated rationale (*control* versus *collaboration*) and one sharing scope (*public* versus *private*).
+Their willingness to comply with the fellow researcher's request was then measured on a scale ranging from 0% (definitely not) to 100% (definitely).
 The hypothetical scenario was, like the survey, designed using oTree [@CSW_2016].
-
-We predicted that the effect of using a collaborative versus controlling rationale increases accounting researchers' willingness to share their research materials because it communicates a potential benefit rather than cost in terms of reputation (our first hypothesis).
-We also predicted that a private sharing request leads to a higher willingness to share than a public sharing requests because the former involves a lower potential downside risk in terms of reputation than the latter (our second hypothesis).
-Finally, we predicted that the effect of stating a collaborative versus controlling rationale is larger in the case of a private sharing request as opposed to a public sharing request (our third hypothesis).
+An overview of the manipulations and the materials can be found in Appendix B.
+
+Building on our discussion in section 2, we predict that using a collaborative versus controlling rationale increases accounting researchers' willingness to share their research materials because it communicates a potential benefit rather than cost in terms of reputation (our first hypothesis).
+We also predict that a private sharing request would be more favorably received due to lower indirect costs triggered by lower reputation risks (our second hypothesis).
+Finally, we predict that the effect of a collaborative rationale is larger in the case of a private sharing request than a public sharing request (our third hypothesis).
 The conceptual reasoning behind this interaction effect is that, besides the additive effects of private sharing and a collaboration rationale, the perceived benefit of sharing under the collaboration rationale should be amplified when the scope of sharing is private rather than public.
@@
 
-#### Hypothetical Scenario - Procedures
-
-After accepting the terms and conditions, respondents were told that they would read a short scenario and that they would answer questions about it.
-The scenario included a description that they just conducted a study and published it in an academic journal.
-Respondents were also told that a fellow researcher contacted them for access to their research materials, which we specified as 'data, code, and research procedures'.
-Next, we provided four pieces of information about the request made by the fellow researcher.
-In this part of the scenario, we manipulated whether the request was to make the research materials publicly accessible (*public scope*) or share them only with the requesting fellow researcher (*private scope*).
-We also featured our second manipulation, specifically, whether the provided rationale was to collaborate with or control the research of the respondent (*collaboration rationale* versus *control rationale*).
-Appendix B contains an overview of the manipulations and the materials.
-
-\centerline{--- Insert Table 7 about here ---}
-
-#### Hypothetical Scenario - Findings
-
-Table 7 shows the findings of the hypothetical scenario.
-On average, we find a relatively high willingness to share research materials in the hypothetical scenario and across different variations of rationale and scope (mean = 72%, s.d.
+\centerline{--- Insert Table 11 about here ---}
+
+Table 11 shows the findings of the hypothetical scenario.
+On average, we find a high willingness to share research materials in the hypothetical scenario and across different variations of rationale and scope (mean = 72%, s.d.
 = 28%).
@@
 First, Table 7 Column 1 reports no significant effect of using a *collaboration rationale* over a *control rationale* (two-tailed p-value \> 0.100).
-Moreover, Column 2 shows no support for a main effect of *private scope* on respondents' willingness to share research materials (two-tailed p-value \> 0.100).
+Moreover, Column 2 reveals no support for a main effect of *private scope* on respondents' willingness to share research materials (two-tailed p-value \> 0.100).
 Lastly, column 3 shows no support for an interaction effect between *collaboration rationale* and *private scope* (two-tailed p-value \> 0.100).
-In sum, although we find that respondents express a high willingness to share research materials in our hypothetical scenario, we don't find any evidence it is affected by the way the request for sharing is made.
+In sum, although we find that respondents express a high willingness to share research materials in our hypothetical scenario, we do not find any evidence it is affected by the way the request for sharing is made.
 At least in our hypothetical scenario, it does not matter whether the request is made to make the materials private (rather than public) and whether the request is made to promote collaboration as a research community or to verify whether the research has been conducted appropriately.
 
-### Sharing Research Materials - Prescriptive versus Descriptive Views
-
-Our respondents report a high willingness to share research materials in a hypothetical scenario and do not seem moved by the circumstances under which requests for research materials are made.
-Next, our survey focuses on the perceived prescriptive and descriptive importance of research material sharing.
-Table 8 Panel A reports data on respondents' answers to the question, "How often do you publicly share research materials (i.e., data, code, and research procedures)?" It also splits the data into main methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
-The results in Panel A reveal that 50% of the respondents state that they at least sometimes publicly share their research materials.
-We also find that stated sharing tendencies are significantly lower for respondents in the Qualitative and Survey categories compared to each of the three other methodological areas, i.e., the respondents in the Analytical, Archival, and Experimental categories (two-tailed p-value \< 0.100).
-
-\centerline{--- Insert Table 8 about here ---}
-
-Table 8 Panel B reports answers to three questions measuring respondents' perceptions of how important others consider research material sharing to be (i.e., prescriptive and descriptive importance).
-Namely, these three questions ask (1) what percentage of accounting researchers in general favor research material sharing, (2) what percentage of editors of the top six accounting journals believe it increases the value of a manuscript, and (3) what percentage of accounting researchers publicly share research materials.
-The data in Panel B reveal that respondents believe about 44% of accounting researchers favor publicly sharing research materials, they believe 60.8% of the top-six accounting editors are in favor of publicly sharing research materials, and they believe 27.6% of accounting researchers actually share research materials.
-
-\centerline{--- Insert Figure 3 about here ---}
-
-To understand the differences between these three questions, Figure 3 displays box plots, one for each question and separately for each methodology.
-First, examining the three box plots for the sample as a whole, the visual pattern emerges that the perceptions of actual sharing behavior among accounting researchers lag behind perceptions of whether accounting researchers favor sharing, which, in turn, lags behind perceptions of whether editors value sharing.
-This pattern seems starker for respondents in the Archival/Field category.
-In this category, the box plot for the perceptions of actual sharing does not overlap with the other two, i.e., the box plots for the perceptions of accounting researchers favoring sharing and the perceptions of whether editors value sharing.
-These findings suggest a contrast between the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior.
-
-### Sharing Research Materials - Observational Data
-
-To contrast the perception of our our survey participants with actual research material sharing behavior, we collect observational data on research material sharing for a random country-stratified sample of `r nrow(authors)` authors from our target population.
-To assess whether these authors share research materials, we systematically search their homepages for evidence and also assess whether they have GitHub, Open Science Foundation, Dataverse, or Zenodo accounts linked to their name.
-If they do, we verify whether they share research materials over these channels.
-In addition, we use Scopus to identify all studies that these authors published since 2016 and verify whether these publications' DOI URLs reference research material sharing.[^7]
-
-[^7]: The data collection manual for this process is available in this project's GitHub repository.
-
-\centerline{--- Insert Table 9 about here ---}
-
-Table 9 reports our findings based on this sample of `r nrow(authors)` authors and their `r nrow(papers)` papers.
-Panel A summarizes the data by author.
-We find that `r sum(by_author$has_made_resmat_available)` % of our authors share research materials.
-This number and its according binomial confidence interval is overall consistent with the perceptions voiced in the survey.
-
-\centerline{--- Insert Figure 4 about here ---}
-
-However, as becomes also apparent from Panel B, our authors only share research materials occasionally.
-Only 7.5 % of the paper DOI URLs reference research material sharing.
-As Figure 4 indicates, this share is mildly increasing over time but even in recent years, the sharing percentage seems relatively modest.
-
-The journal breakdown in Panel B provides clear evidence that the data and code policies established by the Journal of Accounting Research and Management Science affect the tendency of research material sharing.
-This also becomes apparent from Panel A.
-If one omits research material sharing via these journals, the share of sharing accounting researchers drops from 39 % to 23 %.[^8]
-
-[^8]: Untabulated analyses based on small frequencies provide suggestive evidence that, overall, the sharing frequencies are higher for general economics journals than for journals in the areas of accounting and finance.
-
-Overall, our observational data supports the survey findings.
-It seems that research material sharing takes place only occasionally in accounting and in many instances only if required by the publishing journal.
-In the next section, we will return to our survey data to explore stated rationales for or against research material sharing.
-
-### Sharing Research Materials - Rationales
-
-So, what prevents accounting researchers from sharing?
-Our survey also included questions about the rationales against sharing.
-When respondents reported that they did not always publicly share research materials, we asked them which reasons would make them withhold their research materials.
-Respondents were able to provide more than one reason.
-
-\centerline{--- Insert Table 10 about here ---}
-
-Table 10 Panel A displays the frequencies and percentages for each reason featured and provided in our survey.
+### Rationales Related to Research Material Sharing - Survey Evidence
+
+Also, given our experimental findings, we rely on two sources of survey data to shed light on our third research question.
+First, our survey contains a question asking respondents who report that they do not always publicly share research materials to explain which reasons make them withhold their research materials.
+Respondents are able to select multiple reasons.
+
+\centerline{--- Insert Table 12 about here ---}
+
+Table 12 Panel A displays the frequencies and percentages for each reason featured and provided in our survey.
 Aside from reporting the total frequencies for the entire sample, it also (again) splits them up into the five methodological fields (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
@@
 In a shared second place are three more prominent reasons respondents provided, namely, (1) the time that it takes to make materials available (29.9% of all respondents), (2) the fear of being scooped when materials become publicly available (23.2% of all respondents), and (3) no need for sharing as their data are already publicly available (33.9% of all respondents).
-There are some other notable differences across the methods.
-For qualitative researchers, deidentification problems are a relatively important reason (45.8%) compared to the others.
-Also, analytical researchers consider the time that it takes to make materials available far less of a reason than researchers using the other methods (i.e., 9.5%).
-
-Besides these multiple-choice questions soliciting the reasons for not sharing research materials, we also ask our participants to reflect on their answers in our hypothetical sharing scenario.
-The answers they provided in this free-form field have been coded by a research assistant who was not informed about the study's experimental design.
-The resulting categories characterizing the coded answers and their respective frequencies are presented in Panel B, for the total sample as well as for the different treatment cells.
-
-Different from the findings in Panel A, we are now also able to identify reasons for and not just against sharing.
-First and foremost, our participants share this because they believe it enhances the research's quality.
-Another strong argument is that it helps other researchers.
-This argument is significantly more likely to be provided by participants that faced the collaboration treatment, in line with our theoretical predictions and providing evidence that the framing of the sharing situation affects the decision-making of our participants.
+For these reasons, there are some notable differences across the different methodologies.
+For qualitative researchers, deidentification problems are a relatively important reason (45.8%).
+Analytical researchers, in contrast, consider the time that it takes to make materials available relatively less of a reason than researchers using the other methods (i.e., 9.5%).
+
+Besides this multiple-choice question, we also ask our participants to reflect on their answers in our hypothetical sharing scenario.
+This second data source is interesting (a) because it provides unfiltered insights on the reasons for and against data sharing, and (b) it might be influenced by our experimental manipulations, despite that it did not affect the sharing likelihood in the hypothetical scenario.
+To gather these additional insights, we tasked a research assistant, who was not informed about the study's experimental design, to code the answers of the participants.
+The resulting categories, characterizing the answers and their respective frequencies, are presented in Panel B of Table 12.
+It also splits the frequencies by the different experimental cells of the experiment.
+
+We first focus on the benefits of research material sharing.
+Panel B reveals that participants share research materials predominantly because they believe sharing enhances research quality.
+A typical example of such a statement is the following:
+
+```{=tex}
+\begin{displayquote}
+"The purpose of research is to better understand the world, and replication (and scrutiny) of one's research is an essential element of developing a deep understanding of the world."
+\end{displayquote}
+```
+
+While many participants refer to research in general when making this point, there are also responses that focus on the respondents' own work.
+These argue that research material sharing, by uncovering honest mistakes, can improve the quality of the sharing researcher's work.
+See, for example, the following statement:
+
+```{=tex}
+\begin{displayquote}
+"Because if there is a shadow of a doubt, I pay the consequences. Moreover, I care about the results--so if they can be improved upon, I am all for it!."
+\end{displayquote}
+```
+
+Another prominent argument provided by participants is that research material sharing helps other researchers.
+This argument is significantly more likely to be provided by participants who faced the collaboration treatment, providing evidence that the framing of the sharing situation affects the decision-making of our participants.
+We take this as evidence that our participants see the public and also private benefits of data and code sharing.
+The following statement illustrates the importance of research material sharing helping other researchers nicely:
+
+```{=tex}
+\begin{displayquote}
+"I always make supporting information available to other researchers when requested. It may help them learn our process and expand upon our work."
+\end{displayquote}
+```
 
 The main rationales against sharing are related to the materials being considered valuable intellectual property that can potentially be reused for other research projects.
-A typical example of such a statement is:
+A typical example of such a statement reflecting the indirect proprietary costs of data sharing is:
 
@@
 ```
-Another interesting aspect that does not become apparent from the pre-conditioned analysis in Panel A is that a sizable amount of participants indicate that they are concerned about unethical use of their research materials.
+Another interesting aspect that does not become apparent from the pre-conditioned analysis in Panel A is that a sizable amount of participants indicate that they are concerned about the unethical use of their research materials.
 These concerns are related to other researchers using their work for "reverse p-hacking," trying to discredit prior findings to establish a contribution.
-Again, an example of such a statement:
+An example of such a statement:
 
@@
 ```
-Another aspect, which also featured prominently in Panel A, is the time that it takes to entertain research material sharing and potential follow-up requests. For example:
+Another aspect, which is also featured prominently in Panel A, is the time investment that is required to entertain research material sharing and potential follow-up requests. For example:
 
@@
 It is simply impossible to entertain each and every such request, especially when replying to the first might lead to feeling the obligation to answer more questions from the requester in the future.
-A requester can be a relatively inexperienced graduate student exploring a doctoral topic, which has implications to how many questions s/he might have in the future.
+A requester can be a relatively inexperienced graduate student exploring a doctoral topic, which has implications for how many questions s/he might have in the future.
 Thus, the propensity to reply to a request often depends on the status of the requester in the field and the anticipated consequences (or the lack of) of entertaining the request (or not)."
@@
 ```
-The last aspect of this quote also hints at a rationale commonly featured in the "it depends" category: the requesting person's personality and reputation. A final example:
+The last aspect of this quote also hints at a rationale commonly featured in the "it depends" category: the requesting person's personality and reputation. An example of this is:
 
@@
 ```
-These statements indicate the potential for selective sharing among well-connected researchers, which would benefit an "in-crowd" of academics while at the same time unraveling the academic playing field and increasing inequality.
+These statements indicate the potential for selective sharing among well-connected researchers, which would benefit an "in-crowd" of academics while at the same time unleveling the academic playing field and increasing inequality.
+
 Taken together, we conclude from the rationale analysis that our participants give more consideration to potential sharing costs than to potential sharing benefits.
 While the sharing benefits become more prevalent with a collaboration framing, the sharing costs are prominent regardless of the hypothetical scenario.
-
-### Pre-registration
-
-Our survey has so far revealed that accounting researchers who participated in our survey are more skeptical about reproducibility than other social science areas.
-We also find that they are less familiar with research materials sharing as an open science practice that helps address reproducibility and that they find that practice less important.
-There seem to be various reasons why accounting researchers share and even more why they do not share their research materials.
-Besides research material sharing, our survey also covered a second Open Science practice: Pre-registration.
-
-\centerline{--- Insert Table 11 about here ---}
-
-Table 11 lists the frequencies and percentages for three questions about pre-registration.
-Panel A considers respondents' familiarity with the practice itself.
-Namely, we asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^9] The results in Panel A suggest accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
-They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010).
-While this finding might appear surprising at first glance, one has to factor in that the practice of pre-registration is gaining traction over time, and our survey was fielded two years later than the second wave of our benchmark survey.
-
-[^9]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
-
-\centerline{--- Insert Figure 5 about here ---}
-
-Panel B reports data on the first-year respondents pre-registered.
-Namely, we asked them: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^10] The findings exhibit a clear pattern: Accounting researchers started considering pre-registration for the first time significantly later than researchers in other social science fields (two-tailed p-value \< 0.010).
-The take-up started around 2018 compared to 2015-2016 for the other fields.
-This finding is also supported by Figure 5 showing that the take-up of pre-registration in accounting over time lags behind the other social science areas.
-
-[^10]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"
-
-Panel C shows data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^11] Results indicate no apparent differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100).
-However, the perceived increase in trustworthiness when pre-registering is less in accounting compared to psychology and sociology (two-tailed p-value \< 0.010).
-
-[^11]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
-We found this question to be quite broad yet it used a trustworthiness scale.
-So, we chose a more specific framing for our question.
-
-\centerline{--- Insert Table 12 about here ---}
-
-In this final part of our analysis, we examine differences in familiarity, usage, and trustworthiness of pre-registration across the different methodological areas within accounting.
-Table 12 displays respondents' frequencies using three panels.
-Similar to Table 11 Panel A, Panel A of Table 12 reports on familiarity, i.e., the question: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?" Somewhat unsurprisingly, Panel A shows that qualitative accounting researchers are less familiar with the practice than accounting researchers belonging to the Archival, Experimental, and Survey categories (two-tailed p-value \< 0.100).
-Yet, there is no statistical difference between qualitative and analytical accounting researchers.
-Panel B reports on differences in usage, specifically, the question "`r vars$text[100]`", similar to the question featured in Table 11 Panel B.
-We find that accounting researchers in the experimental field report the highest usage of pre-registration, while none of the qualitative accounting researchers report using it.
-Lastly, Panel C reports differences in perceived trustworthiness.
-Specifically, it features answers to the question, "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?" which is identical to the question featured in Table 11 Panel C.
-We find no clear evidence of differences among the different methodologies in whether they trust pre-registered work more than work that has not been pre-registered.[^12]
-
-[^12]: Similar to the observational data on research material sharing, we also collected observational data on pre-registration.
-However, for our random sample of `r nrow(authors)` authors, we find only for `r sum(by_author$has_prereged)` authors clear evidence that they have pre-registered a study.
-These cases are linked to the registered report initiative of JAR.
+Also, while the multiple-choice data highlight direct cost arguments, the unstructured verbal response also features various indirect costs.
 
@@
 
-Our results support the conclusion that we accountants face an "open science dilemma." On the one hand, we are more skeptical about the reproducibility of our influential findings than other social science researchers are about their respective findings.
-On the other hand, we seem to be a little bit behind the curve in terms of research material sharing and research design pre-registration.
-If these conclusions are descriptive, what should be our reaction?
+Informed by a voluntary diclosure themed discussion of the costs and benefits of open science activities in accounting, we conducted a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.
+Our results suggest that accounting researchers face an "open science dilemma." On the one hand, they are more skeptical about the reproducibility of their influential findings than other social science researchers are about their respective findings.
+On the other hand, they seem to be a little bit behind the curve in terms of research material sharing and research design pre-registration.
+If these conclusions are descriptive, what should our reaction be?
 
@@
 First, why are we so skeptical about our work?
-Is this an example of the anecdotal "professional skepticism" that leads us accountants to over-weight wrong signals in general?
+Is this an example of the anecdotal "professional skepticism" that leads us accountants to over-weight negative signals in general?
 Or do we indeed have good reasons to be concerned?
@@
 @LSA_2024 suggest reproduction studies in accounting might not be rare, and a majority of those confirm prior results.
-However, we need more systematic evidence on whether our findings reproduce, with or without new data, and hold in new settings.
+However, we need more systematic evidence on whether our findings reproduce and whether they can be replicated using new data and settings.
 An impressive exercise in that regard is the recent large-scale reproduction attempt of studies published in Management Science [@FGHKO_2023].
@@
 One interesting finding from that study is that accounting studies in Management Science are -if anything- more reproducible than studies in neighboring fields like finance.
-Based on this, it seems that professional skepticism might indeed be partly responsible for our open science dilemma.
+Based on this, it seems that professional skepticism and the resulting overly skeptical view on the reproducibility of our influential studies might indeed be partly responsible for our open science dilemma.
 
 It would be insightful to compare the findings for Management Science, which also documents an impressive effect of their data and code policy, with data on studies published in the Journal of Accounting Research, again pre and post their data policy.
-These findings could, in turn, be compared with those for studies published in other leading journals that do not have a dedicated data and code policy (yet).
+These findings could, in turn, be compared with those for studies published in other leading journals that do not have a dedicated data and code sharing policy (yet).
 But not only systematic large-scale reproduction studies can update our priors about the reproducibility of our work.
@@
 
-The second element of the two-pronged approach would be to promote research material sharing and pre-registration, potentially in combination with other open science measures that aim to increase the accessibility and re-usability of scientific work.
+The second element of the two-pronged approach would be to promote research material sharing and pre-registration, potentially in combination with other open science measures that aim to increase the accessibility and reusability of scientific work.
 The economists among us might be quick to point out the incentive problems in this regard.
@@
 Does sharing code and data help to build academic careers?
-While some associative evidence from other fields indicates that papers that share their data are cited more often [@PDF_2007], currently, as hard as it seems, the answer to this is not clearly affirmative.
+While some associative evidence from other fields indicates that papers that share their data are cited more often [@PDF_2007], currently, the answer to this is not clearly affirmative.
 Research material sharing requires skills and time, and, to the extreme, devoting this time might even be regarded as a negative signal by tenure and promotion committees, assuming that it crowds out time spent on producing "more tenurable output."
@@
 Think about a scientific computing world without open-source contributions.
-Without the BSD/Linux operating system and its tools, without Python, R, git, Latex, and the accompanying library ecosystem.
-The scientific advancements in areas like Econometrics, Machine Learning, and Natural Language Processing would be -if at all feasible- severely delayed.
-As our field builds on the insights of these areas, we benefit from the open science paradigm in our everyday work.
-
-Given that, one might ask whether data and code sharing by accounting researchers can create similar positive externalities.
-As our competitive advantage stems more from institutional expertise than methodological aspects, we are well-suited to become vital for carefully curating and pre-processing data based on extensive firm disclosures.
-Prominent examples include curated word lists for sentiment analyses in financial settings [e.g., @LM_2011], topic model-based measures of specific firm risks [e.g., @H_2019], and industry classifications based on financial disclosures [e.g., @HP_2016].
-
-A closely related area where we see the potential of accounting data to develop an impact is the collection and pre-processing of web and electronic filing data.
+This would be a world without the GNU/Linux operating system and its tools, without Python, R, git, Latex, and the accompanying package ecosystems.
+In such a world, scientific advancements in areas like econometrics, machine learning, and natural language processing would be severely delayed if at all feasible.
+As our field builds on the insights of these areas, we all benefit from the open source/science paradigm in our everyday work.
+
+Given that, one might ask whether research material sharing by accounting researchers can create similar positive externalities.
+As our competitive advantage stems more from institutional than methodological expertise, we, for example, are well-positioned to curate micro-level data based on firm disclosures.
+Prominent examples include word lists for sentiment analyses in financial settings [e.g., @LM_2011], topic model-based measures of specific firm risks [e.g., @H_2019], and industry classifications based on financial disclosures [e.g., @HP_2016].
+
+A closely related area where we see the potential of accounting data to develop a substantial impact is the collection and pre-processing of firm-time level web and electronic filing data.
 For the former, web scraping of corporate webpages can provide informative data [e.g., @BBB_2021], and for the latter, in particular, the upcoming electronic filing requirements for sustainability reports hold promise.
@@
 
-While these flagship projects are useful showcases that data and code sharing in the accounting domain can also be impactful for other domains, to promote reproducible workflows overall, we need to make the case that adopting such a workflow not only contributes to the public good by making research materials accessible but also enhances research efficiency at an individual level.
+While these flagship projects are useful showcases that research material sharing in the accounting domain can also be impactful for other domains, they will likely not change the sharing landscape at large.
+To promote reproducible workflows overall, we need to make the case that adopting such a workflow not only contributes to the public good by making research materials accessible but also enhances research efficiency at an individual level.
 To be able to share research materials, such as code and data, researchers must adopt a workflow that integrates reusability aspects into project development.
@@
 This process becomes significantly more manageable and enjoyable if an open science-oriented workflow is adopted throughout all stages of project development.
-Besides this, it also makes it easier for co-author teams to cooperate.
-
-As the lack of time is one of the biggest roadblocks to research material sharing in our survey, educational activities targeted at the PhD level in scientific computing and project management, in general, seem important.
+Besides this, it also makes it easier for co-author teams to cooperate, and even the researcher's future self might be thankful.
+
+As the lack of time is one of the biggest roadblocks to research material sharing in our survey, educational activities targeted at the PhD level teaching scientific computing and project management, in general, seem important.
 While well-funded research institutions might have the opportunity to outsource these skills to research professionals, the vast majority of researchers worldwide need to acquire them themselves.
@@
 In the early days, many accounting PhD programs were implicit- or explicitly relying on scientific computing skills to be handed down from one PhD generation to another.
-It seems that these days are over and that dedicated scientific computing courses should become a central component of scientific education in the quantitative social sciences as lab training is in the natural sciences.
+It seems that these days are over and that dedicated scientific computing courses should become as central a component of scientific education in the quantitative social sciences as lab training is in the natural sciences.
 
@@
 What about analytical and qualitative researchers and their studies?
-As it becomes apparent from our findings, their views on open science differ pretty prominently from those of the "accounting mainstream." Analytical researchers seem to be much more confident in their work than others, potentially in line with theoretical work being more accessible to verify during the review process.
+As it becomes apparent from our findings, their views on open science differ prominently from those of the "accounting mainstream." Analytical researchers seem to be much more confident in their work than others, potentially in line with theoretical work being easier to verify during the review process.
 Then again, to develop the impact that it deserves, analytical work not only needs to be reproducible but also accessible and reusable, ideally also by non-expert researchers from neighboring methods.
-Qualitative work, on the other hand, faces challenges that set it apart from typical quantitative work.
+Qualitative work, on the other hand, faces conditions that set it apart from typical quantitative work.
 First, its data is often collected under confidentiality, legally restricting future sharing.
 Second, its unique richness makes it inherently challenging to share across subjects, especially if re-identification issues are present.
-Third, related and maybe more epistemological in nature, the assumption of objectivity, which allows research materials to be detached from the individual researcher and re-used by others, is questioned within the qualitative realm.
+Third, related and maybe more epistemological in nature, the assumption of objectivity, which allows research materials to be detached from the individual researcher and reused by others, is questioned within the qualitative realm.
 This implies that qualitative scholars have to develop -and are developing [e.g., @M_2014; @FRV_2022]- their own understanding of what reproducibility means within their methodological paradigm.
@@
 This is human but unfortunate, also because it leads to subtle "home biases" when it comes to sharing, potentially increasing academic inequality and hindering scientific progress.
-While the fear of being "scooped" can be addressed by publishing materials later in the publication process or publicly claiming intellectual ownership of ideas via registration and use of well-established repositories, fears with regards to future researchers pointing to deficiencies in one's work and/or a general lack of trust are more challenging to overcome.
+While the fear of being "scooped" can be addressed by sharing materials later in the publication process or publicly claiming intellectual ownership of ideas via pre-registration and use of well-established repositories, fears with regards to future researchers pointing to deficiencies in one's work and/or a general lack of trust are more challenging to overcome.
 For both aspects, we need to work towards changing the error climate in the academic discipline.
@@
 
-### Figure 1: Reproducibility of Influential Findings Across the Social Sciences {.unnumbered}
-
-```{r Figure1, fig.width=8, fig.height=5}
-likert_plot(mr, "reprod", "demog_discipline", title_str = "How confident are you that the influential reserach findings in your area will replicate/reproduce?", llevels = vars$resp_label[80:84])
+### Figure 1: Sample Comparison between BYU and Our Sample - Subfields {.unnumbered}
+
+```{r Figure1, fig.width=12, fig.height=9}
+byu_fields_comp(byu, sd)
+```
+
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
+This figure compares the distribution of authors' subfields in the BYU sample to the distribution of respondents' self-reported primary subfield in our sample.
+In contrast to our survey, authors are classified in multiple subfields in the BYU sample.
+Therefore, this figure compares the 2,877 subfield classifications of the BYU sample to the 229 primary subfield classifications of our sample.
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
+```
+### Figure 2: Sample Comparison between BYU and Our Sample - Methods {.unnumbered}
+
+```{r Figure2, fig.width=12, fig.height=9}
+byu_methods_comp(byu, sd)
+```
+
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
+This figure compares the distribution of authors' methodologies in the BYU sample to the distribution of respondents' self-reported primary methodology in our sample.
+In contrast to our survey, authors are classified in multiple methodologies in the BYU sample.
+Therefore, this figure compares the 2,114 methodology classifications of the BYU sample to 229 primary methodology classifications of our sample.
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
+```
+### Figure 3: Reproducibility of Influential Findings Across the Social Sciences {.unnumbered}
+
+```{r Figure3, fig.width=8, fig.height=5}
+likert_plot(mr, "reprod", "demog_discipline", title_str = "How confident are you that the influential research findings in your area will replicate/reproduce?", llevels = vars$resp_label[80:84])
 ```
@@
 The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers world-wide.
+Our survey was conducted in 2022 among accounting researchers worldwide.
 Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
@@
 \end{singlespace}
-```
-\newpage
-
-### Figure 2: Importance of Research Material Sharing Across the Social Sciences {.unnumbered}
-
-```{r Figure2, fig.width=9, fig.height=5}
+\newpage
+```
+### Figure 4: Importance of Research Material Sharing Across the Social Sciences {.unnumbered}
+
+```{r Figure4, fig.width=9, fig.height=5}
 mr$sharing_important_rescaled = floor(mr$sharing_important)
@@
 This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
-The question asked in our survey is "`r vars$text[49]`" while the original question used in the survey of @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting data or code online is important for progress in \[Discipline\]?".
+The question asked in our survey is "`r vars$text[49]`" while the original question used in the survey of @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting (data or code \| research instruments) online is important for progress in \[Discipline\]?".
 The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers world-wide.
+Our survey was conducted in 2022 among accounting researchers worldwide.
 Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
@@
 \setlength{\parindent}{4em}
-```
-\newpage
-
-### Figure 3: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}
-
-```{r Figure3, fig.width=8, fig.height=6}
+\newpage
+```
+### Figure 5: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}
+
+```{r Figure5, fig.width=8, fig.height=6}
 pres_desc_plot(sd)
@@
 
-### Figure 4: Share of Papers with Shared Research Materials over Time {.unnumbered}
-
-```{r Figure4, fig.width=8, fig.height=6}
+### Figure 6: Pre-Registration: Take-up over Time Across the Social Sciences {.unnumbered}
+
+```{r Figure7, fig.width=8, fig.height=6}
+pre_reg_over_time_plot(mr)
+```
+
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
+This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
+The question of our survey is "`r vars$text[102]`".
+The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?".
+The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
+Our survey was conducted in 2022 among accounting researchers worldwide.
+Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
+```
+```{=tex}
+\renewcommand{\thetable}{\arabic{table}}
+\setcounter{table}{0}
+```
+\newpage
+
+### Figure 7: Share of Papers with Shared Research Materials over Time {.unnumbered}
+
+```{r Figure6, fig.width=8, fig.height=6}
 plot_resmat_sharing_over_cyear
@@
 \newpage
-```
-### Figure 5: Pre-Registration: Take-up over Time Across the Social Sciences {.unnumbered}
-
-```{r Figure5, fig.width=8, fig.height=6}
-pre_reg_over_time_plot(mr)
-```
-
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
-This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
-The question of our survey is "`r vars$text[102]`".
-The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?".
-The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers world-wide.
-Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
-
-```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
-```{=tex}
-\renewcommand{\thetable}{\arabic{table}}
-\setcounter{table}{0}
 ```
@@
 \end{singlespace}
-```
-\newpage
-
+\newpage
+```
 ### Table 2: Sample Demographics {.unnumbered}
 
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
 #### Panel A: Sample Descriptives {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 ```{r Tab2aDemographics, asis = TRUE}
@@
 
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
+```
+```{=tex}
+\begin{landscape}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
 #### Panel B Regional Representativeness {.unnumbered}
@@
 ```
+
+\newpage
 
@@
 ```
-```{=tex}
-\begin{landscape}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 ### Table 5: Sharing of Research Materials Across the Social Sciences {.unnumbered}
 
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
 #### Panel A: Familiarity {.unnumbered}
@@
 
-This table is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
-For Panel A, the question of our survey is "`r vars$text[44]`" where we code the response "Not at all familiar" as "No".
-The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of publicly posting data or code online for a completed study?".
-For Panel B, the question of our survey is "`r vars$text[49]`".
-The question used in the survey of @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting data or code online is important for progress in \[Discipline\]?" The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers world-wide.
-Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
-The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field.
-(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respectively.
-
 ```{=tex}
@@
 ```
-### Table 7: Scenario Analysis: Hypothetical Sharing Likelihood {.unnumbered}
-
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
-#### Panel A: Descriptive Statistics {.unnumbered}
-
-```{r Tab7aExpDescriptives, asis = TRUE}
-stats <- sd %>%
-	group_by(exp_tment_control, exp_tment_private) %>%
-	select(exp_tment_control, exp_tment_private,exp_pct_share) %>%
-	summarise(
-		N = sprintf("%d", n()),
-		Mean = sprintf("%.1f%%", mean(exp_pct_share)),
-		`Std. Dev.` = sprintf("%.1f%%", sd(exp_pct_share)),
-		Minimum = sprintf("%.1f%%", min(exp_pct_share)),
-		`25%` = sprintf("%.1f%%", quantile(exp_pct_share, 0.25)),
-		Median = sprintf("%.1f%%", median(exp_pct_share)),
-		`75%` = sprintf("%.1f%%", quantile(exp_pct_share, 0.75)),
-		Maximum = sprintf("%.1f%%", max(exp_pct_share))
-	) %>%
-	ungroup() %>%
-	mutate(
-		Rationale = c(rep("Collaboration", 2), rep("Control", 2)),
-		Scope = c(rep(c("Public", "Private"), 2))
-	) %>%
-	select(-exp_tment_control, -exp_tment_private) %>%
-	select(Rationale, Scope, everything())
-tab <- create_pct_cross_tab_table(
-	sd, "reprod_acc", "demog_method", 
-	ctests = TRUE, df_only = TRUE
-) 
-gt(stats) %>% 
-	cols_align("right", -1:-2) %>% 
-	as_latex()
-```
-
-#### Panel B: Regression Results {.unnumbered}
-
-```{r Tab7bExpRegResults, asis = TRUE}
-sd$exp_tment_collab <- 1 - sd$exp_tment_control
-modh1 <- lm(exp_pct_share ~ exp_tment_collab, data = sd)
-modh2 <- lm(exp_pct_share ~ exp_tment_private, data = sd)
-modh3 <- lm(exp_pct_share ~ exp_tment_collab*exp_tment_private, data = sd)
-tab_latex  <- modelsummary(
-	list(H1 = modh1, H2 = modh2, H3 = modh3), output = "gt",
-	coef_rename = function(x) {
-		x <- str_replace(x, fixed("exp_tment_collab"), "Collaboration rationale")
-		x <- str_replace(x, fixed("exp_tment_private"), "Private scope")
-		str_replace(x, fixed(":"), "×")
-	},
-	gof_map = list(
-		list(raw = "adj.r.squared", clean = "Adjusted R2", fmt = 3),
-		list(
-			raw = "nobs", clean = "Number of observations", 
-			fmt = function(x) format(x, big.mark=",")
-		)
-	),
-	stars = c('*' = .1, '**' = 0.05, '***' = .01),
-	estimate  = "{estimate}{stars}",
-) %>% as_latex()
-
-# The below is needed since some tex environment chock on the longtable environment
-# See https://github.com/vincentarelbundock/modelsummary/issues/50
-tab_latex[1] <- sub("\\(Intercept\\)", "Intercept", tab_latex)
-
-sub("Adjusted R2", "\\\\midrule\\\\addlinespace[2.5pt]\nAdjusted R²", tab_latex)
-```
-
-This table reports the results from the pre-registered experimental design contained in our survey.
-Is is based on a hypothetical code and data sharing scenario were we manipulated the sharing rationale (collaboration versus control) and the sharing scope (private versus public).
-All experimental materials are detailed in the Online Appendix of this study.
-The outcome variable is the stated likelihood that the respondent would share their code and data under the hypothetical scenario.
-Panel A reports the descriptive statistics for this outcome, conditional for the different treatment cells.
-Panel B reports the results from OLS regressions of the outcome on the binary treatments (H1 and H2) and their interaction (H3).
-
-```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
-### Table 8: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}
+### Table 7: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}
 
@@
 The response presented in Panel A is based on the question "`r vars$text[55]`" while the response presented in Panel B is based on the questions "`r vars$text[78]`" (general preference for sharing), "`r vars$text[79]`" (editor preference for sharing) and "`r vars$text[54]`" (actual sharing behavior).
-In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other", and one observation from a person who chose not self-classify into a main method are excluded.
+In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other", and one observation from a person who chose not to self-classify into a main method are excluded.
 Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
+Please see Appendix C for an overview of how we adapted these three questions and their answer scales from @FLCPSWMBP_2023.
 
@@
 ```
-### Table 9: Observational Data on Research Material Sharing {.unnumbered}
+### Table 8: Pre-Registration Across the Social Sciences {.unnumbered}
+
+#### Panel A: Awareness {.unnumbered}
+
+```{r Tab11aPreRegAwareSocSciResp, asis = TRUE}
+tab <- create_pct_cross_tab_table(
+	mr, "prereg_heard", "demog_discipline", 
+	resp_label = c("No (0)", "Yes (1)"), 
+	add_num_labels = FALSE, df_only = TRUE
+) 
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+```
+
+#### Panel B: Take-up over Time {.unnumbered}
+
+```{r Tab11bPreRegTimeSocSciResp, asis = TRUE}
+tab <- create_pct_cross_tab_table(
+	mr, "prereg_use_first_time", "demog_discipline", 
+	resp_label = na.omit(sort(unique(mr$prereg_use_first_time))), 
+	add_num_labels = FALSE, df_only = TRUE
+)
+
+# NOTE: This hack Needs to be checked manually whenever something 
+# the underlying data changes - which it should not
+
+up_to_2010 <- c(
+	"<= 2010", 
+	sum(as.numeric(substr(tab$Accounting[1:13], 1, 1))),
+	sum(as.numeric(substr(tab$Economics[1:13], 1, 1))),
+	sum(as.numeric(substr(tab$`Political Science`[1:13], 1, 1))),
+	sum(as.numeric(substr(tab$Psychology[1:13], 1, 1))),
+	sum(as.numeric(substr(tab$Sociology[1:13], 1, 1)))
+)
+up_to_2010[2:6] <- sprintf(
+	"%s (%.1f %%)", 
+	up_to_2010[2:6],
+	100*as.numeric(up_to_2010[2:6])/as.numeric(tab[26,2:6])
+)
+tab <- rbind(up_to_2010, tab[14:28,])
+
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+```
+
+```{=tex}
+\newpage
+\begin{landscape}
+```
+#### Panel C: Trustworthiness {.unnumbered}
+
+```{r Tab11cPreRegTimeSocSciResp, asis = TRUE}
+tab <- create_pct_cross_tab_table(
+	mr, "prereg_opinion", "demog_discipline", 
+	resp_label = get_resp_label("prereg_trust"), df_only = TRUE
+) 
+gt(tab ) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+```
+
+This table is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
+For Panel A, the question of our survey is "`r vars$text[95]`" where we code the response "Not at all familiar" as "No" and all other responses as "Yes." The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
+For Panel B, the question of our survey is "`r vars$text[102]`".
+The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?".
+For Panel C, the question of our survey is "`r vars$text[103]`".
+The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
+The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
+Our survey was conducted in 2022 among accounting researchers worldwide.
+Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
+The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field.
+(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respecively.
+
+```{=tex}
+\newpage
+\setlength{\parindent}{0em}
+```
+### Table 9: Pre-Registration Across Methods {.unnumbered}
+
+#### Panel A: Familiarity {.unnumbered}
+
+```{r Tab12aPreRegFamiliarity, asis = TRUE}
+tab <- create_pct_cross_tab_table(
+	sd, "prereg_familiar", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
+) 
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+```
+
+#### Panel B: Usage {.unnumbered}
+
+```{r Tab12bPreRegUse, asis = TRUE}
+
+tab <- create_pct_cross_tab_table(
+	sd, "prereg_use", "demog_method", include_total = TRUE,
+	drop_levels = "Other", 
+	resp_label = c("No (0)", "Yes (1)"), 
+	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
+) 
+# Adjust levels to be zero based.
+tab[4,2:7] <- t(sprintf("%.2f", as.numeric(tab[4,2:7]) - 1))
+tab[5,2:7] <- t(sprintf("%.2f", as.numeric(tab[5,2:7]) - 1))
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+```
+
+\newpage
+
+#### Panel C: Trustworthiness {.unnumbered}
+
+```{r Tab12cPreRegTrust, asis = TRUE}
+
+tab <- create_pct_cross_tab_table(
+	sd, "prereg_trust", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
+) 
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex()
+```
+
+This table is based on our survey data and three separate questions.
+The response presented in Panel A is based on the question "`r vars$text[95]`", the response presented in Panel B is based on the question "`r vars$text[100]`", and the response presented in Panel C is based on the question "`r vars$text[103]`".
+In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other" are excluded.
+Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{landscape}
+\end{singlespace}
+\newpage
+\begin{singlespace}
+```
+### Table 10: Observational Data on Research Material Sharing {.unnumbered}
 
@@
 ```
-### Table 10: Sharing of Research Materials: Rationales {.unnumbered}
+### Table 11: Scenario Analysis: Hypothetical Sharing Likelihood {.unnumbered}
+
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
+#### Panel A: Descriptive Statistics {.unnumbered}
+
+```{r Tab7aExpDescriptives, asis = TRUE}
+stats <- sd %>%
+	group_by(exp_tment_control, exp_tment_private) %>%
+	select(exp_tment_control, exp_tment_private,exp_pct_share) %>%
+	summarise(
+		N = sprintf("%d", n()),
+		Mean = sprintf("%.1f%%", mean(exp_pct_share)),
+		`S.D.` = sprintf("%.1f%%", sd(exp_pct_share)),
+		Min = sprintf("%.1f%%", min(exp_pct_share)),
+		`25%` = sprintf("%.1f%%", quantile(exp_pct_share, 0.25)),
+		Median = sprintf("%.1f%%", median(exp_pct_share)),
+		`75%` = sprintf("%.1f%%", quantile(exp_pct_share, 0.75)),
+		Max = sprintf("%.1f%%", max(exp_pct_share))
+	) %>%
+	ungroup() %>%
+	mutate(
+		Rationale = c(rep("Collaboration", 2), rep("Control", 2)),
+		Scope = c(rep(c("Public", "Private"), 2))
+	) %>%
+	select(-exp_tment_control, -exp_tment_private) %>%
+	select(Rationale, Scope, everything())
+tab <- create_pct_cross_tab_table(
+	sd, "reprod_acc", "demog_method", 
+	ctests = TRUE, df_only = TRUE
+) 
+gt(stats) %>% 
+	cols_align("right", -1:-2) %>% 
+	as_latex()
+```
+
+#### Panel B: Regression Results {.unnumbered}
+
+```{r Tab7bExpRegResults, asis = TRUE}
+sd$exp_tment_collab <- 1 - sd$exp_tment_control
+modh1 <- lm(exp_pct_share ~ exp_tment_collab, data = sd)
+modh2 <- lm(exp_pct_share ~ exp_tment_private, data = sd)
+modh3 <- lm(exp_pct_share ~ exp_tment_collab*exp_tment_private, data = sd)
+tab_latex  <- modelsummary(
+	list(H1 = modh1, H2 = modh2, H3 = modh3), output = "gt",
+	coef_rename = function(x) {
+		x <- str_replace(x, fixed("exp_tment_collab"), "Collaboration rationale")
+		x <- str_replace(x, fixed("exp_tment_private"), "Private scope")
+		str_replace(x, fixed(":"), "×")
+	},
+	gof_map = list(
+		list(raw = "adj.r.squared", clean = "Adjusted R2", fmt = 3),
+		list(
+			raw = "nobs", clean = "Number of observations", 
+			fmt = function(x) format(x, big.mark=",")
+		)
+	),
+	stars = c('*' = .1, '**' = 0.05, '***' = .01),
+	estimate  = "{estimate}{stars}",
+) %>% as_latex()
+
+# The below is needed since some tex environment chock on the longtable environment
+# See https://github.com/vincentarelbundock/modelsummary/issues/50
+tab_latex[1] <- sub("\\(Intercept\\)", "Intercept", tab_latex)
+
+sub("Adjusted R2", "\\\\midrule\\\\addlinespace[2.5pt]\nAdjusted R²", tab_latex)
+```
+
+This table reports the results from the pre-registered experimental design contained in our survey.
+Is is based on a hypothetical code and data sharing scenario were we manipulated the sharing rationale (collaboration versus control) and the sharing scope (private versus public).
+All experimental materials are detailed in the Online Appendix of this study.
+The outcome variable is the stated likelihood that the respondent would share their code and data under the hypothetical scenario.
+Panel A reports the descriptive statistics for this outcome, conditional for the different treatment cells.
+Panel B reports the results from OLS regressions of the outcome on the binary treatments (H1 and H2) and their interaction (H3).
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
+```
+### Table 12: Sharing of Research Materials: Rationales {.unnumbered}
 
@@
 The response presented in Panel A is based on the multiple choice answer to the close-ended question "`r vars$text[60]`".
+Participants answered this question if they expressed not always sharing their research materials.
 Panel B is based on the answer to the open-ended question that we pose as a follow-up in our experimental scenario: "`r vars$text[7]`".
@@
 ```
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
-### Table 11: Pre-Registration Across the Social Sciences {.unnumbered}
-
-#### Panel A: Awareness {.unnumbered}
-
-```{r Tab11aPreRegAwareSocSciResp, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	mr, "prereg_heard", "demog_discipline", 
-	resp_label = c("No (0)", "Yes (1)"), 
-	add_num_labels = FALSE, df_only = TRUE
-) 
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex()
-```
-
-#### Panel B: Take-up over Time {.unnumbered}
-
-```{r Tab11bPreRegTimeSocSciResp, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	mr, "prereg_use_first_time", "demog_discipline", 
-	resp_label = na.omit(sort(unique(mr$prereg_use_first_time))), 
-	add_num_labels = FALSE, df_only = TRUE
-)
-
-# NOTE: This hack Needs to be checked manually whenever something 
-# the underlying data changes - which it should not
-
-up_to_2010 <- c(
-	"<= 2010", 
-	sum(as.numeric(substr(tab$Accounting[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$Economics[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$`Political Science`[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$Psychology[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$Sociology[1:13], 1, 1)))
-)
-up_to_2010[2:6] <- sprintf(
-	"%s (%.1f %%)", 
-	up_to_2010[2:6],
-	100*as.numeric(up_to_2010[2:6])/as.numeric(tab[26,2:6])
-)
-tab <- rbind(up_to_2010, tab[14:28,])
-
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex()
-```
-
-```{=tex}
-\newpage
-\begin{landscape}
-```
-#### Panel C: Trustworthiness {.unnumbered}
-
-```{r Tab11cPreRegTimeSocSciResp, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	mr, "prereg_opinion", "demog_discipline", 
-	resp_label = get_resp_label("prereg_trust"), df_only = TRUE
-) 
-gt(tab ) %>% 
-	cols_align("right", -1) %>% 
-	as_latex()
-```
-
-This table is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
-For Panel A, the question of our survey is "`r vars$text[95]`" where we code the response "Not at all familiar" as "No".
-The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
-For Panel B, the question of our survey is "`r vars$text[102]`".
-The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?".
-For Panel C, the question of our survey is "`r vars$text[103]`".
-The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
-The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers world-wide.
-Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
-The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field.
-(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respecively.
-
-```{=tex}
-\setlength{\parindent}{4em}
-\newpage
-```
-### Table 12: Pre-Registration Across Methods {.unnumbered}
-
-\setlength{\parindent}{0em}
-
-#### Panel A: Familiarity {.unnumbered}
-
-```{r Tab12aPreRegFamiliarity, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	sd, "prereg_familiar", "demog_method", include_total = TRUE,
-	drop_levels = "Other", ctests = TRUE, df_only = TRUE
-) 
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex()
-```
-
-#### Panel B: Usage {.unnumbered}
-
-```{r Tab12bPreRegUse, asis = TRUE}
-
-tab <- create_pct_cross_tab_table(
-	sd, "prereg_use", "demog_method", include_total = TRUE,
-	drop_levels = "Other", 
-	resp_label = c("No (0)", "Yes (1)"), 
-	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
-) 
-# Adjust levels to be zero based.
-tab[4,2:7] <- t(sprintf("%.2f", as.numeric(tab[4,2:7]) - 1))
-tab[5,2:7] <- t(sprintf("%.2f", as.numeric(tab[5,2:7]) - 1))
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex()
-```
-
-\newpage
-
-#### Panel C: Trustworthiness {.unnumbered}
-
-```{r Tab12cPreRegTrust, asis = TRUE}
-
-tab <- create_pct_cross_tab_table(
-	sd, "prereg_trust", "demog_method", include_total = TRUE,
-	drop_levels = "Other", ctests = TRUE, df_only = TRUE
-) 
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex()
-```
-
-This table is based on our survey data and three separate questions.
-The response presented in Panel A is based on the question "`r vars$text[95]`", the response presented in Panel B is based on the question "`r vars$text[100]`", and the response presented in Panel C is based on the question "`r vars$text[103]`".
-In all method break-ups, but not for the totals, answers from three respondents who classified their method as "Other" are excluded.
-Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
-
-```{=tex}
-\setlength{\parindent}{4em}
-\end{landscape}
-\end{singlespace}
-\newpage
-```
+\setlength{\parindent}{0em}
+
 ## Online Supplement {.unnumbered}
@@
 ```
+```{=tex}
+\begin{landscape}
+\begin{singlespace}
+\begin{center}
+```
+## Appendix C: Comparison of our Survey with Social Science Survey (S3) {.unnumbered}
+
+```{r AppCTab1, asis = TRUE}
+df <- read_csv(
+	"../data/external/s3_osacc_item_comparison.csv", 
+	show_col_types = FALSE
+)
+gt(df[,1:7]) %>% 
+	sub_missing() %>% 
+	cols_width(
+		`S3 Question` ~ pct(15),
+		`Scale S3` ~ pct(15),
+		`Our Question` ~ pct(15),
+		`Our Scale` ~ pct(15),
+		`Recoding` ~ pct(15)
+	) %>%
+	as_latex() %>%
+	gt_add_header_mpage_table()
+```
+
+```{=tex}
+\end{center}
+\end{singlespace}
+\end{landscape}
+```
+
+[^1]: The terms "reproduction" and "replication" are at times used as synonyms but have different meanings.
+Reproduction refers to achieving the same results of a prior study using the same materials (code, procedures, and data), while replication refers to duplicating the results of a of a prior study using the same code and procedures but with new data [@NSF_2015].
+For a more in-depth discussion of the differences and related terminological debate, see @GFI_2016.
+
+[^2]: We pre-registered this experimental part of our study. The pre-registration materials can be accessed [here](https://osf.io/frmzt/).
+
+[^3]: We removed 41 authors because we found no email address, 41 authors because they appeared in the data twice with two author IDs but were the same person, 28 authors because they were a current member of one of our affiliated universities or academic research centers, 5 authors because they gave us advice for this study, 2 authors because they had passed away, and 1 author due to an incorrect email address.
+
+[^4]: The corresponding question in @FLCPSWMBP_2023 is "Have you ever heard of the practice of publicly posting (data and code/study instruments) online for a completed study?" We deviated from this original question by using the term "research materials" and defining it as "sharing data, code, and research procedures" in our version of the question because we wanted to cover all aspects of this Open Science practice in one question.
+
+[^5]: "To what extent do you believe that publicly sharing research materials (i.e., data, code, and research procedures) is important for the advancement of accounting research?" The corresponding question in @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting (data or code \| research instruments) online is important for progress in \[Discipline\]?" We adapted this question for terminological consistency across our survey.
+
+[^6]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
+
+[^7]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"
+
+[^8]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
+This question is quite broad while relying on a five-point Likert scale evaluating self-reported favorability (i.e., Not at all in favor, Moderately not in favor, Neither in favor nor against, Moderately in favor, Very much in favor).
+We chose to use a more specific question asking about whether pre-registration improves trustworthiness while relying on a five-point Likert scale (i.e., Much less trustworthy, Somewhat less trustworthy, Equally trustworthy, Somewhat more trustworthy, Much more trustworthy).
+
+[^9]: The data collection manual for this process is available in this project's GitHub repository.
+
+[^10]: Untabulated analyses based on small frequencies provide suggestive evidence that, overall, the sharing frequencies are higher for general economics journals than for journals in the areas of accounting and finance.

### 2024-10-26 docs/presentation.qmd
presentation changes for brown bag
Pre SSRN

@@
 ---
-title: "Accountants' Attitudes Towards Open Science"
+title: |
+  | How does the Accounting Research Community 
+  | Think About Open Science?
 subtitle: "" # we use this for the venue
@@
 
+## To Compare: Policy Effect for Management Science
+
+\begin{center}
+\includegraphics[width =0.7\textwidth]{"materials/fisar_et_al_2023_policy.jpeg"} \\
+Fišar et al. (2023, Management Science)
+\end{center}
+
 ## Observational Data: Paper-level Sharing over Time

### 2024-10-26 code/figure_functions.R

@@ -1,5 +1,7 @@
 library(tidyverse)
 library(ggbeeswarm)
+library(readr)
+library(readxl)
 
 # Inspiration for plot below is from 
 # http://rnotr.com/likert/ggplot/barometer/likert-plots/
@@ -167,4 +169,139 @@ pre_reg_over_time_plot <- function(df) {
 			text=element_text(family="Times")
 		) 
 	
+}
+
+
+
+byu_fields_comp <- function(byu_author_data, sd_data) {
+  
+  # Method and Research Area Mappings
+  methodarea_map <- c('1' = 'method_archival', '2' = 'method_experimental', '3' = 'method_analytical', '4' = 'method_other')
+  researcharea_map <- c('1' = 'area_financial', '2' = 'area_managerial', '3' = 'area_tax', '4' = 'area_audit', '5' = 'area_ais', '7' = 'area_other')
+  
+  byu_author_data <- byu_author_data %>%
+    mutate(
+      methodarea_cleaned = str_extract_all(methodarea, "\\d+"),
+      researcharea_cleaned = str_extract_all(researcharea, "\\d+")
+    )
+  
+  for (key in names(methodarea_map)) {
+    byu_author_data[[methodarea_map[[key]]]] <- sapply(byu_author_data$methodarea_cleaned, function(x) key %in% x)
+  }
+  
+  for (key in names(researcharea_map)) {
+    byu_author_data[[researcharea_map[[key]]]] <- sapply(byu_author_data$researcharea_cleaned, function(x) key %in% x)
+  }
+  
+  byu_author_data <- byu_author_data %>%
+    select(-methodarea_cleaned, -researcharea_cleaned)
+  
+  # Prepare data for comparison
+  field_order <- c('Financial accounting and reporting', 'Managerial accounting', 'Auditing', 'Taxation', 'Accounting information systems', 'Other')
+  
+  byu_to_sample_field_map <- c('area_financial' = 'Financial accounting and reporting', 'area_managerial' = 'Managerial accounting', 'area_audit' = 'Auditing', 'area_tax' = 'Taxation', 'area_ais' = 'Accounting information systems', 'area_other' = 'Other')
+  
+  byu_field_counts <- colSums(byu_author_data[, names(byu_to_sample_field_map)])
+  names(byu_field_counts) <- byu_to_sample_field_map[names(byu_field_counts)]
+  byu_field_counts <- byu_field_counts[field_order]
+  
+  our_field_counts <- table(factor(sd_data$demog_field, levels = field_order))
[…]

### 2024-10-30 docs/paper.qmd
SSRN paper version

@@
   | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management.
-We thank Kris Hardies as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback.
+We thank Kris Hardies, Maximilian Müller as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback.
 Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings.
@@
 
-Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as were used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods.
+Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as those used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2020; @G_2023; @S_2023; @CGL_2024], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods.
 Open science implies conducting research in ways that allow others to collaborate and contribute.
@@
 
-Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes towards open science clearly differ from those of other social science researchers.
+Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes toward open science clearly differ from those of other social science researchers.
 Most prominently, accounting researchers tend to hold a generally more pessimistic view of the reproducibility of influential work within their field.
@@
 Given this finding, one would expect accounting researchers to take a proactive stance and embrace two prominent open science methods that are expected to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.
-Turning first to the public sharing of research materials, we document that, again compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important.
+Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important.
 Familiarity is largest for respondents using archival, field, and experimental methods and lowest for respondents using qualitative methods, who also perceive the sharing of research materials as less important.
@@
 In addition, our respondents believe that about 44% of them favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials.
-Although this sounds comforting and consistent with a general supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community.
+Although this sounds comforting and consistent with a generally supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community.
 This assessment and the gap it reveals differ significantly across methodological areas.
@@
 This number is similar to the self-reported perception of actual research material sharing in our survey (i.e., 38%).
-However, when we inspect the observational data further, we find that research material sharing in accounting is largely an occasional compliance activity.
-For instance for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing.
+However, when we further inspect the observational data, we find that research material sharing in accounting is largely an occasional compliance activity.
+For instance, for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing.
 Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%.
@@
 We find no evidence that this probability is affected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope of the sharing decision (public versus private sharing).
-Based on the verbal response of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general.
+Based on the verbal responses of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general.
 Also, they share because they want to support their fellow researchers.
@@
 
-Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it.
+Collectively, our evidence speaks to the ongoing debate about reproducibility and openness of accounting research.
+We extend the survey evidence by @HLL_2020 by providing more detailed and current insights on the perceived benefits and costs of open science methods and by benchmarking the attitudes of the fields with neighboring disciplines.
+Also, we collaborate recent evidence on the robustness of empirical accounting [@G_2023; @S_2023; @LSA_2024; @CGL_2024] and management science [@FGHKO_2023] work by exploring some of the underlying reasons why our discipline might (or might not) have a reproducibility issue.
+
+Our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work and the ability of research material sharing and pre-registration to improve it.
 This is consistent with these tools currently being less established in the accounting domain than in other fields.
 The challenges that hinder reproducibility and the potential effectiveness of open science methods vary across methodological paradigms.
-Qualitative research faces different challenges than archival quantitative work, and they both differ again from experimental studies.
+Qualitative research faces challenges different from archival quantitative work, and they both differ again from experimental studies.
 We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.
@@
 Accounting is a field within the social sciences.
-As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting.
-In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@BCLW_2010].
+As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@MS_2019; @AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting.
+In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@LT_2005; @MS_2019; @BCLW_2010].
 For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration.
 Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good.
-To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and very likely also the quality of research.
+To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and, most likely, also the quality of research.
 Even if they are not really reusable or reusing them would be prohibitively costly, they still reduce the costs of reproducing the original work, thereby reducing assurance costs.
-As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions) resulting in better financial reporting quality (better research).
-
-This means that similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large.
-While intrinsic motivation for good research can be expected to be a strong determinant for individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public.
-So, are there any private benefits of research material sharing?
+As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions), resulting in better financial reporting quality (better research).
+
+This means that, similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large.
+While intrinsic motivation for good research can be expected to be a strong determinant of individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public.
+So, are there any private benefits to sharing research materials?
 Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output.
@@
 One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the contemporary disclosure literature.
-Thus, for research materials sharing to be viable it is important that the costs of sharing are sufficiently low, especially for researchers that produce high quality work.
+Thus, for research materials sharing to be viable, it is important that the costs of sharing are sufficiently low, especially for researchers that produce high-quality work.
 Thus, it critically hinges on the above quality assurance process.
-Also, it depends on the direct and indirect costs of research material sharing to be bearable and to be at least comparable for high and low quality researchers.
+Also, it depends on the direct and indirect costs of research material sharing to be bearable and at least comparable for high- and low-quality researchers.
 
@@
 Preparing data, code and research procedures for dissemination requires time.
-While this time can be expected to also have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work.
+While this time can also be expected to have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work.
 Another important factor to consider is the cost of maintaining publicly available materials.
@@
 In a credence good market like research, signaling is a key mechanism to avoid market failure.
-Based on the discussion above, a critical aspect could be the proprietary cost of competition as one could argue that this cost is higher for high quality researchers with innovative ideas than for low quality researchers that will likely face limited demand for their materials.
-Also the risks of reputation costs or misuse of materials could be higher for high quality researchers.
-On the other hand, it can be argued that direct costs should be lower for high quality researchers because of superior skills.
-Finally, outside options should be generally higher for high quality researchers meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.
-
-The discussion should sound somewhat familiar to those that study voluntary disclosures by firms.
+Based on the discussion above, a critical aspect could be the proprietary cost of competition, as one could argue that this cost is higher for high quality researchers with innovative ideas than for low-quality researchers who will likely face limited demand for their materials.
+Also the risks of reputation costs or misuse of materials could be higher for high-quality researchers.
+On the other hand, it can be argued that direct costs should be lower for high-quality researchers because of superior skills.
+Finally, outside options should be generally higher for high-quality researchers, meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.
+
+The discussion should sound somewhat familiar to those who study voluntary disclosures by firms.
 What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs.
 Instead, they are employed by academic institutions or act as civil servants.
-This can to some extend mute the relevance of the benefits and the costs outlined above, at least for those researchers that hold tenured positions.
-In addition, the employing institutions might also interact with the decision whether or not to make research materials available.
+This can, to some extent, mute the relevance of the benefits and the costs outlined above, at least for researchers with tenured positions.
+In addition, the employing institutions might also interact with the decision of whether or not to make research materials available.
 They are designing performance and tenure evaluation criteria that incentivize researchers.
@@
 Based on the public announcements of many leading academic institutions, it seems as if these are generally advocating the positive externalities of research material sharing.
-However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they are valuing individual research achievements in form of publications and only rarely publicly available research materials.
-
-Finally, publishers and journals are influential for research material sharing decisions as well.
-Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision to a mandatory disclosure requirement.
-While journals also compete for the best papers and it is an interesting question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.
+However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they value individual research achievements in form of publications and only rarely publicly available research materials.
+
+Finally, publishers and journals are influential in research material sharing decisions as well.
+Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision into a mandatory disclosure requirement.
+While journals also compete for the best papers and it is interesting to question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.
 
@@
 For a complete overview of the survey questions included in our study, please see Appendix A.
-All answers can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard} and the data itself are available in our public \href{https://github.com/joachim-gassen/osacc/}{GitHub repository} .
+All answers can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard} and the data is available in our public \href{https://github.com/joachim-gassen/osacc/}{GitHub repository} .
 
@@
 Table 2 displays response demographics and characteristics based on a sample of up to 229 observations.
-Panel A reveals that the majority of the respondents is male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).
+Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).
 Panel B of Table 2 contrasts our respondent sample with our sampling population.
@@
 The first research question of our study is to explore how accounting researchers perceive the reproducibility of influential findings in their field.
-Table 3 provides a comprehensive overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers with those of researchers in other disciplines as recorded by @FLCPSWMBP_2023, based on their question, "How confident are you that the influential research findings in \[discipline\] would replicate?" Notably, we adapted the wording in this question from "replicate" to "reproduce" to ensure clarity for our audience, recognizing the nuanced distinctions between these terms across various research methodologies.
-The term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000].
+Table 3 provides a comprehensive overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers with those of researchers in other disciplines, as recorded by @FLCPSWMBP_2023, based on their question, "How confident are you that the influential research findings in \[discipline\] would replicate?" Notably, we adapted the wording in this question from "replicate" to "reproduce" to ensure clarity for our audience, recognizing the nuanced distinctions between these terms across various research methodologies.
+The term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2020].
 It implies the ability to recreate the results of prior studies using the same materials, procedures, and data as were used by the original researchers [@NSF_2015].
@@
 In a field fixed effect regression, in which we use Accounting as the baseline, we find that all four fixed field effects are statistically different from zero (two-tailed p-value \< 0.01).
-This skepticism is consistent with us accountants being more concerned about research quality hinting at the existence of a credence-good problem that open science methods are designed to address.
+This skepticism is consistent with us accountants being more concerned about research quality, hinting at the existence of a credence-good problem that open science methods are designed to address.
 
@@
 Table 4 presents their assessments regarding the reproducibility of influential findings across three panels.
-Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.
+Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B focuses on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.
 
@@
 Given this skepticism and following our discussion in section 2, one might expect accounting researchers to take a proactive stance on open science approaches, particularly regarding the sharing of research materials.
-Following the old proverb by Supreme Court Justice Luis Brandeis "sunlight is the best disinfectant" one would expect accountants to support increased transparency in research.
+Following the old proverb by Supreme Court Justice Luis Brandeis "sunlight is the best disinfectant," one would expect accountants to support increased transparency in research.
 The survey assesses this argument by asking respondents two questions about the practice of sharing research materials, which we define as the practice of sharing data, code, and research procedures.
@@
 To visualize the differences between these three questions, Figure 5 displays scatter box plots, one for each question and separately for each methodology.
-First, examining the three plots for the sample as a whole, the clear visual pattern emerges that the assessments of actual sharing behavior among accounting researchers lag behind assessments of whether accounting researchers favor sharing, which, in turn, lags behind assessment of whether editors value sharing.
+First, examining the three plots for the sample as a whole, a clear visual pattern emerges that the assessments of actual sharing behavior among accounting researchers lag behind assessments of whether accounting researchers favor sharing, which, in turn, lags behind assessments of whether editors value sharing.
 This pattern seems starker for respondents in the Archival/Field category.
 These findings suggest a contrast between the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior.
-In other words: We believe that we should share and we also state that we do but we do not believe that others do.
+In other words: We believe that we should share, and we also state that we do, but we do not believe that others do.
 
@@
 We also find that they are less familiar with research materials sharing as an open science practice that helps address reproducibility and that they find that practice less important.
-Besides research material sharing, our survey also covers a second Open Science practice: Pre-registration.
+Besides research material sharing, our survey also covers a second Open Science practice: Pre-registration.[^6]
 
@@
 Panel A considers respondents' familiarity with the practice itself.
-We asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^6] The results in Panel A suggest accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
+We asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^7] The results in Panel A suggest that accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
 They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010).
@@
 Panel B reports data on the first-time respondents pre-registered.
-It is based on the question: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^7] The findings show a clear pattern: Accounting researchers started pre-registering their studies significantly later than researchers in other social science fields (two-tailed p-value \< 0.010).
+It is based on the question: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^8] The findings show a clear pattern: Accounting researchers started pre-registering their studies significantly later than researchers in other social science fields (two-tailed p-value \< 0.010).
 They started around 2018, compared to 2015-2016 for the other fields.
@@
 
-Panel C examines trustworthiness, showing data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^8] Results indicate no apparent differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100).
+Panel C examines trustworthiness, showing data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^9] Results indicate no apparent differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100).
 However, the perceived increase in trustworthiness when pre-registering is less in accounting compared to psychology and sociology (two-tailed p-value \< 0.010).
@@
 If they do, we collect whether they share research materials over these channels.
-In addition, we use Scopus to identify all studies that these authors published since 2016 and verify whether these publications' DOI URLs reference research material sharing.[^9] We also assess various pre-registration platforms to assess whether our authors have used pre-registration.
-We only were able to identify for `r sum(by_author$has_prereged)` authors clear evidence that they have pre-registered a study.
-These cases are linked to the registered report initiative of JAR.
+In addition, we use Scopus to identify all studies that these authors have published since 2016 and verify whether these publications' DOI URLs reference research material sharing.[^10] We also assess various pre-registration platforms to assess whether our authors have used pre-registration.
+We were only able to identify for `r sum(by_author$has_prereged)` authors clear evidence that they have pre-registered a study.
+These cases are linked to JAR's registered report initiative.
 Therefore, this reminder of this section solely focuses on research material sharing.
@@
 We find that `r sum(by_author$has_made_resmat_available)` % of our authors share research materials.
-This number and its corresponding binomial confidence interval (30 to 49 %) are lower that the percentage of respondents that stated in the survey that they at least sometimes share (57 %) but a little bit higher than the prescriptive sharing frequency that our respondents attributed to other researchers (27 %).
+This number and its corresponding binomial confidence interval (30 to 49 %) are lower that the percentage of respondents who stated in the survey that they at least sometimes share (57 %) but a little bit higher than the prescriptive sharing frequency that our respondents attributed to other researchers (27 %).
 
@@
 Only 7.5 % of the paper DOI URLs reference research material sharing.
-As Figure 7 indicates, this share has mildly increased over time but even in recent years, the paper-level sharing percentage seems relatively modest.
+As Figure 7 indicates, this share has mildly increased over time, but even in recent years, the paper-level sharing percentage seems relatively modest.
 
@@
 This also becomes apparent from Panel A.
-If one omits research material sharing via these journals, the percentage of sharing accounting researchers drops from 39 % to 23 %.[^10]
+If one omits research material sharing via these journals, the percentage of sharing accounting researchers drops from 39 % to 23 %.[^11]
 
@@
 We take this as evidence that our participants see the public and also private benefits of data and code sharing.
-The following statement illustrates the importance of research material sharing helping other researchers nicely:
+The following statement illustrates the importance of research material sharing in helping other researchers nicely:
 
@@
 
-Informed by a voluntary diclosure themed discussion of the costs and benefits of open science activities in accounting, we conducted a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.
+Informed by a voluntary disclosure-themed discussion of the costs and benefits of open science activities in accounting, we conducted a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.
 Our results suggest that accounting researchers face an "open science dilemma." On the one hand, they are more skeptical about the reproducibility of their influential findings than other social science researchers are about their respective findings.
@@
 The only way to find out is to take stock.
-@LSA_2024 suggest reproduction studies in accounting might not be rare, and a majority of those confirm prior results.
-However, we need more systematic evidence on whether our findings reproduce and whether they can be replicated using new data and settings.
+A study that provides large-scale evidence in that matter is @CGL_2024 studying the discontinuity of p-values in empirical accounting research.
+They document that it exists and is somewhat larger than in economics [@BCH_2020] but smaller than in political science [@GM_2008a] and sociology [@GM_2008a].
+Using a different approach based on a set of replication exercises, @G_2023 finds post 2000 accounting studies to be "very fragile" and links this observation to p-hacking.
+Similar to us, both authors teams discuss research material sharing and pre-registration as potential remedies.[^12] On the other hand, @LSA_2024 suggest reproduction studies in accounting not to be rare, and that a majority of those confirm prior results.
+
+Given these and our insights, we argue that we need more systematic evidence on whether our findings reproduce and whether they can be replicated using new data and settings.
 An impressive exercise in that regard is the recent large-scale reproduction attempt of studies published in Management Science [@FGHKO_2023].
@@
 A closely related area where we see the potential of accounting data to develop a substantial impact is the collection and pre-processing of firm-time level web and electronic filing data.
-For the former, web scraping of corporate webpages can provide informative data [e.g., @BBB_2021], and for the latter, in particular, the upcoming electronic filing requirements for sustainability reports hold promise.
+For the former, web scraping of corporate webpages can provide informative data [e.g., @BBB_2024], and for the latter, in particular, the upcoming electronic filing requirements for sustainability reports hold promise.
 While researchers compete with established commercial data providers in this area, the need for research to study unstructured textual data makes it necessary and valuable to build research-focused data pipelines and products instead of simply trusting (and paying) commercial data vendors.
@@
 This is human but unfortunate, also because it leads to subtle "home biases" when it comes to sharing, potentially increasing academic inequality and hindering scientific progress.
-While the fear of being "scooped" can be addressed by sharing materials later in the publication process or publicly claiming intellectual ownership of ideas via pre-registration and use of well-established repositories, fears with regards to future researchers pointing to deficiencies in one's work and/or a general lack of trust are more challenging to overcome.
+While the fear of being "scooped" can be addressed by sharing materials later in the publication process or publicly claiming intellectual ownership of ideas via pre-registration and use of well-established repositories, fears with regard to future researchers pointing to deficiencies in one's work and/or a general lack of trust are more challenging to overcome.
 For both aspects, we need to work towards changing the error climate in the academic discipline.
@@
 
-[^6]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
-
-[^7]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"
-
-[^8]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
+[^6]: While parts of the economic [@O_2015; @BCHH_2024] and accounting literature [@CGL_2024] differentiate between pre-registrations (relatively short and standardized descriptions of study design) and pre-analysis plans (more detailed and elaborate plans outlining the technical details of a study, potentially also including analysis code, mock-up tables and figures), we use the term pre-registration as a broader notion, in line with @FLCPSWMBP_2023.
+
+[^7]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
+
+[^8]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"
+
+[^9]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
 This question is quite broad while relying on a five-point Likert scale evaluating self-reported favorability (i.e., Not at all in favor, Moderately not in favor, Neither in favor nor against, Moderately in favor, Very much in favor).
@@
 
-[^9]: The data collection manual for this process is available in this project's GitHub repository.
-
-[^10]: Untabulated analyses based on small frequencies provide suggestive evidence that, overall, the sharing frequencies are higher for general economics journals than for journals in the areas of accounting and finance.
+[^10]: The data collection manual for this process is available in this project's GitHub repository.
+
+[^11]: Untabulated analyses based on small frequencies provide suggestive evidence that, overall, the sharing frequencies are higher for general economics journals than for journals in the areas of accounting and finance.
+
+[^12]: In a related study, @BCHH_2024 study randomized controlled trial studies in economics and find that only pre-registrations that include pre-analysis plans show muted p-value discontinuities.

### 2025-02-18 docs/paper.qmd
new paper version

@@
 ---
+editor: source
 title: |
-  | How does the Accounting Research Community
-  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management.
-We thank Kris Hardies, Maximilian Müller as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback.
+  | How Does the Accounting Research Community
+  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin, while Jacqueline Klug and Victor van Pelt are affiliated with WHU - Otto Beisheim School of Management.
+We thank Kris Hardies, Stephan Hollander, and Maximilian Müller, as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, the TRR 266 Annual Conference, and WHU for providing helpful feedback.
 Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings.
 Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged.
-This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
+This study was approved by the WHU Ethical Review Board and supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
 author: 
@@
     documentclass: article
+    template-partials:
+      - materials/title.tex
     number-sections: true
@@
     ident: yes
-
-editor: visual
+ourabstract: We explore the attitudes of the accounting research community towards open science practices by surveying a sample of scholars who have published in leading accounting journals.
+Building on a discussion of the costs and benefits of open accounting research, we find that accounting researchers, compared to peers from other social science disciplines, are more skeptical about the reproducibility of their influential findings.
+Additionally, they state to be less familiar with publicly sharing research materials and to pre-register their study designs less frequently.
+Despite believing that both the accounting research community and journal editors support the sharing of research materials, there is skepticism regarding its actual prevalence.
+To supplement these survey insights, we analyze observational data, revealing that research material sharing is relatively uncommon and predominantly associated with journals enforcing data and code sharing policies.
+Finally, our data suggests that accounting researchers view research material sharing as yielding low private benefits but high private costs.
+We interpret our evidence as indicative of an "accounting open science dilemma" and propose strategies for effectively addressing this issue.
 
@@
 
-sd <- readRDS("../data/generated/survey_response.rds")
+sr <- readRDS("../data/generated/survey_response.rds")
 mr <- readRDS("../data/generated/merged_response.rds")
+vr <- readRDS("../data/generated/verbal_response_coded.rds")
+
 vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
@@
 papers <- read_csv("../data/external/obs_data_papers_anon.csv", show_col_types = FALSE)
+
+sr$exp_tment_collab <- 1 - sr$exp_tment_control
+svr <-sr %>% left_join(vr %>% select(-exp_reflect), by = "id")
+
+modh1 <- lm(exp_pct_share ~ exp_tment_collab, data = sr)
+modh2 <- lm(exp_pct_share ~ exp_tment_private, data = sr)
+modh3 <- lm(exp_pct_share ~ exp_tment_collab*exp_tment_private, data = sr)
 
@@
 }
-
-```
+```
+
+::: {.content-visible when-meta="paper-titlepage"}
 
@@
 \singlespace
-To understand how the accounting research community thinks about open science, we survey a sample of scholars who have published in leading accounting journals.
-Building on a voluntary disclosure-themed discussion of the costs and benefits of open accounting research, we document that accounting researchers tend to be more skeptical about the reproducibility of their influential findings than researchers from other social science areas are about theirs.
-Also, they are less familiar with the public sharing of research materials and pre-register their study designs less often.
-While they believe that accounting researchers in general and editors in particular favor research material sharing, they are skeptical about its actual prevalence in the accounting research community.
-We contrast these survey results with observational data, documenting that research material sharing is indeed relatively rare and often linked to journals with data and code sharing policies.
-We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
+```
+
+{{< meta ourabstract >}}
+
+```{=tex}
 \end{abstract}
-```
-```{=tex}
 \vspace{0.5cm}
@@
 ```
+
+:::
+
+::: {.content-visible when-meta="paper-body"}
+
+```{=tex}
 \pagebreak
-
 \setcounter{page}{1}
+```
+
+::: {.content-visible when-meta="anonymize"}
+
+```{=tex}
+\begin{center}
+\Large
+\textbf{How Does the Accounting Research Community\\Think About Open Science?}
+\normalsize
+\end{center}
+\begin{abstract}
+\singlespace
+```
+
+{{< meta ourabstract >}}
+
+```{=tex}
+\end{abstract}
+\vspace{0.5cm}
+```
+
+:::
 
@@
 
-Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as those used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2020; @G_2023; @S_2023; @CGL_2024], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods.
+Cumulative research relies on reproducibility, which refers to the ability to recreate the results of previous studies using the same materials as the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2020; @G_2023; @S_2023; @CGL_2024], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods.
 Open science implies conducting research in ways that allow others to collaborate and contribute.
-Two central open science methods that have been put forward as strategies to improve the reproducibility of our work are the public sharing of research materials and the pre-registration of study plans.
-Over the last years, there has been a significant uptake of these open sciences methods in social science areas outside of accounting [@FLCPSWMBP_2023].
-
-Research material sharing and pre-registrations can be understood as disclosure mechanisms that allow researchers to contribute public goods to the research community while also signaling the quality of their work.
-However, limited individual benefits and significant direct as well as indirect costs make it likely that researchers, on average, will rationally under-engage in these activities, potentially resulting in a socially sub-optimal under-provision of public research materials and on overall lacking research transparency.
-Following these thoughts and building on prior literature in neighboring fields, we conduct a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.
-
-Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes toward open science clearly differ from those of other social science researchers.
-Most prominently, accounting researchers tend to hold a generally more pessimistic view of the reproducibility of influential work within their field.
-Compared to economists and sociologists, for example, accounting researchers are about half a point more skeptical on a 5-point Likert scale.
-Exploring this assessment across the respondents' demographics, we find this skepticism to be relatively stable.
-Analytical and qualitative researchers are somewhat more pessimistic.
-Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.
-
-Given this finding, one would expect accounting researchers to take a proactive stance and embrace two prominent open science methods that are expected to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.
-Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important.
-Familiarity is largest for respondents using archival, field, and experimental methods and lowest for respondents using qualitative methods, who also perceive the sharing of research materials as less important.
-
-Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in accounting researchers' perceived (prescriptive) importance of research material sharing, their stated willingness to share research materials, and their (descriptive) perception about actual sharing behavior in the accounting research community.
-57% of our respondents state that they, at least sometimes, publicly share their research materials.
-In addition, our respondents believe that about 44% of them favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials.
-Although this sounds comforting and consistent with a generally supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community.
-This assessment and the gap it reveals differ significantly across methodological areas.
-Analytical researchers have the most narrow gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials).
-Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share).
-The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).
-
-Regarding pre-registration, accounting researchers seem as familiar with the concept as other social science researchers.
-However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%).
-Their trust in pre-registered work is generally comparable with other social science researchers but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rate of pre-registration).
-A detailed look into differences across methodological fields also reflects this, as we find that experimental researchers use pre-registration most (28%) and express the strongest belief that it increases the trustworthiness of research.
-
-To contrast these perceptions from our survey with actual behavior, we gather additional observational data from a country-stratified random sample of `r nrow(authors)` authors of our target population.
-We find evidence for at least some form of research material sharing for 39% of the authors in this sample.
-This number is similar to the self-reported perception of actual research material sharing in our survey (i.e., 38%).
-However, when we further inspect the observational data, we find that research material sharing in accounting is largely an occasional compliance activity.
-For instance, for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing.
+Two key open science methods proposed to enhance the reproducibility of research include the public sharing of research materials and the pre-registration of study plans.
+In recent years, there has been a noticeable increase in the adoption of these open science methods in social sciences [@FLCPSWMBP_2023].
+
+[^1]: The terms "reproduction" and "replication" are at times used as synonyms but have different meanings.
+Reproduction refers to achieving the same results of a prior study using the same materials (code, procedures, and data), while replication refers to duplicating the results of a of a prior study using the same code and procedures but new data [@NSF_2015; @BCKU_2024].
+For a more in-depth discussion of the differences and related terminological debate, see @DJ_2024.
+
+The sharing of research materials and the use of pre-registrations can be understood as disclosure mechanisms that enable researchers to contribute public goods to the academic community while also signaling the quality of their work.
+Despite their potential benefits, researchers may rationally under-engage in these activities due to limited private benefits and substantial direct and indirect costs.
+This could lead to a socially sub-optimal provision of public research materials causing a general lack of research transparency.
+Starting from this conceptual framework, we conduct a survey among accounting researchers to explore their perceptions and attitudes towards open science.
+
+Based on the responses of `r nrow(sr)` published accounting researchers, our findings reveal that the accounting community's attitudes towards open science clearly differ from the views of other social scientists.
+Notably, accounting researchers exhibit a generally more pessimistic perspective on the reproducibility of their domain's influential work.
+In contrast to economists and sociologists, for instance, accounting researchers are approximately half a point more skeptical on a 5-point Likert scale.
+Both analytical and qualitative researchers demonstrate heightened levels of skepticism.
+Analytical researchers are particularly critical of research employing non-analytical methods.
+This indicates that methodological differences might influence perceptions of research reproducibility within the field of accounting.
+
+Given these findings, it could be expected that accounting researchers would adopt a proactive stance and embrace open science practices to enhance research reproducibility.
+However, our data reveal that, compared to their counterparts in other social science disciplines, accounting researchers state to be less familiar with the practice of publicly sharing research materials and assign it less importance.
+Respondents using archival, field, and experimental methods demonstrate the highest familiarity with this practice.
+Conversely, those employing qualitative methods report both the least familiarity and a diminished perception of its significance.
+This suggests that methodological orientation may influence attitudes toward the adoption of open science practices within the field of accounting.
+
+Similar to, albeit even more pronounced than, other social science researchers, accounting researchers exhibit a disparity between their perceived importance of sharing research materials (prescriptive), their willingness to do so (stated), and their perception of actual sharing practices within their community (descriptive).
+While 57% of respondents report that they at least sometimes share their research materials publicly, only about 44% believe that this practice is favored among their peers.
+Interestingly, they estimate that 61% of top-six accounting journal editors support material sharing.
+This might suggest a generally supportive stance within the community.
+However, the view of the reality is more sobering: when asked about actual sharing behavior, our respondents estimate on average that only 27% of accounting researchers actually publicly share research materials.
+These perceptions vary significantly across methodological areas too.
+Analytical researchers demonstrate the narrowest gap, expecting 43% of accounting researchers to be in favor of sharing, while estimating that 38% actually do so.
+In contrast, archival researchers report the widest gap, with 45% expected to support sharing but only 24% expected to engage in it.
+Qualitative researchers report the lowest figures overall, with just 36% perceiving support for sharing and estimating that only 18% engage in the practice.
+This variability underscores a significant disparity between the perceived and actual sharing of research materials in accounting academia, particularly across different methodological approaches.
+
+In terms of pre-registration, accounting researchers exhibit a familiarity with the concept similar to that of their peers in other social sciences.
+Despite this, they report adopting pre-registration practices approximately two years later than their counterparts and using it less often, with only 17% practicing pre-registration compared to 27% in other fields.
+While their trust in pre-registered work aligns with that of other social science researchers, it notably falls short of the high trust levels seen in Psychology, where pre-registration is most prevalent.
+
+To contrast these perceptions with actual behavior, we collected additional observational data from a country-stratified random sample of `r nrow(authors)` authors within our target population.
+Our findings indicate that 39% of these authors engage in some form of research material sharing, significantly lower than the 57% of our respondents claiming that they at least sometimes share research data but higher than the skeptical mean of 27% that they estimate for the actual sharing rate.
+A deeper analysis of the observational data reveals that in accounting, material sharing often appears as an occasional compliance measure.
+Specifically, only 7.5% of the papers authored by individuals in this dataset are published with accessible research materials.
 Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%.
-Furthermore, we document very few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.
-
-In light of these numbers, a logical next step is to explore the main rationales for and against sharing research materials.
-We do so based on a short experimental design using a hypothetical scenario and by using our survey data.[^2] In our hypothetical scenario involving a fellow researcher requesting access to participants' research materials, our participants state that they would be very likely to share on average (mean probability is 72%).
-We find no evidence that this probability is affected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope of the sharing decision (public versus private sharing).
-Based on the verbal responses of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general.
-Also, they share because they want to support their fellow researchers.
-The most commonly stated reasons for not sharing research materials are the proprietary nature of the data used (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%).
-The reasons differ across methods.
-For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).
-
-Collectively, our evidence speaks to the ongoing debate about reproducibility and openness of accounting research.
-We extend the survey evidence by @HLL_2020 by providing more detailed and current insights on the perceived benefits and costs of open science methods and by benchmarking the attitudes of the fields with neighboring disciplines.
-Also, we collaborate recent evidence on the robustness of empirical accounting [@G_2023; @S_2023; @LSA_2024; @CGL_2024] and management science [@FGHKO_2023] work by exploring some of the underlying reasons why our discipline might (or might not) have a reproducibility issue.
-
-Our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work and the ability of research material sharing and pre-registration to improve it.
-This is consistent with these tools currently being less established in the accounting domain than in other fields.
-The challenges that hinder reproducibility and the potential effectiveness of open science methods vary across methodological paradigms.
-Qualitative research faces challenges different from archival quantitative work, and they both differ again from experimental studies.
-We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.
+Furthermore, we document relatively few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.
+
+In light of these findings, a logical next step is to investigate the primary rationales for and against sharing research materials.
+We approach this through a brief experimental design involving a hypothetical scenario.[^2] In the scenario, accounting researchers were asked how likely they would be to share their research materials with a fellow researcher upon request.
+They reported an average likelihood of 72%.
+The probability of sharing was unaffected by the randomized rationale provided (i.e., whether the fellow researcher expressed an intent to collaborate or control) or the decision's scope (i.e., whether the fellow researcher requested to share the research materials publicly versus privately).
+Their reflections reveal that research material sharing in the hypothetical scenario is driven by a belief that it enhances both the quality of respondents' research and of research in general.
+Additionally, there is a desire to support fellow researchers.
+The most frequently cited reasons for not sharing include the proprietary nature of the data (noted by 56% of respondents), the time required to make materials available (30% of respondents), and the fear of being scooped once materials are public (23% of the respondents).
+The reasons given for withholding research materials in the hypothetical scenario vary across research methodologies.
+For qualitative researchers, issues with deidentification are notably prominent (46%).
+Meanwhile, analytical researchers view the time investment needed to prepare materials as less of a deterrent compared to other researchers (only 9.5% versus 30% overall).
+
+[^2]: We pre-registered this experimental part of our study at the [Open Science Foundation (link omitted for review)]{.content-visible when-meta="anonymize"}[[Open Science Foundation](https://osf.io/frmzt/)]{.content-visible unless-meta="anonymize"}.
+
+Collectively, our findings indicate an "accounting open science dilemma": while accounting researchers express skepticism about the reproducibility of their research, they also question the efficacy of open science methods, such as research material sharing and pre-registration, in improving it.
+This dual skepticism may explain why these open science methods are currently less established in the accounting domain than in other fields.
+The assessments vary across methodological paradigms.
+Qualitative research faces challenges different from archival work, and they both differ again from experimental studies.
+In the concluding section of our paper, we discuss these challenges and offer recommendations to how the diagnosed dilemma might be overcome.
+
+Our study contributes to the ongoing debate on reproducibility and transparency of accounting research.
+By building on the survey evidence presented by @HLL_2020, we provide more comprehensive and timely insights into accounting researchers' views regarding the reproducibility of their influential work, as well as the perceived advantages and disadvantages of open science practices.
+Furthermore, our study benchmarks these findings against those from related disciplines within the social sciences, facilitating a rough comparative analysis of how accounting researchers' perceptions align or differ from their peers in economics, psychology, sociology, and political science.
+Additionally, we corroborate recent evidence concerning the robustness of empirical work in accounting [@G_2023; @S_2023; @LSA_2024; @CGL_2024] and management science [@FGHKO_2023] by delving deeper into potential reasons why the discipline of accounting may, or may not, face issues with reproducibility.
 
@@
 
-Accounting is a field within the social sciences.
-As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@MS_2019; @AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting.
-In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@LT_2005; @MS_2019; @BCLW_2010].
-For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration.
+Many of the arguments that have been crafted around the costs and benefits of open science in general [@MS_2019; @AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023; @BCKU_2024] also apply to the field of accounting.
+Below, we present and extend some of these thoughts in a voluntary disclosure-inspired framework [@LT_2005; @MS_2019; @BCLW_2010].
+For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration as well.
 Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good.
 To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and, most likely, also the quality of research.
-Even if they are not really reusable or reusing them would be prohibitively costly, they still reduce the costs of reproducing the original work, thereby reducing assurance costs.
-As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions), resulting in better financial reporting quality (better research).
+Even if they are not reusable, they still reduce the costs of reproducing the original work, thereby reducing assurance costs.
+In analogy to classic auditing research [e.g., @S_1980]: reduced assurance costs should lead to an overall increase in assurance activities, ultimately resulting in better research quality.
 
@@
 Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output.
-First, it increases the likelihood that mistakes, conditionally on being present, are being detected.
-As it seems safe to assume that such incidents impose a cost on sharing researchers, this should increase their incentives to increase research quality prior to sharing.
-Second, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study.
-Finally, uncovered mistakes are an important learning opportunity, likely improving research quality in the long run.
+First, it increases the likelihood that mistakes, if present, are being detected.
+As such incidents likely impose a cost on sharing researchers, this should increase research care prior to sharing.
+Second and related, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study.
+Uncovered mistakes can also be an important learning opportunity, improving research quality in the long run.
 
@@
 In ideal circumstances, we should obtain the well-known unraveling result where researchers even share and improve low-quality research because the research community would otherwise assume the worst [@M_1981].
-One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the contemporary disclosure literature.
-Thus, for research materials sharing to be viable, it is important that the costs of sharing are sufficiently low, especially for researchers that produce high-quality work.
-Thus, it critically hinges on the above quality assurance process.
-Also, it depends on the direct and indirect costs of research material sharing to be bearable and at least comparable for high- and low-quality researchers.
-
-The direct costs of research material sharing can be sizable.
-Preparing data, code and research procedures for dissemination requires time.
-While this time can also be expected to have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work.
+One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the disclosure literature.
+For research materials sharing to unravel, it is important that the costs of sharing are sufficiently low, especially for researchers that produce high-quality work.
+
+The direct costs of research material sharing can be sizable as preparing data, code and research procedures for dissemination requires care, and care requires time.
+While care will also improve quality (see above), at least some of the documentation and code refactoring work to increase accessibility and reusability will not directly pay off on the quality of the underlying work.
 Another important factor to consider is the cost of maintaining publicly available materials.
-While some replication packages or similar materials are static in nature and require only limited maintenance, data and code packages can require ongoing updating and support activities.
+While some replication packages or similar materials are static in nature and require only limited maintenance, most data and code packages require ongoing updating and support activities.
 One important aspect of maintenance costs is that they increase significantly with public demand.
-As demand is directly linked to the scientific impact of the underlying work it can be argued that high maintenance cost sharing activities are likely to also be high benefit activities.
-
-The indirect costs of research material sharing are first and foremost linked to the quality assurance process outlined above.
-Flaws in publicly shared research materials can trigger more behavioral effects (shame, regret) but also reputation costs.
+As demand is directly linked to the scientific impact of the underlying work, high maintenance cost sharing activities are likely to also be high parivate and public benefit activities.
+
+The indirect costs of research material sharing are, first and foremost, linked to the quality assurance process outlined above.
+Flaws in publicly shared research materials can trigger behavioral (shame and regret) and reputation costs.
+Specifically, accounting researchers may implicitly assume that reproduction failures could lead others to suspect questionable research practices.
+However, this suspicion might be unwarranted, as failed reproductions can result from honest mistakes.
 Another important aspect are proprietary costs from scientific competition.
@@
 
-Rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs.
+In this simplified disclosure framework, rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs.
 Whether this happens will critically depend on whether the signaling mechanism outlined above unfolds.
@@
 Based on the discussion above, a critical aspect could be the proprietary cost of competition, as one could argue that this cost is higher for high quality researchers with innovative ideas than for low-quality researchers who will likely face limited demand for their materials.
-Also the risks of reputation costs or misuse of materials could be higher for high-quality researchers.
+Also, the risks of reputation costs or misuse of materials could be higher for high-quality researchers.
 On the other hand, it can be argued that direct costs should be lower for high-quality researchers because of superior skills.
-Finally, outside options should be generally higher for high-quality researchers, meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.
-
-The discussion should sound somewhat familiar to those who study voluntary disclosures by firms.
+Finally, outside options should be generally higher for high-quality researchers, meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their research materials private.
+
+The discussion should sound familiar to those who study voluntary disclosures by firms.
 What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs.
@@
 They are designing performance and tenure evaluation criteria that incentivize researchers.
-Also, they compensate researchers for their time and they provide them with infrastructure that influences and at times drastically reduces the direct costs of research material sharing.
+Also, they compensate researchers for their time and they provide them with infrastructure that influences and, at times, drastically reduces the direct costs of research material sharing.
 They might even hold property rights on the intellectual capital that their employees generate.
@@
 Finally, publishers and journals are influential in research material sharing decisions as well.
-Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision into a mandatory disclosure requirement.
-While journals also compete for the best papers and it is interesting to question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.
+Leading journals have established rigorous data and code sharing guidelines, essentially transforming the voluntary disclosure decision into a mandatory disclosure requirement.
+While it is interesting to question how journal competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.
 
@@
 The first two questions are descriptive in nature.
-Assuming that the signaling mechanism above or other incentives have not succeeded in removing all insecurity about the reproducibility of influential accounting work, we expect to find some variation in our response with regard to research question one.
-More importantly, we want to compare the response of our sample with responses by researchers from other social science fields.
-The second question explores whether accounting researchers believe that research material sharing and pre-registration are viable strategies to increase the reproducibility of research.
-Again, comparing the views of accounting academics with the views of neighboring fields will be instrumental here.
+We compare the response of our sample with responses by researchers from other social science fields.
+While the first question sets the stage by assessing whether our participants sense accounting research to face a reproducibility crisis, the second question explores whether accounting researchers believe that research material sharing and pre-registration are viable strategies and sufficiently common to increase the reproducibility of research.
+Here too, comparing the views of accounting academics with the views of neighboring fields is essential for a comprehensive understanding of these practices within the wider academic community.
 
 The third question strives to understand the potential causes behind these assessments.
-Using a small experimental component, our survey tests whether two aspects of a hypothetical sharing request, its rationale (collaboration or control) and its scope (public versus private), affect the stated hypothetical likelihood of sharing.
+Using a small experimental component within our survey, we ask respondents how likely they would be to share their research materials with a fellow researcher.
+We examine whether respondents' sharing likelihood depends on two aspects of a hypothetical sharing request by a fellow researcher, namely, its rationale (i.e., whether the fellow researcher expressed an intent to collaborate or control) and its scope (i.e., whether the fellow researcher requests to share the research materials publicly versus privately).
 Our motivation for the treatments is that the rationale should shift the focus from benefits (collaboration) to costs (control) while the scope treatment should manipulate the salience of indirect costs.
-Besides studying the effect of these two experimental treatments, we also use verbal and structured survey response data to uncover perceived benefits and costs from research material sharing.
+Besides studying the effect of these two experimental treatments, we also use structured and unstructured survey response data to uncover perceived benefits and costs from research material sharing.
 
@@
 
-To ensure that our findings with respect to research questions one and two are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], published in Nature Communications.
-Similar to our survey, this study solicits the views of published researchers and PhD students on reproducibility, research material sharing, and pre-registration.
-However, there are key differences between the depth and target audience of our study and the study of @FLCPSWMBP_2023, warranting some adjustments.
-The latter lasted approximately 45 minutes and had a compensation element rewarding respondents for their participation.
-Our study, in contrast, is anonymous and has been designed to be completed in less than 10 minutes.
-It includes only mild incentivization in the form of a donation to UNICEF.
-Regardless of our adaptions, the ordering, phrasing, and answering scales of questions in our survey are similar.
-The adaptions enable us to considerably shorten the survey and to ensure that accounting researchers can relate the questions to their commonly accepted research practices.
-We pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions.
-Appendix C includes a matching table providing an overview of every question and answer scale that we adapted from @FLCPSWMBP_2023.
-
-Our survey has been designed using oTree [@CSW_2016].
+To strengthen the descriptive appeal of our findings by ensuring their comparability with those from other social science disciplines, we modified key questions from the "Survey of Open Science Practices and Attitudes in the Social Sciences" [@FLCPSWMBP_2023], published in Nature Communications.[^3] Like our survey, this study collects insights from published researchers and PhD students on topics such as reproducibility, sharing research materials, and pre-registration.
+However, due to differences in the scope and target audience, some adjustments were necessary for our study.
+While the referenced study [@FLCPSWMBP_2023] involved a 45-minute session with participant compensation, our survey is anonymous, designed for completion in under 10 minutes, and offers mild incentivization through donations to UNICEF.
+Our changes allow us to significantly condense the survey while ensuring relevance to accounting researchers and their established research practices.
+We pre-tested our adapted questions among a group of accounting doctoral students, and no issues were reported.
+[Online-]{.content-visible when-meta="online-appendix"}Appendix D provides a comprehensive matching table that contrasts each adapted question and its corresponding scale with the original questions used by @FLCPSWMBP_2023.
+
+[^3]: The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) while we collected our data towards the end of 2022.
+While it is plausible that the passage of time has led to increased awareness and adoption of open science practices among researchers, including those in accounting, the findings of @FLCPSWMBP_2023 document that the increasing time trend in the social sciences has faded out towards the end of their survey period.
+In addition, an increasing awareness and adoption of open science methods over time would not undermine our main findings that accounting research faces an Open Science dilemma.
+Specifically, compared to their peers, we find accounting researchers are more skeptical about the reproducibility of their work and lag behind in adopting two key Open Science practices designed to address these concerns even though they are surveyed two years later.
+
+Our survey was developed using oTree [@CSW_2016].
 The first stage of the survey includes questions about respondents' views on publicly sharing research materials, which we describe as comprising data, code, and research procedures.
@@
 We also ask them about their perceptions of the prevalence of sharing in the accounting research community, how often they tend to share, and whether they plan to share in the future.
-Conditional on whether respondents indicate that they do not always share, we also ask them for the reasons behind not sharing.
-Lastly, we ask respondents to estimate what percentage of accounting researchers favor sharing and their approximation of the percentage of editors of the top six accounting journals that believe sharing increases the value of a manuscript.
+For those who indicate less than consistent sharing practices, we further explore the reasons for not sharing.
+We also ask respondents to estimate the proportion of accounting researchers who support sharing and to gauge what percentage of editors from the top six accounting journals believe that sharing enhances a manuscript's value.
 
@@
 After eliciting respondents' perceptions on reproducibility, a set of questions explores their familiarity and experience with the practice of pre-registration.
-Lastly, we ask them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research.
+Lastly, we ask respondents about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research.
 The survey ends with a few demographic questions.
-For a complete overview of the survey questions included in our study, please see Appendix A.
-All answers can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard} and the data is available in our public \href{https://github.com/joachim-gassen/osacc/}{GitHub repository} .
+For a complete overview of the survey questions included in our study, please see [Online-]{.content-visible when-meta="online-appendix"}Appendix A.
+All answers can be explored using our [[survey dashboard](https://jgassen.shinyapps.io/osacc/)]{.content-visible unless-meta="anonymize"}[survey dashboard (link omitted for review)]{.content-visible when-meta="anonymize"} and the data is available in our public [[GitHub repository](https://github.com/joachim-gassen/osacc/)]{.content-visible unless-meta="anonymize"}[GitHub repository (link omitted for review)]{.content-visible when-meta="anonymize"}.
 
@@
 
-To recruit respondents for our survey, we identified authors who published in the "Top 6" accounting journals, i.e., Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review, over the period 2016 to 2021.
-We chose these six accounting journals because they are commonly characterized as the leading accounting journals within the academic accounting community.
-We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community.
-Yet, we believe that, taken together, these journals provide a sufficiently broad target population of accounting academics.
-
-We start compiling the list of authors from 2016 because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017].
-After receiving approval from an ethical review board and guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total of three reminders.
-We allowed potential respondents to opt out of future emails every time we reached out to them.
-Please see Appendix A for the invitation emails and all reminders.
+To recruit respondents for our survey, we targeted authors who published in the "Top 6" accounting journals between 2016 and 2021.[^4] These journals include Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, and The Accounting Review.[^5] Following approval from an ethical review board and ensuring the anonymity of participating respondents, we distributed initial survey invitations in November 2022, accompanied by three subsequent reminders.
+At each point of contact, we provided potential respondents with the option to opt-out from receiving further emails.
+For details on the invitation emails and all reminders, please refer to [Online-]{.content-visible when-meta="online-appendix"}Appendix A.
+
+[^4]: We started in 2016 as this marks the year when Open Science, and more specifically research reproducibility, became a prominent topic of discussion among academics in the social sciences, including accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017].
+
+[^5]: We selected these six journals because they are widely regarded as the leading journals within the academic accounting community.
+While we acknowledge that this is not an exhaustive list and understand there are varying views regarding the ranking of journals in the field, we believe that collectively, these six journals represent a sufficiently broad spectrum of accounting academics for our research purposes.
 
@@
 
-Table 1 presents our sample selection procedures.
-Out of 2,660 potential respondents identified, 118 were excluded due to operational reasons.[^3] Additionally, 206 respondents' initial emails bounced, indicating unreachable email addresses.
+Table 1 details our sample construction.
+Out of 2,660 potential respondents identified, 118 were excluded due to operational reasons.[^6] Additionally, 206 respondents' initial emails bounced, indicating unreachable email addresses.
 Among the remaining 2,336 successfully contacted accounting researchers, 391 initiated the study (15.4% of the total emails sent), 254 partially completed it (10.9% of the total emails sent), and 222 fully completed it (8.7% of the total emails sent).
-For our analyses, we employed a floating sample, which dynamically changes based on specific criteria, to maximize the use of the available data.
-For most descriptive analyses, we relied on the number of respondents who completed the entire study (n = 222).
-However, for certain descriptive analyses, depending on the specific question, we utilized a broader sample (n = 229) as seven respondents decided to leave out some of the demographic questions.
-Since our survey experiment component forms the first part of the study, we use the sample of respondents who completed the study up to that point (n = 254) for analysis.
+For our analyses, we employ a floating sample, which dynamically changes based on specific criteria, to maximize the use of the available data.
+For most descriptive analyses, we rely on the number of respondents who completed the entire study (n = 222).
+However, for certain descriptive analyses, depending on the specific question, we use a broader sample (n = 229) as seven respondents decided to leave out some of the demographic questions.
+Since our survey experiment component forms the first part of the instrument, we use the sample of respondents who completed the study up to that point (n = 254) for analysis.
+
+[^6]: We removed 41 authors because we found no email address, 41 authors because they appeared in the data twice with two author IDs but were the same person, 28 authors because they were a current member of one of our affiliated universities or academic research centers, 5 authors because they gave us advice for this study, 2 authors because they had passed away, and 1 author due to an incorrect email address.
 
@@
 Table 2 displays response demographics and characteristics based on a sample of up to 229 observations.
-Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).
+Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), and has Archival or Field Research as their primary research method (55.9%).
 Panel B of Table 2 contrasts our respondent sample with our sampling population.
 Given the anonymity of our response and the data that we can collect about our population, we can only directly compare the geographic dispersion of our sample.
-Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample.
+Panel B reveals that, in particular, researchers from North America (65.2%) and Europe (16.5%) are over-represented, and researchers from Asia are under-represented in the sample.
 Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance.
 However, it seems likely that the study's all-European author team might have positively influenced the European response.
-While we control for geographical effects in our response (not-tabulated but available using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.
+While we control for geographical effects in our response (not-tabulated but available using our [[survey dashboard](https://jgassen.shinyapps.io/osacc/)]{.content-visible unless-meta="anonymize"}[survey dashboard (link omitted for review)]{.content-visible when-meta="anonymize"}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.
 
@@
 Specifically, the BYU accounting rankings rank individual authors based on classifications of peer-reviewed articles in 12 accounting journals since 1990.
-We contacted the team behind the BYU rankings, and they generously provided their data to us.
+We contacted the team behind the BYU rankings, and they generously made their data available to us.
 The data includes `r format(nrow(byu), big.mark = ",")` authors and information on their methodologies as well as subfields.
@@
 A chi-square test does not reject the null that the two frequency distributions are the same (chi-square = 2.270, two-tailed p-value = 0.518).
+We conclude from these comparisons that our respondents reflect the methodological composition of accounting research reasonably well.
 
@@
 
-The first research question of our study is to explore how accounting researchers perceive the reproducibility of influential findings in their field.
-Table 3 provides a comprehensive overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers with those of researchers in other disciplines, as recorded by @FLCPSWMBP_2023, based on their question, "How confident are you that the influential research findings in \[discipline\] would replicate?" Notably, we adapted the wording in this question from "replicate" to "reproduce" to ensure clarity for our audience, recognizing the nuanced distinctions between these terms across various research methodologies.
-The term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2020].
-It implies the ability to recreate the results of prior studies using the same materials, procedures, and data as were used by the original researchers [@NSF_2015].
-In contrast, the term "replication" has different interpretations for different fields.
-For instance, for experimental researchers, it refers to a distinct activity than reproduction (i.e., repeating an experimental study with new participants), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same or similar data using the same procedures).
-In turn, the definition that @FLCPSWMBP_2023 use for replication ("test of whether new studies on the same topic in a broadly similar sample support the same results.") seems relatively close to what we believe the common understanding of reproduction is in the area of accounting is.
-If anything, our notion of reproduction seems less demanding than the replication definition by @FLCPSWMBP_2023.
+The first research question of our study investigates how accounting researchers perceive the reproducibility of influential findings within their field.
+Table 3 offers a detailed summary of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers with those of researchers in other disciplines, as documented by @FLCPSWMBP_2023, based on their question, "How confident are you that the influential research findings in \[discipline\] would replicate?" We deliberately adjusted the wording from "replicate" to "reproduce" to enhance clarity for our audience, recognizing the subtle distinctions between these terms across various research methodologies.
+The concept of "reproducibility" serves as a central theme in discussions throughout the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2020].
+It signifies the ability to recreate the results of prior studies using the same materials, procedures, and data as employed by the original researchers [@NSF_2015].
+In contrast, the term "replication" carries different interpretations across fields.
+For experimental researchers, it typically refers to conducting a new study with different participants, while for archival researchers, it involves re-analyzing the same or similar data using identical procedures.
+Notably, the definition provided by @FLCPSWMBP_2023 for replication—"a test of whether new studies on the same topic in a broadly similar sample support the same results"—aligns closely with what we conceive as the common understanding of reproduction in accounting.
+If anything, our notion of reproduction appears to be less stringent than the replication definition offered by @FLCPSWMBP_2023.
 
@@
 
-The results in Table 3 reveal that accounting researchers generally hold a more critical view of the reproducibility of our influential findings.
-Compared to their peers in economics and sociology, accounting researchers exhibit a greater degree of doubt about the reproducibility of their influential work, with a difference of about half a point on a 5-point Likert scale.
-This difference is less stark when we compare accounting researchers to researchers in the fields of Political Science and Psychology.
-In a field fixed effect regression, in which we use Accounting as the baseline, we find that all four fixed field effects are statistically different from zero (two-tailed p-value \< 0.01).
-This skepticism is consistent with us accountants being more concerned about research quality, hinting at the existence of a credence-good problem that open science methods are designed to address.
+The findings presented in Table 3 indicate that accounting researchers generally harbor a more critical perspective on the reproducibility of their field's influential findings.
+Specifically, compared to their counterparts in economics and sociology, accounting researchers demonstrate a heightened level of skepticism regarding the reproducibility of their significant work, with an observed difference of approximately half a point on a 5-point Likert scale.
+This disparity appears less pronounced when accounting researchers are compared to those in political science and psychology.
+However, using two-sample t-tests for assessing mean differences across fields, we find that Accounting academics are significantly more skeptical compared to those of the other four fields (all two-tailed p-values \<= `r myfmt(max(ct_pvalue(mr, "reprod", "demog_discipline", "Accounting", format = FALSE), 0.001))`).
+This is consistent with accountants being more concerned about research quality, hinting at the existence of a credence-good problem that open science methods are designed to address.
 
@@
 
-Figure 3 visually represents this skepticism, showing that 10.5% of accounting researchers are "Not at all confident" about the reproducibility of influential findings in their field.
-This percentage starkly contrasts the skepticism reported by economists (0.7%), political scientists (2.1%), psychologists (1.1%), and sociologists (1.3%), as found by @FLCPSWMBP_2023.
-In addition, this figure reveals that Accounting also has the lowest percentage of non-skeptics (i.e., researchers who are either moderately or extremely confident in the reproducibility of influential findings).
-That is, Accounting has about 39.3% non-skeptics, while Economics has 61.1%, Political Science has 45.8%, Psychology has 41.3%, and Sociology has 61.7%.
-The differences to Economics and Sociology, again, are the largest, while the differences to Political Science and Psychology are smaller.
-
-To delve deeper, we examine the assessments of reproducibility across different methodologies within Accounting.
-Accounting is not only a diverse discipline in terms of orientation and topic but also in terms of the methodologies its researchers employ.
-We distinguish among five categories: Analytical, Archival/Field, Experimental, Qualitative, and Survey.
-We asked respondents which of those categories best described their main methodological area, enabling us to categorize them in the data.
-Table 4 presents their assessments regarding the reproducibility of influential findings across three panels.
-Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B focuses on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.
+Figure 3 graphically illustrates the prevailing skepticism, revealing that 10.5% of accounting researchers express "Not at all confident" attitudes toward the reproducibility of influential findings in their field.
+This percentage starkly contrasts with the lower levels of skepticism observed among economists (0.7%), political scientists (2.1%), psychologists (1.1%), and sociologists (1.3%) as reported by @FLCPSWMBP_2023.
+Additionally, the figure indicates that accounting has the lowest proportion of non-skeptics—those moderately or extremely confident in the reproducibility of key findings—with only 39.3% falling into this category.
+In comparison, 61.1% of economists, 45.8% of political scientists, 41.3% of psychologists, and 61.7% of sociologists exhibit greater confidence.
+
+To gain a more nuanced understanding, we examine the assessments of reproducibility across various methodologies employed within the field of accounting.
+Accounting is characterized not only by its diversity in orientation and subject matter but also by the range of methodologies adopted by its researchers.
+We categorize these methodologies into five distinct groups: Analytical, Archival/Field, Experimental, Qualitative, and Survey.
+We asked respondents to identify which of these categories best described their primary methodological approach, allowing for clear categorization in our dataset.
+Table 4 presents their evaluations regarding the reproducibility of influential findings, organized into three panels.
+Panel A offers insights into reproducibility assessments within accounting as a whole, Panel B delves into evaluations specific to each respondent's main methodological area, and Panel C highlights the differences in assessments between accounting at large and their primary methodological focus.
 
@@
 
-The findings in Table 4 Panel A suggest that analytical and qualitative researchers are more pessimistic and skeptical about the reproducibility of influential findings in accounting as a whole than accounting researchers using other methodologies.
-In particular, analytical researchers are significantly less confident about the reproducibility of influential findings in accounting in general compared to those using Archival/Field and Experimental categories (two-tailed p-value \< 0.100).
-Interestingly, when evaluating their own methodological areas, analytical researchers display the highest confidence levels, as their average confidence is statistically higher than those reported by the other four methodologies (two-tailed p-value \< 0.100), suggesting a discrepancy between their views on the field as a whole and their specific research approaches.
-Qualitative research reports significantly lower average confidence than Analytical, Archival/Field, and Experimental Research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).
-
-Panel C presents the "assessment gap," which captures the difference in assessments of the reproducibility of influential findings in respondents' own methodological area versus accounting in general.
-A higher (lower) assessment gap indicates that respondents are more (less) confident in the reproducibility of influential findings in their methodological area compared to accounting in general.
-The findings of Panel C report that analytical researchers report the largest assessment gap, implying greater skepticism about the field's reproducibility as a whole compared to their own methodology.
-The average assessment gap reported for the Analytical category is also statistically different from the averages reported in the other four categories (two-tailed p-value \< 0.100).
-In contrast, the other methodological categories show no significant differences, suggesting a more uniform view across different research approaches within accounting.
+The findings presented in Table 4 Panel A highlight that both analytical and qualitative researchers exhibit a more skeptical outlook regarding the reproducibility of influential findings in the field of accounting compared to their counterparts employing different methodologies.
+Notably, analytical researchers demonstrate significantly lower confidence in the reproducibility of such findings in general when contrasted with those utilizing Archival/Field (`r ct_pvalue(sr, "reprod_acc", "demog_method", "Analytical")["Archival/Field"]`) and Experimental methodologies (`r ct_pvalue(sr, "reprod_acc", "demog_method", "Analytical")["Experimental"]`).
+Conversely, when assessing their own methodological domains in Table 4 Panel B, analytical researchers show the highest levels of confidence, with their average confidence being statistically greater than that reported by peers following the other four methodologies (all two-tailed p-values \<= `r myfmt(max(ct_pvalue(sr, "reprod_method", "demog_method", "Analytical", format = FALSE), 0.001))`).
+This indicates a notable discrepancy between their perception of the field at large and that of their specific research approaches.
+Additionally, qualitative researchers report significantly lower average confidence than those engaged in Analytical (`r ct_pvalue(sr, "reprod_method", "demog_method", "Qualitative")["Analytical"]`), Archival/Field (`r ct_pvalue(sr, "reprod_method", "demog_method", "Qualitative")["Archival/Field"]`), and Experimental Research (`r ct_pvalue(sr, "reprod_method", "demog_method", "Qualitative")["Experimental"]`).
+However, their confidence levels are similar to those in the Survey category.
+
+Panel C introduces the concept of the "assessment gap," measures the difference in assessments of the reproducibility of influential findings in respondents' own methodological area versus accounting as a whole.
+A larger assessment gap signifies greater confidence in the reproducibility of influential findings within one's own methodology relative to the broader field of accounting.
+The results displayed in Panel C reveal that analytical researchers exhibit the most substantial assessment gap, indicating a pronounced skepticism regarding the overall reproducibility of the field compared to their specialized methodological practices.
+Moreover, the average assessment gap for the Analytical category is significantly different from the averages reported across the other four categories (all two-tailed p-values \<= `r sr$reprod_method_delta <- as.numeric(sr$reprod_method) - as.numeric(sr$reprod_acc);  myfmt(max(ct_pvalue(sr, "reprod_method_delta", "demog_method", "Analytical", format = FALSE), 0.001))`).
+In contrast, no significant differences are observed among the other methodological categories, suggesting a more uniform view across different research approaches within accounting.
 
@@
 
-Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field relative to neighboring fields.
-Given this skepticism and following our discussion in section 2, one might expect accounting researchers to take a proactive stance on open science approaches, particularly regarding the sharing of research materials.
-Following the old proverb by Supreme Court Justice Luis Brandeis "sunlight is the best disinfectant," one would expect accountants to support increased transparency in research.
-The survey assesses this argument by asking respondents two questions about the practice of sharing research materials, which we define as the practice of sharing data, code, and research procedures.
-These two questions are also close adaptions of the survey done by @FLCPSWMBP_2023.
+Given the observed skepticism and as discussed in Section 2, one might anticipate that accounting researchers would adopt a proactive stance on open science methodologies.
+In line with the proverb by Supreme Court Justice Louis Brandeis, "sunlight is the best disinfectant," it seems reasonable to expect accountants to advocate for increased transparency in research practices.
+To evaluate this notion, the survey poses two questions regarding the practice of sharing research materials, which it defines as the practice of sharing data, code, and research procedures.
+These questions are closely adapted from the survey conducted by @FLCPSWMBP_2023, allowing for a comparative analysis of perspectives across fields.
 
@@
 
-The first question assesses respondents' familiarity with the practice of research materials sharing: "How familiar are you with the practice of publicly sharing research materials (i.e., data, code, and research procedures) for a completed study?"[^4] Table 5 Panel A shows that accounting researchers are generally less familiar with research materials sharing than their counterparts in other social sciences from the survey by @FLCPSWMBP_2023.
-Generally speaking, academics in the social sciences report being relatively aware of and familiar with the practice of research material sharing.
-However, the results do suggest that, compared to each of the other four fields in the social sciences, accounting researchers are significantly less familiar with the practice (two-tailed p-value \< 0.010).
-The second question captures respondents' perceived importance of research material sharing.
-[^5] Table 5 Panel B suggests a similar trend, whereby accounting researchers consider this practice less important than researchers in other social sciences (two-tailed p-value \< 0.010), a finding that underscores potential barriers to the adoption of open science principles.
+The first question evaluates respondents' familiarity with the practice of sharing research materials.
+Table 5, Panel A reveals that accounting researchers exhibit lower familiarity with research materials sharing compared to their peers in other social science disciplines.
+In general, academics within the social sciences report a reasonable degree of awareness and familiarity with this practice.
+However, our findings indicate that accounting researchers are significantly less familiar with it than those in all four other social science fields surveyed (all two-tailed p-values \<= `r myfmt(max(ct_pvalue(mr, "sharing_heard", "demog_discipline", "Accounting", format = FALSE), 0.001))`).
+The second question assesses respondents' perceived importance of research materials sharing.
+Table 5, Panel B highlights a similar trend: accounting researchers view this practice as less important compared to researchers in Economics (`r ct_pvalue(mr, "sharing_important", "demog_discipline", "Accounting")['Economics']`), Political Science (`r ct_pvalue(mr, "sharing_important", "demog_discipline", "Accounting")['Political Science']`), and Psychology (`r ct_pvalue(mr, "sharing_important", "demog_discipline", "Accounting")['Psychology']`) while viewing it as more important compared to researchers in Sociology (`r ct_pvalue(mr, "sharing_important", "demog_discipline", "Accounting")['Sociology']`).
 
@@
 
-Figure 4 graphically presents these findings, showing the frequencies along horizontal axes and centering them to a neutral midpoint.
-Only 39.6% of the accounting researchers deem research material sharing "very important" compared to higher percentages in other fields like Economics (51.7%), Political Science (48.1%), and Psychology (43.8%).
-Sociologists report a lower percentage of strong supporters (29.4%) than the accounting researchers in our sample, suggesting varied attitudes towards open science across the disciplines.
+Figure 4 provides a graphical representation of these findings, depicting frequencies along horizontal axes and aligning them to a neutral midpoint.
+In our study, only 39.6% of accounting researchers consider research material sharing "very important." This is notably lower than the percentages observed in other fields: Economics at 51.7%, Political Science at 48.1%, and Psychology at 43.8%.
+Sociologists report an even lower percentage of strong advocates, at 29.4%, compared to accounting researchers.
+These variations indicate differing attitudes towards open science across academic disciplines.
 
@@
 
-We further examine attitudes, namely familiarity with and the perceived importance of research materials sharing across methodologies within accounting.
-Again, we distinguish between five methodological areas (i.e., Analytical, Archival/Field, Experimental, Qualitative, and Survey).
-Table 6 displays assessments of the practice of research material sharing using two panels.
-Similar to Table 5, Table 6 Panel A reports about the familiarity with the practice (i.e., "How familiar are you with the practice of publicly sharing research materials (i.e., data, code, and research procedures) for a completed study?") and Panel B reports about assessed importance ("To what extent do you believe that publicly sharing research materials (i.e., data, code, and research procedures) is important for the advancement of accounting research?").
-
-Panel A shows that familiarity is larger for respondents using Archival and Field methods compared to respondents using Qualitative, Analytical, and Survey methods (two-tailed p-value \< 0.100).
-Moreover, we also find that respondents using Qualitative methods are less familiar with research material sharing compared to all four other categories (two-tailed p-value \< 0.100).
-Panel B shows that there are few significant differences in terms of the perceived importance of research material sharing across the methodologies.
-Only respondents in the Archival/Field category assess research material sharing as significantly more important than respondents using the Qualitative and Survey categories.
-Overall, these findings indicate that accounting researchers are, at the very least, not strong believers in the signaling value of research material sharing.
-This might be because they are simply relatively more unaware of the activity and/or they are assessing the benefits to be relatively lower or the costs to be relatively higher.
+We delve deeper into attitudes concerning the familiarity with, and perceived importance of, sharing research materials across different methodologies in accounting.
+Our analysis again distinguishes between five methodological domains: Analytical, Archival/Field, Experimental, Qualitative, and Survey.
+Panel A of Table 6 reveals that respondents who primarily use Archival and Field methods exhibit greater familiarity with research material sharing compared to those using Qualitative (`r ct_pvalue(sr, "sharing_familiar", "demog_method", "Archival/Field")['Qualitative']`), Analytical (`r ct_pvalue(sr, "sharing_familiar", "demog_method", "Archival/Field")['Analytical']`), and Survey methods (`r ct_pvalue(sr, "sharing_familiar", "demog_method", "Archival/Field")['Survey']`).
+Additionally, it is evident that individuals employing Qualitative methods are significantly less familiar with the practice than their counterparts in the other four methodological categories (all two-tailed p-values \<= `r myfmt(max(ct_pvalue(sr, "sharing_familiar", "demog_method", "Qualitative", format = FALSE), 0.001))`).
+In contrast, Panel B indicates that there are few notable differences in the perceived importance of research material sharing across the various methodologies.
+The only significant distinction is observed among respondents in the Archival/Field category, who view research material sharing as considerably more important than those using Qualitative (`r ct_pvalue(sr, "sharing_important", "demog_method", "Archival/Field")['Qualitative']`) and Survey (`r ct_pvalue(sr, "sharing_important", "demog_method", "Archival/Field")['Survey']`) methods.
+Overall, these findings suggest that accounting researchers may not strongly endorse the signaling value of research material sharing.
+This could be attributed to their relative unfamiliarity with the practice or the perception that its benefits are relatively low while costs appear high.
 
@@
 Next, our survey focuses on the perceived prescriptive and descriptive importance of research material sharing.
-Table 7 Panel A reports data on the frequency of sharing, revealing that an impressive 57% of the respondents state that they at least sometimes publicly share their research materials.
-We also find that stated sharing tendencies are significantly lower for respondents in the Qualitative and Survey categories compared to each of the three other methodological areas, i.e., the respondents in the Analytical, Archival, and Experimental categories (two-tailed p-value \< 0.100).
+Table 7 Panel A reports data on the frequency of sharing, revealing that 57% of the respondents state that they at least sometimes publicly share their research materials.
+We also find that stated sharing tendencies are significantly lower for respondents in the Qualitative (all two-tailed p-values \<= `r myfmt(max(ct_pvalue(sr, "sharing_use", "demog_method", "Qualitative", format = FALSE)[c("Analytical", "Archival/Field", "Experimental")], 0.001))`) and Survey (all two-tailed p-values \<= `r myfmt(max(ct_pvalue(sr, "sharing_use", "demog_method", "Survey", format = FALSE)[c("Analytical", "Archival/Field", "Experimental")], 0.001))`) categories compared to each of the three other methodological areas, i.e., the respondents in the Analytical, Archival, and Experimental categories.
 
@@
 
-Table 7 Panel B reports answers to three questions measuring respondents' perceptions of how important others consider research material sharing to be (i.e., prescriptive and descriptive importance).
+Table 7 Panel B reports answers to three questions measuring respondents' perceptions of how important others consider research material sharing to be.
 Namely, these three questions ask (1) what percentage of accounting researchers in general favor research material sharing, (2) what percentage of editors of the top six accounting journals believe it increases the value of a manuscript, and (3) what percentage of accounting researchers publicly share research materials.
@@
 First, examining the three plots for the sample as a whole, a clear visual pattern emerges that the assessments of actual sharing behavior among accounting researchers lag behind assessments of whether accounting researchers favor sharing, which, in turn, lags behind assessments of whether editors value sharing.
-This pattern seems starker for respondents in the Archival/Field category.
-These findings suggest a contrast between the perceived (prescriptive) importance of research material sharing and the perceived (descriptive) actual sharing behavior.
-In other words: We believe that we should share, and we also state that we do, but we do not believe that others do.
+This pattern is starker for respondents in the Archival/Field category, compared to respondents using analytical (`r sr$sharing_perc_divide <- sr$sharing_perc_editor_prefer - sr$sharing_perc_other_share; ct_pvalue(sr, "sharing_perc_divide", "demog_method", "Archival/Field")['Analytical']`) and experimental methods (`r ct_pvalue(sr, "sharing_perc_divide", "demog_method", "Archival/Field")['Experimental']`).
+This finding highlights a contrast between the perceived prescriptive importance of research material sharing and the perceived (descriptive) actual sharing behavior.
+In other words: We believe that we should share and claim we do, yet we do not believe that others do.
 
@@
 We also find that they are less familiar with research materials sharing as an open science practice that helps address reproducibility and that they find that practice less important.
-Besides research material sharing, our survey also covers a second Open Science practice: Pre-registration.[^6]
+Besides research material sharing, our survey also covers a second Open Science practice: Pre-registration.[^7]
+
+[^7]: While parts of the economic [@O_2015; @BCHH_2024] and accounting literature [@CGL_2024] differentiate between pre-registrations (relatively short and standardized descriptions of study design) and pre-analysis plans (more detailed and elaborate plans outlining the technical details of a study, potentially also including analysis code, mock-up tables and figures), we use the term pre-registration as a broader notion, in line with @FLCPSWMBP_2023.
 
@@
 Panel A considers respondents' familiarity with the practice itself.
-We asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^7] The results in Panel A suggest that accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
-They seem to be slightly more familiar than researchers in Economics and Sociology (two-tailed p-value \< 0.010).
+We asked respondents: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?"[^8] The results in Panel A suggest that accounting researchers are equally familiar with the practice as researchers in Political Science and Psychology.
+They seem to be more familiar than researchers in Economics (`r ct_pvalue(mr, "prereg_heard", "demog_discipline", "Accounting")['Economics']`) and Sociology (`r ct_pvalue(mr, "prereg_heard", "demog_discipline", "Accounting")['Sociology']`).
 While this finding might appear surprising at first glance, one has to factor in that the practice of pre-registration is gaining traction over time, and our survey was fielded two years later than the second wave of our benchmark survey.
 
+[^8]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
+To ease comparison of the respective findings, we recode our response data to imply 'No' for participants that answer 'Not at all familiar'.
+
 \centerline{--- Insert Figure 6 about here ---}
 
-Panel B reports data on the first-time respondents pre-registered.
-It is based on the question: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"[^8] The findings show a clear pattern: Accounting researchers started pre-registering their studies significantly later than researchers in other social science fields (two-tailed p-value \< 0.010).
+Figure 6 reports data on the takeup of pre-registration over time.
+It is based on the question: "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?" The findings show a clear pattern: Accounting researchers started pre-registering their studies significantly later than researchers in other social science fields (all two-tailed p-values \<= `r myfmt(max(ct_pvalue(mr, "prereg_use_first_time", "demog_discipline", "Accounting", format = FALSE), 0.001))`).
 They started around 2018, compared to 2015-2016 for the other fields.
-This finding is also supported by Figure 6, which shows that the take-up of pre-registration in accounting over time lags behind the other social science areas.
-
-Panel C examines trustworthiness, showing data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?"[^9] Results indicate no apparent differences in perceived trustworthiness in accounting compared to economics and political science (two-tailed p-value \> 0.100).
-However, the perceived increase in trustworthiness when pre-registering is less in accounting compared to psychology and sociology (two-tailed p-value \< 0.010).
-However, it should be noted that for this question, the comparability across fields is limited as we asked explicitly about trustworthiness, whereas @FLCPSWMBP_2023 referred more generally on a general opinion.
+
+Panel B of Table 8 presents data on answers to the question: "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?" Results indicate no apparent differences in response in accounting compared to economics (`r ct_pvalue(mr, "prereg_opinion", "demog_discipline", "Accounting")['Economics']`) and political science (`r ct_pvalue(mr, "prereg_opinion", "demog_discipline", "Accounting")['Political Science']`).
+However, the assessment of pre-registration is less positive in accounting compared to psychology (`r ct_pvalue(mr, "prereg_opinion", "demog_discipline", "Accounting")['Psychology']`) but higher than in sociology (`r ct_pvalue(mr, "prereg_opinion", "demog_discipline", "Accounting")['Sociology']`).
+However, it should be noted that for this question, the comparability across fields is limited as we asked explicitly about trustworthiness, whereas @FLCPSWMBP_2023 referred more generally on a general opinion.[^9]
+
+[^9]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
+This question is quite broad and uses a five-point Likert scale (Not at all in favor, Moderately not in favor, Neither in favor nor against, Moderately in favor, Very much in favor).
+We chose to use a more specific question asking about whether pre-registration improves trustworthiness while also relying on a five-point Likert scale (Much less trustworthy, Somewhat less trustworthy, Equally trustworthy, Somewhat more trustworthy, Much more trustworthy).
 
@@
 Table 9 displays respondents' frequencies using three panels.
-Similar to Table 8 Panel A, Panel A of Table 9 reports on familiarity, i.e., the question: "How familiar are you with the practice of pre-registering hypotheses or analyses in advance of a study?" Somewhat unsurprisingly, Panel A shows that qualitative accounting researchers are less familiar with the practice than accounting researchers belonging to the Archival, Experimental, and Survey categories (two-tailed p-value \< 0.100).
-Yet, there is no statistical difference between qualitative and analytical accounting researchers.
-Panel B reports on differences in usage, specifically, the question "`r vars$text[100]`", similar to the question featured in Table 8 Panel B.
+Panel A shows that qualitative accounting researchers are less familiar with the practice than accounting researchers belonging to the Archival (`r ct_pvalue(sr, "prereg_familiar", "demog_method", "Qualitative")["Archival/Field"]`), Experimental (`r ct_pvalue(sr, "prereg_familiar", "demog_method", "Qualitative")["Experimental"]`), and Survey (`r ct_pvalue(sr, "prereg_familiar", "demog_method", "Qualitative")["Survey"]`) categories.
+Yet, there is no significant difference between qualitative and analytical accounting researchers (`r ct_pvalue(sr, "prereg_familiar", "demog_method", "Qualitative")["Analytical"]`).
+Panel B reports on differences in usage, specifically, the question "`r vars$text[100]`".
 We find that accounting researchers in the experimental field report the highest usage of pre-registration, while none of the qualitative accounting researchers report using it.
 Lastly, Panel C reports differences in perceived trustworthiness.
-Specifically, it features answers to the question, "How trustworthy do you find the work of scholars who tend to pre-register hypotheses or analyses as compared to the work of those who don't?" which is identical to the question featured in Table 8 Panel C.
 We find no clear evidence of differences among the different methodologies in whether they trust pre-registered work more than work that has not been pre-registered.
@@
 
-To contrast these perceptions with reality, we collect observational data on actual research material sharing behavior and the use of pre-registration behavior for a random country-stratified sample of `r nrow(authors)` authors from our target population.
+To contrast these perceptions with reality, we collect observational data on actual research material sharing and pre-registration for a random country-stratified sample of `r nrow(authors)` authors from our target population.
 To assess whether these authors share research materials, we systematically search their homepages for evidence and also verify whether they have relevant online accounts linked to their names on platforms such as GitHub, Open Science Foundation, Dataverse, or Zenodo.
@@
 
+[^10]: The data collection manual for this process is available in this project's [[GitHub repository](https://github.com/joachim-gassen/osacc/)]{.content-visible unless-meta="anonymize"}[GitHub repository (link omitted for review)]{.content-visible when-meta="anonymize"}.
+
 \centerline{--- Insert Table 10 about here ---}
@@
 We find that `r sum(by_author$has_made_resmat_available)` % of our authors share research materials.
-This number and its corresponding binomial confidence interval (30 to 49 %) are lower that the percentage of respondents who stated in the survey that they at least sometimes share (57 %) but a little bit higher than the prescriptive sharing frequency that our respondents attributed to other researchers (27 %).
+This number and its corresponding binomial confidence interval (30 to 49 %) are lower that the percentage of respondents who stated in the survey that they at least sometimes share (57 %) but higher than the prescriptive sharing frequency that our respondents attributed to other researchers (27 %).
 
@@
 
-Overall, our observational data supports the survey findings. It seems that research material sharing only takes place sporadically in accounting and is often driven by journal requirements.
+[^11]: Untabulated analyses based on small frequencies provide suggestive evidence that, overall, the sharing frequencies are also higher for general economics journals, which generally require code and data sharing, than for journals in the areas of accounting and finance.
+
+Overall, our observational data corroborates the survey findings, indicating that research material sharing in accounting occurs infrequently and is primarily driven by journal requirements.
 
@@
 The hypothetical scenario was, like the survey, designed using oTree [@CSW_2016].
-An overview of the manipulations and the materials can be found in Appendix B.
+An overview of the manipulations and the materials can be found in [Online-]{.content-visible when-meta="online-appendix"}Appendix B.
 
@@
 Namely, for a private scope, a collaboration rationale implies more direct benefits of sharing than for a public scope.
-We pre-registered our predictions and design at the \href{https://osf.io/4akyd}{Open Science Foundation}.
+We pre-registered our predictions and design at the [[Open Science Foundation](https://osf.io/4akyd)]{.content-visible unless-meta="anonymize"}[Open Science Foundation (link omitted for review)]{.content-visible when-meta="anonymize"}.
 
@@
 However, we do not find statistical support for our three predictions.
-First, Table 7 Column 1 reports no significant effect of using a *collaboration rationale* over a *control rationale* (two-tailed p-value \> 0.100).
-Moreover, Column 2 reveals no support for a main effect of *private scope* on respondents' willingness to share research materials (two-tailed p-value \> 0.100).
-Lastly, column 3 shows no support for an interaction effect between *collaboration rationale* and *private scope* (two-tailed p-value \> 0.100).
+First, Panel B Column 1 reports no significant effect of using a *collaboration rationale* over a *control rationale* (two-tailed p-value `r myfmt(coef(summary(modh1))[2,4], p = T)`).
+Moreover, Column 2 reveals no support for a main effect of *private scope* on respondents' willingness to share research materials (two-tailed p-value `r myfmt(coef(summary(modh2))[2,4], p = T)`).
+Lastly, column 3 shows no support for an interaction effect between *collaboration rationale* and *private scope* (two-tailed p-value `r myfmt(coef(summary(modh3))[4,4], p = T)`).
 In sum, although we find that respondents express a high willingness to share research materials in our hypothetical scenario, we do not find any evidence it is affected by the way the request for sharing is made.
-At least in our hypothetical scenario, it does not matter whether the request is made to make the materials private (rather than public) and whether the request is made to promote collaboration as a research community or to verify whether the research has been conducted appropriately.
+At least in our hypothetical scenario, it does not matter whether the request is made to make the materials private (rather than public) and whether the request is made to promote collaboration as a research community or to verify whether the research has been conducted appropriately.[^12]
+
+[^12]: To shed some light on whether our null results could be the outcome of a low powered test caused by our modest response rate, we report a simulation-based post hoc power analysis in [Online-]{.content-visible when-meta="online-appendix"}Appendix C.
+We find the post hoc minimum detectable effect size of our sample to be around 12 percentage points for our main effects, reflecting that we would have been able to detect a medium-sized effect (Cohen's d \~0.5) for H1 and H2.
+Thus, we conclude that our results are not driven by low power.
 
@@
 
-Also, given our experimental findings, we rely on two sources of survey data to shed light on our third research question.
+Given our experimental findings, we rely on two sources of survey data to shed light on our third research question.
 First, our survey contains a question asking respondents who report that they do not always publicly share research materials to explain which reasons make them withhold their research materials.
@@
 
-```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-```
 
@@
 \end{displayquote}
-```
 
 Another prominent argument provided by participants is that research material sharing helps other researchers.
-This argument is significantly more likely to be provided by participants who faced the collaboration treatment, providing evidence that the framing of the sharing situation affects the decision-making of our participants.
-We take this as evidence that our participants see the public and also private benefits of data and code sharing.
+This argument is raised significantly more often by participants who faced the collaboration treatment, suggesting that the framing of the situation affects decision-making (`r ct_pvalue(svr, "verbal_pos_helps_other_researchers", "exp_tment_collab", 1)`).
+We interpret this as evidence that our participants see both the public and private benefits of data and code sharing.
 The following statement illustrates the importance of research material sharing in helping other researchers nicely:
 
-```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-```
+
 Another interesting aspect that does not become apparent from the pre-conditioned analysis in Panel A is that a sizable amount of participants indicate that they are concerned about the unethical use of their research materials.
@@
 \end{displayquote}
-```
+
 But even without reverse p-hacking, research material sharing requests can create career concerns. An example:
 
-```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-```
-Another aspect, which is also featured prominently in Panel A, is the time investment that is required to entertain research material sharing and potential follow-up requests. For example:
-
-```{=tex}
+
+Another aspect, which is also featured prominently in Panel A, is the time investment required to entertain research material sharing and potential follow-up requests. For example:
+
 \begin{displayquote}
@@
 \end{displayquote}
-```
+
 The last aspect of this quote also hints at a rationale commonly featured in the "it depends" category: the requesting person's personality and reputation. An example of this is:
 
-```{=tex}
 \begin{displayquote}
@@
 \end{displayquote}
-```
+
 These statements indicate the potential for selective sharing among well-connected researchers, which would benefit an "in-crowd" of academics while at the same time unleveling the academic playing field and increasing inequality.
@@
 While the sharing benefits become more prevalent with a collaboration framing, the sharing costs are prominent regardless of the hypothetical scenario.
-Also, while the multiple-choice data highlight direct cost arguments, the unstructured verbal response also features various indirect costs.
+Also, while the multiple-choice data highlight direct cost arguments, the unstructured response also features various indirect costs.
 
@@
 
-Informed by a voluntary disclosure-themed discussion of the costs and benefits of open science activities in accounting, we conducted a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.
-Our results suggest that accounting researchers face an "open science dilemma." On the one hand, they are more skeptical about the reproducibility of their influential findings than other social science researchers are about their respective findings.
-On the other hand, they seem to be a little bit behind the curve in terms of research material sharing and research design pre-registration.
-If these conclusions are descriptive, what should our reaction be?
-
-While we are not in a position to advise our profession on how to proceed, we feel that a two-pronged approach might be desirable.
-First, why are we so skeptical about our work?
-Is this an example of the anecdotal "professional skepticism" that leads us accountants to over-weight negative signals in general?
-Or do we indeed have good reasons to be concerned?
-The only way to find out is to take stock.
-A study that provides large-scale evidence in that matter is @CGL_2024 studying the discontinuity of p-values in empirical accounting research.
-They document that it exists and is somewhat larger than in economics [@BCH_2020] but smaller than in political science [@GM_2008a] and sociology [@GM_2008a].
-Using a different approach based on a set of replication exercises, @G_2023 finds post 2000 accounting studies to be "very fragile" and links this observation to p-hacking.
-Similar to us, both authors teams discuss research material sharing and pre-registration as potential remedies.[^12] On the other hand, @LSA_2024 suggest reproduction studies in accounting not to be rare, and that a majority of those confirm prior results.
-
-Given these and our insights, we argue that we need more systematic evidence on whether our findings reproduce and whether they can be replicated using new data and settings.
-An impressive exercise in that regard is the recent large-scale reproduction attempt of studies published in Management Science [@FGHKO_2023].
-This endeavor systematically reproduced almost 500 articles published in Management Science before and after the establishment of a Data and Code Policy in 2019.
-One interesting finding from that study is that accounting studies in Management Science are -if anything- more reproducible than studies in neighboring fields like finance.
-Based on this, it seems that professional skepticism and the resulting overly skeptical view on the reproducibility of our influential studies might indeed be partly responsible for our open science dilemma.
-
-It would be insightful to compare the findings for Management Science, which also documents an impressive effect of their data and code policy, with data on studies published in the Journal of Accounting Research, again pre and post their data policy.
-These findings could, in turn, be compared with those for studies published in other leading journals that do not have a dedicated data and code sharing policy (yet).
-But not only systematic large-scale reproduction studies can update our priors about the reproducibility of our work.
-Replication games, potentially embodied in doctoral education, are an alternative means to assess the reproducibility of our work while at the same time helping researchers to grow their network and empirical skill sets alike.
-Taken together, we believe that the academic accounting profession should be well-positioned to take a leading role in verifying its output.
-In the end, assessing the reproducibility of scientific work is an assurance and auditing process, an area we know quite a bit about!
-
-The second element of the two-pronged approach would be to promote research material sharing and pre-registration, potentially in combination with other open science measures that aim to increase the accessibility and reusability of scientific work.
-The economists among us might be quick to point out the incentive problems in this regard.
-Why should we do it?
-Does sharing code and data help to build academic careers?
-While some associative evidence from other fields indicates that papers that share their data are cited more often [@PDF_2007], currently, the answer to this is not clearly affirmative.
-Research material sharing requires skills and time, and, to the extreme, devoting this time might even be regarded as a negative signal by tenure and promotion committees, assuming that it crowds out time spent on producing "more tenurable output."
-
-To us, this mindset seems to be the core of the problem.
-We believe that it is misguided as research material sharing constitutes a public good that is crucial for scientific progress.
-Think about a scientific computing world without open-source contributions.
-This would be a world without the GNU/Linux operating system and its tools, without Python, R, git, Latex, and the accompanying package ecosystems.
-In such a world, scientific advancements in areas like econometrics, machine learning, and natural language processing would be severely delayed if at all feasible.
-As our field builds on the insights of these areas, we all benefit from the open source/science paradigm in our everyday work.
-
-Given that, one might ask whether research material sharing by accounting researchers can create similar positive externalities.
-As our competitive advantage stems more from institutional than methodological expertise, we, for example, are well-positioned to curate micro-level data based on firm disclosures.
+Guided by a voluntary disclosure-inspired discussion on the costs and benefits of open science initiatives in accounting, we conducted a comprehensive survey among accounting researchers to examine their perceptions and attitudes towards open science practices.
+Our findings suggest an "open science dilemma." While our participants, relative to other social scientists, exhibit greater skepticism about the reproducibility of their influential findings, they also appear more reluctant to adopt research material sharing and pre-registering research designs.
+These findings are also supported by observational data and might be explained by accounting researchers assessing open science practices to be high cost, low private benefit activities.
+
+If our findings are descriptive: What should we do?
+We propose a two-pronged approach.
+First, we should question whether our skepticism towards our work is justified.
+Is this just accountants' "professional skepticism" at work, or should we really be concerned?
+To gain clarity, it is essential to take stock.
+Notably, @CGL_2024 conducted a study on the discontinuity of p-values within empirical accounting research, revealing that this discontinuity exists and is more pronounced than in economics [@BCH_2020] but less so than in political science [@GM_2008a] and sociology [@GM_2008a].
+Using a different approach based on a set of replication exercises, @G_2023 finds post-2000 accounting studies to be "very fragile" and links this observation to p-hacking.
+Both studies, similar to ours, advocate for enhanced sharing of research materials and pre-registration as effective remedies.[^13] Conversely, @LSA_2024 suggests that reproduction studies in accounting are not uncommon and that most these studies corroborate existing findings.
+
+[^13]: In a related study, @BCHH_2024 study randomized controlled trial studies in economics and find that only pre-registrations that include pre-analysis plans show muted p-value discontinuities.
+
+These insights notwithstanding, more systematic evidence seems necessary.
+A notable effort in this direction is the recent large-scale reproduction attempt of studies published in Management Science [@FGHKO_2023].
+This initiative systematically reproduced nearly 500 articles from Management Science both before and after the implementation of a Data and Code Policy in 2019.
+Remarkably, the results of this study suggest that accounting studies published in Management Science are, if anything, more reproducible than those in related fields such as finance.
+
+It would be insightful to compare the findings for Management Science, which also document an impressive effect of their data and code policy, with data on studies published in the Journal of Accounting Research, again pre and post their data policy.
+These findings could, in turn, be compared with those for studies published in other leading accounting journals that do not have a dedicated data and code sharing policy (yet).
+Besides systematic large-scale reproduction studies replication games, potentially embodied in doctoral education, are an alternative means to assess the reproducibility of our work while at the same time helping researchers to grow their network and empirical skill sets.
+Overall, the academic accounting profession should be well-positioned to verify scientific output.
+Ultimately, assessing the reproducibility of prior work is an assurance and auditing process, an area we know quite a bit about!
+
+The second element of the two-pronged approach would be to promote research material sharing and pre-registration, potentially alongside other open science initiatives that aim to increase the accessibility and reusability of scientific work.
+As discussed, the incentive problems in this regard are substantial.
+What is the private benefit of such practices?
+Does sharing code and data help building academic careers?
+While associative evidence from other disciplines suggests that papers sharing their data tend to receive more citations [@PDF_2007], sharing research materials demands both skill and time.
+Tenure and promotion committees seem to rarely acknowledge its positive impact and in extreme cases, they may even perceive it as a negative signal, assuming it diverts effort away from producing outputs deemed more favorable for tenure.
+
+We contend that this mindset lies at the heart of the problem, and we argue that it is fundamentally misguided.
+Sharing research materials creates important public goods.
+Consider a world of scientific computing absent of open-source contributions — it would lack the GNU/Linux operating system and its tools, as well as Python, R, Git, LaTeX, and their diverse package ecosystems.
+In such a world, scientific progress in fields like econometrics, machine learning, and natural language processing would be significantly hindered, if not entirely unfeasible.
+Our field thrives on the insights gained from these areas, and thus, we collectively benefit from  open source and open science paradigms in our everyday work.
+
+But can sharing accounting research materials generate similar positive externalities?
+As our competitive advantage primarily arises from institutional, rather than methodological expertise, we, for example, are well-positioned to curate regulatory and firm-level data.
 Prominent examples include word lists for sentiment analyses in financial settings [e.g., @LM_2011], topic model-based measures of specific firm risks [e.g., @H_2019], and industry classifications based on financial disclosures [e.g., @HP_2016].
-
-A closely related area where we see the potential of accounting data to develop a substantial impact is the collection and pre-processing of firm-time level web and electronic filing data.
-For the former, web scraping of corporate webpages can provide informative data [e.g., @BBB_2024], and for the latter, in particular, the upcoming electronic filing requirements for sustainability reports hold promise.
-While researchers compete with established commercial data providers in this area, the need for research to study unstructured textual data makes it necessary and valuable to build research-focused data pipelines and products instead of simply trusting (and paying) commercial data vendors.
-Another aspect is that freely licensable research data can remove one of the most significant entry hurdles for empirical archival accounting researchers.
-
-While these flagship projects are useful showcases that research material sharing in the accounting domain can also be impactful for other domains, they will likely not change the sharing landscape at large.
-To promote reproducible workflows overall, we need to make the case that adopting such a workflow not only contributes to the public good by making research materials accessible but also enhances research efficiency at an individual level.
-To be able to share research materials, such as code and data, researchers must adopt a workflow that integrates reusability aspects into project development.
-The data and code requirements of leading journals in economics, finance, and accounting are not only pushing the availability of research materials but also imposing substantial costs on researchers who have to provide more or less complete replication packages upon acceptance.
-As many researchers affected by these regulations will admit, transforming an empirical project from an internal "well it works" scripting exercise to a well-documented replication package that ideally works across multiple platforms is far from trivial.
-This process becomes significantly more manageable and enjoyable if an open science-oriented workflow is adopted throughout all stages of project development.
-Besides this, it also makes it easier for co-author teams to cooperate, and even the researcher's future self might be thankful.
-
-As the lack of time is one of the biggest roadblocks to research material sharing in our survey, educational activities targeted at the PhD level teaching scientific computing and project management, in general, seem important.
-While well-funded research institutions might have the opportunity to outsource these skills to research professionals, the vast majority of researchers worldwide need to acquire them themselves.
-This is not necessarily undesirable, as having these skills enables one to develop more creative research projects than researchers unaware of what is feasible with state-of-the-art scientific computing.
-In the early days, many accounting PhD programs were implicit- or explicitly relying on scientific computing skills to be handed down from one PhD generation to another.
-It seems that these days are over and that dedicated scientific computing courses should become as central a component of scientific education in the quantitative social sciences as lab training is in the natural sciences.
-
-Much of the above applies primarily to our discipline's empirical and quantitative areas.
-What about analytical and qualitative researchers and their studies?
-As it becomes apparent from our findings, their views on open science differ prominently from those of the "accounting mainstream." Analytical researchers seem to be much more confident in their work than others, potentially in line with theoretical work being easier to verify during the review process.
-Then again, to develop the impact that it deserves, analytical work not only needs to be reproducible but also accessible and reusable, ideally also by non-expert researchers from neighboring methods.
-Qualitative work, on the other hand, faces conditions that set it apart from typical quantitative work.
-First, its data is often collected under confidentiality, legally restricting future sharing.
-Second, its unique richness makes it inherently challenging to share across subjects, especially if re-identification issues are present.
-Third, related and maybe more epistemological in nature, the assumption of objectivity, which allows research materials to be detached from the individual researcher and reused by others, is questioned within the qualitative realm.
-This implies that qualitative scholars have to develop -and are developing [e.g., @M_2014; @FRV_2022]- their own understanding of what reproducibility means within their methodological paradigm.
-
-Finally, fears and a general lack of trust in fellow researchers are also essential deterrents to adopting open science methods.
-This is human but unfortunate, also because it leads to subtle "home biases" when it comes to sharing, potentially increasing academic inequality and hindering scientific progress.
-While the fear of being "scooped" can be addressed by sharing materials later in the publication process or publicly claiming intellectual ownership of ideas via pre-registration and use of well-established repositories, fears with regard to future researchers pointing to deficiencies in one's work and/or a general lack of trust are more challenging to overcome.
-For both aspects, we need to work towards changing the error climate in the academic discipline.
-Additionally, it might be helpful to move away from the "policing" aspect of reproducibility and instead stress the collaborative public good character of open science activities.
-With them, we can help each other, promote our field, and make the research process even more fun!
+Another promising area where accounting data can have a significant impact is the collection and pre-processing of disclosure data.
+Web scraping of corporate webpages, for example, can yield valuable and informative data [e.g., @BBB_2024].
+Additionally, the imminent electronic filing requirements for sustainability reports offer considerable potential.
+Although researchers face competition from established commercial data providers in this area, the demand for analyzing unstructured textual data necessitates the creation of research-focused data pipelines and products instead of simply trusting (and paying) commercial data vendors.
+Furthermore, freely licensable research data can remove a major entry barrier for empirical archival accounting researchers, thereby fostering innovation in the field.
+
+While these flagship projects demonstrate that research material sharing in accounting can also be impactful for other domains, to increase the reproducibility of our work more broadly, we need to bring down the costs of research material sharing.
+For researchers to share materials effectively, reprodicibility and reusability need to be integrated into project development.
+Data and code policies of leading journals in economics, finance, and accounting might be promoters.
+As many researchers affected by these policies will agree, transforming an empirical project from a "well it works" scripting exercise to a well-documented replication package that works across multiple platforms is far from trivial.
+However, this process becomes significantly easier when an open science-oriented workflow is adopted throughout all stages of project development.
+Additionally, such a workflow eases collaboration among co-authors and helps kick-starting new projects by reusing materials from prior projects.
+
+So, adopting an open science workflow not only reduces the costs of research material sharing but also creates direct benefits for the researcher.
+However, in our survey, lack of time emerged as a significant barrier to research material sharing.
+To address this, PhD level courses in scientific computing and project management seem helpful.
+While well-funded research institutions might have the opportunity to outsource these skills to research professionals, the vast majority of researchers worldwide must acquire them independently.
+This is not necessarily disadvantageous, as these skills speed up the development of innovative research projects.
+Traditionally, many accounting PhD programs relied on informal transmission of scientific computing skills from one PhD generation to the next.
+It seems that these days are over and that dedicated scientific computing courses should become a central component of scientific education in the quantitative social sciences, comparable to the role of lab training in the natural sciences.
+
+The discussion so far primarily concerns the quantitative empirical fields within our discipline.
+What about analytical and qualitative researchers and their work?
+As our findings show, their views on open science diverge significantly from those of the "accounting mainstream." Analytical researchers tend to exhibit greater confidence in their work, possibly in line with theoretical work being easier to verify during the review process.
+But to achieve the impact it deserves, analytical research must not only be reproducible but also accessible and reusable, ideally even by researchers employing different methodologies.
+Qualitative work, however, faces conditions that set it apart from typical quantitative work.
+First, its data are often collected under confidentiality agreements, legally restricting future sharing.
+Second, its unique richness poses inherent challenges for sharing across subjects, particularly when re-identification issues arise.
+Third, from a more epistemological perspective, the assumption of objectivity — which permits research materials to be detached from the individual researcher and reused — is scrutinized within the qualitative domain.
+Consequently, qualitative scholars are developing their own understanding of reproducibility within their methodological paradigm [e.g., @M_2014; @FRV_2022].
+
+Finally, fears and a general lack of trust among researchers significantly hinder the adoption of open science practices.
+This is human but also unfortunate, as it can lead to subtle "home biases" in sharing, potentially exacerbating academic inequality and hindering scientific progress.
+The fear of being "scooped" can be mitigated by sharing materials later in the publication process or asserting intellectual ownership through pre-registration and well-established repositories.
+However, concerns about future researchers identifying flaws and questionable research practices in one's work and a general distrust are more complex challenges to overcome.
+To address these issues, we must work towards transforming the error climate within the academic discipline.
+Emphasizing the collaborative and public good nature of open science, rather than a "policing" approach to reproducibility, could be beneficial.
+By adopting such a climate, we can support each other, advance our field, and make the research process (even) more enjoyable.
 
@@
 
-\newpage
+:::
+
+::: {.content-visible when-meta="paper-figures"}
+
+[\newpage]{.content-visible when-meta="paper-body"}
 
@@
 
-```{r Figure1, fig.width=12, fig.height=9}
-byu_fields_comp(byu, sd)
+```{r Figure1, fig.align='center', fig.width=10, fig.height=6}
+byu_fields_comp(byu, sr)
 ```
@@
 ```
+
 This figure compares the distribution of authors' subfields in the BYU sample to the distribution of respondents' self-reported primary subfield in our sample.
@@
 \end{singlespace}
-\newpage
-```
+```
+
 ### Figure 2: Sample Comparison between BYU and Our Sample - Methods {.unnumbered}
 
-```{r Figure2, fig.width=12, fig.height=9}
-byu_methods_comp(byu, sd)
+```{r Figure2, fig.align='center', fig.width=10, fig.height=6}
+byu_methods_comp(byu, sr)
 ```
@@
 ```
+
 This figure compares the distribution of authors' methodologies in the BYU sample to the distribution of respondents' self-reported primary methodology in our sample.
@@
 ```
+
 ### Figure 3: Reproducibility of Influential Findings Across the Social Sciences {.unnumbered}
 
-```{r Figure3, fig.width=8, fig.height=5}
+```{r Figure3, fig.align='center', fig.width=9, fig.height=5}
 likert_plot(mr, "reprod", "demog_discipline", title_str = "How confident are you that the influential research findings in your area will replicate/reproduce?", llevels = vars$resp_label[80:84])
@@
 ```
+
 This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
 The question asked in our survey is "`r vars$text[80]`" while the original question used in the survey of @FLCPSWMBP_2023 is "How confident are you that the influential research findings in \[Discipline\] would replicate?".
-The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers worldwide.
 Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
@@
 \end{singlespace}
-\newpage
-```
+```
+
 ### Figure 4: Importance of Research Material Sharing Across the Social Sciences {.unnumbered}
 
-```{r Figure4, fig.width=9, fig.height=5}
-mr$sharing_important_rescaled = floor(mr$sharing_important)
-likert_plot(mr, "sharing_important_rescaled", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53])
+```{r Figure4, fig.align='center', fig.width=9, fig.height=5}
+likert_plot(mr, "sharing_important", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53])
 ```
@@
 ```
+
 This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
 The question asked in our survey is "`r vars$text[49]`" while the original question used in the survey of @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting (data or code \| research instruments) online is important for progress in \[Discipline\]?".
-The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers worldwide.
 Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
@@
 ```
+
 ### Figure 5: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}
 
-```{r Figure5, fig.width=8, fig.height=6}
-pres_desc_plot(sd)
+```{r Figure5, fig.align='center', fig.width=8, fig.height=6}
+pres_desc_plot(sr)
 ```
@@
 ```
+
 This figure is based on our survey data and summarizes the findings from three separate questions.
@@
 \end{singlespace}
-```
-\newpage
+\newpage
+```
 
@@
 
-```{r Figure7, fig.width=8, fig.height=6}
-pre_reg_over_time_plot(mr)
+```{r Figure6, fig.align='center', fig.width=6, fig.height=4}
+pre_reg_over_time_plot(mr) + theme(title = element_text(size = 10))
 ```
@@
 ```
+
 This figure is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
@@
 The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?".
-The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers worldwide.
 Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
@@
 \end{singlespace}
-\newpage
-```
-```{=tex}
-\renewcommand{\thetable}{\arabic{table}}
-\setcounter{table}{0}
-```
-\newpage
+```
 
@@
 
-```{r Figure6, fig.width=8, fig.height=6}
+```{r Figure7, fig.align='center', fig.width=6, fig.height=4}
 plot_resmat_sharing_over_cyear
@@
 ```
+
 This figure is based on `r nrow(papers)` papers, published since 2016 by a country-stratified random sample of `r nrow(authors)` authors from our target participant population.
@@
 \end{singlespace}
-\newpage
-```
+```
+
+:::
+
+::: {.content-visible when-meta="paper-tables"}
+
+[\newpage]{.content-visible when-meta="paper-figures"}
+
 ## Tables {.unnumbered}
@@
 ```{=tex}
+\renewcommand{\thetable}{\arabic{table}}
+\setcounter{table}{0}
 \begin{singlespace}
@@
 ```
+
 |                                 |                    N (%) |
@@
 ```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
+\newpage
+```
+
 ### Table 2: Sample Demographics {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel A: Sample Descriptives {.unnumbered}
@@
 extract_df <- function(dvar, title) {
-	df <- create_demog_table(sd, dvar, df_only = TRUE)
+	df <- create_demog_table(sr, dvar, df_only = TRUE)
 	names(df) <- c("Characteristic", "n", "%")
@@
 	extract_df("demog_age", "Age Group"),
-	extract_df("demog_gender", "Gender"),
-	extract_df("demog_region", "Geographic Region")
+	extract_df("demog_gender", "Gender")
 )
@@
 
-\newpage
-
-```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
-```{=tex}
-\begin{landscape}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel B Regional Representativeness {.unnumbered}
@@
 ```{r Tab2bGeoRep, asis = TRUE}
-tab <- create_regions_rep_table(pop, sd)
+tab <- create_regions_rep_table(pop, sr, shorten = TRUE)
 tab_latex <- gt(tab) %>% 
@@
 ```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
+\newpage
+\begin{landscape}
+```
+
 ### Table 3: Reproducibility of Influential Findings Across the Social Sciences {.unnumbered}
-
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
-How confident are you that the influential research findings in your field would reproduce/replicate?
 
@@
 The question asked in our survey is "`r vars$text[80]`" while the original question used in the survey of @FLCPSWMBP_2023 is "How confident are you that the influential research findings in \[Discipline\] would replicate?".
-The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers worldwide.
 Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
-The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field.
-(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respectively.
-
-```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
+The asterisks report the results of t-tests for mean differences between the respective field and Accounting.
+(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) level, respectively.
+
+```{=tex}
+\newpage
+```
+
 ### Table 4: Reproducibility of Influential Findings: Assessment Across Methods {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel A: General Assessment by Method {.unnumbered}
@@
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_acc", "demog_method", include_total = TRUE,
+	sr, "reprod_acc", "demog_method", include_total = TRUE,
 	drop_levels = "Other", ctests = TRUE, df_only = TRUE
@@
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_method", "demog_method", include_total = TRUE,
+	sr, "reprod_method", "demog_method", include_total = TRUE,
 	drop_levels = "Other", ctests = TRUE, df_only = TRUE
@@
 
-\newpage
+```{=tex}
+\newpage
+```
 
@@
 ```{r Tab4cReprMethod, asis = TRUE}
-sd$reprod_method_delta <- as.numeric(sd$reprod_method) - as.numeric(sd$reprod_acc)
+sr$reprod_method_delta <- as.numeric(sr$reprod_method) - as.numeric(sr$reprod_acc)
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_method_delta", "demog_method", include_total = TRUE,
+	sr, "reprod_method_delta", "demog_method", include_total = TRUE,
 	drop_levels = "Other", 
-	resp_label = sort(na.omit((unique(sd$reprod_method_delta)))),
+	resp_label = sort(na.omit((unique(sr$reprod_method_delta)))),
 	ctests = TRUE, add_num_labels = FALSE, df_only = TRUE 
@@
 ```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
+\newpage
+```
+
 ### Table 5: Sharing of Research Materials Across the Social Sciences {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel A: Familiarity {.unnumbered}
@@
 tab <- create_pct_cross_tab_table(
-	mr, "sharing_important_rescaled", "demog_discipline", 
+	mr, "sharing_important", "demog_discipline", 
 	resp_label = get_resp_label("sharing_important"), df_only = TRUE
@@
 
-```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
+This table is based on our survey data merged with the data collected by @FLCPSWMBP_2023.
+For Panel A, the question of our survey is "`r vars$text[44]`" where "Not at all familiar" is coded as "No".
+The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of publicly posting (data and code \| study instruments) online for a completed study?".
+For Panel B, the question of our survey is "`r vars$text[49]`".
+The question used in the survey of @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting (data or code \| research instruments) online is important for progress in \[Discipline\]?" Our survey and the merging process of the data are discussed in more detail in section 2.
+The asterisks report the results of t-tests for mean differences between the respective field and Accounting.
+(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) level, respectively.
+
+```{=tex}
+\newpage
+```
+
 ### Table 6: Sharing of Research Materials Across Methods {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel A: Familiarity {.unnumbered}
@@
 tab <- create_pct_cross_tab_table(
-	sd, "sharing_familiar", "demog_method", include_total = TRUE,
+	sr, "sharing_familiar", "demog_method", include_total = TRUE,
 	drop_levels = "Other", ctests = TRUE, df_only = TRUE
@@
 ```{r Tab6bSharingImportance, asis = TRUE}
-
 tab <- create_pct_cross_tab_table(
-	sd, "sharing_important", "demog_method", include_total = TRUE,
+	sr, "sharing_important", "demog_method", include_total = TRUE,
 	drop_levels = "Other", ctests = TRUE, df_only = TRUE
@@
 ```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
 \end{landscape}
@@
 ```
+
 ### Table 7: Sharing of Research Materials: Prescriptive versus Descriptive Views {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel A: Stated sharing frequency across methods {.unnumbered}
@@
 ```{r Tab8aSharingUse, asis = TRUE}
-
 tab <- create_pct_cross_tab_table(
-	sd, "sharing_use", "demog_method", include_total = TRUE, 
+	sr, "sharing_use", "demog_method", include_total = TRUE, 
 	drop_levels = "Other", ctests = TRUE, df_only = TRUE
@@
 ```{r Tab8bSharingPreDes, asis = TRUE}
-base_df <- sd %>%
+base_df <- sr %>%
 	select(
@@
 sub("Believes About Actual Sharing Behavior &  &  &  &  &  &", "\\\\multicolumn{7}{l}{Believes About Actual Sharing Behavior}", tab_latex)
-
 ```
@@
 Methods where the answers differ at the two-sided 10%-level are indicated by their first two letters.
-Please see Appendix C for an overview of how we adapted these three questions and their answer scales from @FLCPSWMBP_2023.
-
-```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
+Please see [Online-]{.content-visible when-meta="online-appendix"}Appendix D for an overview of how we adapted these three questions and their answer scales from @FLCPSWMBP_2023.
+
+```{=tex}
+\newpage
+\begin{landscape}
+```
+
 ### Table 8: Pre-Registration Across the Social Sciences {.unnumbered}
@@
 
-#### Panel B: Take-up over Time {.unnumbered}
-
-```{r Tab11bPreRegTimeSocSciResp, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	mr, "prereg_use_first_time", "demog_discipline", 
-	resp_label = na.omit(sort(unique(mr$prereg_use_first_time))), 
-	add_num_labels = FALSE, df_only = TRUE
-)
-
-# NOTE: This hack Needs to be checked manually whenever something 
-# the underlying data changes - which it should not
-
-up_to_2010 <- c(
-	"<= 2010", 
-	sum(as.numeric(substr(tab$Accounting[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$Economics[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$`Political Science`[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$Psychology[1:13], 1, 1))),
-	sum(as.numeric(substr(tab$Sociology[1:13], 1, 1)))
-)
-up_to_2010[2:6] <- sprintf(
-	"%s (%.1f %%)", 
-	up_to_2010[2:6],
-	100*as.numeric(up_to_2010[2:6])/as.numeric(tab[26,2:6])
-)
-tab <- rbind(up_to_2010, tab[14:28,])
-
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex()
-```
-
-```{=tex}
-\newpage
-\begin{landscape}
-```
-#### Panel C: Trustworthiness {.unnumbered}
+#### Panel B: Trustworthiness {.unnumbered}
 
@@
 For Panel A, the question of our survey is "`r vars$text[95]`" where we code the response "Not at all familiar" as "No" and all other responses as "Yes." The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
-For Panel B, the question of our survey is "`r vars$text[102]`".
-The question used in the survey of @FLCPSWMBP_2023 is "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?".
-For Panel C, the question of our survey is "`r vars$text[103]`".
+For Panel B, the question of our survey is "`r vars$text[103]`".
 The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
-The data of @FLCPSWMBP_2023 has been collected in two waves (2018 and 2020) from a population of researchers located in the U.S.
-Our survey was conducted in 2022 among accounting researchers worldwide.
 Our survey and the merging process of the data are discussed in more detail in section 2 of the paper.
-The asterisks report the results of an OLS regression regressing the response on a series of field fixed effects with Accounting acting as the base field.
-(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) significant level, respecively.
-
-```{=tex}
-\newpage
-\setlength{\parindent}{0em}
-```
+The asterisks report the results of t-tests for mean differences between the respective field and Accounting.
+(\*/\*\*/\*\*\*) indicate two-sided significance at the (10%/5%/1%) level, respectively.
+
+```{=tex}
+\newpage
+```
+
 ### Table 9: Pre-Registration Across Methods {.unnumbered}
@@
 tab <- create_pct_cross_tab_table(
-	sd, "prereg_familiar", "demog_method", include_total = TRUE,
+	sr, "prereg_familiar", "demog_method", include_total = TRUE,
 	drop_levels = "Other", ctests = TRUE, df_only = TRUE
@@
 tab <- create_pct_cross_tab_table(
-	sd, "prereg_use", "demog_method", include_total = TRUE,
+	sr, "prereg_use", "demog_method", include_total = TRUE,
 	drop_levels = "Other", 
@@
 tab <- create_pct_cross_tab_table(
-	sd, "prereg_trust", "demog_method", include_total = TRUE,
+	sr, "prereg_trust", "demog_method", include_total = TRUE,
 	drop_levels = "Other", ctests = TRUE, df_only = TRUE
@@
 ```{=tex}
-\setlength{\parindent}{4em}
 \end{landscape}
-\end{singlespace}
-\newpage
-\begin{singlespace}
-```
+\newpage
+```
+
 ### Table 10: Observational Data on Research Material Sharing {.unnumbered}
@@
 For each paper, we observe whether research material availability is mentioned on the paper's DOI URL.
-The data collection manual for this process is available in this project's GitHub repository.
+The data collection manual for this process is available in this project's [[GitHub repository](https://github.com/joachim-gassen/osacc/)]{.content-visible unless-meta="anonymize"}[GitHub repository (link omitted for review)]{.content-visible when-meta="anonymize"}.
 In Panel A, the overall share of authors that we identify to share research materials is reported, along with its binomial confidence interval in brackets.
@@
 ```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
+\newpage
+```
+
 ### Table 11: Scenario Analysis: Hypothetical Sharing Likelihood {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel A: Descriptive Statistics {.unnumbered}
@@
 ```{r Tab7aExpDescriptives, asis = TRUE}
-stats <- sd %>%
+stats <- sr %>%
 	group_by(exp_tment_control, exp_tment_private) %>%
@@
 tab <- create_pct_cross_tab_table(
-	sd, "reprod_acc", "demog_method", 
+	sr, "reprod_acc", "demog_method", 
 	ctests = TRUE, df_only = TRUE
@@
 ```{r Tab7bExpRegResults, asis = TRUE}
-sd$exp_tment_collab <- 1 - sd$exp_tment_control
-modh1 <- lm(exp_pct_share ~ exp_tment_collab, data = sd)
-modh2 <- lm(exp_pct_share ~ exp_tment_private, data = sd)
-modh3 <- lm(exp_pct_share ~ exp_tment_collab*exp_tment_private, data = sd)
 tab_latex  <- modelsummary(
@@
 	),
-	stars = c('*' = .1, '**' = 0.05, '***' = .01),
-	estimate  = "{estimate}{stars}",
+	estimate  = "{estimate}",
+	statistic = c("conf.int", "({p.value})")
 ) %>% as_latex()
@@
 Is is based on a hypothetical code and data sharing scenario were we manipulated the sharing rationale (collaboration versus control) and the sharing scope (private versus public).
-All experimental materials are detailed in the Online Appendix of this study.
+All experimental materials are detailed in the [Online-]{.content-visible when-meta="online-appendix"}Appendix of this study.
 The outcome variable is the stated likelihood that the respondent would share their code and data under the hypothetical scenario.
@@
 Panel B reports the results from OLS regressions of the outcome on the binary treatments (H1 and H2) and their interaction (H3).
-
-```{=tex}
-\setlength{\parindent}{4em}
-\end{singlespace}
-\newpage
-```
+95% confidence intervals and two-sided t-test based p-values in parentheses are reported below the coefficients.
+
+```{=tex}
+\newpage
+```
+
 ### Table 12: Sharing of Research Materials: Rationales {.unnumbered}
 
-```{=tex}
-\begin{singlespace}
-\setlength{\parindent}{0em}
-```
 #### Panel A: Reasons against Sharing (Close-Ended Question) {.unnumbered}
@@
 ```{r Tab10aSharingReasons, asis = TRUE}
-tab <- sd %>%
+tab <- sr %>%
 	select(starts_with("sharing_reason"), -starts_with("sharing_reason_other")) %>% 
@@
 	left_join(
-		sd %>%
+		sr %>%
 			select(demog_method, starts_with("sharing_reason"), -starts_with("sharing_reason_other")) %>% 
@@
 ```
+
 #### Panel B: Rationales about Sharing (Open-Ended based on Hypothetical Scenario) {.unnumbered}
@@
 ```{r Tab10bSharingRationales, asis = TRUE}
-df <- sd %>% left_join(
-	readRDS("../data/generated/verbal_response_coded.rds") %>% 
-		select(-exp_reflect),
-	by = "id"
-) %>% mutate(
+df <- svr %>% 
+	mutate(
 	verbal_gave_reasons = !is.na(verbal_n_reasons),
@@
 ```{=tex}
-\setlength{\parindent}{4em}
 \end{landscape}
 \end{singlespace}
-\newpage
-```
-\setlength{\parindent}{0em}
-
-## Online Supplement {.unnumbered}
-
-The public GitHub repository at \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc} contains the data and the code of this project.
-
-To explore our survey data in more depth, we encourage the use of our [online survey dashboard](https://jgassen.shinyapps.io/osacc/).
+```
+
+:::
+
+::: {.content-visible when-meta="appendix"}
+
+[\newpage]{.content-visible when-meta="paper-tables"}
+
+## [Online-]{.content-visible when-meta="online-appendix"}Appendix {.unnumbered}
+
+::: {.content-visible unless-meta="anonymize"}
+
+The public GitHub repository at [https://github.com/joachim-gassen/osacc](https://github.com/joachim-gassen/osacc) contains the data and the code of this project.
+To evaluate our survey data in more depth, we encourage the use of our [online survey dashboard](https://jgassen.shinyapps.io/osacc/).
 Using this dashboard, you can explore the response to all survey questions, partitioning it by respondents' demographics.
 
-\newpage
-
-## Appendix A: Survey Administration and Instrument {.unnumbered}
+:::
+
+## [Online-]{.content-visible when-meta="online-appendix"}Appendix A: Survey Administration and Instrument {.unnumbered}
 
@@
 ```
+
 ### Initial Invitation - November 21, 2022 {.unnumbered}
@@
 
+[[omitted for review]]{.content-visible when-meta="anonymize"}
+
+::: {.content-visible unless-meta="anonymize"}
+
 Joachim Gassen\
@@
 
+:::
+
 Click here to unsubscribe from future e-mails. Click here to view our data protection guidelines.
@@
 
-This study has been approved by the ethical review board of the WHU -- Otto Beisheim School of Management.
+This study has been approved by the ethical review board of [the WHU -- Otto Beisheim School of Management]{.content-visible unless-meta="anonymize"}[[omitted for review]]{.content-visible when-meta="anonymize"}.
 
@@
 Sincerely,
+
+[[omitted for review]]{.content-visible when-meta="anonymize"}
+
+::: {.content-visible unless-meta="anonymize"}
 
@@
 
-Click here to unsubscribe from future e-mails.
-
-Click here to view our data protection guidelines.
+:::
+
+Click here to unsubscribe from future e-mails. Click here to view our data protection guidelines.
 
@@
 
-Click here to view our data protection guidelines.
+:::
+
+Click here to unsubscribe from future e-mails. Click here to view our data protection guidelines.
 
@@
 
-\newpage
-
-```{=tex}
+```{=tex}
+\newpage
+
 \includepdf[scale=0.7, pages=1,pagecommand={\hypertarget{survey-instrument}{\subsection*{Survey Instrument}\label{survey-instrument}}\addcontentsline{toc}{subsubsection}{Survey Instrument}}]{materials/survey.pdf}
@@
 ```
-## Appendix B: Scenario Manipulations and Instrument {.unnumbered}
+
+## [Online-]{.content-visible when-meta="online-appendix"}Appendix B: Scenario Manipulations and Instrument {.unnumbered}
 
 ### Manipulations {.unnumbered}
+
+::: {#table-stretch}
+\renewcommand{\arraystretch}{2} 
+:::
+
+: {tbl-colwidths="\[20,40,40\]"}
 
@@
 
-: {tbl-colwidths="\[20,40,40\]"}
-
 ```{=tex}
@@
 ```
-```{=tex}
-\includepdf[scale=0.7, pages=1,pagecommand={\hypertarget{scenario-instrument}{\subsection*{Instrument}\label{scenario-instrument}}\addcontentsline{toc}{subsubsection}{Scenario Instrument}}]{materials/scenario.pdf}
-\includepdf[scale=0.7, pages=2-, pagecommand={}]{materials/scenario.pdf}
-```
-```{=tex}
+
+```{=tex}
+\includepdf[scale=0.7, pages=1,pagecommand={\hypertarget{scenario-instrument}{\subsection*{Instrument}\label{scenario-instrument}}\addcontentsline{toc}{subsubsection}{Scenario Instrument}}]{materials/scenario.pdf} \includepdf[scale=0.7, pages=2-, pagecommand={}]{materials/scenario.pdf}
+```
+
+## [Online-]{.content-visible when-meta="online-appendix"}Appendix C: Power Analysis {.unnumbered}
+
+```{r AppCFigure1, fig.width=12, fig.height=9}
+power_res <- readRDS("../data/static/power_sim_10000_results.rds")
+post_hoc_power_figure(power_res)
+```
+
+```{=tex}
+\begin{singlespace}
+\setlength{\parindent}{0em}
+```
+
+This figure reports the results of a post hoc power analysis for our experimental findings.
+To infer the power of our experimental setting and its minimum detectable effect sizes conditional on various response rates, we calibrate a simulated dependent variable on distributional moments that are close to our observed sharing probability (Mean = 60%, Standard Deviation = 25%).
+To reflect that our outcome measure is naturally bounded and that participants are likely to give round estimates, we round the resulting simulated data to 5% intervals between 0% and 100%.
+We model our treatment effects for H1 and H2 in percentage points (PP) to be identical (depicted on the horizontal axis) and assume the interaction treatment effect of H3 to be 50% of the main treatment effects.
+The data presented below are based on 10,000 simulation runs.
+The vertical axis presents power, measured as the percentage share of collaboration treatment effect 95% confidence intervals that are strictly larger than zero.
+The family of curves reflects treatment cell sizes ranking from 40 (right-most curve, representing a response rate of \~6.3%) to 100 (left-most curve, representing a response rate of \~15.7%), where response rates are relative to the emails sent.
+The minimum detectable effect sizes for the various sample sizes can be inferred at the horizontal red dashed 80% power line.
+They rank from \~10 PP (100 observations per treatment cell) to \~15 PP (40 observations per treatment cell).
+The black curve reflects a treatment cell size of 60 observations, which is close to our sample size.
+For this, the minimum detectable effect size is \~12 PP.
+
+```{=tex}
+\setlength{\parindent}{4em}
+\end{singlespace}
+\newpage
 \begin{landscape}
@@
 ```
-## Appendix C: Comparison of our Survey with Social Science Survey (S3) {.unnumbered}
-
-```{r AppCTab1, asis = TRUE}
+
+## [Online-]{.content-visible when-meta="online-appendix"}Appendix D: Comparison of our Survey with Social Science Survey (S3) {.unnumbered}
+
+```{r AppDTab1, asis = TRUE}
 df <- read_csv(
@@
 
-[^1]: The terms "reproduction" and "replication" are at times used as synonyms but have different meanings.
-Reproduction refers to achieving the same results of a prior study using the same materials (code, procedures, and data), while replication refers to duplicating the results of a of a prior study using the same code and procedures but with new data [@NSF_2015].
-For a more in-depth discussion of the differences and related terminological debate, see @GFI_2016.
-
-[^2]: We pre-registered this experimental part of our study. The pre-registration materials can be accessed [here](https://osf.io/frmzt/).
-
-[^3]: We removed 41 authors because we found no email address, 41 authors because they appeared in the data twice with two author IDs but were the same person, 28 authors because they were a current member of one of our affiliated universities or academic research centers, 5 authors because they gave us advice for this study, 2 authors because they had passed away, and 1 author due to an incorrect email address.
-
-[^4]: The corresponding question in @FLCPSWMBP_2023 is "Have you ever heard of the practice of publicly posting (data and code/study instruments) online for a completed study?" We deviated from this original question by using the term "research materials" and defining it as "sharing data, code, and research procedures" in our version of the question because we wanted to cover all aspects of this Open Science practice in one question.
-
-[^5]: "To what extent do you believe that publicly sharing research materials (i.e., data, code, and research procedures) is important for the advancement of accounting research?" The corresponding question in @FLCPSWMBP_2023 is "To what extent do you believe that publicly posting (data or code \| research instruments) online is important for progress in \[Discipline\]?" We adapted this question for terminological consistency across our survey.
-
-[^6]: While parts of the economic [@O_2015; @BCHH_2024] and accounting literature [@CGL_2024] differentiate between pre-registrations (relatively short and standardized descriptions of study design) and pre-analysis plans (more detailed and elaborate plans outlining the technical details of a study, potentially also including analysis code, mock-up tables and figures), we use the term pre-registration as a broader notion, in line with @FLCPSWMBP_2023.
-
-[^7]: The question used in the survey of @FLCPSWMBP_2023 is "Have you ever heard of the practice of pre-registering hypotheses or analyses in advance of a study?".
-
-[^8]: The question used in @FLCPSWMBP_2023 was "Approximately when was the first time you pre-registered hypotheses or analyses in advance of a study?"
-
-[^9]: The question used in the survey of @FLCPSWMBP_2023 is "What is your opinion of pre-registering hypotheses or analyses?".
-This question is quite broad while relying on a five-point Likert scale evaluating self-reported favorability (i.e., Not at all in favor, Moderately not in favor, Neither in favor nor against, Moderately in favor, Very much in favor).
-We chose to use a more specific question asking about whether pre-registration improves trustworthiness while relying on a five-point Likert scale (i.e., Much less trustworthy, Somewhat less trustworthy, Equally trustworthy, Somewhat more trustworthy, Much more trustworthy).
-
-[^10]: The data collection manual for this process is available in this project's GitHub repository.
-
-[^11]: Untabulated analyses based on small frequencies provide suggestive evidence that, overall, the sharing frequencies are higher for general economics journals than for journals in the areas of accounting and finance.
-
-[^12]: In a related study, @BCHH_2024 study randomized controlled trial studies in economics and find that only pre-registrations that include pre-analysis plans show muted p-value discontinuities.
+:::

### 2025-02-18 docs/presentation.qmd
new paper version

@@
 title: |
-  | How does the Accounting Research Community 
+  | How Does the Accounting Research Community 
   | Think About Open Science?
@@
 ```{r Figure2, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
-mr$sharing_important_rescaled = floor(mr$sharing_important)
-p <- likert_plot(mr, "sharing_important_rescaled", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53]) +
+p <- likert_plot(mr, "sharing_important", "demog_discipline", title_str = "To what extent do you believe that publicly sharing research materials is important?", llevels = vars$resp_label[49:53]) +
 	theme(legend.text = element_text(size = 6))

### 2025-02-18 code/figure_functions.R

@@ -2,6 +2,7 @@ library(tidyverse)
 library(ggbeeswarm)
 library(readr)
 library(readxl)
+library(gghighlight)
 
 # Inspiration for plot below is from 
 # http://rnotr.com/likert/ggplot/barometer/likert-plots/
@@ -223,7 +224,7 @@ byu_fields_comp <- function(byu_author_data, sd_data) {
   # Set axes = FALSE to prevent barplot from drawing axes
   bar_positions <- barplot(fields_matrix, beside = TRUE, col = c("skyblue", "lightgreen"), ylim = c(0, 100), 
                            names.arg = field_labels, las = 1, border = "black", 
-                           cex.names = 1.25, axes = FALSE)
+                           cex.names = 1.1, axes = FALSE)
   
   # Redraw the X-axis line
   abline(h = 0, col = "black")
@@ -290,7 +291,7 @@ byu_methods_comp <- function(byu_author_data, sd_data) {
   
   # Set axes = FALSE to prevent barplot from drawing axes
   bar_positions <- barplot(methods_matrix, beside = TRUE, col = c("skyblue", "lightgreen"), ylim = c(0, 100), 
-                           names.arg = method_labels, las = 1, border = "black", main = "Comparison of Methods between BYU and our Sample", 
+                           names.arg = method_labels, las = 1, border = "black", 
                            cex.names = 1.25, axes = FALSE)
   
   # Redraw the X-axis line
@@ -305,3 +306,21 @@ byu_methods_comp <- function(byu_author_data, sd_data) {
   # Manually add y-axis labels only horizontally
   axis(2, cex.axis = 1.25, las = 1)  # las = 1 makes the labels horizontal
 }
+
+post_hoc_power_figure <- function(power_res) {
+	ggplot(
+		power_res %>% filter(term == "collabTRUE"), 
+		aes(x = teffect, y = power, group = n_bin)
+	) +
+		geom_line() + geom_point() +
+		gghighlight(n_bin == 60, use_direct_label = F, use_group_by = F) + 
+		geom_hline(yintercept = 0.8, lty = 2, color = "red") + 
+		labs(x = "Main Effect (H1/H2)", y = "Power", color = "Bin size") +
+		scale_y_continuous(labels = scales::percent) +
+		scale_x_continuous(labels = function(x) paste(round(100*x), "PP")) +
+		theme_classic(base_size = 18) +
+		theme(
+			text=element_text(family="Times")
+		) 
+}
+

### 2025-02-18 code/merge_3s_data.R

@@ -59,7 +59,7 @@ comp_sss <- sss_resp %>%
 			"Qualitative or Theoretical", "Other"
 		)),
 		sharing_heard = sharing_dc_ever | sharing_inst_ever,
-		sharing_important = (sharing_dc_opinion + sharing_inst_opinion)/2,
+		sharing_important = floor((sharing_dc_opinion + sharing_inst_opinion)/2),
 		sharing_use = sharing_dc_how_many != "0" | sharing_inst_how_many != "0", 
 		sharing_perc_other_share = sharing_dc_share,
 		sharing_perc_other_prefer = sharing_dc_pref_other,

### 2025-02-18 code/run_post_hoc_power_sim.R

@@ -1,0 +1,70 @@
+suppressMessages({
+	library(tidyverse)
+	library(broom)
+	library(purrr)
+})
+
+set.seed(42)
+
+N_BIN = 64
+BLINE_PROB = 0.6 # Control/Public
+BLINE_SD = 0.25
+
+NRUNS <- 10000
+FNAME_STUB <- "power_sim"
+
+fname_sim_dta <- paste0("data/generated/", FNAME_STUB, "_", NRUNS, "_data.rds")
+
+if (file.exists(fname_sim_dta)) {
+	sim_dta <- readRDS(fname_sim_dta)
+} else {
+	sim_sample <- function(
+		teffect_collab, teffect_private, teffect_iaction,
+		n_bin = N_BIN, bline = BLINE_PROB, bline_sd = BLINE_SD
+	) {
+		tibble(
+			collab = c(rep(F, 2*n_bin), rep(T, 2*n_bin)),
+			private = c(rep(F, n_bin), rep(T, n_bin), rep(F, n_bin), rep(T, n_bin)),
+			share_prob  = round(20*pmin(
+				pmax(
+					rep(0, 4*n_bin), 
+					bline + teffect_collab*collab + teffect_private*private + 
+						teffect_iaction*collab*private + rnorm(4*n_bin, 0, bline_sd)
+				), 
+				rep(1, 4*n_bin)
+			))/20
+		)
+	}
+	
+	test <- function(df) {
+		rv <- lm(share_prob ~ collab*private, data = df)
+		tidy(rv, conf.int = TRUE)
+	}
+	
+	do_run <- function(teffect, n_bin, run) {
+		df <- sim_sample(teffect, teffect, teffect/2, n_bin)
+		bind_cols(tibble(run = run, teffect = teffect, n_bin = n_bin, test(df)))
+	}
+	
+	sim_grid <- expand_grid(
+		n_bin = seq(40, 100, 10),
+		teffect = seq(0.01, 0.15, 0.01),
+		run = 1:NRUNS
+	)
+	
+	sim_dta <- bind_rows(
+		pmap(sim_grid, do_run, .progress = paste("Simulating", NRUNS, "runs"))
+	)
+	
+	saveRDS(sim_dta, fname_sim_dta)
+}
+
+power_res <- sim_dta %>% 
+	group_by(n_bin, teffect, term) %>%
+	summarise(power = mean(conf.low > 0), .groups = "drop")
+
[…]

### 2025-02-18 code/table_functions.R

@@ -15,7 +15,11 @@ GROUPS <- c(
 	"qualitative", "risk", "trust", "tment_ctrl", "tment_prvt"
 )
 
-myfmt <- function(x, ndigits = 3) format(round(x, ndigits), nsmall = ndigits)
+myfmt <- function(x, ndigits = 3, p = FALSE) {
+	rv <- format(round(x, ndigits), nsmall = ndigits)
+	if (!p) return(rv)
+	ifelse(x < 0.001, "< 0.001", paste("=", rv))
+}
 
 get_resp_label <- function(v) {
 	# relies on vars being present in environment
@@ -236,8 +240,8 @@ create_continuous_table <- function(df, var, groups = GROUPS) {
 }
 
 ttest_group_by_group <- function(df, var, groupvar, xg, yg) {
-	x <- as.numeric(df[df[, groupvar] == xg, var]) %>% na.omit()
-	y <- as.numeric(df[df[, groupvar] == yg, var]) %>% na.omit()
+	x <- as.numeric(df[[var]][df[, groupvar] == xg]) %>% na.omit()
+	y <- as.numeric(df[[var]][df[, groupvar] == yg]) %>% na.omit()
 	if (length(x) <= 1) return(1)
 	if (length(y) <= 1) return(1)
 	rv <- t.test(x, y)
@@ -245,7 +249,8 @@ ttest_group_by_group <- function(df, var, groupvar, xg, yg) {
 }
 
 ttest_group_by_other_groups <- function(df, var, groupvar, xg) {
-	other_groups <- levels(df[, groupvar])[which(levels(df[, groupvar]) != xg)]
+	groups = levels(as.factor(df[[groupvar]]))
+	other_groups <- groups[groups != xg]
 	sapply(other_groups, function(y) ttest_group_by_group(df, var, groupvar, xg, y))
 }
 
@@ -305,7 +310,7 @@ create_pct_cross_tab_table <- function(
 		add_num_labels = TRUE, df_only = FALSE
 ) {
 	df$var <- as.numeric(df[[var]])
-	df$cross_var <- df[[cross_var]]
+	df$cross_var <- as.factor(df[[cross_var]])
 	if (include_total) full_df <- df
 	if (drop_levels != "") {
 		df <- df %>% filter(! as.character(cross_var) %in% drop_levels) 
@@ -361,7 +366,10 @@ create_pct_cross_tab_table <- function(
 		ctests <- NULL
 		for (g in levels(df$cross_var)) {
[…]

### 2025-02-25 docs/paper.qmd
Small fixes

@@
 
-[^1]: The terms "reproduction" and "replication" are at times used as synonyms but have different meanings.
+[^1]: [We received institutional approval for this study.]{.content-visible when-meta="anonymize"} The terms "reproduction" and "replication" are at times used as synonyms but have different meanings.
 Reproduction refers to achieving the same results of a prior study using the same materials (code, procedures, and data), while replication refers to duplicating the results of a of a prior study using the same code and procedures but new data [@NSF_2015; @BCKU_2024].

### 2025-02-25 docs/presentation.qmd
Small fixes

@@
 	x[1] <- paste0("\\begin{center}", x[1], "\\end{center}")
+	x
+}
+
+script_size <- function(x) {
+	x[1] <- paste0("\\scriptsize", x[1], "\\normalsize")
+	x
+}
+
+tiny_size <- function(x) {
+	x[1] <- paste0("\\tiny", x[1], "\\normalsize")
 	x
@@
 
-```{r}
+```{r, asis = TRUE}
 
-# Later quotes need checking still - lots of potentially interesting stuff
 quotes <-c(11, 16, 18, 66, 67, 72, 80, 82, 84)
-# 83, 87, 88, 91, 105, 110
- sd %>%
+df <- sd %>%
  	filter(row_number() %in% quotes) %>%
@@
  		Quote = exp_reflect
- 	) %>% kable(booktabs = TRUE, linesep = "") %>% 
- 	kable_styling(full_width = TRUE, font_size = 7)  %>% 
- 	column_spec(1, width = "1.5cm")
+ 	)
 
+gt(df) %>% 
+	cols_width(
+		`Condition` ~ pct(15),
+		`Quote` ~ pct(85)
+	) %>%
+	tab_options(table.font.size = 7) %>%
+	as_latex() %>%
+	tiny_size()
 ```

### 2025-03-13 docs/presentation.qmd
slide deck update

@@
   library(showtext)
-
+	library(tufte)
   devtools::source_url(
@@
 mr <- readRDS("../data/generated/merged_response.rds")
+byu <- read_csv("../data/external/byu_author_data_anon.csv", show_col_types = FALSE)
 vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
@@
 source("../code/obs_data_analyses.R")
+
+create_quote <- function(idval) {
+	obs <- sd %>% filter(id == idval)
+	tment_str <- paste0(
+		ifelse(obs$exp_tment_control == 1, "Control", "Collab"), "/",
+		ifelse(obs$exp_tment_private == 1, "Private", "Public")
+	) 
+	paste(obs$exp_reflect, "\\\\", quote_footer(paste("---", tment_str)))
+}
 
@@
 
-## Motivation
+## Motivation: Estimating The Reproducibility of Psychological Science
+
+\begin{center}
+\includegraphics[height =0.7\textheight]{"materials/osc_2015.jpeg"} \\
+Open Science Collaboration (2015, Science)
+\end{center}
+
+## Motivation: 1,500 Scientists Lift the Lid on Reproducibility
+
+\begin{center}
+\includegraphics[height =0.7\textheight]{"materials/baker_2016.jpeg"} \\
+Baker (2016, Nature)
+\end{center}
+
+## Motivation: Survey of OS Practices and Attitudes in the Social Sciences
 
@@
 
-Survey of authors that published in top six accounting journals over the period 2016-2021
+Survey of authors that published in top six accounting journals over the period 2016-2021 to address three research questions:
 
-Descriptive Research Questions (relative to general social science results)
+1.  How does the accounting research community assess the reproducibility of their influential work?
 
-- How do accountants assess the reproducibility of influential accounting work?
-- How do they perceive and use two prominent open science approaches to promote reproducibility:
-	- Public sharing of research materials (i.e., data, code, and procedures)
-	- Pre-registration of study designs
+2.  What are the views of the accounting research community about research material sharing and pre-registration, two prominent open science methods to increase the reproducibility of research?
 
-Experimental Question: Is the stated willingness to share research materials ...
+3.  What are the (perceived) costs and benefits of research material sharing?
 
-- ... affected by the rationale (collaboration versus control) and/or
-- ... affected by the scope (public or private sharing) of the sharing request?
+## Theoretical Framework
 
-## Invitation Email
+The acts of research material sharing and pre-registration can be understood as voluntary disclosure decisions.
 
-\begin{small}
+- **Lack of unravelling**: Non-trivial direct costs and researchers might be unaware of their research' quality
+- **Substantial indirect costs**: Competetive effects and reputational concerns
+- **Limited private benefits**: Researchers are incentivized by publication success and less by research quality per se
+- **Positive externalities**: Activities are likely to benefit other researchers without direct compensation for acting researcher (but: 'warm glow')
 
-Subject: Share your views on Accounting Research
-
-Dear colleague,
-
-We are conducting a study about sharing research materials, reproducibility, and pre-registration in accounting research.
-You have been chosen to provide your opinion on this subject because you are a published author in one of the leading accounting journals.
-We obtained your email address from publicly available sources.
-
-Participating in our study takes around 7 minutes of your time. We will publicly share the anonymized data and results with the academic community in due course.
-
-As a token of gratitude for your time, we will donate 1,000 € multiplied by the response rate to the United Nations International Children's Emergency Fund (UNICEF).
-
-[...]
-
-\end{small}
-
-## Sample Composition
+## Sample Composition {#sample}
 
@@
 
-## Geographical Response Representation
+\placebutton{skip}{email}{invitation email}
+
+## Representativeness by Geographical Region
 
@@
 
-## Reproducibility Assessed Across the Social Sciences
+## Representativeness by Field
+
+```{r FigureRespField, fig.width=12, fig.height=6, fig.align="center", fig.showtext = TRUE}
+byu_fields_comp(byu, sd)
+```
+
+## Representativeness by Method
+
+```{r FigureRespMethod, fig.width=9, fig.height=4.5, fig.align="center", fig.showtext = TRUE}
+byu_methods_comp(byu, sd)
+```
+
+## Reproducibility Assessed Across the Social Sciences {#reproducibility}
 
@@
 ```
+
+\placebutton{skip}{terminology}{Terminology}
 
@@
 
+## Pre-Registration: Take-up over Time Across the Social Sciences
+
+```{r Figure5, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
+p <- pre_reg_over_time_plot(mr) + theme(legend.position = "right") 
+if (trr266_fonts_available) {
+	p + theme(text = element_text(family = "Calibri Light", size = 12))
+} else p
+
+```
+
+## Pre-Registration: Opinion Across the Social Sciences
+
+```{r Tab10cPreRegTimeSocSciResp, asis = TRUE}
+tab <- create_pct_cross_tab_table(
+	mr, "prereg_opinion", "demog_discipline", 
+	resp_label = get_resp_label("prereg_trust"), df_only = TRUE
+) 
+gt(tab ) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+<!---
+## Pre-Registration: Familiarity by Method
+
+```{r Tab11aPreRegFamiliarity, asis = TRUE}
+tab <- create_pct_cross_tab_table(
+	sd, "prereg_familiar", "demog_method", include_total = TRUE,
+	drop_levels = "Other", 
+	ctests = TRUE, df_only = TRUE
+) 
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+--->
+
+## Pre-Registration: Usage by Method {#preregmethod}
+
+```{r Tab11bPreRegUse, asis = TRUE}
+
+tab <- create_pct_cross_tab_table(
+	sd, "prereg_use", "demog_method", include_total = TRUE,
+	drop_levels = "Other", resp_label = c("No (0)", "Yes (1)"), 
+	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
+) 
+# Adjust levels to be zero based.
+tab[4,2:7] <- t(sprintf("%.2f", as.numeric(tab[4,2:7]) - 1))
+tab[5,2:7] <- t(sprintf("%.2f", as.numeric(tab[5,2:7]) - 1))
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+\placebutton{skip}{preregtrust}{trust in pre-registration by method}
+
+## Observational Data: Author Level
+
+```{r, asis = TRUE}
+gt(tab_by_author) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+## Observational Data: Journal Level
+
+```{r, asis = TRUE}
+gt(tab_by_journal) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+## To Compare: Policy Effect for Management Science
+
+\begin{center}
+\includegraphics[width =0.7\textwidth]{"materials/fisar_et_al_2023_policy.jpeg"} \\
+Fišar et al. (2023, Management Science)
+\end{center}
+
+## Observational Data: Paper-level Sharing over Time
+
+```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
+p <- plot_resmat_sharing_over_cyear
+if (trr266_fonts_available) {
+	p + theme(text = element_text(family = "Calibri Light", size = 12))
+} else p
+```
+
 ## Sharing Determinants: Experimental Manipulation
@@
 
-## Experimental Findings on Sharing Determinants
+## Costs and Benefits of Research Material Sharing: Experimental Findings
 
@@
 
-## Rationales for/against Sharing: Some Quotes
+## Quotes about Sharing Benefits: Helping Others
+\begin{quote}
+`r create_quote(295)`
+\end{quote}
+\vspace{1cm}
+\begin{quote}
+`r create_quote(403)`
+\end{quote}
 
-```{r, asis = TRUE}
+## Quotes about Sharing Benefits: Helping Yourself
 
-quotes <-c(11, 16, 18, 66, 67, 72, 80, 82, 84)
-df <- sd %>%
- 	filter(row_number() %in% quotes) %>%
- 	transmute(
- 		Condition = sprintf(
- 			"%s/%s", ifelse(exp_tment_collab, "Collab", "Control"),
- 			ifelse(exp_tment_private, "Private", "Public")
- 		),
- 		Quote = exp_reflect
- 	)
+\begin{quote}
+`r create_quote(249)`
+\end{quote}
+\vspace{1cm}
+\begin{quote}
+`r create_quote(186)`
+\end{quote}
 
-gt(df) %>% 
-	cols_width(
-		`Condition` ~ pct(15),
-		`Quote` ~ pct(85)
-	) %>%
-	tab_options(table.font.size = 7) %>%
-	as_latex() %>%
-	tiny_size()
-```
+## Quotes about Sharing Costs: Direct Costs
 
-## Observational Data on Sharing Behavior: Author Level
+\begin{quote}
+`r create_quote(154)`
+\end{quote}
 
-```{r, asis = TRUE}
-gt(tab_by_author) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
+## Quotes about Sharing Costs: Valuable Intellectual Property
 
-## Observational Data on Sharing Behavior: Journal Level
+\begin{quote}
+`r create_quote(47)`
+\end{quote}
 
-```{r, asis = TRUE}
-gt(tab_by_journal) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
+## Quotes about Sharing Costs: Unethical Usage Concerns
 
-## To Compare: Policy Effect for Management Science
+\begin{quote}
+`r create_quote(169)`
+\end{quote}
 
-\begin{center}
-\includegraphics[width =0.7\textwidth]{"materials/fisar_et_al_2023_policy.jpeg"} \\
-Fišar et al. (2023, Management Science)
-\end{center}
+## Quotes about Sharing Benefits/Costs: Depends on Researcher
 
-## Observational Data: Paper-level Sharing over Time
-
-```{r Figure4, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
-p <- plot_resmat_sharing_over_cyear
-if (trr266_fonts_available) {
-	p + theme(text = element_text(family = "Calibri Light", size = 12))
-} else p
-```
-
-<!---
-## Pre-Registration: Awareness Across the Social Sciences
-
-```{r Tab10aPreRegAwareSocSciResp, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	mr, "prereg_heard", "demog_discipline", 
-	resp_label = c("No (0)", "Yes (1)"), 
-	add_num_labels = FALSE, df_only = TRUE
-) 
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
---->
-
-## Pre-Registration: Take-up over Time Across the Social Sciences
-
-```{r Figure5, fig.width=8, fig.height=3.5, fig.align="center", fig.showtext = TRUE}
-p <- pre_reg_over_time_plot(mr) + theme(legend.position = "right") 
-if (trr266_fonts_available) {
-	p + theme(text = element_text(family = "Calibri Light", size = 12))
-} else p
-
-```
-
-## Pre-Registration: Opinion Across the Social Sciences
-
-```{r Tab10cPreRegTimeSocSciResp, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	mr, "prereg_opinion", "demog_discipline", 
-	resp_label = get_resp_label("prereg_trust"), df_only = TRUE
-) 
-gt(tab ) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
-
-## Pre-Registration: Familiarity by Method
-
-```{r Tab11aPreRegFamiliarity, asis = TRUE}
-tab <- create_pct_cross_tab_table(
-	sd, "prereg_familiar", "demog_method", include_total = TRUE,
-	drop_levels = "Other", 
-	ctests = TRUE, df_only = TRUE
-) 
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
-
-## Pre-Registration: Usage by Method
-
-```{r Tab11bPreRegUse, asis = TRUE}
-
-tab <- create_pct_cross_tab_table(
-	sd, "prereg_use", "demog_method", include_total = TRUE,
-	drop_levels = "Other", resp_label = c("No (0)", "Yes (1)"), 
-	add_num_labels = FALSE, ctests = TRUE, df_only = TRUE
-) 
-# Adjust levels to be zero based.
-tab[4,2:7] <- t(sprintf("%.2f", as.numeric(tab[4,2:7]) - 1))
-tab[5,2:7] <- t(sprintf("%.2f", as.numeric(tab[5,2:7]) - 1))
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
-
-## Pre-Registration: Trust Effect by Method
-
-```{r Tab11cPreRegTrust, asis = TRUE}
-
-tab <- create_pct_cross_tab_table(
-	sd, "prereg_trust", "demog_method", include_total = TRUE,
-	drop_levels = "Other", ctests = TRUE, df_only = TRUE
-) 
-gt(tab) %>% 
-	cols_align("right", -1) %>% 
-	as_latex() %>%
-	fit_gt_table_to_slide()
-```
+\begin{quote}
+`r create_quote(317)`
+\end{quote}
 
@@
 - We are skeptical about the reproducibility of our work and at the same time
-- somewhat behind the curve with regards to research material sharing and pre-registration
+- somewhat behind the curve with regards to research material sharing and pre-registration.
+
+Our findings suggest that weighting direct and indirect costs higher than private and public benefits might be a rationale for this behavior.
 
@@
 
-## Taking stock... It might not be as bad as we think!
+## Taking stock: Distributions of Test Statistics in Archival Accounting Studies
+
+\begin{center}
+\includegraphics[height =0.7\textheight]{"materials/chang_gao_li_2025.jpeg"} \\
+Chang, Gao, and Li (2025, JAR)
+\end{center}
+
+## Taking stock: Relatively speaking...
 
@@
 
-## Reproducibility Across Methods
+## Taking stock: Reproducibility Across Methods
 
@@
 \end{center}
+
+# Backup
+
+## Invitation Email {#email}
+
+\begin{small}
+
+Subject: Share your views on Accounting Research
+
+Dear colleague,
+
+We are conducting a study about sharing research materials, reproducibility, and pre-registration in accounting research.
+You have been chosen to provide your opinion on this subject because you are a published author in one of the leading accounting journals.
+We obtained your email address from publicly available sources.
+
+Participating in our study takes around 7 minutes of your time. We will publicly share the anonymized data and results with the academic community in due course.
+
+As a token of gratitude for your time, we will donate 1,000 € multiplied by the response rate to the United Nations International Children's Emergency Fund (UNICEF).
+
+[...]
+
+\end{small}
+
+\placebutton{return}{sample}{Return}
+
+## Some Terminology (Dreber and Johannesson, 2024) {#terminology}
+
+Types of reproducibility:
+
+- **Computational reproducibility**: Results of original study can be reproduced based on data and code posted or provided by the original authors.	
+- **Recreate reproducibility**:	Results of original study can be reproduced based on the information in the paper and access to the same raw data source.	
+- **Robustness reproducibility**:	Results og original study are robust to alternative reasonable analytical decisions on the same data.
+
+Types of replicability:
+
+- **Direct replicability**:	Results of original studies can be repeated on new data using the same research design and analysis as the original study.	
+- **Conceptual replicability**:Results of original study can be repeated on new data using an alternative research design and/or analysis to test the same hypothesis.
+
+\placebutton{return}{reproducibility}{Return}
+
+## Pre-Registration: Trust Effect by Method {#preregtrust}
+
+```{r Tab11cPreRegTrust, asis = TRUE}
+
+tab <- create_pct_cross_tab_table(
+	sd, "prereg_trust", "demog_method", include_total = TRUE,
+	drop_levels = "Other", ctests = TRUE, df_only = TRUE
+) 
+gt(tab) %>% 
+	cols_align("right", -1) %>% 
+	as_latex() %>%
+	fit_gt_table_to_slide()
+```
+
+\placebutton{return}{preregmethod}{Return}
